---
title: "mak_demographics.RMD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

##Summarize Age, sex, race, ethnicity, & income for final Risk N = 154

### Environment and setup
```{r,results="hide"}
# Libraries
library("tidyverse")
library("StudySupport")
library("scales")


# Set paths
data_path <- "P:/studydata/risk/data_processed/shared"
rppr_path <- "P:/grants/Curtin_R01_NIAAA(RiskPrediction)/NIH Correspondence/Final RPPR 2022"
```

### Get Valid subIDs
```{r,results="hide"}
visit_dates <- read_csv(file.path(data_path,"visit_dates.csv"))

started_subs <- visit_dates %>% filter(!is.na(intake)) %>% select(subid)
valid_subs <- visit_dates %>% filter(!is.na(followup_1)) %>% select(subid)

```

### Open and process ID data file containing demographics
```{r,results="hide"}
dem_data <- read_csv(file.path(data_path, "screen.csv")) %>%
  select(subid,  
         age = dem_1, 
         sex = dem_2, 
         race = dem_3, 
         hispanic = dem_4) %>%
         mutate(hispanic = if_else(str_detect(hispanic, "Yes"), "1", "0")) %>% 
    mutate(american_native = ifelse(str_detect(race,"American Indian/Alaska Native"),1,0),
        asian = ifelse(str_detect(race,"Asian"),1,0),
        pacific = ifelse(str_detect(race,"Native Hawaiian or Other Pacific Islander"),1,0),
        black = ifelse(str_detect(race,"Black/African American"),1,0),
        white = ifelse(str_detect(race,"White/Caucasian"),1,0),
        other = ifelse(str_detect(race,"Other/Multiracial"),1,0),
        )

#add pilot data for NIH
pilot_subs <- read_csv(file.path(rppr_path, "pilot_participants.csv")) %>%
         mutate(hispanic = if_else(str_detect(hispanic, "Yes"), "1", "0")) %>% 
    mutate(american_native = ifelse(str_detect(race,"American Indian/Alaska Native"),1,0),
        asian = ifelse(str_detect(race,"Asian"),1,0),
        pacific = ifelse(str_detect(race,"Native Hawaiian or Other Pacific Islander"),1,0),
        black = ifelse(str_detect(race,"African American"),1,0),
        white = ifelse(str_detect(race,"White"),1,0),
        other = ifelse(str_detect(race,"Other/Multiracial"),1,0),
        not_specified = ifelse(str_detect(race,"Not specified"),1,0),)

pilot_subids <- pilot_subs %>% select(subid)


dem_data <- full_join(dem_data %>% mutate(subid = as.character(subid)), pilot_subs) %>%
  mutate_if(is.numeric , replace_na, replace = 0)

```


All subs including screen fails
```{r}
#N
dem_data  %>% nrow()

#by sex
dem_data %>% group_by(sex) %>% tally()  


# non-hispanic
dem_data %>%
  filter(hispanic == 0) %>%
  group_by(sex,  american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()

# hispanic
dem_data %>%
  filter(hispanic == 1) %>%
  group_by(sex, american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()
  
```


Only started subs (screened in)
```{r}
#N
dem_data  %>% 
  filter(subid %in% started_subs$subid | subid %in% pilot_subids$subid) %>%
  nrow()

#by sex
dem_data %>% 
    filter(subid %in% started_subs$subid | subid %in% pilot_subids$subid) %>%
    group_by(sex) %>% 
  tally()  


# non-hispanic
dem_data %>%
  filter(subid %in% started_subs$subid | subid %in% pilot_subids$subid) %>%
  filter(hispanic == 0) %>%
  group_by(sex,  american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()

# hispanic
dem_data %>%
  filter(subid %in% started_subs$subid | subid %in% pilot_subids$subid) %>%
  filter(hispanic == 1) %>%
  group_by(sex, american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()
  
```



Only valid subs (made to FU1)
```{r}
#N
dem_data  %>% 
  filter(subid %in% valid_subs$subid | subid %in% pilot_subids$subid) %>%
  nrow()

#by sex
dem_data %>% 
    filter(subid %in% valid_subs$subid | subid %in% pilot_subids$subid) %>%
    group_by(sex) %>% 
  tally()  


# non-hispanic
dem_data %>%
  filter(subid %in% valid_subs$subid | subid %in% pilot_subids$subid) %>%
  filter(hispanic == 0) %>%
  group_by(sex,  american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()

# hispanic
dem_data %>%
  filter(subid %in% valid_subs$subid | subid %in% pilot_subids$subid) %>%
  filter(hispanic == 1) %>%
  group_by(sex, american_native, asian, pacific, black, white, other, not_specified) %>%
  tally()
  
```



### Age
```{r}

age_summary <- dem_data %>%
  summarize(mean=round(mean(age),1), sd=round(sd(age),1), min=min(age), max=max(age))
age_summary
```


### Sex
```{r}
sex_summary <- dem_data %>%
  group_by(sex) %>%
  summarize(n = n()) %>%
  mutate(`%` = percent(n/sum(n)))
sex_summary
```


### Race
```{r}
race_summary <- dem_data %>%
  group_by(race) %>%
  summarize(n = n()) %>%
  mutate(`%` = percent(n/sum(n)))
race_summary
```


### Ethnicity
```{r}
hisp_summary <- dem_data %>%
  group_by(hispanic) %>%
  summarize(n = n()) %>%
  mutate(`%` = percent(n/sum(n)))
hisp_summary  
```


### Income
```{r}
income_summary <- dem_data %>%
  summarize(mean=dollar(round(mean(income))), sd=dollar(round(sd(income))), min=dollar(min(income)), max=dollar(max(income)))
income_summary
```


### Conclusions

This sample contains `r nrow(valid_subs)` Risk participants who completed through Followup Visit 1. Mean age is `r age_summary[[1]]` (sd=`r age_summary[[2]]`) and `r sex_summary[[1,3]]` are `r sex_summary[[1,1]]`. The sample is `r race_summary[[5,3]]` `r race_summary[[5,1]]` and `r hisp_summary[[2,3]]` are hispanic.  The average sample income is `r income_summary[[1]]` (sd=`r income_summary[[2]]`).
