---
title: "Phone models used by completed participants"
output: html_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, echo = FALSE}
library(tidyverse)
library(readxl)
library(janitor) #tabyl

path_qualtrics <- "P:/StudyData/RISK/raw_data/qualtrics"
path_admin <- "P:/StudyData/RISK/administration/Participants/Technology Tracking"
path_data <- "P:/StudyData/RISK/analysis/shared/data"
```


```{r, echo = FALSE}
phone_models <- read_csv(file.path(path_admin,"phone_models.csv")) %>% select(subid=`Sub ID`, model=`Phone type`, carrier=Carrier,subsidized=`State Subsidized Phone?`,notes=Notes)
s3 <- read_csv(file.path(path_qualtrics,"session_screen_3.csv")) %>% filter(Q97==1, !is.na(Q89)) %>% select(subid = Q89, model=Q108, carrier=Q109,notes=Q78, notes2=Q54) %>% mutate(subid=str_pad(subid, 3, "left",pad="0"))

s3$subid[s3$subid == "2:30 pm"] = "256" #verified correct subID per google calendar

phone_models <- full_join(phone_models, s3, by="subid") %>% filter(!is.na(subid))

#identify duplicate entries
x <-  phone_models %>% filter(duplicated(phone_models))
View(phone_models %>% filter(subid %in% x$subid)) #these are all exact duplicates so we will remove the duplicated lines

phone_models <- phone_models %>% distinct()

#fix some issues
phone_models$model.x[phone_models$subid == "254"] <- phone_models$model.y[phone_models$subid == "254"]
phone_models$model.x[phone_models$subid == "260"] <- phone_models$model.y[phone_models$subid == "260"]
phone_models$model.x[phone_models$subid == "019"] <- phone_models$notes.x[phone_models$subid == "019"]
phone_models$model.x[phone_models$subid == "187"] <- 	"iPhone 6 or 7"
phone_models$model.x[phone_models$subid == "085"] <- 	"iPhone 5"
phone_models$model.x[phone_models$subid == "163"] <- 	"iPhone X"
phone_models$model.x[phone_models$subid == "221"] <- 	"iPhone X"
phone_models$model.x[phone_models$subid == "099"] <- 	"Samsung Galaxy S7"
phone_models$model.x[phone_models$subid == "193"] <- 	"Pixel"

phone_models$model.x[phone_models$subid == "271"] <- phone_models$model.y[phone_models$subid == "271"]
phone_models$carrier.x[phone_models$subid == "271"] <- "Boost"

phone_models$model.x[phone_models$subid == "272"] <- phone_models$model.y[phone_models$subid == "272"]
phone_models$carrier.x[phone_models$subid == "272"] <- "US Cellular"

phone_models$model.x[phone_models$subid == "135"] <- "ZTE"
phone_models$carrier.x[phone_models$subid == "135"] <- "Qlink Wireless"
phone_models$model.x[phone_models$subid == "064"] <- "ZTE"
phone_models$carrier.x[phone_models$subid == "064"] <- "Qlink Wireless"

phone_models$model.x[phone_models$subid == "012"] <- NA
phone_models$model.x[phone_models$subid == "209"] <- "LG Phoneix"
phone_models$model.x[phone_models$subid == "171"] <- "Motorola"
phone_models$model.x[phone_models$subid == "223"] <- "Motorola"
phone_models$model.x[phone_models$subid == "174"] <- "Motorola (Moto G)"
phone_models$model.x[phone_models$subid == "224"] <- "Samsung Galaxy"
phone_models$model.x[phone_models$subid == "178"] <- "Honor/Huawei"
phone_models$model.x[phone_models$subid == "196"] <- "Motorola 7.0"
phone_models$model.x[phone_models$subid == "117"] <- "Lenovo"
phone_models$model.x[phone_models$subid == "116"] <- "LG"
phone_models$model.x[phone_models$subid == "118"] <- "LG"
phone_models$model.x[phone_models$subid == "128"] <- "LG"
phone_models$model.x[phone_models$subid == "090"] <- "LG Nexus"
phone_models$model.x[phone_models$subid == "151"] <- "Motorola 4G"
phone_models$model.x[phone_models$subid == "060"] <- "ZTE"
phone_models$model.x[phone_models$subid == "082"] <- "ZTE"
phone_models$model.x[phone_models$subid == "084"] <- "ZTE"




#clean up
phone_models <- phone_models %>% mutate(OS = "") %>% 
  select(subid, OS, model = model.x, carrier = carrier.x, subsidized) %>%
  mutate(OS = case_when(str_detect(model, "iPhone") ~"iOS",
                        str_detect(model, "iphone") ~"iOS",
                        !str_detect(model, "iPhone") ~"Android")
         )

#get a simplified model column
phone_models <- phone_models %>% 
  mutate(make = case_when(str_detect(model, "iPhone") ~"iPhone",
                        str_detect(model, "iphone") ~"iPhone",
                        str_detect(model, "Samsung") ~"Samsung",
                        str_detect(model, "LG") ~"LG",
                        str_detect(model, "Huawei") ~"Huawei",
                        str_detect(model, "Moto") ~"Motorola",
                        model == "Android" ~"Android, type unknown",
                        str_detect(model, "Pixel") ~"Google Pixel",
                        str_detect(model, "BlackBerry") ~"BlackBerry",
                        str_detect(model, "Flip Phone") ~"Flip Phone",
                        str_detect(model, "Alcatel") ~"Alcatel",
                        str_detect(model, "Lenovo") ~"Lenovo", 
                        str_detect(model, "ZTE") ~"ZTE", 
                        str_detect(model, "HTC") ~"HTC")
  )
```

### OS distribution

The general OS distribution was slightly in favor of Android (42% to 37%); and this does not account for participants who were ported from Android to iPhone (about 19 users).

Phone data was not collected for about 21% of the 272 consented participants.

```{r}

tabyl(phone_models$OS)


library(ggthemes)
theme_set(theme_classic())
ggplot(data = phone_models , aes(y = OS), stat="count") + 
  geom_bar()
```

### Phone Manufacturer distribution

However an overwhelming percentage (37%) used iPhones. This does include users who were enrolled using a study iPhone instead of their personal phone so is a slight overestimate. Samsung was the next most frequent model.

```{r}

tabyl(phone_models$make)


library(ggthemes)
theme_set(theme_classic())
ggplot(data = phone_models , aes(y = make), stat="count") + 
  geom_bar()

```


### Phone Model distribution

There are a far greater variety of phone models among Android phones vs iPhones. This is visible even just looking at Samsungs: we recorded about 23 flavors of Samsung, vs about 16 flavors of iPhone (this table was not corrected for differences in spelling). This warns we may see some trouble with subtle differences in installation, permissions, and notification controls in Androids for Risk2.

```{r}
options(tibble.print_max = Inf)
phone_models %>% filter(str_detect(model,"Samsung")) %>% select(model) %>% unique()

phone_models %>% filter(str_detect(model,"iPhone")) %>% select(model) %>% unique()
options(tibble.print_max = 10)
```


### Carrier distribution

Unfortunately carrier (cell provider) was not collected for a significant number of consented participants (55%).

For those that we did collect (N=95 out of 272 consented), 58% used US Cellular (33%) or Verizon (25%); another 16% used AT&T. This helpfully gives us some carriers that were not on our list for Risk2.

```{r}

carriers <- phone_models %>% filter(!is.na(carrier))

tabyl(carriers$carrier)


library(ggthemes)
theme_set(theme_classic())
ggplot(data = carriers , aes(y = carrier), stat="count") + 
  geom_bar()

```