---
title: "Phone use stats for AJ Goldstein"
output: html_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, echo = FALSE}
library(tidyverse)
library(readxl)
library(janitor) #tabyl

path_rawdata <- "P:/StudyData/RISK/raw_data"
path_data <- "P:/StudyData/RISK/analysis/shared/data"
```


```{r, echo = FALSE}
fin_sample <- read_rds(file.path(path_data,"valid_subids.rds")) %>% 
  pull(SubID)

dem <- read_rds(file.path(path_data, "ID.rds")) %>%
  select(subid = SubID, 
         age = DEM_1, 
         sex = DEM_2, 
         race = DEM_3, 
         hispanic = DEM_4,
         income = DEM_7) %>% 
  mutate(sex = recode(sex, 
                         `1`="Female",
                         `2`="Male"),
         race = recode(race,
           `1` = "American Indian/Alaska Native",
           `2` = "Asian",
           `3` = "Native Hawaiian or Other Pacific Islander",
           `4` = "Black/African American",
           `5` = "White/Caucasian",
           `6` = "Other/Multiracial"),
         hispanic = recode(hispanic,
           `1` = "No",
           `2` = "Yes",
           `3` = "Yes",
           `4` = "Yes",
           `5` = "Yes")) %>%
  filter(subid %in% fin_sample)

phones <- read_xlsx(path = file.path(path_rawdata,"phones.xlsx")) %>% 
  mutate(subid = as.numeric(subid)) %>%
  filter(subid %in% fin_sample) %>%
  mutate(own_phone = case_when(own_phone == "OWN" ~ "own",
                               own_phone == "Own" ~ "own",
                               own_phone == "Study Phone" ~ "study",   
                               own_phone == "Port" ~ "study", 
                               own_phone == "Other-Study iPhone" ~ "study", 
                               own_phone == "Other" ~ "study")) %>%
  mutate(phone_os = case_when(str_detect(phone_type,fixed("phoneix", ignore_case=TRUE)) == TRUE ~ "android",
                          str_detect(phone_type,fixed("phone", ignore_case=TRUE)) == TRUE ~ "iphone",
                          str_detect(phone_type,fixed("phone", ignore_case=TRUE)) == FALSE ~ "android")) 

d <- left_join(dem, phones)
```

### Sample demographics

We have a pretty wisconsin sample.   Not much racial/ethnic diversity.   But we do see a range of income.
```{r}

tabyl(d$sex)
tabyl(d$race)
tabyl(d$hispanic)

library(ggthemes)
theme_set(theme_classic())
ggplot(data = d , aes(x = income)) + 
  geom_histogram()
```

### Phone OS info

These analyses are limited to only those phones that were owned by our participants. We gave phones to participants who didnt own a smartphone that was sufficient to run study apps.

There is a clear income difference between iPhone and Android users (see below) but many low income participants do own iPhones and iPhones were owned by almost half our sample.
```{r}
d_own <- d %>%
  filter(own_phone == "own")

tabyl(d_own$phone_os)

d_own %>% 
  select(phone_os, income) %>% 
  group_by(phone_os) %>% 
  summarise(mean(income), median(income), min(income), max(income))

ggplot(data = d_own , aes(x = phone_os, y = income)) + 
  geom_boxplot() +
  geom_violin(alpha = .05) 

```