---
title: "Make EMA disposition file"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/ema", 
      "/Volumes/private/studydata/risk/knits/ema")
    )
  })
---

### Notes
Purpose: The output of this file will be used to create a consort diagram of participant retention. 

Inputs:  

* visit_dates.csv  
* raw_notes.csv  
* screen.csv  
* session_screen.csv  
* session_intake.csv  
* session_followup_12.csv  
* session_followup_3.csv  


Output:  

* disposition.csv  

### Setup

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
library(here)
```

Paths 
```{r}
path_notes <- here("shared/notes")
path_raw <- "P:/studydata/risk/data_raw"
path_shared <- "P:/studydata/risk/data_processed/shared"
path_ema <- "P:/studydata/risk/data_processed/ema"
```

Read in data
```{r}
visits <- read_csv(here(path_shared, "visit_dates.csv"), col_types = cols())
notes <- read_csv(here(path_notes, "raw_notes.csv"), col_types = cols())
```


### Creat disposition file

Read in subids for all participants who showed up to the screen visit (N = `r nrow(notes)`) and add visit dates for all subids with at least a completed screen visit (N = `r nrow(visits)`)   

Note: reading in all possible subids from raw data

```{r}
disposition <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>%
  as.numeric() %>%  
  enframe(name = NULL, value = "subid") %>% 
  left_join(visits, by = "subid") %>% 
  glimpse()
```

### Calculate disposition status 

determine last completed visit  
```{r}
disposition <- disposition %>% 
  mutate(last_visit = case_when(!is.na(final_visit) ~ "followup_3",
                                !is.na(followup_2) & is.na(final_visit) ~ "followup_2",
                                !is.na(followup_1) & is.na(followup_2) & is.na(final_visit) ~ "followup_1",
                                !is.na(intake) & is.na(followup_1) & is.na(followup_2) ~ "intake",
                                !is.na(screen) & is.na(intake) ~ "screen",
                                TRUE ~ as.character(NA))) %>% 
  select(subid, last_visit, start_study, end_study) %>% 
  glimpse()
```


```{r}
tabyl(disposition$last_visit) %>% 
  adorn_totals("row")
```


One participant enrolled in study and discontinued on same day. Adjust last visit to be screen since per discussion with JC we do not consider them enrolled.

```{r}
disposition %>% 
  filter(start_study == end_study)

disposition <- disposition %>% 
  mutate(last_visit = case_when(start_study == end_study ~ "screen", 
                                TRUE ~ last_visit))
```



The following numbers are confirmed:   
`r nrow(subset(disposition, last_visit %in% c("intake", "followup_1", "followup_2", "followup_3")))` participants completed the intake (i.e., enrolled).   
`r nrow(subset(disposition, last_visit %in% c("followup_1", "followup_2", "followup_3")))` participants completed followup 1   
`r nrow(subset(disposition, last_visit %in% c("followup_2", "followup_3")))`  participants made it to followup 2  
`r nrow(subset(disposition, last_visit %in% c("followup_3")))`  participants completed followup 3  



### Determine who screen failed and who declined to participate

`r nrow(subset(disposition, last_visit == "screen"))` participants showed to screen but did not enroll    
An additional `r nrow(subset(disposition, is.na(last_visit)))` participants showed to the screening visit but did not complete the screen. (i.e., last_visit is noted as NA)    


#### Check eligibility info from screen survey and session form 

screen survey
```{r}
screen <- read_csv(file.path(path_shared, "screen.csv"), col_types = cols()) %>%
  rename(screen_date = end_date) %>% 
  mutate(dsm5_1 = dplyr::recode(dsm5_1, No = 0, Yes = 1),
         dsm5_2 = dplyr::recode(dsm5_2, No = 0, Yes = 1),
         dsm5_3 = dplyr::recode(dsm5_3, No = 0, Yes = 1),
         dsm5_4 = dplyr::recode(dsm5_4, No = 0, Yes = 1),
         dsm5_5 = dplyr::recode(dsm5_5, No = 0, Yes = 1),
         dsm5_6 = dplyr::recode(dsm5_6, No = 0, Yes = 1),
         dsm5_7 = dplyr::recode(dsm5_7, No = 0, Yes = 1),
         dsm5_8 = dplyr::recode(dsm5_8, No = 0, Yes = 1),
         dsm5_9 = dplyr::recode(dsm5_9, No = 0, Yes = 1),
         dsm5_10 = dplyr::recode(dsm5_10, No = 0, Yes = 1),
         dsm5_11 = dplyr::recode(dsm5_11, No = 0, Yes = 1),
         scl90_8 = dplyr::recode(scl90_8, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_18 = dplyr::recode(scl90_18, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_43 = dplyr::recode(scl90_43, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_68 = dplyr::recode(scl90_68, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_76 = dplyr::recode(scl90_76, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_83 = dplyr::recode(scl90_83, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_7 = dplyr::recode(scl90_7, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_16 = dplyr::recode(scl90_16, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_35 = dplyr::recode(scl90_35, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_62 = dplyr::recode(scl90_62, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_77 = dplyr::recode(scl90_77, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_84 = dplyr::recode(scl90_84, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_85 = dplyr::recode(scl90_85, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_87 = dplyr::recode(scl90_87, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_88 = dplyr::recode(scl90_88, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         scl90_90 = dplyr::recode(scl90_90, `Not At All` = 0, `A Little Bit` = 1, Moderately = 2, `Quite A Bit` = 3, Extremely = 4),
         auh_8_year = as.character(auh_8_year),
         auh_8_day = as.character(auh_8_day)) %>%
  unite("quit_date", auh_8_year, auh_8_month, auh_8_day, sep = "-") %>% 
  mutate(quit_date = as_date(quit_date, format = "%Y-%B-%d"),
         days_quit = as.double(difftime(screen_date, quit_date, units = "days"))) %>% 
  rowwise() %>% 
  mutate(dsm_total_score = sum(dsm5_1, dsm5_2, dsm5_3, dsm5_4, dsm5_5, dsm5_6, dsm5_7 ,dsm5_8, dsm5_9, dsm5_10, dsm5_11),
         scl90_paranoia = (sum(scl90_8, scl90_18, scl90_43, scl90_68, scl90_76, scl90_83) - 6)/6,
         scl90_psychosis = (sum(scl90_7, scl90_16, scl90_35, scl90_62, scl90_77, scl90_84, scl90_85, scl90_87, scl90_88, scl90_90) - 10)/10) %>% 
  ungroup() %>% 
  select(subid, screen_date, quit_date, days_quit, dsm_total_score, scl90_paranoia, scl90_psychosis) %>% 
  glimpse()
```

add relevant session form variables
```{r}
screen <- read_csv(file.path(path_shared, "session_screen.csv"), col_types = cols()) %>% 
  unite("quit_date_session", sfsr_10_3_1, sfsr_10_1_1, sfsr_10_2_1, sep = "-") %>% 
  mutate(quit_date_screen_session = as_date(quit_date_session, format = "%Y-%B-%d"),
         days_quit_screen_session = as.double(difftime(start_date, quit_date_screen_session, units = "days"))) %>% 
  select(subid,
         screen_session_date = start_date,
         quit_date_screen_session,
         days_quit_screen_session,
         screen_consent = sfsr_5,
         screen_consent_no = sfsr_6,
         screen_consent_no_explain = sfsr_6_text,
         screen_continue_study = sfsr_9,
         screen_complete = sfsr_39,
         screen_incomplete_explain = sfsr_40,
         screen_weeks_sober = sfsr_11,
         screen_last_drink = sobr_check,
         screen_complete_id = sfsr_14,
         screen_incomplete_id_explain = sfsr_15,
         screen_eligibility = sfsr_16,
         screen_consult_eligibility_continue = sfsr_18,
         screen_ineligibility_reason = sfsr_19,
         screen_ineligibility_reason_explain = q62_text,
         screen_intake_scheduled = sfsr_28,
         screen_intake_not_scheduled_explain = sfsr_30,
         screen_feasability = q76_1,
         screen_notes = sfsr_41) %>% 
  # filter out no shows 
  filter(subid %in% disposition$subid) %>% 
  # keep only most recent form to prevent duplicates
  group_by(subid) %>% 
  arrange(desc(screen_session_date)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  full_join(screen, by = "subid") %>% 
  glimpse()
```


Filter to subids that did not enroll (N = `r nrow(subset(screen, subid %in% c(disposition %>% filter(last_visit == "screen" | is.na(last_visit)) %>% pull(subid))))`)
```{r}
screen %>% 
  filter(subid %in% c(disposition %>%   
                        filter(last_visit == "screen" | is.na(last_visit)) %>% 
                        pull(subid))) %>%
  arrange(subid) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### Update status with new info

```{r}
screen <- screen %>% 
  filter(subid %in% c(disposition %>%   
                        filter(last_visit == "screen" | is.na(last_visit)) %>% 
                        pull(subid))) %>% 
  mutate(reason_not_enrolled = case_when(screen_consent == "No" ~ "no_consent",
                                      dsm_total_score < 4 ~ "ineligible",
                                      screen_eligibility == "No" ~ "ineligible",
                                      screen_incomplete_explain == "Screen ineligible - consult with Candace" ~ "ineligible",
                                      TRUE ~ as.character(NA))) %>% 
  select(subid, reason_not_enrolled)
```

Status determined from qualtrics surveys
```{r}
tabyl(screen$reason_not_enrolled)
```


Status determined from notes    
Update variable documenting if participant was not_interested or ineligible or if it is unclear to explain why they didn't enroll   
No show or multiple reschedules before cancelling interpreted as not interested
```{r}
disposition <- disposition %>% 
  full_join(screen %>% select(subid, reason_not_enrolled), by = "subid") %>% 
  mutate(reason_not_enrolled = case_when(subid == 4 ~ "not_interested",
                                      subid == 68 ~ "ineligible",
                                      subid == 75 ~ "ineligible",
                                      subid == 142 ~ "ineligible",
                                      subid == 144 ~ "ineligible",
                                      subid == 12 ~ "ineligible",
                                      subid == 13 ~ "ineligible",
                                      subid == 14 ~ "ineligible",
                                      subid == 22 ~ "not_interested",
                                      subid == 35 ~ "ineligible",
                                      subid == 36 ~ "not_interested",
                                      subid == 45 ~ "unclear",
                                      subid == 46 ~ "unclear",
                                      subid == 49 ~ "unclear",
                                      subid == 57 ~ "ineligible",
                                      subid == 60 ~ "ineligible",
                                      subid == 67 ~ "ineligible",
                                      subid == 69 ~ "unclear",
                                      subid == 91 ~ "not_interested",
                                      subid == 101 ~ "not_interested",
                                      subid == 108 ~ "not_interested",
                                      subid == 112 ~ "not_interested",
                                      subid == 124 ~ "unclear",
                                      subid == 125 ~ "unclear",
                                      subid == 165 ~ "ineligible",
                                      subid == 168 ~ "unclear",
                                      subid == 174 ~ "not_interested",
                                      subid == 216 ~ "not_interested",
                                      subid == 219 ~ "unclear",
                                      subid == 220 ~ "not_interested",
                                      subid == 227 ~ "unclear",
                                      subid == 233 ~ "not_interested",
                                      subid == 235 ~ "unclear",
                                      subid == 254 ~ "not_interested",
                                      subid == 260 ~ "ineligible",
                                      subid == 272 ~ "ineligible",
                                      TRUE ~ reason_not_enrolled))
```

```{r}
disposition %>% 
  filter(last_visit == "screen" | is.na(last_visit)) %>% 
  tabyl(reason_not_enrolled) %>% 
  janitor::adorn_totals("row")
```

Without more info - unclear cases will be defaulted to participant not being interested in study
```{r}
disposition <- disposition %>% 
  mutate(reason_not_enrolled = case_when(reason_not_enrolled == "unclear" ~ "not_interested",
                                      TRUE ~ reason_not_enrolled))
```

Notes these dispositions were derived from
```{r}
# notes %>% 
#   filter(subid %in% c(disposition %>%   
#                         filter(last_visit == "screen" | is.na(last_visit)) %>% 
#                         pull(subid))) %>% 
#   kbl() %>% 
#   kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
#   scroll_box(width = "100%", height = "500px")
```

### Create final variables

eligible sample
```{r}
disposition <- disposition %>% 
  mutate(eligible = case_when(reason_not_enrolled == "ineligible" ~ "no",
                              TRUE ~ "yes"))

tabyl(disposition$eligible)
```

consented sample
```{r}
disposition <- disposition %>% 
  filter(eligible == "yes") %>% 
  mutate(consented = case_when(reason_not_enrolled == "no_consent" ~ "no",
                              TRUE ~ "yes")) 

tabyl(disposition$consented)
```

enrolled sample
```{r}
disposition <- disposition %>% 
  mutate(enrolled = case_when(last_visit %in% c("intake", "followup_1", "followup_2", "followup_3") ~ "yes",
                              TRUE ~ "no"))

tabyl(disposition$enrolled)
```

followup sample
```{r}
disposition <- disposition %>% 
  mutate(completed_followup = case_when(last_visit %in% c("followup_1", "followup_2", "followup_3") ~ "yes",
                              TRUE ~ "no"))

tabyl(disposition$completed_followup)
```


analysis sample   
Exclude subids 104, 269, and 204 from analysis per notes in mak_lapses.Rmd
```{r}
disposition <- disposition %>% 
  mutate(analysis = case_when(completed_followup == "yes" & !subid %in% c(104, 269, 204) ~ "yes",
                              TRUE ~ "no"))

tabyl(disposition$analysis)
```


Add reasons for discontinuation for consort diagram   
NOTE: These were manually determined from raw_notes.csv 
```{r}
disposition <- disposition %>% 
  mutate(consented_reason = case_when(subid == 133 ~ "Did not wish to participate", 
                                    TRUE ~ NA_character_),
         enrolled_reason = case_when(subid %in% c(4, 148, 271) ~ "No longer interested",
                                     subid == 22 ~ "Health concerns",
                                     subid == 233 ~ "No transportation",
                                     subid %in% c(91, 108, 174, 216, 220, 235, 254) ~ "Participant rescheduled before cancelling/no-showing",
                                     subid %in% c(36, 45, 46, 67, 69, 112, 125, 168, 219, 227,  49, 101, 124) ~ "Unknown",
                                     TRUE ~ NA_character_),
         completed_followup_reason = case_when(subid == 8 ~ "Family crisis",
                                               subid %in% c(17, 237) ~ "Entered treatment",
                                               subid %in% c(24, 151, 105) ~ "No longer sober",
                                               subid == 41 ~ "No longer interested",
                                               subid == 173 ~ "Withdrawn due to poor compliance",
                                               subid %in% c(87, 177, 182) ~ "Participant rescheduled before cancelling/no-showing",
                                               subid %in% c(50, 61, 62, 267) ~ "Unknown",
                                               TRUE ~ NA_character_),
         analysis_reason = case_when(subid == 104 ~ "No goal of abstinence",
                                     subid == 269 ~ "Evidence of careless responding",
                                     subid == 204 ~ "Poor compliance", 
                                     TRUE ~ NA_character_))
```


### Example code for consort diagram
```{r fig.width=10, fig.height=8}
library(consort)

consort_plot(data = disposition,
             orders = c(eligible = "Eligible Sample",
                        consented_reason = "Not Consented",
                        consented = "Consented",
                        enrolled_reason = "Not Enrolled",
                        enrolled = "Enrolled",
                        completed_followup_reason = "Discontinued",
                        completed_followup = "Completed through Followup 1",
                        analysis_reason = "Excluded",
                        analysis = "Final Analysis"),
             side_box = c("consented_reason", 
                          "enrolled_reason", 
                          "completed_followup_reason",
                          "analysis_reason"),
             cex = .9)
```






### Write csv
```{r}
write_csv(disposition, here(path_ema, "disposition.csv")) %>% 
  glimpse()
```

