---
title: "Clean Sleep Data"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

### Notes
Purpose: This script aggregates the sleep monitor data from the raw JSON files and does light EDA.    

Inputs:  
* [subid]_.json  


### Setup
```{css, include = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths 
```{r}
path_raw <- "raw_data"
path_out <- "analysis/shared/data"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(tidyjson)
library(lubridate)
```


### Read in sleep JSON files

#### Function
```{r}
read_sleep <- function(subid) {
    # message(str_c("reading sleep file for subid ", subid))
    sleep_log <- tibble(subid = character(),
                   message = character())
    sleep_files <- list.files(file.path(path_raw, subid), pattern = "_Sleep|_sleep", include.dirs = FALSE)
    if(length(sleep_files) > 0) {
      for(file in sleep_files) {
        if(str_detect(file, ".json") | str_detect(file, ".JSON")) {
          # convert file name to lower case .json 
          if(str_detect(file, ".JSON")) {
            file <- str_replace(file, ".JSON", ".json")
          }
          # read in JSON file and flatten
          sleep <- read_json(file.path(path_raw, subid, file))
          sleep <- sleep %>% gather_array %>% spread_all
          # Add subid and file name to tibble
          sleep <- sleep %>% 
            mutate(subid = subid,
                   file_name = file) %>% 
            as_tibble()
          # Join log files
          sleep_log <- sleep_log %>%
            full_join(sleep) %>%
            suppressMessages()
        }
      }
      return(sleep_log)
    } else if(length(sleep_files) == 0){
        sleep_log <- sleep_log %>% add_row(subid = subid, message = "No sleep file found")
        return(sleep_log)
    }
}
```

#### Get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```

FIX: temp filtering out subids with errors until I can troubleshoot why their files are read in with an error.
```{r}
subids <- subids %>% 
  filter(!subid %in% c("007", "048", "067", "076", "077", "109", "136"))
```

#### Read in all sleep files
```{r}
all_sleep <- tibble(subid = character())
all_sleep <- map_df(subids$subid, ~read_sleep(.)) %>% 
  full_join(all_sleep, by = "subid") %>% 
  glimpse()
```

<br>

### Trouble shooting  

FIX: 7 subids not in file (7, 48, 67, 76, 77, 109, 136)  

parse error with subid 7's sleep file - premature EOF
```{r eval = FALSE}
# with tidyjson package
sleep <- read_json(file.path(path_raw, "007/007_Sleep.json"))

# with jsonlite package
sleep <- readLines(file.path(path_raw, "007/007_Sleep.json"), warn=FALSE)
df <- jsonlite::fromJSON(sleep, flatten = TRUE)
# listcols <- colnames(df[lapply(colnames(df), function(x) class(df[,x])) == "list"])
# for (col in listcols) df[col] = data.frame(unlist(lapply(df[,col], function(x) toString(unlist(x)))))
# 

sleep <- jsonlite::fromJSON(paste(readLines(file.path(path_raw, "007/007_Sleep.json"), warn=FALSE),
                             collapse=""))

```

48, 67, 76, and 77 have html in their JSON sleep files 
```{r eval = FALSE}
sleep <- read_json(file.path(path_raw, "048/048_Sleep.json"))
sleep <- read_json(file.path(path_raw, "067/067_Sleep.json"))
```

109 and 136 have nothing in sleep file and throwing an error
```{r eval = FALSE}
read_json(file.path(path_raw, "109/109_sleep.json")) %>%
  kbl() %>%
  kable_styling()

read_json(file.path(path_raw, "136/136_sleep.json")) %>%
  kbl() %>%
  kable_styling()
```

<br>

### EDA 

```{r}
table(all_sleep$message)

sleep <- all_sleep %>% 
  filter(is.na(message)) %>% 
  select(-c(message, document.id, array.index)) %>% 
  mutate(date = date(date)) %>% 
  glimpse()

no_sleep <- all_sleep %>% 
  filter(message == "No sleep file found") %>% 
  select(subid, message) %>% 
  glimpse()
```

`r nrow(sleep)` sleep observations from `r length(unique(sleep$subid))` subids.  
`r length(unique(no_sleep$subid))` subids have no sleep file.   

Sleep data ranges from `r min(sleep$date)` to `r max(sleep$date)`  

*FIX: 7 subids have sleep files that need to be troubleshooted*  
*FIX: In burden analysis we may lose sleep monitor burden data by using last survey*  

#### Check subids

2 subids have 2 sleep files
```{r}
sleep %>% 
  group_by(subid, file_name) %>% 
  slice(1) %>% 
  ungroup() %>% 
  count(subid) %>% 
  filter(n > 1)
```

```{r}
sleep %>% 
  group_by(subid, file_name) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(subid %in% c("043", "052")) %>% 
  select(subid, file_name)
```

Compare start and end dates and number of observations
```{r}
# subid 43
sleep %>% 
  filter(subid == "043") %>% 
  group_by(file_name) %>% 
  summarise(min_date = min(date),
            max_date = max(date),
            n = n())

sleep %>% 
  filter(subid == "043") %>% 
  filter(file_name == "043_Sleep.json")

# subid 52
sleep %>% 
  filter(subid == "052") %>% 
  group_by(file_name) %>% 
  summarise(min_date = min(date),
            max_date = max(date),
            n = n())
```

Note: for subid 52 there is no overlap between these two files.  
FIX: check to see if 2 entries in subid's 43 file are in the other file. Doesn't appear to be any duplicates in file.    

No duplicates
```{r}
sleep <- sleep %>% 
  distinct() %>% 
  glimpse()
```



### Write csv
```{r}
write_csv(sleep, file.path(path_out, "sleep.csv")) %>% 
  glimpse()
```

