---
title: "Contacts"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Notes
Purpose: This file reads in all individual excel contact files from participants' raw data folders and creates an aggregate data file. Light EDA is also included as part of this cleaning script.   

Inputs:   
[subid]_Contacts.xlsx   

Output:   
contacts.csv  

### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},
        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"})
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
# conflict_prefer("filter", "dplyr")
# conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(readxl)
library(lubridate)
library(janitor)

theme_set(theme_classic())

source(here(path_lab_support, "fun_phone_numbers.R"))
```

Relative Paths
```{r}
path_log <- "shared/notes"
```

### Create function
```{r}
read_contacts <- function(subid) {
    filepath <- list.files(file.path(path_raw, subid), pattern = "Contacts", include.dirs = FALSE, full.names = TRUE)
    if(length(filepath) > 0) {
      contacts <- read_excel(filepath) %>% 
             mutate(across(everything(), as.character), # for merging
                    subid = as.numeric(subid)) 
      return(contacts)
    }
}
```

### Get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```

### Read in data and glimpse
```{r}
contacts <- map_df(subids$subid, ~read_contacts(.)) %>% 
  glimpse()
```


<br>


### Clean data from log
cleaning function
```{r}
clean_contacts <- function(d, log){
  # recode_one log entries
  log_recode_one <- dplyr::filter(log, log_action == "recode_one")

  for (i in seq_along(log_recode_one$index)){

    log_subid <- pluck(log_recode_one, "subid", i)
    log_var_name <- pluck(log_recode_one, "var_name", i)
    log_new_value <- pluck(log_recode_one, "new_value", i)
    log_old_value <- pluck(log_recode_one, "old_value", i)

    # check that only one matching data row
    if (is.na(log_old_value)) {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(is.na(get(log_var_name))) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    } else {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    }

    if (length(row_id) != 1) {
      stop("Rows matching subid: ", log_subid, " does not equal 1")
    }

    # make change to rowid
    if (is.numeric(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.numeric(log_new_value)
    if (is_character(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.character(log_new_value)
    if (is.POSIXt(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as_datetime(log_new_value)

  }

  # recode_all entries
  # Involves changing recurrent typo patterns in variable response labels
  log_recode_all <- dplyr::filter(log, log_action == "recode_all")

  for (i in seq_along(log_recode_all$index)){

    log_var_name <- pluck(log_recode_all, "var_name", i)
    log_new_value <- pluck(log_recode_all, "new_value", i)
    log_old_value <- pluck(log_recode_all, "old_value", i)

    # pull out row ids that need to be recoded
    row_ids <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)

    for (i in seq_along(row_ids)) {

      if (is.numeric(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.numeric(log_new_value)
      if (is_character(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.character(log_new_value)
      if (is.POSIXt(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as_datetime(log_new_value)
    }
  }

  return(d)
}
```

read in log and summarize
```{r}
log <- read_csv(file.path(path_log, "log_contacts.csv"), col_types = cols()) %>%
  rowid_to_column("index") %>%
  glimpse()

# view log actions
table(log$log_action)

# print notes
log %>%
  dplyr::filter(log_action == "note") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed"))
```

clean data
```{r}
contacts <- contacts %>%
  clean_contacts(., log) %>%
  glimpse()
```


### tidy data
Tidy variable names
```{r}
contacts <- contacts %>%
  clean_names() %>%
  glimpse()
```


Check for any legitimate missing phone numbers before transforming dataframe to long
```{r}
contacts %>%
  dplyr::filter(is.na(home_phone) & is.na(cell_phone) & is.na(other_phone1) & is.na(other_phone2)) %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

# Temporarily turn NA into character to preserve
contacts <- contacts %>%
  mutate(cell_phone = case_when(subid == 41 & is.na(cell_phone) & is.na(other_phone1) ~ "NA",
                                TRUE ~ cell_phone))
```


pivot longer and reorder variables
```{r}
contacts <- contacts %>%
  pivot_longer(home_phone:other_phone2, names_to = "phone_type", values_to = "phone_number") %>%
  dplyr::filter(!is.na(phone_number)) %>%
  select(subid, utc, contact_type = type, phone_type, phone_number, contact_drank_past:state, utc) %>%
  glimpse()
```

replace all string NAs to actual missing value NAs
```{r}
contacts <- contacts %>%
  naniar::replace_with_na_if(.predicate = is.character, condition = ~.x == "NA")
```


<br>


### EDA

`r length(unique(contacts$subid))` subids have contact information.

Check to see who completed intake that don't have contacts
NOTE: Subids 8 and 235 do not have a contacts file
```{r}
visit_dates <- read_csv(file.path(path_shared, "visit_dates.csv"), col_types = cols())
notes <- read_csv(file.path(path_raw, "raw_notes.csv"), col_types = cols()) %>%
  select(subid, notes_general)

visit_dates %>%
  dplyr::filter(!is.na(intake)) %>%
  dplyr::filter(!subid %in% as.numeric(contacts$subid))

notes %>%
  dplyr::filter(subid %in% c(8, 235)) %>%
  kbl() %>%
  kable_styling()
```


NOTE: subid 67 has contacts but never completed intake/started study - leaving contacts in because they will be filtered out at the project-level depending on final sample
```{r}
intake <- visit_dates %>%
  dplyr::filter(!is.na(intake))
contacts %>%
  dplyr::filter(!as.numeric(subid) %in% intake$subid)

visit_dates %>%
  dplyr::filter(subid == 67)

notes %>%
  dplyr::filter(subid == 67) %>%
  kbl() %>%
  kable_styling()
```


Check for duplicate entries
FIX: Some duplicates are errors (2 entries on same date with discrepant answers) and some are not (updating address, home phone number belongs to 2 parents, etc.)
NOTE: leaving as project-level pre-processing decision of how to handle error and non-error duplicates
```{r}
# filter out identical entries
contacts <- contacts %>%
  distinct(across(-utc), .keep_all = TRUE)

# count duplicate numbers listed for each subid
duplicates <- contacts %>%
  group_by(subid, phone_number) %>%
  summarise(n = n()) %>%
  dplyr::filter(n > 1)

print(duplicates, n = Inf)

contacts %>%
  dplyr::filter(phone_number %in% duplicates$phone_number & subid %in% duplicates$subid) %>%
  arrange(subid, phone_number) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  scroll_box(width = "100%", height = "500px")
```

<br>

#### Missing data
```{r}
naniar::miss_var_summary(contacts)
```

2 Missing phone numbers
```{r}
contacts %>%
  dplyr::filter(is.na(phone_number))
```

<br>

* subid 81: from data log - "Participant’s partner is incarcerated. She reported that all of the phone calls that come up as restricted or unknown are incoming calls from her partner. She reported that she speaks to him frequently." Also, note the state is Illinois which might give some clues as to which unknown/restricted numbers are him
* subid 41: No info as to why this number is blank

<br>


Missing contact type values have an actual NA in the excel file - what could this mean?
```{r}
contacts %>%
  dplyr::filter(is.na(contact_type)) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  column_spec(3, color = "red") %>%
  scroll_box(width = "100%")
```

Missing context variables
Most missing context variables are self, other or spam entries - still a considerable amount of missing values for co-workers and family-other
```{r}
contacts %>%
  dplyr::filter(is.na(recovery)) %>%
  dplyr::filter(contact_type != "Self" & contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  scroll_box(width = "100%", height = "500px")
```


<br>

#### contact type

```{r}
contacts %>%
  tabyl(contact_type)
```

<br>

#### Phone numbers

Raw number format
```{r}
contacts %>%
  dplyr::filter(!is.na(phone_number)) %>%
  select(phone_number) %>%
  print(n = Inf)
```

Check for non-numeric characters
```{r}
contacts %>%
  dplyr::filter(str_detect(phone_number, "[[:space:][:punct:][:alpha:]]")) %>%
  select(phone_number)
```

Numbers not 10 digits
Only 3 are known contacts
```{r}
contacts %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  print(n = Inf)
```

Filter out short codes
```{r}
contacts %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  dplyr::filter(str_length(phone_number) != 5 & str_length(phone_number) != 6) %>%
  print(n = Inf)
```

Check country code on these numbers
```{r}
numbers <- contacts %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  dplyr::filter(str_length(phone_number) != 5 & str_length(phone_number) != 6) %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)

valid_country_code <- NULL

for (i in 1:length(numbers)) {
  if(check_country_code(numbers[i])) {
     valid_country_code <- append(valid_country_code, numbers[i])
  }
}

valid_country_code
```


Check area code for all 10 digit numbers
Print numbers without valid area code
```{r}
numbers <- contacts %>%
  dplyr::filter(str_length(phone_number) == 10) %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)

not_valid_area_code <- NULL

for (i in 1:length(numbers)) {
  if(!check_area_code(numbers[i])) {
     not_valid_area_code <- append(not_valid_area_code, numbers[i])
  }
}

contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  select(subid, phone_number, contact_type) %>%
  print(n = Inf)
```

FIX: 600 area code under subid 29 is probably supposed to be 608 since 600 is not a valid US area code and no log entries exist with that area code
```{r}
logs <- read_csv(file.path(path_shared, "voice_ios.csv"), col_types = "iTiiiiiniiiincccccccTTcc") %>%
  glimpse()

logs %>%
  dplyr::filter(zaddress == "6008904796") %>%
  select(subid, zaddress)
```

```{r}
logs %>%
  dplyr::filter(zaddress == "6088904796") %>%
  dplyr::filter(subid == 29) %>%
  select(subid, zaddress)
```

No contacts already listed as this number for subid 29
```{r}
contacts %>%
  dplyr::filter(phone_number == "6088904796") %>%
  dplyr::filter(subid == "029")
```

Filter out spam from other numbers with invalid area codes
```{r}
contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  print(n = Inf)
```


Check country codes for international numbers
```{r}
numbers <- contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  dplyr::filter(contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)

valid_country_code <- NULL

for (i in 1:length(not_valid_area_code)) {
  if(check_country_code(not_valid_area_code[i])) {
     valid_country_code <- append(valid_country_code, not_valid_area_code[i])
  }
}

valid_country_code
```

* 47 is germany country code and 44 is UK country code but these have too few digits
* The rest all belong to one subid and so I am wondering if these are internet numbers or something that isn't registering as a valid number.
```{r}
contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  dplyr::filter(!phone_number %in% valid_country_code) %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  print(n = Inf)
```



<br>

#### Monthly visit
NOTE: monthly visit means participant visits home of contact at least monthly
```{r}
contacts %>%
  tabyl(monthly_visit)
```

Should have been gathering addresses when monthly_visit = yes
We have addresses for all but 11 of the contacts who participants visited monthly
```{r}
contacts %>%
  dplyr::filter(monthly_visit == "Yes") %>%
  count(!is.na(street_address))

contacts %>%
  dplyr::filter(monthly_visit == "Yes") %>%
  dplyr::filter(!is.na(street_address)) %>%
  select(subid, contact_type, street_address, city, state) %>%
  print(n = Inf)
```

Locations for other contacts
We only have 6 address for contacts that don't have monthly_visit as yes
```{r}
contacts %>%
  dplyr::filter(monthly_visit == "No" | is.na(monthly_visit)) %>%
  count(!is.na(street_address))
```

<br>

#### Context variables

```{r}
contacts %>%
  tabyl(contact_drank_past)

contacts %>%
  tabyl(drink_status)

contacts %>%
  tabyl(contact_drink_future)

contacts %>%
  tabyl(recovery)

contacts %>%
  tabyl(support_status)
```

FIX: No is not a valid response - error, but not enough info to resolve (note entry in log)
```{r}
contacts %>%
  dplyr::filter(support_status == "No") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  column_spec(10, color = "red") %>%
  scroll_box(width = "100%")
```

```{r}
contacts %>%
  tabyl(contact_experience)
```

FIX: unpleasant/mixed is not a valid response option - error, but not enough info to resolve (note entry in log)
```{r}
contacts %>%
  dplyr::filter(contact_experience == "Unpleasant/mixed") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  column_spec(11, color = "red") %>%
  scroll_box(width = "100%")
```

<br>

#### Other Distributions

Number of contacts per subid
NOTE: this should be interpreted as number of unique phone numbers per participant since this plot is not accounting for the fact that contacts could have more than one number (e.g., home, cell, work)
```{r message = FALSE}
contacts %>%
  group_by(subid) %>%
  summarise(n_contacts = length(unique(phone_number))) %>%
  ggplot(aes(x = n_contacts)) +
  geom_histogram(color = "black", fill = "light grey") +
  labs(title = "Number of contacts per participant") +
  geom_vline(aes(xintercept = mean(n_contacts)), contacts %>%
               group_by(subid) %>%
               summarise(n_contacts = length(unique(phone_number))), linetype = "dashed")
```

Number of contacts per subid faceted by spam vs not spam
```{r message = FALSE}
contacts %>%
  mutate(spam = case_when(contact_type == "Irrelevant/Spam" ~ "spam",
                          TRUE ~ "contact")) %>%
  group_by(subid, spam) %>%
  summarise(n_contacts = length(unique(phone_number))) %>%
  ggplot(aes(x = n_contacts)) +
  geom_histogram(color = "black", fill = "light grey") +
  facet_wrap(~ spam) +
  labs(title = "Number of contacts per participant") +
  geom_vline(aes(xintercept = mean(n_contacts)), contacts %>%
               mutate(spam = case_when(contact_type == "Irrelevant/Spam" ~ "spam",
                          TRUE ~ "contact")) %>%
               group_by(subid, spam) %>%
               summarise(n_contacts = length(unique(phone_number))), linetype = "dashed")
```


<br>

### Write CSV
```{r}
write_csv(contacts, file.path(path_shared, "contacts.csv")) %>%
  glimpse()
```

<br>
