---
title: "Session FU3 Clean File"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---


### Code Status

These data are fully cleaned and checked with EDA.       


### Conclusions 

* Reminder that session forms are considered notes not data.         
* For this reason times on start and end dates may not have accurate precision. For example, study staff may have started session form prior to participant arriving or gone back into the survey to make updates which changes the start and end time. That being said at the date level all start and end times are accurate.   
* UTC time stamp is actually in British Summer time which gains an hour during daylight savings.   
* 133 subids completed followup 3, but we have only have 128 session forms due to some participants completing the survey from home.   


### Notes
This script creates a single csv file from the four raw data session FU3 files. Includes file merging and minimal variable renaming (only to merge files with inconsistent names).    

Inputs:   

* session_followup_3_v1.csv  
* session_followup_3_v2.csv  
* session_followup_3_v3.csv
* session_followup_3_v4.csv

* log_session_followup_3_v4.csv

Output:  

* session_followup_3.csv 

### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
```

Absolute Paths 
```{r absolute_paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_in <- "P:/studydata/risk/data_raw/qualtrics"
          path_out <- "P:/studydata/risk/data_processed/shared"
          path_raw <- "P:/studydata/risk/data_raw"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_in <- "/Volumes/private/studydata/risk/data_raw/qualtrics"
          path_out <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"}
        )
```

Relative paths
```{r}
path_log <- "shared/notes"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages
```{r message = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(kableExtra)

source(here(path_lab_support, "clean_qualtrics_by_log.R"))
```


### Read in session screen csvs

```{r}
session_1 <- read_csv(here(path_in, "session_followup_3_v1.csv"), col_types = cols()) %>%
  rename(subid = SSFU3_3, response_id = ResponseID) %>% 
  glimpse()
session_2 <- read_csv(here(path_in, "session_followup_3_v2.csv"), col_types = cols()) %>% 
  rename(subid = SSFU3_3, response_id = ResponseID) %>% 
  glimpse()
session_3 <- read_csv(here(path_in, "session_followup_3_v3.csv"), col_types = cols()) %>% 
  rename(subid = SSFU3_3, response_id = ResponseID) %>% 
  glimpse()
session_4 <- read_csv(here(path_in, "session_followup_3_v4.csv"), col_types = cols()) %>% 
  rename(subid = SSFU3_3, response_id = ResponseID) %>% 
  glimpse()
```

###  Clean and merge

```{r}
log_1 <- read_csv(here(path_log, "log_session_followup_3_v1.csv"), col_types = cols())  %>% 
  rowid_to_column("index") %>% 
  glimpse()
```

#### Log actions

```{r}
tabyl(log_1$log_action) 
```

Variables with recode_one edits
```{r}
log_1 %>% 
  filter(log_action == "recode_one") %>% 
  tabyl(var_name)
```

Changes to subid variable
```{r}
log_1 %>%
  filter(var_name == "subid") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

Entries removed
```{r}
log_1 %>% 
  filter(log_action == "remove") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

#### Clean session data

```{r}
session_1 <- clean_qualtrics_by_log(session_1, log_1)
```


### Tidy data

```{r}
session_1 <- session_1 %>% 
  rename("real_data" = SFFU3_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFFU3_4 = as.character(Q47_TEXT),
         SFFU3_32 = as.character(Q64),
         across(where(is.logical), as.character)) %>% 
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFFU3_4,
         SFFU3_5,
         SFFU3_12,
         SFFU3_13,
         SFFU3_14,
         SFFU3_15,
         SFFU3_16,
         Q37,
         SFFU3_23,
         SFFU3_24,
         SFFU3_25,
         SFFU3_26,
         SFFU3_27,
         SFFU3_28,
         SFFU3_29,
         SFFU3_30,
         SFFU3_31 = SSFU3_31,
         SFFU3_32,
         SFFU3_33,
         SFFU3_34) %>% 
  clean_names() %>% 
  glimpse()

session_2 <- session_2 %>% 
  rename("real_data" = SFFU3_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFFU3_4 = as.character(SFFU3_4),
         SFFU3_32 = as.character(SFFU3_32),
         across(where(is.logical), as.character)) %>% 
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFFU3_4,
         SFFU3_5,
         SFFU3_6,
         SFFU3_7,
         SFFU3_12,
         SFFU3_13,
         SFFU3_14,
         SFFU3_15,
         SFFU3_16,
         SFFU3_19,
         SFFU3_20,
         Q37,
         SFFU3_23,
         SFFU3_24,
         SFFU3_25,
         SFFU3_26,
         SFFU3_27,
         SFFU3_28,
         SFFU3_29,
         SFFU3_30,
         SFFU3_31 = SSFU3_31,
         SFFU3_32,
         SFFU3_33,
         SFFU3_34) %>% 
  clean_names() %>% 
  glimpse()

session_3 <- session_3 %>% 
  rename("real_data" = SFFU3_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFFU3_4 = as.character(SFFU3_4),
         SFFU3_32 = as.character(SFFU3_32),
         across(where(is.logical), as.character)) %>% 
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFFU3_4,
         SFFU3_5,
         SFFU3_6,
         SFFU3_7,
         SFFU3_8,
         SFFU3_9,
         SFFU3_10,
         SFFU3_11,
         SFFU3_12,
         SFFU3_13,
         SFFU3_14,
         SFFU3_15,
         SFFU3_16,
         SFFU3_17,
         SFFU3_18,
         SFFU3_19,
         SFFU3_20,
         SFFU3_21,
         SFFU3_22,
         SFFU3_23,
         SFFU3_24,
         SFFU3_25,
         SFFU3_26,
         SFFU3_27,
         SFFU3_28,
         SFFU3_29,
         SFFU3_30,
         SFFU3_31 = SSFU3_31,
         SFFU3_32,
         SFFU3_33,
         SFFU3_34) %>% 
  clean_names() %>% 
  glimpse()

session_4 <- session_4 %>% 
  rename("real_data" = SFFU3_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFFU3_4 = as.character(SFFU3_4),
         SFFU3_32 = as.character(SFFU3_32),
         across(where(is.logical), as.character)) %>% 
  select(response_id,
         subid,
         StartDate,
         EndDate,
         Finished,
         SFFU3_4,
         SFFU3_5,
         SFFU3_6,
         SFFU3_7,
         SFFU3_8,
         SFFU3_9,
         SFFU3_10,
         SFFU3_11,
         SFFU3_12,
         SFFU3_13,
         SFFU3_14,
         SFFU3_15,
         SFFU3_16,
         SFFU3_17,
         SFFU3_18,
         SFFU3_19,
         SFFU3_20,
         SFFU3_21,
         SFFU3_22,
         SFFU3_23,
         SFFU3_24,
         SFFU3_25,
         SFFU3_26,
         SFFU3_27,
         SFFU3_28,
         SFFU3_29,
         SFFU3_30,
         SFFU3_31 = SSFU3_31,
         SFFU3_32,
         SFFU3_33,
         SFFU3_34) %>% 
  clean_names() %>% 
  glimpse()
```


### Merge data sets
```{r}
fu_3 <- session_1 %>% 
  full_join(session_2, by = c("response_id", "subid", "start_date", "end_date", 
                              "utc", "finished", "sffu3_4", "sffu3_5", "sffu3_12", 
                              "sffu3_13", "sffu3_14", "sffu3_15", "sffu3_16", "q37", 
                              "sffu3_23", "sffu3_24", "sffu3_25", "sffu3_26", 
                              "sffu3_27", "sffu3_28", "sffu3_29", "sffu3_30", 
                              "sffu3_31", "sffu3_32", "sffu3_33", "sffu3_34")) %>% 
  full_join(session_3, by = c("response_id", "subid", "start_date", "end_date", 
                              "utc", "finished", "sffu3_4", "sffu3_5", "sffu3_12", 
                              "sffu3_13", "sffu3_14", "sffu3_15", "sffu3_16", 
                              "sffu3_23", "sffu3_24", "sffu3_25", "sffu3_26", 
                              "sffu3_27", "sffu3_28", "sffu3_29", "sffu3_30", 
                              "sffu3_31", "sffu3_32", "sffu3_33", "sffu3_34", 
                              "sffu3_6", "sffu3_7", "sffu3_19", "sffu3_20")) %>% 
  full_join(session_4,  by = c("response_id", "subid", "start_date", "end_date", 
                               "finished", "sffu3_4", "sffu3_5", "sffu3_12", 
                               "sffu3_13", "sffu3_14", "sffu3_15", "sffu3_16", 
                               "sffu3_23", "sffu3_24", "sffu3_25", "sffu3_26", 
                               "sffu3_27", "sffu3_28", "sffu3_29", "sffu3_30", 
                               "sffu3_31", "sffu3_32", "sffu3_33", "sffu3_34", 
                               "sffu3_6", "sffu3_7", "sffu3_19", "sffu3_20", 
                               "sffu3_8", "sffu3_9", "sffu3_10", "sffu3_11", 
                               "sffu3_17", "sffu3_18", "sffu3_21", "sffu3_22")) %>% 
  glimpse()

rm(session_1, session_2, session_3)
```


### EDA

The earliest recorded report is from `r min(fu_3$start_date, na.rm = TRUE)` 
and the most recent is from `r max(fu_3$start_date, na.rm = TRUE)`. 

All timezones in UTC
```{r}
fu_3 %>% 
  select(start_date, end_date) %>% 
  map(tz)
```

UTC values that do not fall within range of start_date to end_date
```{r}
options(tibble.print_max = Inf)

fu_3 %>% 
  mutate(utc = as_datetime(utc, tz = "UTC")) %>% 
  select(subid, start_date, end_date, utc) %>% 
  filter(!(utc >= start_date & utc <= end_date))

fu_3 %>% 
  mutate(utc = as_datetime(utc, tz = "UTC")) %>% 
  select(subid, start_date, end_date, utc) %>% 
  filter(date(utc) != date(start_date))
```

UTCs match start date (1 hour ahead for some in months End of March - October). No date inconsistencies.  

#### Duplicate subids

`r length(unique(fu_3$subid))` participants contribute to a total of `r nrow(fu_3)` 
reports.  

Duplicate subids due to no shows    

Note that this 128 is less than the 133 participants that completed the qualtrics followup 3 survey because some were emailed survey link since they were not able to make it in in-person.  

<br>

No shows 
```{r}
fu_3 %>% 
  filter(is.na(sffu3_4)) %>% 
  kbl() %>% 
  kable_classic() %>% 
  scroll_box(width = "100%")
```

#### Missing values

Missing (NA) values
```{r}
fu_3 %>% 
  naniar::miss_var_summary() %>% 
  kbl(digits = 2, table.attr = "style='width:40%;'") %>% 
  kable_classic(position = "l") %>% 
  add_header_above(c("Missing values by variable" = 3), bold = TRUE) %>% 
  scroll_box(height = "500px")
```

All participants are missing values for sffu3_13, sffu3_26, sffu3_28, sffu3_34, sffu3_18, and sffu3_22 - which are all "if no, please explain" questions.   

Missing ssfu3_4 (time arrived) values represent no shows.  

Subid 1 had their own version of followup 3 and no UTC was on the survey as a variable.  
Subids 149 and and 166 also missing UTC variables

Nothing else appears problematic in missing data.      

Reasons for missing data include:  
* participants discontinuing or being withdrawn due to eligibility reasons before completing session  
* questions changed across 3 versions so some were only asked on a single survey version  
* questions were conditional  


#### Descriptives

```{r}
kabyl <- compose(
  partial(kable_classic, position = "left"),
  partial(kbl, digits = 2, table.attr = "style='width:50%;'"),
  partial(tabyl, dat = fu_3)
)
```

Has the participant drank alcohol since you last saw them?
```{r}
kabyl(sffu3_5) %>% 
  add_header_above(c("Has the participant drank alcohol since you last saw them?" = 4),
                   align = "l")
```

Does participant want to complete a BMI/MET session? 
```{r}
kabyl(sffu3_6) %>% 
  add_header_above(c("Does participant want to complete a BMI/MET session?" = 4),
                   align = "l")
```

Did lab staff retrieve phone log and sms content from participant's phone? 
```{r}
kabyl(sffu3_14) %>% 
  add_header_above(c("Did lab staff retrieve phone log and sms content from participant's phone?" = 4),
                   align = "l")
```

If no please explain below
```{r}
fu_3 %>% 
  select(subid, sffu3_15) %>% 
  filter(!is.na(sffu3_15)) %>% 
  kbl() %>% 
  kable_classic() %>% 
  add_header_above(c("If no please explain below" = 2),
                   align = "l")
```

Did participant complete the ID followup 3 Battery?
```{r}
kabyl(sffu3_12) %>% 
  add_header_above(c("Did participant complete the ID followup 3 Battery?" = 4),
                   align = "l")
```

Were all wristband items returned (wristband, charging cradle, and USB cord)?
```{r}
kabyl(sffu3_17) %>% 
  add_header_above(c("Were all wristband items returned (wristband, charging cradle, and USB cord)?" = 4),
                   align = "l")
```

Was the sleep monitor returned? 
```{r}
kabyl(sffu3_19) %>% 
  add_header_above(c("Was the sleep monitor returned?" = 4),
                   align = "l")
```

If no, please explain why. If participant plans to return it, note what the plan is below. 
```{r}
fu_3 %>% 
  select(subid, sffu3_20) %>% 
  filter(!is.na(sffu3_20)) %>% 
  kbl() %>% 
  kable_classic()  %>% 
  add_header_above(c("If no, please explain why. If participant plans to return it, note what the plan is below." = 2),
                   align = "l")
```

Was the tablet and power cord returned?
```{r}
kabyl(sffu3_21) %>% 
  add_header_above(c("Was the tablet and power cord returned?" = 4),
                   align = "l")
```

Was the iPhone battery case returned? 
```{r}
kabyl(sffu3_23) %>% 
  add_header_above(c("Was the iPhone battery case returned?" = 4),
                   align = "l")
```

If no, please explain why. If participant plans to return it, note what the plan is below. 
```{r}
fu_3 %>% 
  select(subid, sffu3_24) %>% 
  filter(!is.na(sffu3_24)) %>% 
  kbl() %>% 
  kable_classic()  %>% 
  add_header_above(c("If no, please explain why. If participant plans to return it, note what the plan is below" = 2),
                   align = "l")
```

Did the participant use a study iPhone?
```{r}
kabyl(q37) %>% 
  add_header_above(c("Did the participant use a study iPhone?" = 4),
                   align = "l")
```

Did participant complete the followup #3 session?
```{r}
kabyl(sffu3_33) %>% 
  add_header_above(c("Did participant complete the followup #3 session?" = 4),
                   align = "l")
```

Did participant complete feedback form? 
```{r}
kabyl(sffu3_25) %>% 
  add_header_above(c("Did participant complete feedback form? " = 4),
                   align = "l")
```

Additional Notes on Followup #3
```{r}
fu_3 %>% 
  select(subid, sffu3_31) %>% 
  filter(!is.na(sffu3_31) & sffu3_31 != "None" & sffu3_31 != "N/a" & sffu3_31 != "N/A" & sffu3_31 != "none" & sffu3_31 != "None." & sffu3_31 != "n/a" & sffu3_31 != "Na" & sffu3_31 != "No") %>% 
  kbl() %>% 
  kable_classic() %>% 
  kable_styling(bootstrap_options = c("striped")) %>% 
  add_header_above(c("Additional Notes on Followup #3" = 2),
                   align = "l") %>% 
scroll_box(height = "500px")
```


### Save

```{r}
write_csv(fu_3, here(path_out, "session_followup_3.csv")) %>% 
  glimpse()
```





