---
title: "Clean and process location data from interviews"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/gps", 
      "/Volumes/private/studydata/risk/knits/gps")
    )
  })
---
### Code status

No cleaning of addresses at this point b/c we only use the GPS coordinates, not addresses
for feature engineering at this point


### Notes

This script opens the individual raw excel files for frequent locations in the 
individual subject folders, merges them, and then does EDA.   Final clean, merged
file is saved in shared folder

### Set up Environment

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Absolute paths
```{r, paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_processed/gps"
          path_shared <- "/Volumes/private/studydata/data_raw"
          path_lab_support <- "/Volumes/toolboxes/lab_support"}
        )
```

Relative Paths 
```{r}
path_log <- "shared/notes"
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}

# for data wrangling
library(tidyverse)  # always need this
library(janitor)
library(purrr)
library(readxl)
library(stringr)

source(here("shared", "fun_risk.R"))  # for merge_excel_files()
```


### Import locations files
Import
```{r}
locations <- merge_excel_files("Locations", path_raw) %>% 
  rename(lon = long) %>% 
  mutate(context_id = row_number()) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  relocate(subid, context_id)
```

### Cleaning

Correct case to lower
```{r}
locations <- locations %>% 
  mutate(type = str_to_lower(type),
         drank = str_to_lower(drank),
         alcohol = str_to_lower(alcohol),
         emotion = str_to_lower(emotion),
         risk = str_to_lower(risk),
         avoid = str_to_lower(avoid),
         vacation = str_to_lower(vacation))
```

Fix errors and mis-spellings

Will also change 

* coffee shop/cafe to cafe
* gym/fitness center to fitness
* aa/recovery meeting to aa
* health care to healthcare
* home of family member to family
* home of friend  to friend
* liquor store to liquorstore 
```{r}
locations <- locations %>% 
  mutate(type = str_replace(type, "coffee shop/cafe", "cafe"),
         type = str_replace(type, "coffe shop/café", "cafe"),
         type = str_replace(type, "coffee shop/café", "cafe"),
         type = str_replace(type, "gym/fitness center", "fitness"),
         type = str_replace(type, "aa/recovery meeting", "aa"),
         type = str_replace(type, "health care", "healthcare"),
         type = str_replace(type, "home of family member", "family"),
         type = str_replace(type, "home of friend", "friend"),
         type = str_replace(type, "liquor store", "liquorstore"))
```

### EDA

General
```{r}
locations %>% glimpse

locations %>% 
  pull(subid) %>% 
  unique() %>% 
  length()

locations %>% 
  tabyl(subid) %>% 
  arrange(n)

locations %>% 
  tabyl(subid) %>% 
  summarize(min(n), max(n))

locations %>% 
  summarize(across(.fns = ~sum(is.na(.)))) %>% 
  glimpse()
```

Main context
```{r}
locations %>% tabyl(type)

locations %>% 
  filter(is.na(type)) %>% 
  print

locations %>% tabyl(drank)
locations %>% tabyl(alcohol)
locations %>% tabyl(emotion)
locations %>% tabyl(risk)
locations %>% tabyl(avoid)
locations %>% tabyl(vacation)
```


### Save final locations file

```{r}
locations %>% 
  write_csv(here(path_shared, "locations.csv"))
```
