---
title: "Clean and process the raw qualtrics follow-up 3"
author: "John Curtin and Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
  toc: true 
toc_depth: 4
editor_options: 
  chunk_output_type: console
---
  
### Notes
Purpose: This file does cleaning and basic processing of the qualtrics follow-up 12 survey.

Inputs:  

Opens data file in path_in  

* followup_3.csv

Opens log file in path_log  

* log_followup_3.csv



Output:  

Creates file in path_out  

* followup_3.csv


### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hold",  message = FALSE)
```


```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```


Paths 
```{r}
path_in <- "raw_data/qualtrics"
path_out <- "analysis/shared/data"
path_log <- "analysis/shared/notes" 
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(kableExtra)
library(psych)


source('/Volumes/private/toolboxes/lab_support/clean_qualtrics_by_log.R')
```

### Followup 3

#### Clean it
Load surveys, join, and remove unused variables

Rename subid and response_id to tidy case because these variables are used by name in clean_qualtrics_by_log()
```{r}
main3 <- read_csv(file.path(path_in, 'followup_3.csv'), col_types = cols())  
burden_sleep <- read_csv(file.path(path_in, 'followup_3_beddit_burden.csv'), col_types = cols())  %>% 
  select(ResponseID, RBM_5, RBM_6, RBM_7, RBM_8) 
burden_empatica <- read_csv(file.path(path_in, 'followup_3_empatica_burden.csv'), col_types = cols()) %>% 
  select(ResponseID, RBM_1, RBM_2, RBM_3, RBM_4) 

fu3 <- left_join(main3,burden_empatica, by = "ResponseID") %>% 
  left_join(burden_sleep, by = "ResponseID") %>% 
  select(-c(ResponseSet, IPAddress, RecipientLastName, RecipientFirstName,
            RecipientEmail, ExternalDataReference, Status, 
            LocationLatitude, LocationLongitude, LocationAccuracy,
            DataType, StudyName, RBM_Inst)) %>% 
  rename(subid = SubID, response_id = ResponseID)  %>%  #update to tidy case for use in clean_qualtrics_by_log()
  relocate(subid) %>% 
  relocate(any_of(str_c("RBM_", 1:8)), .before = "RBM_9")
```

Open and summarize log
```{r}
log_fu3 <- read_csv(file.path(path_log, "log_followup_3.csv"), col_types = cols()) %>% 
  rowid_to_column("index") %>%
  glimpse()
```

```{r}
tabyl(log_fu3$log_action)
```

remove log entries:  
No entries removed  

recode_one log entries:
```{r}
log_fu3 %>% 
  filter(log_action == "recode_one") %>% 
  tabyl(var_name)
```

Changes to subid variable
```{r}
log_fu3 %>% 
  filter(var_name == "subid") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

Changes to UTC variable
```{r}
log_fu3 %>% 
  filter(var_name == "UTC") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

Changes to start or end date variable
```{r}
log_fu3 %>% 
  filter(var_name == "StartDate" | var_name == "EndDate") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

note log entries:  
```{r}
log_fu3 %>% 
  filter(log_action == "note") %>% 
  kbl %>% 
  kable_classic()
```

Clean raw data using log
```{r}
fu3 <- fu3 %>% 
  # temporarily change start and end date to character string for cleaning function to work
  mutate(StartDate = as.character(StartDate),
         EndDate = as.character(EndDate)) %>% 
  clean_qualtrics_by_log(., log_fu3) %>% 
  # change start and end date back to date time
   mutate(StartDate = as_datetime(StartDate),
         EndDate = as_datetime(EndDate)) 
```

Tidy variable names
```{r}
fu3 <- clean_names(fu3, "snake") 
```

Tidy response options 
Some text response options became slightly distorted, fixing for consistency
```{r}
fu3 <- fu3 %>% 
  mutate(across(where(is.character), str_replace_all, pattern = "\\\\", replacement = " "))
```



#### EDA and Save

```{r}
fu3 %>% 
  glimpse()
```

`r length(unique(fu3$subid))` participants contribute to a total of `r nrow(fu3)` reports.  

- 133 is the expected number of participants who completed followup 3.  

<br>

##### Dates and Times

The earliest recorded report is from `r min(fu3$start_date, na.rm = TRUE)` and the most recent is from `r max(fu3$start_date, na.rm = TRUE)`.  

All timezones in UTC
```{r}
fu3 %>% 
  select(start_date, end_date) %>% 
  map(tz)
```

**Time difference in start_date and utc**
```{r}
options(tibble.print_max = Inf)
fu3 %>% 
  select(subid, start_date, end_date, utc) %>% 
  mutate(utc = lubridate::as_datetime(utc, tz = "utc")) %>% 
  mutate(diff = round(difftime(utc, start_date, units = "mins")), 0) %>% 
  tabyl(diff)
```

- Can see clusters around start time and one hour after start time (*this is expected due to daylight savings issues surrounding British Summer Time*).  
- Check on Qualtrics shows UTC gets piped in immediately after header block (subid, RA, real_data, etc.)  

No notes for subid with over two hour start and UTC difference  
```{r}
notes <- read_csv("./raw_data/raw_notes.csv", col_types = cols()) %>% 
  select(subid, notes_general)
sub_2hr <- fu3 %>% 
  select(subid, start_date, end_date, utc) %>% 
  mutate(utc = lubridate::as_datetime(utc, tz = "utc")) %>% 
  mutate(diff = round(difftime(utc, start_date, units = "mins")), 0) %>% 
  filter(diff > 120)
notes %>% 
  filter(subid %in% sub_2hr$subid) %>% 
  kbl() %>% 
  kable_styling()
```


**Time difference in start and end date**  
```{r}
fu3_diff <- fu3 %>% 
  mutate(diff = round(difftime(end_date, start_date, units = "mins")),
         diff_mins = as.numeric(str_replace(diff, " mins", "")))

freq <- hist(fu3_diff$diff_mins, breaks = c(seq(0, 220, 10)), include.lowest=TRUE, plot=FALSE)
tibble(mins = freq$breaks[-1], frequency = freq$counts)
```

Take a closer look at subid that that has 220 min time difference between start and end time - no notes explaining why  
```{r}
fu3 %>% 
  mutate(diff = round(difftime(end_date, start_date, units = "mins")),
         diff_mins = as.numeric(str_replace(diff, " mins", ""))) %>% 
  filter(diff_mins >= 220) %>% 
  kbl %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

notes %>% 
  filter(subid == 117) %>% 
  kbl() %>% 
  kable_styling()
```



<br>

##### Missing values

```{r}
fu3 %>% 
  naniar::miss_var_summary() %>% 
  kbl(table.attr = "style='width:40%;'") %>% 
  kable_classic(position = "l") %>% 
  add_header_above(c("Missing values by variable" = 3), bold = TRUE) %>% 
  scroll_box(height = "500px")
```

Missing values all seem to be appropriate:  
rbm_1 through rbm_8 represent wristband and sleep monitor  
rbm_24 and rbm_31 are both free-text responses  

##### Finished

```{r}
fu3 %>% 
  tabyl(finished)
```

All followup 3 surveys are complete and marked as finished.  


##### RA

```{r}
fu3 %>% 
  tabyl(ra) %>% 
  kbl() %>% 
  kable_classic()
```

##### Burden Survey (rbm)
```{r}
fu3 %>% 
  select(contains("rbm")) %>% 
  select(-c(rbm_4, rbm_8, rbm_13, rbm_17, rbm_21, rbm_24, rbm_31)) %>% 
  map(., table)
```


Save final clean data.  Variables will open with proper class on next load of data
```{r}
fu3 %>% 
  select(-utc) %>% 
  glimpse() %>% 
  write_csv(file.path(path_out, "followup_3.csv")) 
```