---
title: "Clean and process the raw qualtrics intake"
author: "John Curtin and Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Status

These data are fully cleaned. EDA on all variables.    


### Conclusions

* If your study is using start or end times you will want to explore these variables further. EDA in script is extensive and all dates are accurate, but for hour or minute precision, more exploration on time component will be needed (e.g., see bullet below).     
* 4 subids have start and end time less than 10 minutes apart - likely due to staff re-entering Qualtrics survey.   
* UTC unix time stamp is actually in British Summer Time which has daylight savings.   


### Notes
Purpose: This file does cleaning and basic processing of the qualtrics intake survey.

Inputs:  

Opens data file in path_in  

* intake.csv

Opens log file in path_log  

* log_intake.csv

Opens supporting files in path_raw

* raw_notes.csv


Output:  

Creates file in path_out  

* intake.csv


### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
```

Absolute Paths 
```{r absolute_paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_in <- "P:/studydata/risk/data_raw/qualtrics"
          path_out <- "P:/studydata/risk/data_processed/shared"
          path_raw <- "P:/studydata/risk/data_raw"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_in <- "/Volumes/private/studydata/risk/data_raw/qualtrics"
          path_out <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"}
        )
```

Relative paths
```{r}
path_log <- "shared/notes"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(kableExtra)
library(psych)

source(here(path_lab_support, "clean_qualtrics_by_log.R"))
```
   
### Intake survey

#### Load data and glimpse
Load survey and remove unused variables

Rename subid and response_id to tidy case because these variables are used by name in clean_qualtrics_by_log()
```{r}
intake <- read_csv(here(path_in, 'intake.csv'), col_types = cols())  %>% 
  select(-c(ResponseSet, IPAddress, RecipientLastName, RecipientFirstName,
            RecipientEmail, ExternalDataReference, Status,
            LocationLatitude, LocationLongitude, LocationAccuracy, DataType,
            StudyName, PACS_Inst, AASE_Inst, MAM_Inst, DASS21_Inst,
            PSS_Inst, QOL_Inst, DAS_Inst, MSPSS_Inst)) %>% 
  rename(subid = SubID, response_id = ResponseID)  %>%  #update to tidy case for use in clean_qualtrics_by_log()
  relocate(subid)
```

Open and summarize data log
```{r}
log_intake <- read_csv(here(path_log, "log_intake.csv"), col_types = cols()) %>% 
  rowid_to_column("index") %>% 
  glimpse()
```

```{r}
tabyl(log_intake$log_action)
```

remove log entries:
```{r}
log_intake %>% 
  filter(log_action == "remove") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_styling()
```

recode_one log entries:
```{r}
log_intake %>% 
  filter(log_action == "recode_one") %>% 
  tabyl(var_name)
```

Changes to UTC variable  
Appears both UTC entries are replacing missing values
```{r}
log_intake %>% 
  filter(var_name == "UTC") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_styling()
```

*No changes to subids, start_date or end_date*   
All other recode_one entries look good. Most entries are due to adding new questions and getting participant responses at next visit.  

note log entries:  
no note log entries  

Clean raw data using log
```{r}
intake <- clean_qualtrics_by_log(intake, log_intake)
```

Tidy variable names
```{r}
intake <- clean_names(intake, "snake") 
```

Tidy response options 
Some text response options became slightly distorted, fixing for consistency
```{r}
intake <- intake %>% 
  mutate(across(where(is.character), str_replace_all, pattern = "&mdash;", replacement = " - "),
         across(where(is.character), str_replace_all, pattern = '<span style=;white-space:nowrap;">', replacement = ""),
         across(where(is.character), str_replace_all, pattern = "’", replacement = "'"))
```



#### EDA and Save

```{r}
kabyl <- compose(
  partial(kable_classic, position = "left"),
  partial(kbl, digits = 2, table.attr = "style='width:50%;'"),
  partial(tabyl, dat = intake)
)
```

```{r}
intake %>% 
  glimpse()
```

`r length(unique(intake$subid))` participants contribute to a total of `r nrow(intake)` reports.  

- This matches the number of intake session forms (170)  


##### Dates and Times

The earliest recorded report is from `r min(intake$start_date, na.rm = TRUE)` and the most recent is from `r max(intake$start_date, na.rm = TRUE)`.   

All timezones in UTC
```{r}
intake %>% 
  select(start_date, end_date) %>% 
  map(tz)
```

**Time difference in start_date and utc**
```{r}
options(tibble.print_max = Inf)
intake %>% 
  select(subid, start_date, end_date, utc) %>% 
  mutate(utc = lubridate::as_datetime(utc, tz = "utc")) %>% 
  mutate(diff = round(difftime(utc, start_date, units = "mins")), 0) %>% 
  tabyl(diff)
```

- Can see clusters around start time and one hour after start time (*this is expected due to daylight savings issues surrounding British Summer Time*).  
- Check on Qualtrics shows UTC gets piped in immediately after header block (subid, RA, real_data, etc.)
- 3 subids have difference times of over 2 hour difference between start time and utc.  

no helpful info from notes on subids with a 2 hour difference    
```{r}
notes <- read_csv(here(path_log, "raw_notes.csv"), col_types = cols()) %>% 
  select(subid, notes_general)

subs_2hrs <- intake %>% 
  select(subid, start_date, end_date, utc) %>% 
  mutate(utc = lubridate::as_datetime(utc, tz = "utc")) %>% 
  mutate(diff = difftime(utc, start_date, units = "mins")) %>% 
  filter(diff > 120)

notes %>% 
  filter(subid %in% subs_2hrs$subid) %>% 
  kbl() %>% 
  kable_styling()
```



**Time difference in start and end date**  
```{r}
intake_diff <- intake %>% 
  mutate(diff = round(difftime(end_date, start_date, units = "mins")),
         diff_mins = as.numeric(str_replace(diff, " mins", "")))

freq <- hist(intake_diff$diff_mins, breaks = c(seq(0, 180, 10)), include.lowest=TRUE, plot=FALSE)
tibble(mins = freq$breaks[-1], frequency = freq$counts)
```

3 subids have almost 3 hour difference in start and end time.   


Start and end dates less than 10 minutes apart   
4 subids have start and end time less than 10 minutes apart 
```{r}
subs_10min <- intake %>% 
  select(subid, start_date, end_date, utc) %>% 
  mutate(utc = lubridate::as_datetime(utc, tz = "utc")) %>% 
  mutate(diff = difftime(end_date, start_date, units = "mins")) %>% 
  filter(diff < 10)
notes %>% 
  filter(subid %in% subs_10min$subid) %>% 
  kbl() %>% 
  kable_styling()
```



##### Missing values

```{r}
intake %>% 
  naniar::miss_var_summary() %>% 
  kbl(table.attr = "style='width:40%;'") %>% 
  kable_classic(position = "l") %>% 
  add_header_above(c("Missing values by variable" = 3), bold = TRUE) %>% 
  scroll_box(height = "500px")
```

Missing values all seem to be appropriate:  
missing das values are because it was only given to individuals in a relationship  
missing mam values are also conditional  


##### Finished

```{r}
kabyl(finished)
```
All intakes are complete and marked as Finished  

##### RA

```{r}
kabyl(ra)
```

##### PACS
```{r}
intake %>% 
  select(contains("pacs")) %>% 
  map(., table)
```

##### AASE
```{r}
intake %>% 
  select(contains("aase")) %>% 
  map(., table)
```

##### MAM
living arrangement
```{r}
kabyl(mam_1)
kabyl(mam_1_1)
```

live alone
```{r}
kabyl(mam_1_2)
```

Who do you live with
```{r}
kabyl(mam_1_3_1)
kabyl(mam_1_3_2)
kabyl(mam_1_3_3)
kabyl(mam_1_3_4)
kabyl(mam_1_3_5)
```

How many children in household?
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_1_4), na.rm = TRUE),
            max = max(as.numeric(mam_1_4), na.rm = TRUE),
            mean = mean(as.numeric(mam_1_4), na.rm = TRUE))
```

How many parents?
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_1_5), na.rm = TRUE),
            max = max(as.numeric(mam_1_5), na.rm = TRUE),
            mean = mean(as.numeric(mam_1_5), na.rm = TRUE))
```

How many relatives?
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_1_6), na.rm = TRUE),
            max = max(as.numeric(mam_1_6), na.rm = TRUE),
            mean = mean(as.numeric(mam_1_6), na.rm = TRUE))
```

How many non-relatives?
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_1_7), na.rm = TRUE),
            max = max(as.numeric(mam_1_7), na.rm = TRUE),
            mean = mean(as.numeric(mam_1_7), na.rm = TRUE))
```

Yes/no questions about past 30 days
```{r}
intake %>% 
  select(c(mam_2:mam_7, mam_11, mam_17, mam_19)) %>% 
  map(., table)
```

individual counseling sessions past 30 days
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_8), na.rm = TRUE),
            max = max(as.numeric(mam_8), na.rm = TRUE),
            mean = mean(as.numeric(mam_8), na.rm = TRUE))
```

group counseling sessions
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_9), na.rm = TRUE),
            max = max(as.numeric(mam_9), na.rm = TRUE),
            mean = mean(as.numeric(mam_9), na.rm = TRUE))
```

self-help meetings
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_10), na.rm = TRUE),
            max = max(as.numeric(mam_10), na.rm = TRUE),
            mean = mean(as.numeric(mam_10), na.rm = TRUE))
```

other counseling
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_12), na.rm = TRUE),
            max = max(as.numeric(mam_12), na.rm = TRUE),
            mean = mean(as.numeric(mam_12), na.rm = TRUE))
```

days with supportive friends/family
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_13), na.rm = TRUE),
            max = max(as.numeric(mam_13), na.rm = TRUE),
            mean = mean(as.numeric(mam_13), na.rm = TRUE))
```

days with unsupportive friends/family
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_14), na.rm = TRUE),
            max = max(as.numeric(mam_14), na.rm = TRUE),
            mean = mean(as.numeric(mam_14), na.rm = TRUE))
```

days at work, school, volunteering
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_15), na.rm = TRUE),
            max = max(as.numeric(mam_15), na.rm = TRUE),
            mean = mean(as.numeric(mam_15), na.rm = TRUE))
```

Has your religion or spirituality helped support your recovery within the past 30 days
```{r}
kabyl(mam_16)
```

Days taken alcohol medication as prescribed
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_18), na.rm = TRUE),
            max = max(as.numeric(mam_18), na.rm = TRUE),
            mean = mean(as.numeric(mam_18), na.rm = TRUE))
```

Days taken other medication as prescribed
```{r}
intake %>% 
  summarise(min = min(as.numeric(mam_20), na.rm = TRUE),
            max = max(as.numeric(mam_20), na.rm = TRUE),
            mean = mean(as.numeric(mam_20), na.rm = TRUE))
```

How satisfied are you with your progress toward achieving your recovery goals in the past 30 days?
```{r}
kabyl(mam_21)
```

Is your goal still to remain abstinent in the future?
```{r}
kabyl(mam_22)
```

In the next 30 days, how confident are you in your ability to be completely abstinent from alcohol?
```{r}
kabyl(mam_23)
```

##### DASS
```{r}
intake %>% 
  select(contains("dass")) %>% 
  map(., table)
```

##### PSS
```{r}
intake %>% 
  select(contains("pss")) %>% 
  map(., table)
```

##### QOL
```{r}
intake %>% 
  select(contains("qol")) %>% 
  map(., table)
```

##### DAS
```{r}
intake %>% 
  select(das_0:das_32) %>% 
  map(., table)
```

##### MSPSS
```{r}
intake %>% 
  select(contains("mspss")) %>% 
  map(., table)
```


Save final clean data.  Variables will open with proper class on next load of data
```{r}
intake %>% 
  select(-utc) %>% 
  glimpse() %>% 
  write_csv(here(path_out, "intake.csv")) 
```