---
title: "Session Intake Clean File"
author: "Kendra Wyant with updates by John"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Status

These data are fully cleaned and checked with EDA.        

**Reminder that session forms are considered notes not data.**      
**For this reason times on start and end dates may not have accurate precision.**   

### Notes
This script creates a single csv file from the three raw data session intake files. Uses cleaning function to clean according to data log. Includes file merging and minimal variable renaming.    

Inputs:   

* session_intake_v1.csv  
* session_intake_v2.csv  
* session_intake_v3.csv  
* log_session_intake_v1.csv  
* log_session_intake_v2.csv  
* log_session_intake_v3.csv  


Output:  

* session_intake.csv   

### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
```

Absolute Paths 
```{r absolute_paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_in <- "P:/studydata/risk/data_raw/qualtrics"
          path_out <- "P:/studydata/risk/data_processed/shared"
          path_raw <- "P:/studydata/risk/data_raw"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_in <- "/Volumes/private/studydata/risk/data_raw/qualtrics"
          path_out <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"}
        )
```

Relative paths
```{r}
path_log <- "shared/notes"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Packages
```{r message = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(kableExtra)

source(here(path_lab_support, "clean_qualtrics_by_log.R"))
```


### Read in session intake csvs

```{r}
session_1 <- read_csv(here(path_in, "session_intake_v1.csv"), col_types = cols()) %>% 
  rename(subid = SFIR_3, response_id = ResponseID) %>% 
  glimpse()
session_2 <- read_csv(here(path_in, "session_intake_v2.csv"), col_types = cols()) %>% 
  rename(subid = SFIR_3, response_id = ResponseID) %>% 
  glimpse()
session_3 <- read_csv(here(path_in, "session_intake_v3.csv"), col_types = cols()) %>% 
  rename(subid = SFIR_3, response_id = ResponseID) %>% 
  glimpse()
```


### Clean session forms from logs

open data logs

```{r}
log_1 <- read_csv(here(path_log, "log_session_intake_v1.csv"), col_types = cols())  %>% 
  rowid_to_column("index") %>% 
  glimpse()

log_2 <- read_csv(here(path_log, "log_session_intake_v2.csv"), col_types = cols()) %>% 
  rowid_to_column("index") %>% 
  glimpse()

log_3 <- read_csv(here(path_log, "log_session_intake_v3.csv"), col_types = cols()) %>% 
  rowid_to_column("index") %>% 
  glimpse()
```

Review logs

```{r}
tabyl(log_1$log_action) 
tabyl(log_2$log_action) 
tabyl(log_3$log_action) 
```

Entries removed
```{r}
log_1 %>% 
  filter(log_action == "remove") %>% 
  select(-index) %>% 
  kbl %>% 
  kable_classic()
```

#### Clean session data

```{r}
session_1 <- clean_qualtrics_by_log(session_1, log_1)
session_2 <- clean_qualtrics_by_log(session_2, log_2)
session_3 <- clean_qualtrics_by_log(session_3, log_3)
```


### Rename variables

#### Rename variables tidy and filter out incomplete/fake data

```{r}
session_1 <- session_1 %>% 
  rename("real_data" = SFIR_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFIR_4 = as.character(Q129_TEXT), 
         SFIR_55 = as.character(SFIR_55),
         SFIR_21 = as.character(SFIR_21),
         SFIR_17 = as.character(SFIR_17),
         Q185 = as.character(Q185)) %>%
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFIR_4,
         SFIR_5.1_1,
         SFIR_5.2_1,
         SFIR_5.3_1,
         SFIR_6,
         Q197,
         Q122,
         Q131,
         SFIR_9 = Q118,
         SFIR_10,
         SFIR_11,
         SFIR_14,
         Q183,
         Q185,
         SFIR_16,
         SFIR_17,
         SFIR_20,
         SFIR_21,
         Q112,
         Q113,
         Q115,
         SFIR_46 = Q114,
         Q141,
         Q198,
         SFIR_32,
         SFIR_33,
         SFIR_34,
         SFIR_35,
         SFIR_36,
         SFIR_32_android = Q157,
         SFIR_33_android = Q159,
         SFIR_34_android = Q161,
         SFIR_35_android = Q163,
         SFIR_36_android = Q165,
         SFIR_37,
         SFIR_38,
         SFIR_39,
         SFIR_40,
         SFIR_41,
         SFIR_42,
         SFIR_47,
         SFIR_48,
         SFIR_49,
         SFIR_50,
         SFIR_51,
         SFIR_52,
         SFIR_55,
         SFIR_56,
         SFIR_57,
         SFIR_58) %>% 
  clean_names() %>% 
  glimpse()

session_2 <- session_2 %>%
  rename("real_data" = SFIR_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFIR_4 = as.character(SFIR_4), 
         SFIR_55 = as.character(SFIR_55),
         SFIR_21 = as.character(SFIR_21),
         SFIR_17 = as.character(SFIR_17),
         SFIR_14 = as.character(SFIR_14)) %>%
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFIR_4,
         SFIR_5.1_1,
         SFIR_5.2_1,
         SFIR_5.3_1,
         SFIR_6,
         SFIR_7,
         SFIR_8,
         SFIR_9,
         SFIR_10,
         SFIR_11,
         SFIR_14,
         SFIR_16,
         SFIR_17,
         SFIR_20,
         SFIR_21,
         Q112,
         Q113,
         Q115,
         SFIR_46 = Q114,
         SFIR_28,
         SFIR_29,
         SFIR_30,
         SFIR_31,
         SFIR_32,
         SFIR_33,
         SFIR_34,
         SFIR_35,
         SFIR_36,
         SFIR_37,
         SFIR_38,
         SFIR_39,
         SFIR_40,
         SFIR_41,
         SFIR_42,
         SFIR_47,
         SFIR_48,
         SFIR_49,
         SFIR_50,
         SFIR_51,
         SFIR_52,
         SFIR_55,
         SFIR_56,
         SFIR_57,
         SFIR_58) %>% 
  clean_names() %>% 
  glimpse()

session_3 <- session_3 %>%
  rename("real_data" = SFIR_1) %>% 
  filter(real_data == "Real data") %>% 
  mutate(SFIR_4 = as.character(SFIR_4), 
         SFIR_55 = as.character(SFIR_55),
         SFIR_21 = as.character(SFIR_21),
         SFIR_17 = as.character(SFIR_17),
         SFIR_14 = as.character(SFIR_14),
         SFIR_8 = as.character(SFIR_8)) %>%
  select(response_id,
         subid,
         StartDate,
         EndDate,
         UTC,
         Finished,
         SFIR_4,
         SFIR_5.1_1,
         SFIR_5.2_1,
         SFIR_5.3_1,
         SFIR_6,
         SFIR_7,
         SFIR_8,
         SFIR_9,
         SFIR_10,
         SFIR_11,
         SFIR_14,
         SFIR_16,
         SFIR_17,
         SFIR_18,
         SFIR_19,
         SFIR_20,
         SFIR_21,
         SFIR_43,
         SFIR_44,
         SFIR_45,
         SFIR_46,
         SFIR_22,
         SFIR_23,
         SFIR_24,
         SFIR_25,
         SFIR_26,
         SFIR_27,
         SFIR_28,
         SFIR_29,
         SFIR_30,
         SFIR_31,
         SFIR_32,
         SFIR_33,
         SFIR_34,
         SFIR_35,
         SFIR_36,
         SFIR_37,
         SFIR_38,
         SFIR_39,
         SFIR_40,
         SFIR_41,
         SFIR_42,
         SFIR_47,
         SFIR_48,
         SFIR_49,
         SFIR_50,
         SFIR_51,
         SFIR_52,
         SFIR_55,
         SFIR_56,
         SFIR_57,
         SFIR_58) %>% 
  clean_names() %>% 
  glimpse()
```


### Recoding and merging


remove repetitive/unnecessary columns for merge

```{r}
session_1 <- session_1 %>% 
  mutate(sfir_47 = coalesce(sfir_47, q183),
         sfir_48 = coalesce(sfir_48, q185),
         sfir_58 = coalesce(sfir_58, sfir_14),
         sfir_32 = coalesce(sfir_32, sfir_32_android),
         sfir_33 = coalesce(sfir_33, sfir_33_android),
         sfir_34 = coalesce(sfir_34, sfir_34_android),
         sfir_35 = coalesce(sfir_35, sfir_35_android),
         sfir_36 = coalesce(sfir_36, sfir_36_android)) %>% 
  select(-c(q183, q185, sfir_14, q122, sfir_32_android, sfir_33_android, sfir_34_android,
            sfir_35_android, sfir_36_android))

session_2 <- session_2 %>% 
  mutate(sfir_58 = coalesce(sfir_58, sfir_14))

session_3 <- session_3 %>% 
  mutate(sfir_58 = coalesce(sfir_58, sfir_14))
```


```{r}
intake_session <- session_1 %>% 
  full_join(session_2,  by = c("response_id", "subid", "start_date", "end_date", 
                               "utc", "finished", "sfir_4", "sfir_5_1_1", "sfir_5_2_1", 
                               "sfir_5_3_1", "sfir_6", "sfir_9", "sfir_10", "sfir_11", 
                               "sfir_16", "sfir_17", "sfir_20", "sfir_21", "q112", 
                               "q113", "q115", "sfir_46", "sfir_32", "sfir_33", 
                               "sfir_34", "sfir_35", "sfir_36", "sfir_37", "sfir_38", 
                               "sfir_39", "sfir_40", "sfir_41", "sfir_42", "sfir_47", 
                               "sfir_48", "sfir_49", "sfir_50", "sfir_51", "sfir_52", 
                               "sfir_55", "sfir_56", "sfir_57", "sfir_58")) %>% 
  full_join(session_3, by = c("response_id", "subid", "start_date", "end_date", 
                              "utc", "finished", "sfir_4", "sfir_5_1_1", "sfir_5_2_1", 
                              "sfir_5_3_1", "sfir_6", "sfir_9", "sfir_10", "sfir_11", 
                              "sfir_16", "sfir_17", "sfir_20", "sfir_21", "sfir_46", 
                              "sfir_32", "sfir_33", "sfir_34", "sfir_35", "sfir_36", 
                              "sfir_37", "sfir_38", "sfir_39", "sfir_40", "sfir_41", 
                              "sfir_42", "sfir_47", "sfir_48", "sfir_49", "sfir_50", 
                              "sfir_51", "sfir_52", "sfir_55", "sfir_56", "sfir_57", 
                              "sfir_58", "sfir_7", "sfir_8", "sfir_14", "sfir_28", 
                              "sfir_29", "sfir_30", "sfir_31")) %>% 
  glimpse()

rm(session_1, session_2, session_3)
```

### Tidy response options
Some responses vary slightly across survey versions. Correcting for consistency.  
```{r}
intake_session <- intake_session %>% 
  mutate(sfir_6 = case_when(sfir_6 == "No" ~ "No (or more than 7 days since last drink of alcohol)",
                            sfir_6 == "Yes" ~ "Yes (or less than 7 days since last drink of alcohol)",
                            TRUE ~ sfir_6),
         sfir_9 = case_when(sfir_9 == "Over 8 Weeks" ~ "Over 8 Weeks-Consult with Candace/Susan/John before continuing",
                            TRUE ~ sfir_9))
```



### EDA and Save

The earliest recorded report is from `r min(intake_session$start_date, na.rm = TRUE)` 
and the most recent is from `r max(intake_session$start_date, na.rm = TRUE)`. 

All timezones in UTC
```{r}
intake_session %>% 
  select(start_date, end_date) %>% 
  map(tz)
```

UTC values that do not fall within range of start_date to end_date
```{r}
options(tibble.print_max = Inf)

intake_session %>% 
  mutate(utc = as_datetime(utc, tz = "UTC")) %>% 
  select(subid, start_date, end_date, utc) %>% 
  filter(!(utc >= start_date & utc <= end_date))

intake_session %>% 
  mutate(utc = as_datetime(utc, tz = "UTC")) %>% 
  select(subid, start_date, end_date, utc) %>% 
  filter(date(utc) != date(start_date))
```

All UTCs match Qualtrics date/times.  

#### Duplicate subids

`r length(unique(intake_session$subid))` participants contribute to a total of `r nrow(intake_session)` 
reports.  

Duplicate subids due to no shows and having to return to finish intake   

177 unique subids - 4 never showed up (45, 46, 124, 254), 1 has two intakes under different subids (55 and 61).  
172 participants showed up to intake, 2 were ineligible due to not being one week sober, **170 enrolled in study**.  


#### Missing values

Missing (NA) values
```{r}
intake_session %>% 
  naniar::miss_var_summary() %>% 
  kbl(digits = 2, table.attr = "style='width:40%;'") %>% 
  kable_classic(position = "l") %>% 
  add_header_above(c("Missing values by variable" = 3), bold = TRUE) %>% 
  scroll_box(height = "500px")
```

sfir_4 is the arrival time of the participant - 5 no shows documented (subid 46 has 2 no shows).  
```{r}
intake_session %>% 
  filter(is.na(sfir_4)) %>% 
  kbl() %>% 
  kable_classic() %>% 
  scroll_box(width = "100%")
```

Missing UTC for subid 1  
```{r}
intake_session %>% 
  filter(is.na(utc)) 
```


Nothing else appears problematic in missing data.    

Reasons for missing data include:  
* participants discontinuing or being withdrawn due to eligibility reasons before completing session  (subid 260 and 262 withdrawn prior to sfir_9)
* questions changed across 3 versions so some were only asked on a single survey version  
* questions were conditional (e.g., sfir_57 = "If session was incomplete, explain why")  


#### Descriptives

```{r}
kabyl <- compose(
  partial(kable_classic, position = "left"),
  partial(kbl, digits = 2, table.attr = "style='width:50%;'"),
  partial(tabyl, dat = intake_session)
)
```


Has the participant drank alcohol since you last saw them?
```{r}
kabyl(sfir_6) %>% 
  add_header_above(c("Has the participant drank alcohol since you last saw them?" = 4),
                   align = "l")
```

Note: For survey version 2 and 3 it was not assumed that if participant drank since screen visit that it was automatically less than 7 days since last drink. Only the two subids labeled as Yes (or less than 7 days...) were not able to continue according to next survey item (q197).  

Is the participant able to continue the session?
```{r}
kabyl(q197) %>% 
  add_header_above(c("Is the participant able to continue the session?" = 4),
                   align = "l")
```

Will participant continue with study today? (after description of intake process)
```{r}
kabyl(q131) %>% 
  add_header_above(c("Will participant continue with study today?" = 4),
                   align = "l")
```

Does participant want to complete MET session? 
```{r}
kabyl(sfir_7) %>% 
  add_header_above(c("Does participant want to complete MET session? " = 4),
                   align = "l")
```

How many weeks has the participant gone without alcohol?
```{r}
kabyl(sfir_9) %>% 
  add_header_above(c("How many weeks has the participant gone without alcohol?" = 4),
                   align = "l")
```

Did participant complete recovery environment interview? 
```{r}
kabyl(sfir_16) %>% 
  add_header_above(c("Did participant complete recovery environment interview?" = 4),
                   align = "l")
```

Did participant complete the Intake Battery?
```{r}
kabyl(sfir_20) %>% 
  add_header_above(c("Did participant complete the Intake Battery?" = 4),
                   align = "l")
```

Is participant using their own phone?
```{r}
kabyl(q112) %>% 
  add_header_above(c("Is participant using their own phone?" = 4),
                   align = "l")
```

Is the Participant using an iPhone or an Android?
```{r}
kabyl(q141) %>% 
  add_header_above(c("Is the Participant using an iPhone or an Android?" = 4),
                   align = "l")
```

Did participant complete the intake session?
```{r}
kabyl(sfir_56) %>% 
  add_header_above(c("Did participant complete the intake session?" = 4),
                   align = "l")
```


#### Save

write csv
```{r}
write_csv(intake_session, here(path_out, "session_intake.csv")) %>% 
  glimpse()
```




