---
title: "Andriod/SMS Logs"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 2
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Notes
Purpose: This script contains code to open and merge all SMS log files in xml format from participants raw data folders. This is a study-level clean script so cleaning is minimal. Errors that don't have an obvious solution are highlighted in this clean script but are not corrected for. These will need to be corrected during pre-processing at the study-level.     

**Note: File not ready for analysis on text content. Emojis are accidently stripped in the aggregated csv file (may result in blank messages), still working on how to extract them from the xml files and will update.**    


Inputs:   
[subid]_SMS_1.xml  
[subid]_SMS_2.xml   
[subid]_SMS_3.xml  
etc. for as many sms xml logs in the subid's folder  


### Setup
```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"},
        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"})
```


Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(janitor)
library(kableExtra)
library(lubridate)
library(XML)
library(xml2)
```

Relative Paths
```{r}
library(here)

path_log <- "shared/notes"
```

### Android SMS Logs (XML) 

#### Create function to read in subid logs

```{r}
read_xml <- function(subid) {
    logs <- tibble(subid = character(),
                   message = character())
    filepaths <- list.files(file.path(path_raw, subid), pattern = "SMS", include.dirs = FALSE, full.names = TRUE)
    # subids 1-15 have a RawSMSVoice folder in addition to XML logs - not including this folder 
    filepaths <- discard(filepaths, filepaths == file.path(path_raw, subid, "RawSMSVoice"))
    if(length(filepaths) > 0) {
      for(file in filepaths) {
        if(str_detect(file,'.xml')) {
          
          # xml code adapted from Susan's fun_database script
          # use read_html instead of read_xml to avoid problem with emojis in contacts
          xml <- xml_children(read_html(file.path(file)))
 
          # fix for problem with nested list after switching to read_html()
          while (length(xml) == 1) {
            xml <- xml_children(xml) #loop to find lower level of xml children 
          }    

          log <- data.frame(
           protocol = xml_attr(xml,'protocol'),
           address = xml_attr(xml,'address'),
           date = xml_attr(xml,'date'),
           type = xml_attr(xml,'type'),
           subject = xml_attr(xml,'subject'),
           body = xml_attr(xml,'body'),
           toa = xml_attr(xml,'toa'),
           sc_toa = xml_attr(xml,'sc_toa'),
           service_center = xml_attr(xml,'service_center'),
           read = xml_attr(xml,'read'),
           status = xml_attr(xml,'status'),
           locked = xml_attr(xml,'locked'),
           date_sent = xml_attr(xml,'date_sent'),
           readable_date = xml_attr(xml,'readable_date'),
           contact_name = xml_attr(xml,'contact_name'),
           stringsAsFactors = FALSE)
          
          # Add subid and log information to dataframe
          log <- log %>% 
            mutate(subid = subid,
                   log_file = file,
                   created = file.info(file)$ctime,
                   modified = file.info(file)$mtime)
          
          # Join log files
          logs <- logs %>% 
            full_join(log)
        }
      }
      return(logs)
    } 
}
```

```{r}
get_xml_ids <- function(subid) {
    log <- tibble(subid = character())
    log_files <- list.files(file.path(path_raw, subid), pattern = "SMS", include.dirs = FALSE)
    log_files <- discard(log_files, log_files == "RawSMSVoice")
    if(length(log_files) > 0) {
      for(file in log_files) {
        if(str_detect(file,'xml')) {
         log <- log %>% 
            add_row(subid = subid)
          return(log) }
      }   
      
    }
}
```

#### get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")

# subids with xml files
xml_subids <- tibble(subid = character())
xml_subids <- map_df(subids$subid, ~get_xml_ids(.)) %>% 
  glimpse()
```


#### read in all XML logs
```{r message = FALSE}
all_logs <- tibble(subid = character())
all_logs <- map_df(xml_subids$subid, ~read_xml(.)) %>% 
  glimpse()
```

#### Remove duplicates

```{r}
all_logs <- all_logs %>%
  distinct(across(-c(log_file, created, modified)), .keep_all = TRUE) %>% 
  glimpse()
```


#### Clean with cleaning log
cleaning function
```{r}
clean_logs <- function(d, log){
  # recode_one log entries
  log_recode_one <- dplyr::filter(log, log_action == "recode_one")

  for (i in seq_along(log_recode_one$index)){

    log_subid <- pluck(log_recode_one, "subid", i)
    log_date <- pluck(log_recode_one, "date", i)
    log_address <- pluck(log_recode_one, "address", i)
    log_var_name <- pluck(log_recode_one, "var_name", i)
    log_new_value <- pluck(log_recode_one, "new_value", i)
    log_old_value <- pluck(log_recode_one, "old_value", i)

    # pull out row id
    row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      # match on subid, date, phone number, and old value
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      dplyr::filter(date == log_date) %>%
      dplyr::filter(address == log_address) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    }
    
    # check that only one matching data row
    if (length(row_id) != 1) {
      stop("Rows matching subid: ", log_subid, " does not equal 1")
    }

    # make change to rowid
    if (is.numeric(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.numeric(log_new_value)
    if (is_character(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.character(log_new_value)
    if (is.POSIXt(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as_datetime(log_new_value)

  
  return(d)
}
```

read in log and summarize
```{r}
log <- read_csv(here(path_log, "log_sms_android.csv"), col_types = "ccccccccc") %>%
  rowid_to_column("index") %>%
  glimpse()

# view log actions
table(log$log_action)
```

clean data
```{r}
all_logs <- all_logs %>%
  clean_logs(., log) %>%
  glimpse()
```



#### Convert utc to date time 
Check all dates encoded as 13 digit utc in milliseconds    
```{r}
all_logs %>% 
  filter(!nchar(date) == 13)
```

Convert dates to date time object
```{r}
all_logs <- all_logs %>% 
  mutate(date = round(as.numeric(date)/1000, 0), 
         date = as_datetime(date, tz = "utc"))
```

#### Date sent
Check encoded as 13 digit utc   
FIX: Date sent not all 13 digit utcs - need to look into this before converting to date time
```{r}
all_logs %>% 
  filter(!nchar(date_sent) == 13) %>% 
  count(date_sent) %>% 
  arrange(desc(n)) 
```


#### Other data updates for eda

Replace empty and null character strings with NA
```{r}
all_logs <- all_logs %>% 
  mutate(across(where(is.character), ~na_if(., c(""))),
         across(where(is.character), ~na_if(., c("null")))) %>% 
  glimpse()
```


Remove survey signal messages from study staff
```{r}
(test_messages <- str_subset(all_logs$body, "SurveySignal"))
all_logs <- all_logs %>% 
  filter(!body %in% test_messages) %>% 
  glimpse()
```

<br>

### EDA

`r length(unique(all_logs$subid))` subids had xml sms data logs read in.    


#### Missing data
```{r}
all_logs %>% 
  naniar::miss_var_summary()
```

100% of texts missing message (note text message content is in body variable)       

toa and sc_toa are 0 or NA for all log entries   
```{r}
all_logs %>% 
  janitor::tabyl(toa)

all_logs %>% 
  janitor::tabyl(sc_toa)
```

Subject of text message should always be null/NA in SMS
```{r}
all_logs %>% 
  filter(!is.na(subject)) %>% 
  select(subject) %>% 
  print(n = Inf)
```

All non-null subjects belong to one subid  
Not clear why there is a subject on these messages
```{r}
all_logs %>% 
  filter(!is.na(subject)) %>% 
  tabyl(subid)
```

Remove variables with > 98% missing values
```{r}
all_logs <- all_logs %>%
  select(-c(message, subject, toa, sc_toa)) %>% 
  glimpse()
```


NOTE: Not sure if service center is useful, but keeping for now    

service_center = "The service center (SC) through which to send the message, if present."    
https://developer.android.com/reference/android/provider/Telephony.TextBasedSmsColumns#SERVICE_CENTER
```{r}
all_logs %>% 
  janitor::tabyl(service_center)
```


<br>

#### Dates
Date = date message was received   
Dates range from `r min(all_logs$date, na.rm = TRUE)` to `r max(all_logs$date, na.rm = TRUE)`   

Check dates against readable_date variable   
```{r}
all_logs %>% 
  # convert readable date to date time object
  mutate(date_str = as_datetime(readable_date, tz = "America/Chicago", 
                                                   format = "%b %e, %Y %I:%M:%S %p")) %>% 
  # convert utc date to central time
  mutate(date = with_tz(date, tzone = "America/Chicago")) %>% 
  select(date, date_str)
```

Compare two date entries for discrepancies    
Readable date for 3 entries are 1 hour off. May be due to traveling?   
FIX: Doesn't look like 60 minute difference?
```{r}
all_logs %>% 
  mutate(date_str = as_datetime(readable_date, tz = "America/Chicago", 
                                                   format = "%b %e, %Y %I:%M:%S %p"),
         date = with_tz(date, tzone = "America/Chicago"),
         diff = round(difftime(date, date_str, units = "mins"), 0)) %>%
  filter(diff != 0)  %>% 
  select(subid, address, date, date_str, diff)
```

Removing readable date - will be using unix time stamp from here on out
```{r}
all_logs <- all_logs %>% 
  select(-readable_date)
```


Date sent - Either has a date or 0. Not sure what 0 is yet, doesn't seem to be completely related to type of message and not limited to a subset of subids.
```{r}
all_logs %>% 
  tabyl(date_sent == 0)

all_logs %>% 
  filter(date_sent == 0) %>% 
  tabyl(type)
```

<br>

#### phone numbers
Missing numbers mostly belong to subid 240
```{r}
all_logs %>% 
  filter(is.na(address)) 
```

Raw number format   
Note: email address is possible phone number
```{r}
all_logs %>% 
  filter(!is.na(address)) %>% 
  select(address) %>% 
  head(n = 1000) %>% 
  print(n = Inf)
```



#### text content

Random sample of truncated text content    
FIX: Not seeing many emojis - may have accidently been stripped, working on solution.
```{r}
all_logs %>% 
  select(body) %>% 
  mutate(body = str_trunc(body, 20)) %>% 
  sample_n(., 200) %>% 
  print(n = Inf)
```

All group messages are NA - I think this is because group messages are MMS not SMS   
FIX: confirm they are blank in xml logs 
```{r}
logs %>% 
  filter(str_detect(address, "~")) %>% 
  select(body) %>% 
  print(n = Inf)
```

#### type

Valid options = 1-5
```{r}
all_logs %>% 
  tabyl(type)
```

* 1 = inbox  
* 2 = sent  
* 3 = draft  
* 4 = temporary state of outbox (ultimately ends up in sent or failed)   
* 5 = failed  

Type 19's all belong to one subid and contain alerts   
FIX: should be incoming/type 1?
```{r}
all_logs %>% 
  filter(type == 19) %>% 
  select(subid, address, body)
```

Check type for other alerts
```{r}
all_logs %>% 
  filter(str_detect(address, "alert") | str_detect(address, "Alert") | str_detect(address, "Amber")) %>% 
  select(address, contact_name, type) %>% 
  print(n = Inf)
```


Type -1 may signify an outgoing message to a group of people  
https://www.ijser.org/researchpaper/Identification-of-Fake-SMS-generated-using-Android-Applications-in-Android-Devices.pdf
```{r}
all_logs %>% 
  filter(type == -1) %>% 
  count(contact_name) %>% 
  print(n = Inf)
```

Check for other group messages    
All group messages are type -1 or NA
```{r}
all_logs
logs %>% 
  filter(str_detect(address, "~")) %>% 
  count(type)
```

Type -1 responses all belong to 6 subids. Their type of Android may be creating variables not consistent with other subids.
```{r}
all_logs %>% 
  filter(!type %in% c(1:5, NA)) %>% 
  count(subid)
```

However 37 subids have group messages
```{r}
all_logs %>% 
  filter(str_detect(address, "~")) %>% 
  count(subid)
```

FIX: Due to inconsistent coding likely will want to recode type -1 as NA and use address column to identify group messages   

Type 3 is drafts  
```{r}
all_logs %>% 
  filter(type == 3)
```


#### read
Boolean value for "Has the message been read"?
```{r}
all_logs %>% 
  tabyl(read)
```

* 0 = no   
* 1 = yes  

All unread messages are incoming or type unknown   
```{r}
all_logs %>% 
  filter(read == 0) %>% 
  count(type)
```


#### status
TP-Status value for the message (TP = transfer protocol)
```{r}
all_logs %>% 
  tabyl(status)
```

* -1 = no status  
* 0 = status complete  
* 32 = status pending   
* 64 = status failed   

All failed calls (status = 64) also show type as failed (type = 5)
```{r}
all_logs %>% 
  filter(status == 64) %>% 
  tabyl(type)
```

Some failed calls with type = 5 have no status (-1)   
*Type might be more informative if interested in failed calls*
```{r}
all_logs %>% 
  filter(type == 5) %>% 
  tabyl(status)
```

#### protocol

Protocol identifier code - 0 is default value for SMS (short message service)       
All but 17 entries are 0 or NA
```{r}
all_logs %>% 
  tabyl(protocol)
```

All 57 cases belong to subid 117 and all 95 cases belong to subid 191
```{r}
all_logs %>% 
  filter(protocol == 57 | protocol == 95)
```

Since there doesn't seem to be much info in this variable, I am removing it
```{r}
all_logs <- all_logs %>%
  select(-protocol) %>%
  glimpse()
```

#### locked
Boolean value for "Is the message locked"?   
Locking a text message marks the message to prevent it from being deleted.
```{r}
all_logs %>% 
  tabyl(locked)
```

15 subids have locked messages
```{r}
all_logs %>% 
  filter(locked == 1) %>% 
  count(subid) %>% 
  arrange(desc(n))
```


#### contact name
```{r}
all_logs %>% 
  group_by(contact_name) %>% 
  slice(1) %>% 
  select(contact_name) %>% 
  print(n = Inf)
```

Many email address numbers have unknown contact names
```{r}
all_logs %>% 
  filter(str_detect(address, "@")) %>% 
  tabyl(contact_name)
```



#### log files
more than 3 logs
```{r}
all_logs %>% 
  group_by(subid) %>% 
  summarise(n_logs = length(unique(log_file))) %>% 
  filter(n_logs > 3)

all_logs %>% 
  filter(subid == "032") %>% 
  janitor::tabyl(log_file)

all_logs %>% 
  filter(subid == "052") %>% 
  janitor::tabyl(log_file)

all_logs %>% 
  filter(subid == "223") %>% 
  janitor::tabyl(log_file)
```

32 and 52 also have 4 voice call logs:  
subid 32 bought a new phone in the first month of the study and so we collected call/sms logs from both phones at Follow Up 1.  
subid 52 got a new phone while on study - likely explains extra log.   
subid 223 got a new phone and phone number so they came in on 5/20/2019 to get apps put on their phone and to register for surveys. Participant brought their deactivated phone with to delete apps and to transfer calls and SMS files (labeled SMS_1 and Calls_1); Participant did not have a Voice_4 file at their Final Visit they had no phone calls in their phone call log

<br>

log creation dates range from `r min(all_logs$created)` to `r max(all_logs$created)`.      
log modification dates range from `r min(all_logs$modified)` to `r max(all_logs$modified)`.   


### Add categorical labels

Type
```{r}
all_logs <- all_logs %>% 
  mutate(type = case_when(type == 1 ~ "inbox",
                          type == 2 ~ "sent",
                          type == 3 ~ "draft",
                          type == 4 ~ "outbox",
                          type == 5 ~ "failed",
                          TRUE ~ as.character(type)))
```

Status
```{r}
all_logs <- all_logs %>% 
  mutate(status = case_when(status == -1 ~ "no status",
                            status == 0 ~ "status complete",
                            status == 32 ~ "status pending",
                            status == 64 ~ "status failed",
                            TRUE ~ as.character(status)))
```

Read
```{r}
all_logs <- all_logs %>% 
  mutate(read = case_when(read == 0 ~ "no",
                          read == 1 ~ "yes",
                          TRUE ~ as.character(read)))
```

Locked
```{r}
all_logs <- all_logs %>% 
  mutate(locked = case_when(locked == 0 ~ "no",
                            locked == 1 ~ "yes",
                            TRUE ~ as.character(locked)))
```



### Write csv
```{r}
write_csv(all_logs, file.path(path_shared, "sms_android.csv")) %>% glimpse()
```

**Note: date saved as UTC**

<br>