---
title: "Make processed GPS df"
author: "Hannah Moshontz & John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Update

Code has had paths and other updates to github and current lab standards.

The existing EDA looks fine but it is pretty coarse.  Consider adding more EDA
as studies start to use these data


### Notes
Purpose: This script creates the analysis gps dataset and conducts EDA

Inputs:

* participants' raw gps data files

Outputs

* gps.csv

### Setup

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_processed <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_processed <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("first", "dplyr")
conflict_prefer("last", "dplyr")
conflict_prefer("hour", "lubridate")

library(here)  # establish project directory consistently as working directory
```


Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(purrr)
library(readxl)
library(janitor)
library(geosphere)
library(lubridate)
library(plotKML)
library(janitor)
library(psych)
library(kableExtra)
library(readxl)
library(data.table)
library(ggplot2)
```

### Functions

Function to import and standardize moves data
```{r}
convert_moves <- function(file_name){
  
  message('......loading: ', file_name)
  
  d_moves <- readGPX(file_name,
                     metadata = FALSE, bounds = FALSE, 
                     waypoints = TRUE, tracks = TRUE, routes = FALSE) %>%
    .$tracks %>% 
    purrr::flatten(.) %>% # as a list of dfs
    enframe(.) %>% # as a nested df
    unnest(keep_empty = TRUE) %>% # as one tibble
    rename(long = lon) #renaming for coherence
  
  
  if (
    any(is.na(d_moves$time) & !(is.na(d_moves$lat) & is.na(d_moves$long)))
  ) stop("Missing value detected for time on non-missing day") 
  
  # drop initial missing obs and impute time for missing obs and 
  # fill in the last second of the next day;  Retain time zone from previous observation
  d_moves <- d_moves %>% 
    fill(time) %>% 
    mutate(time = if_else(is.na(long), 
                          str_c(lubridate::mdy(name), 
                                "T23:59:59.000-", 
                                str_extract(time, "\\d{2}:\\d{2}$")),
                          time)) %>% 
    select(-name) %>% 
    mutate(time = as_datetime(time, tz = 'America/Chicago')) %>% 
    arrange(time) %>% #sort on time
    mutate(
      data_type = 'gps',
      speed_kmh = NA,
      altitude_meters = NA,
      direction = NA,
      accuracy = NA,
      app_source = 'moves',
      count = NA
    ) %>% 
    select(lat, long, time, accuracy, sgmnt_type, trckpnt_type, 
           app_source, data_type, speed_kmh, altitude_meters,
           direction, count)
  
  return(d_moves)
}
```

Function to import and standardize followmee data
```{r}
convert_followmee <- function(file_name){
  
  #multiple GPX exist for 52 58 59 63 64 65 66 76 77 78 79 80 81 82
  message('......Loading: ', file_name)
  
  d_followmee <- read_rds(file_name) %>% 
    clean_names("snake") %>% 
    mutate(
      raw_orig_time = date,
      time = as_datetime(date, tz = 'America/Chicago')
    ) %>%  # convert time to dttm
    arrange(time) %>% 
    mutate(
      lat = latitude,
      long = longitude,
      data_type = str_to_lower(type),
      speed_kmh = speed_km_h,
      altitude_meters = altitude_m,
      app_source = 'followmee',
      count = NA,
      sgmnt_type = NA,
      trckpnt_type = NA
    ) %>% 
    select(lat, long, time, accuracy, sgmnt_type, trckpnt_type, 
           app_source, data_type, speed_kmh, altitude_meters,
           direction, count)
  
  return(d_followmee)
  
}
```

Function to make the final gps df (calls previous functions)
```{r}
make_gps <- function(subid, file_path) {
  
  raw_file <- file.path(file_path, subid)
  location_file <-  file.path(file_path, subid, str_c(subid, "_Locations.xlsx"))
  subid_numeric <- as.numeric(subid)
  
  message('...importing gps for subject ', subid)
  
  # list gpx files
  gpx_files <- list.files(
    path = raw_file, 
    pattern = '.gpx', 
    full.names = TRUE, 
    recursive = FALSE, 
    include.dirs = FALSE
  )
  
  # list followmee files
  followmee_files <- list.files(
    path = raw_file,
    pattern = '\\d{3}_GPSFollowRaw.rds',
    full.names = TRUE,
    recursive = FALSE,
    include.dirs = FALSE
  )
  
  #store type of gps data source
  only_gpx <- ifelse(length(gpx_files) >= 1 & 
                       length(followmee_files) == 0, 
                     TRUE, FALSE)
  
  only_followmee <- ifelse(length(gpx_files) == 0 & 
                             length(followmee_files) == 1, 
                           TRUE, FALSE)
  
  both <- ifelse(length(gpx_files) >= 1 & 
                   length(followmee_files) == 1, 
                 TRUE, FALSE)
  
  gps_absent <- !xor(xor(only_gpx, only_followmee), both)
  
  #create empty dfs
  d_moves <- NULL
  d_follow <- NULL
  
  #process and save gpx (accommodates multiple)
  if (length(gpx_files) != 0) {
    
    d_moves <- map_df(gpx_files, ~convert_moves(.x)) %>% #import, convert, bind each file
      filter(!is.na(long), !is.na(lat)) %>% #drop obs without lat and long
      distinct() #eliminate fully duplicated rows
  }
  
  
  #process and save followmee file
  if (length(followmee_files) == 1) {
    
    d_follow <- convert_followmee(followmee_files[1])
  }
  
  if (!gps_absent) { #if subject has gps data, create the dataset and return
    #create database rds
    database <- bind_rows(d_moves, d_follow) %>% 
      arrange(time) %>% 
      select(-count) %>% #this is NA for all
      filter(!is.na(lat) && !is.na(long)) %>% 
      mutate(subid = subid_numeric)
    
    return(database)
  }
}
```

### Creating the gps data

Store subids
```{r}
subid_all <- list.dirs(path_raw, recursive = FALSE) %>% 
  str_extract("\\d{3}$") %>% 
  na.exclude()
```

bind all individual files
```{r}
gps <- map_dfr(subid_all, ~make_gps(.x, file_path = path_raw)) %>% 
  glimpse()
```

Handle/remove points without timestamps - we cant do anything with these points

BUT: could look at raw data.  Note SUBIDs for further work on recovering these points
```{r}
gps %>% 
  filter(is.na(time))

gps <- gps %>% 
  filter(!is.na(time))
```

Create and save the gps data
```{r}
gps %>% 
  write_csv(file = file.path(path_processed, "gps.csv"))
```

## EDA

### Import Data and glimpse()

GPS data
```{r}
gps <- fread(file.path(path_processed, "gps.csv"), #need fread because data is huge, crashes r otherwise
             stringsAsFactors = TRUE) %>%  
  mutate(raw_orig_time = as.character(time)) %>% 
  glimpse()

notes <- read_csv(here("shared/notes/raw_notes.csv")) 

visit_dates <- read_csv(file.path(path_processed, "visit_dates.csv"))

```

There are `r length(unique(gps$subid))` subjects contributing `r nrow(gps)` gps observations. 

We have gps-specific notes from staff on `r length(na.omit(notes$notes_gps))` subjects.

### Checking each data source

#### Lat and long
```{r}
gps %>% 
  filter(is.na(lat) | is.na(long))
```

This is not surprising. We filtered on NA lat / long (one of the apps would create a missing point if no signals were detected in a day).

```{r}
gps %>% 
  filter(lat <= 1 & long <= 1, lat >= -1 & long >= -1)
```

There are no "Null Island" points at 0,0.

#### Time
```{r}
gps %>% 
  filter(is.na(time))
```
No points b.c we filtered them out above

#### Accuracy, speed, altitude, direction
```{r}
gps %>% 
  select(accuracy, speed_kmh, altitude_meters, direction) %>% 
  describe()
```


#### Data type
```{r}
gps %>% 
  tabyl(data_type, app_source, show_na = TRUE) %>% 
  adorn_totals(c("row", "col")) %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

The vast majority of gps observations were labeled as gps as opposed to network-type observations. Only followmee produced network-type observations.

#### App source
```{r}
gps %>% 
  tabyl(app_source, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

About half of observations came from each app.

### Number of Observations per Person

```{r}
gps %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 10) +
  xlab("number of gps observations") +
  ggtitle("Histogram of gps observations per subject") +
  theme_classic()
```


### Number of Observations per Non-Missing Day

```{r}
mean_avg_obs_per_day <- gps %>%    
  mutate(date_central = date(time)) %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_obs_per_day = mean(n_obs)) %>% 
  .$avg_obs_per_day %>% 
  mean()

max_obs_per_day <- gps %>% 
  mutate(date_central = date(time)) %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_obs_per_day = mean(n_obs),
            sd = sd(n_obs),
            min = min(n_obs),
            max = max(n_obs)) %>% 
  .$max %>% max()
```

On average, participants provided an average of `r mean_avg_obs_per_day` observations per non-missing day (max = `r max_obs_per_day`).

```{r}
gps %>% 
  mutate(date_central = date(time)) %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_obs_per_day = mean(n_obs),
            min = min(n_obs),
            max = max(n_obs)) %>%  
  ggplot(aes(x = avg_obs_per_day)) +
  geom_histogram(bins = 10) +
  xlab("avg number of gps observations") +
  ggtitle("Histogram of average observations per non-missing day") +
  theme_classic()
```
