---
title: "Clean the raw qualtrics EMA surveys"
author: "Sarah Sant'Ana and Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Status

KW currently working on this clean script. 

Need to discuss flagged EMA log entries in flagged_entries.Rmd with JC.   

Still working on:   

- clean up and manually check all log entries     
- match all lapses to log note entries    
- Recode_tz log entries not currently handled with clean function       
- Check how many days between EMAs (large gaps?)    
- Check subid 269, 66, and 84's data with multiple surveys on some days and other subids averaging over 4 surveys a day        
- Check if participants without lapses are missing EMAs     
- Look at surveys completed in under 12 seconds    
  

### Conclusions

- All unfinished surveys (finished = 0) have at least ema_1 answered which reports if there have been any lapses since the last survey.    

- Many participants completed more than 4 EMAs per day. This may be due to several reasons, including trying to make up for missed surveys the day before, receiving too many prompts via survey signal, or forgetting whether they already did it.   

- Subids 104 and 128 have over 100 reported lapses.     
  - They both also each have 27 log entries to make corrections to typos and incorrect data.   
  - According to notes, subid 104 reported lapses everyday on study.     
  - Audio messages seem to support 128's frequent lapses - notes say "Audio message for 10/05 reports that the sub has been drinking off and on for the last 2 or 3 days; Lots of lapses reported on 10/03-10/05; Some overlap but not all which further emphasizes info from audio message; Audio message on 10/17 reported drinking the night before - Lots of lapses being reported during time; Participant mentioned that she drank some on 11/18 but not a ton; She also reported on 11/17 that she has not been fighting any urges; No explicit mention of drinking in audio message just that sub was not looking forward to going home; Lots of little lapses reported around this time (12/3/18)"        

- Subid 269 and 84 averages over 4 surveys a day - goes for several days with 10-15 completed surveys.   

- 5 lapses are included in surveys completed in under 30 seconds.   


Supporting notes for lapse/no lapse labels:    

- Subid 47 was not receiving EMA messages between 4/6 - 4/17/18. This should not be a reliable no lapse period though because according to staff they reported a lapse on 4/10/18 at their tech troubleshooting appointment on 4/11/18.   

- Note about a lapse for subid 79 - "Data log says this sub had a brain injury and suffers from memory issues; This could explain why it took so long to report this lapse; However he did report a lapse on 09/02 20:00 at 10am on 09/03 which makes me a little skeptical and think it is possible that that this is supposed to be 09/03"     

- Note about a lapse/non-lapse for subid 119 - "On 10/31 subs audio mentioned that they had missed several days because they relapsed and were trying to get back on track; This is the only lapse that was reported while on study; However it is unclear if this lapse report is correct. They had answered 4 surveys on 10/28 saying they did not lapse"    

- No surveys for subid 173 between 2/5 - 2/14 - they called to say they were interested in continuing with the study but having trouble getting back on track - so this time period is likely not reliable for non-lapse or lapse.    

- Note about subid 204 lapse - "Participant did not do many surveys during their second month of participation. At their Follow-up 2 visit they reported several lapses that were not documented in their EMAs - estimated lapse days/times in subid's raw data log; Participant did a total of 5 surveys in between follow-up2 and follow-up3. Participant reported that she did not like doing the surveys after a while so she stopped completing them. I collected lapses from her even though she did not complete her surveys and she reported that the lapse she reported with timestamp: 1558123879 was not 1 long drinking episode, but 3 individual ones lasting from 9pm each night and going until Midnight. She also reported that she probably drank beginning 05/16 through 06/04 from 9pm until Midnight."    

- Subid 212 note about unreported lapses "	Audio on 4/17 reported that drinking has been an issue. No specific info about the lapse. They denied having a lapse to report 3 times during the alleged lapse; Participant divulged at their follow up visit that they drank the night before their visit (5/15/19 - 5/16/19) but they never formally reported the lapse."    

- Subid 213 note about lapse "Participant reported having drank alcohol nearly every day during the lapse dates provided - They reported the first day (05/13/2019) being the heaviest day and the subsequent dates being a little lighter. They did not recall times for lapses when asked during their Follow-up 2 visit; The participant did not complete any ema between 5/7-5/21; They did not complete any audio messages between 5/04-5/22; Their 5/22 and 5/27 audio messages both reference that they've "been drinking" and on 5/30 they say they are "trying to get back on track"; Participant reported having drank at the following times on listed dates: 5/25: 11pm-12am 5/26: 6pm -8pm 5/27: 6pm-8pm. Participant reported these were estimates of the times spent drinking on this weekend."    

- Subid 225 note about lapse "This is the only lapse she reported during her participation but her audio messages definitely do not reflect her drinking during this entire period; On 6/19 participant reported that they felt like crap because they relapsed; On 6/20 participant reported that they were 2 days sober; They did not complete an audio message between 6/14-6/19 however messages between 6/5-6/14 do not give any indication that she was drinking"   


### Notes

Purpose: This file cleans the qualtrics EMA surveys and performs EDA on all EMA variables. The focus of this script is to clean/check all EMA lapse reports so that the cleaned data can be used to create lapse labels for individual studies.   


Inputs (path_raw):  

* ema_morning.csv
* ema_later.csv

Outputs (path_shared):   

* ema_morning.csv
* ema_later.csv


### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw/qualtrics"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"}
        )
```

Relative paths
```{r}
path_log <- "shared/notes"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)  # always need this
library(janitor) # cleaning and EDA
library(lubridate)

# for plots and tables
library(ggplot2)
theme_set(theme_bw()) # or theme_set(theme_classic())
library(kableExtra)
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_lab_support, "clean_qualtrics_by_log.R"))
```



### Read in raw data 

Rename subid and response_id to tidy case because these variables are used by name in clean_qualtrics_by_log()
```{r}
ema_morning <- vroom::vroom(here(path_raw, 'ema_morning.csv'), col_types = vroom::cols()) %>% 
  rename(subid = SubID) %>% 
  rename(response_id = ResponseID) %>% 
  # put start and end date in central time
  mutate(StartDate = with_tz(StartDate, tzone = "America/Chicago"),
         EndDate = with_tz(EndDate, tzone = "America/Chicago")) %>% 
  glimpse()

ema_later <- vroom::vroom(here(path_raw, 'ema_later.csv'), col_types = vroom::cols()) %>% 
  rename(subid = SubID) %>% 
  rename(response_id = ResponseID) %>% 
  # put start and end date in central time
  mutate(StartDate = with_tz(StartDate, tzone = "America/Chicago"),
         EndDate = with_tz(EndDate, tzone = "America/Chicago")) %>% 
  glimpse()
```

Read in raw notes for supporting info
```{r}
notes <- vroom::vroom(here(path_log, "raw_notes.csv"), col_types = vroom::cols())
```

### Read in Logs

```{r}
log_morning <- vroom::vroom(here(path_log, "log_ema_morning.csv"), col_types = vroom::cols()) %>% 
  glimpse()

log_later <- vroom::vroom(here(path_log, "log_ema_later.csv"), col_types = vroom::cols()) %>% 
  glimpse()
```


### Log EDA

Join logs for EDA
```{r}
log_all <- log_morning %>% 
  bind_rows(log_later)
```

Log actions
```{r}
tabyl(log_all$log_action)
```

#### remove entries   

All entries have been confirmed to be accurate removals   
- Most removed entries belong to subid 55 who renrolled as subid 61 with a new start_study date     
- 2 other removals are due to subids putting an incorrect answer for lapse and then retaking it to fix it    
```{r}
log_all %>% 
  filter(log_action == "remove") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```
    
#### recode_one entries

variables with recode_one entries
```{r}
log_all %>% 
  filter(log_action == "recode_one") %>% 
  tabyl(var_name)
```

Some subids have more log entries than others and may be more prone to unreliable reports
```{r}
log_all %>% 
  tabyl(subid) %>% 
  arrange(desc(n))
```

Subid 101's entries are all due to correcting their EMAs that were initially registered under "test"   
```{r}
log_all %>% 
  filter(subid == "101") %>% 
  tabyl(var_name)
```

subid 131 has several flagged entries as having start_diff's over 10 hours
```{r}
log_all %>% 
  filter(subid == "131") %>% 
  tabyl(log_reason)
```

Same with subid 48
```{r}
log_all %>% 
  filter(subid == "048") %>% 
  tabyl(log_reason)
```

Subid 104 made typos about midnight being the next day
```{r}
log_all %>% 
  filter(subid == "104") %>% 
  tabyl(var_name)

log_all %>% 
  filter(subid == "104" & var_name == "EMAL_1.3")
```

Several long lapses for subid 128
```{r}
log_all %>% 
  filter(subid == "128") %>% 
  tabyl(log_reason)
```


**subids recoded**  

All recoded subids are appropriate   
```{r}
log_all %>% 
  filter(var_name == "subid") %>% 
  tabyl(subid)
```

subid 66 and 136 are recoded due to piping error in survey
```{r}
log_all %>% 
  filter(subid == "066" | subid == "136") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%")
```

subid 31 recoded according to data_log where test was used as subid incorrectly
```{r}
log_all %>% 
  filter(subid == "031" & var_name == "subid") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

subid 101 recoded to 135 - 135 was receiving surveys under someone else's subid number (this person was ineligible so all occurrences of 101 should be changed to 135)
```{r}
log_all %>% 
  filter(subid == "101" & var_name == "subid") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


**Lapses recoded**    
Recoded lapses to non-lapses due to error or duplicate reports of a single lapse with varying timetables   
```{r}
log_all %>% 
  filter(var_name == "EMAL_1" | var_name == "EMAM_1") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Lapse dates recoded to correct format of date, remove incorrect lapse information to line up with recoded lapses, correct known errors from data log, or fix dates that are clearly an error to the most likely date (from supporting evidence - audio files, other EMA's, data log notes, etc.). Additionally, many date errors are associated with participants not reporting midnight as being the next day.    

I went through every log entry and they all seem to be appropriate assumptions - one's that I was unsure about were flagged for discussion with JC.   
```{r}
log_all %>% 
  filter(var_name %in% c("EMAL_1.1", "EMAL_1.3", "EMAM_1.1", "EMAM_1.3")) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Lapse times recoded    
I went through every log entry and they all seem to be appropriate assumptions - one's that I was unsure about were flagged for discussion with JC.  
```{r}
log_all %>% 
  filter(var_name %in% c("EMAL_1.2", "EMAL_1.4", "EMAM_1.2", "EMAM_1.4")) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Desire to remain abstinent    
Adds retrospective answers after this new question was added to the EMA, also recodes for lapses removed due to already having been reported.    
```{r}
log_all %>% 
  filter(var_name == "EMAL_1.5" | var_name == "EMAM_1.5") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


**UTCs recoded**     

These all seem appropriate and all are for our first 3 subids.
```{r}
log_all %>% 
  filter(var_name == "UTC") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### recode_tz entries   

*FIX: Need to implement these log entries into clean Qualtrics function*

```{r}
log_all %>% 
  filter(log_action == "recode_tz") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### note entries
```{r}
log_all %>% 
  filter(log_action == "note") %>% 
  select(-c(var_name, new_value, old_value)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```



### Clean Data with Cleaning Function

```{r}
ema_morning <- ema_morning %>% 
  clean_qualtrics_by_log(log_morning) %>% 
  glimpse()

ema_later <- ema_later %>% 
  clean_qualtrics_by_log(log_later) %>% 
  glimpse()
```


### Tidy variable names

```{r}
ema_morning <- ema_morning %>% 
  clean_names() %>% 
  glimpse()

ema_later <- ema_later %>% 
  clean_names() %>% 
  glimpse()
```

### EDA

Combine EMA files for EDA
```{r}
ema_all <- ema_morning %>% 
  rename_with(~ str_replace(.x, "emam_", "ema_")) %>% 
  # add temp variable to trace which ema file an entry came from for EDA
  mutate(ema_type = "morning") %>% 
  bind_rows(ema_later %>% 
              rename_with(~ str_replace(.x, "emal_", "ema_")) %>% 
              mutate(ema_type = "later")) %>% 
  glimpse()
```

#### Test data

`r nrow(subset(ema_all, subid == "test"))` test surveys remain.   

Most test entries are complete
```{r}
ema_all %>% 
  filter(subid == "test") %>% 
  tabyl(finished)
```

Clusters of test data have Brogdens Longitude/Latitude (43.07, 89.41) 
```{r}
ema_all %>% 
  filter(subid == "test") %>% 
  count(location_latitude, location_longitude) %>% 
  arrange(desc(n))
```

Filter out test data
```{r}
ema_morning <- ema_morning %>% 
  filter(subid != "test")
ema_later <- ema_later %>% 
  filter(subid != "test")
ema_all <- ema_all %>% 
  filter(subid != "test")
```



#### Missing data
```{r}
ema_all %>% 
  naniar::miss_var_summary()
```

Remove Qualtrics variables with 100% missing data and variables with 0 variance   
```{r}
ema_morning <- ema_morning %>% 
  select(-c(recipient_last_name, recipient_first_name, recipient_email,
            external_data_reference, response_set, location_accuracy))
ema_later <- ema_later %>% 
  select(-c(recipient_last_name, recipient_first_name, recipient_email,
            external_data_reference, response_set, location_accuracy))
ema_all <- ema_all %>% 
  select(-c(recipient_last_name, recipient_first_name, recipient_email,
            external_data_reference, response_set, location_accuracy))
```

missing ema_1_1 - ema_1_5 variables    
These are follow up variables for participants who report a lapse on ema_1
```{r}
ema_all %>% 
  filter(is.na(ema_1_1) | is.na(ema_1_2) | is.na(ema_1_3) | is.na(ema_1_4) | is.na(ema_1_5)) %>% 
  tabyl(ema_1)
```

82 participants report a lapse but do not provide full information about lapse   
Some do fill out ema_1_1 - ema_1_4 which are the dates/times of lapse
```{r}
ema_all %>% 
  filter(ema_1 == "Yes" & (is.na(ema_1_1) | is.na(ema_1_2) | is.na(ema_1_3) | 
                             is.na(ema_1_4) | is.na(ema_1_5))) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


missing ema_2_1 - ema_7_1 variables    
All are marked as not finished
```{r}
ema_all %>% 
  filter(is.na(ema_2_1) | is.na(ema_3_1) | is.na(ema_4_1) | is.na(ema_5_1) |
           is.na(ema_6_1) | is.na(ema_7_1)) %>% 
  tabyl(finished)
```

missing ema_8_1 - ema_10_1 variables   
These variables were only on the morning survey    
All missing values on later surveys or on morning surveys marked as not finished
```{r}
ema_all %>% 
  filter(is.na(ema_8_1) | is.na(ema_9_1) | is.na(ema_10_1)) %>% 
  tabyl(ema_type, finished)
```

missing location_latitude and longitude    
These variables are only recorded when a survey is complete - all missing values are on unfinished surveys
```{r}
ema_all %>% 
  filter(is.na(location_latitude) | is.na(location_longitude)) %>% 
  tabyl(finished)
```


missing 93% send_date and send_time    
Not sure what these variables are (from SurveySignal?) but too much missing data to likely be helpful
```{r}
ema_all %>% 
  filter(is.na(send_date)) %>% 
  slice_sample(n = 500) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### EMA counts and frequencies

`r nrow(ema_all)` EMAS across `r length(unique(ema_all$subid))` unique subids  

This is the expected number for all enrolled subids       


EMA counts per subid
```{r}
ema_all %>% 
  count(subid) %>% 
  arrange(desc(n))
```

Bring in study start and end dates
```{r}
visits <- vroom::vroom(here(path_shared, "visit_dates.csv"), col_types = vroom::cols()) %>% 
  mutate(across(c(everything(), -subid), ~ force_tz(.x, tzone = "America/Chicago"))) %>% 
  glimpse()

ema_all_visits <- ema_all %>% 
  mutate(subid = as.numeric(subid)) %>% 
  left_join(visits %>% 
              select(subid, start_study, end_study), 
            by = "subid")
```

Calculate days on study
```{r}
ema_all_visits <- ema_all_visits %>% 
  mutate(days_on_study = as.numeric(round(end_study - start_study))) %>% 
  glimpse()
```

Participants were on study for `r min(ema_all_visits$days_on_study)` - `r max(ema_all_visits$days_on_study)` days     

NOTE: 5 subids have over 90 days on study  
```{r}
ema_all_visits %>% 
  filter(days_on_study > 90) %>% 
  group_by(subid) %>% 
  slice(1) %>% 
  select(subid, days_on_study)
```


EMAs completed per study day    
```{r}
ema_all_visits <- ema_all_visits %>% 
  group_by(subid, days_on_study) %>% 
  summarise(n_emas = n(), .groups = "drop") %>% 
  mutate(avg_emas = n_emas/days_on_study)
```

On average participants completed `r round(mean(ema_all_visits$avg_emas), 2)` EMAs per day.  

```{r}
ema_all_visits %>% 
  ggplot(aes(x = avg_emas)) +
  geom_histogram(bins = 20, color = "black", fill = "light grey")
```

NOTE: This does not cap out possible daily EMAs at 4. Almost all participants completed more than 4 EMAs in a single day at some point.    
Days with more than 4 EMAs
```{r}
ema_all_more_than_4 <- ema_all %>% 
  mutate(date = date(start_date)) %>% 
  count(subid, date) %>% 
  filter(n > 4)

print(ema_all_more_than_4)
```


There are `r nrow(ema_all_more_than_4)` instances of days with more than 4 surveys from `r length(unique(ema_all_more_than_4$subid))` participants.   

The most surveys in one day are `r max(ema_all_more_than_4$n)` surveys.  

Subid 269 seems to have completed more than 4 surveys on most study days. Unclear why because they did not have missed surveys the day before to make up for. No staff notes about EMA.    

*FIX: investigate 269's data*   

```{r}
ema_all %>% 
  filter(subid == 269) %>% 
  mutate(date = date(start_date)) %>% 
  count(date)
```

*FIX: investigate why 66 has more surveys completed in first days on study*   

```{r}
ema_all %>% 
  filter(subid == "066") %>% 
  mutate(date = date(start_date)) %>% 
  count(date)
```

*FIX: investigate why 84 has several days with more than 4 surveys*    

```{r}
ema_all %>% 
  filter(subid == "084") %>% 
  mutate(date = date(start_date)) %>% 
  count(date)
```

*FIX: investigate subids averaging more than 4 surveys a day*
```{r}
ema_all_visits %>% 
  filter(avg_emas > 4)
```



*FIX: count days between EMAs - look for large gaps*    
```{r}

```



#### Start and End dttms for EMAs

Duration of EMA
```{r}
ema_all <- ema_all %>%  
  mutate(duration_min = round(as.numeric(difftime(end_date, start_date, units = "mins"))))

ema_all %>% 
  filter(subid != "test") %>% 
  tabyl(duration_min)
```

Closer look at surveys under half a minute
```{r}
ema_all %>%  
  mutate(duration_min = as.numeric(difftime(end_date, start_date, units = "mins"))) %>%
  filter(duration_min < .5) %>% 
  filter(subid != "test") %>% 
  tabyl(duration_min)
```

Most surveys under half a minute either had no lapse or were not finished
```{r}
ema_all %>%  
  mutate(duration_min = as.numeric(difftime(end_date, start_date, units = "mins"))) %>%
  filter(duration_min < .5) %>% 
  filter(subid != "test") %>% 
  tabyl(finished, ema_1)
```

Surveys that took less than 12 seconds
```{r}
ema_all_less_than_12_sec <- ema_all %>%  
  mutate(duration_min = as.numeric(difftime(end_date, start_date, units = "mins"))) %>%
  filter(duration_min < .2) %>% 
  filter(subid != "test") 
```

`r nrow(subset(ema_all_less_than_12_sec, finished == 1))` of the `r nrow(ema_all_less_than_12_sec)` surveys with a duration of less than 12 seconds were marked complete   
All of these surveys report no lapses and were completed later in the day - which significantly shortens the survey length
```{r}
ema_all_less_than_12_sec %>% 
  filter(finished == 1) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


Surveys that took more than 5 minutes
```{r}
ema_all_more_than_5_min <- ema_all %>%  
  mutate(duration_min = as.numeric(difftime(end_date, start_date, units = "mins"))) %>%
  filter(duration_min > 5) %>% 
  filter(subid != "test") 
```

`r nrow(ema_all_more_than_5_min)` surveys took over 5 minutes to complete.    

Most (N = `r nrow(subset(ema_all_more_than_5_min, finished == 1))`) were marked as complete.   
```{r}
ema_all_more_than_5_min %>% 
  filter(finished == 1) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Different start and end days   
NOTE: Includes 2 lapses
```{r}
ema_all_more_than_5_min %>% 
  mutate(start_day = as_date(start_date),
         end_day = as_date(end_date)) %>% 
  filter(start_day != end_day) %>% 
  select(c(subid, start_date, end_date, finished, ema_1:ema_10_1, ema_type, duration_min)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### Finished

`r nrow(subset(ema_all, finished == 0 & subid != "test"))` surveys are marked as incomplete

Keep unfinished surveys - all have at least ema_1 answered
```{r}
ema_all %>% 
  filter(subid != "test") %>% 
  filter(finished == 0) %>% 
  select(subid, ema_1:ema_1_5)
```


#### Status

`r nrow(subset(ema_all, status == 8))` surveys have status = 8     

The value in the Status column indicates the type of response collected     
0 = A normal response   
8 = A possible spam response   

```{r}
ema_all %>% 
  tabyl(status)
```

All flagged surveys were completed in under 5 min
```{r}
ema_all %>% 
  filter(status == 8) %>% 
  tabyl(duration_min)
```

But they don't seem to be related to any particular subid
```{r}
ema_all %>% 
  filter(status == 8) %>% 
  tabyl(subid)
```


#### Lapses

Reported lapses   
**ema_1**    
"Have you drank any alcohol that you have not yet reported?"
```{r}
ema_all %>% 
  tabyl(ema_1)
```

**ema_1_1**    
"Please indicate the date of the first drink that you have not yet reported"    
```{r}
ema_all <- ema_all %>% 
  mutate(ema_1_1 = as_datetime(ema_1_1, format = "%m-%d-%Y", tz = "America/Chicago"))
```

Dates of first drink in lapse range from `r min(ema_all$ema_1_1, na.rm = TRUE)` - `r max(ema_all$ema_1_1, na.rm = TRUE)`.    


**ema_1_2**    
"Please select the hour of the first drink that you have not yet reported"
```{r}
ema_all %>% 
  filter(ema_1 == "Yes") %>% 
  tabyl(ema_1_2)
```


**ema_1_3**    
"Please indicate the date of the last drink that you have not yet reported"
```{r}
ema_all <- ema_all %>% 
  mutate(ema_1_3 = as_datetime(ema_1_3, format = "%m-%d-%Y", tz = "America/Chicago"))
```

Dates of last drink in lapse range from `r min(ema_all$ema_1_3, na.rm = TRUE)` - `r max(ema_all$ema_1_3, na.rm = TRUE)`.     


**ema_1_4**    
"Please select the hour of the last drink that you have not yet reported"
```{r}
ema_all %>% 
  filter(ema_1 == "Yes") %>% 
  tabyl(ema_1_4)
```

**ema_1_5**    
"Is your goal still to remain abstinent in the future?"
```{r}
ema_all %>% 
  filter(ema_1 == "Yes") %>% 
  tabyl(ema_1_5)
```


Participants with lapses    
`r nrow(count(subset(ema_all, ema_1 == "Yes" & subid != "test"), subid))` subids have a reported lapse    
```{r}
ema_all_lapse <- ema_all %>% 
  filter(ema_1 == "Yes") %>% 
  filter(subid != "test") %>% 
  count(subid) %>% 
  arrange(desc(n))

ema_all_lapse 
```

Participants with over 40 reported lapses     
```{r}
ema_all_lapse %>% 
  filter(n > 40) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  rename(n_lapses = n) %>% 
  left_join(notes %>% select(subid, notes_ema), by = "subid") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


Participants with no lapses    
`r nrow(count(subset(ema_all, subid != "test" & !subid %in% ema_all_lapse$subid), subid))` subids have no lapses
```{r}
ema_all %>% 
  filter(subid != "test") %>% 
  count(subid) %>% 
  filter(!subid %in% ema_all_lapse$subid) %>% 
  select(subid) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  left_join(notes %>% select(subid, notes_ema), by = "subid") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### 13-Point (0-12) Likert Scale Questions

"How intense was your greatest urge to drink alcohol?"
```{r}
ema_all %>% 
  tabyl(ema_2_1)
```


"Did you encounter any risky situations (people, places, or things)?  If yes, rate the intensity of the situation. If you experienced more than one risky situation, rate the most intense one."
```{r}
ema_all %>% 
  tabyl(ema_3_1)
```

"Has a hassle or stressful event occurred? If yes, rate the intensity of the event. If you experienced more than one hassle or stressful event, rate the most intense one."
```{r}
ema_all %>% 
  tabyl(ema_4_1)
```


"Has a pleasant or positive event occurred? If yes, rate the intensity of the event. If you experienced more than one pleasant or positive event, rate the most intense one."
```{r}
ema_all %>% 
  tabyl(ema_5_1)
```

#### 11-Point (1-11) Likert Scale Questions

"How are you feeling right now? Unpleasant/unhappy - Pleasant/happy"
```{r}
ema_all %>% 
  tabyl(ema_6_1)
```


"How are you feeling right now? Calm/sleepy - Aroused/alert"
```{r}
ema_all %>% 
  tabyl(ema_7_1)
```


"How likely are you to encounter risky situations (people, places, or things) within the next week?" (moring EMA only)
```{r}
ema_all %>% 
  filter(ema_type == "morning") %>% 
  tabyl(ema_8_1)
```

"How likely are you to encounter a stressful event within the next week?" (morning EMA only)
```{r}
ema_all %>% 
  filter(ema_type == "morning") %>% 
  tabyl(ema_9_1)
```

"How likely are you to drink any alcohol within the next week?" (morning EMA only)
```{r}
ema_all %>% 
  filter(ema_type == "morning") %>% 
  tabyl(ema_10_1)
```



### Write csvs

```{r}
ema_morning %>%
  write_csv(file.path(path_shared, "ema_morning.csv"))

ema_later %>%
  write_csv(file.path(path_shared, "ema_later.csv"))
```
