---
title: "Contacts"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Notes
Purpose: This file reads in all individual excel contact files from participants' raw data folders and creates an aggregate data file. Light EDA is also included as part of this cleaning script.   

Inputs:   
[subid]_Contacts.xlsx   

Output:   
contacts.csv  

### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},
        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          # temporary directory to use check country code function not merged into production version
          path_lab_support <- "~/lab_support"})
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
# conflict_prefer("filter", "dplyr")
# conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(readxl)
library(lubridate)
library(janitor)

theme_set(theme_classic())

source(file.path(path_lab_support, "fun_phone_numbers.R"))
```

Relative Paths
```{r}
path_log <- "shared/notes"
```

### Create function
```{r}
read_contacts <- function(subid) {
    filepath <- list.files(file.path(path_raw, subid), pattern = "Contacts", include.dirs = FALSE, full.names = TRUE)
    if(length(filepath) > 0) {
      contacts <- read_excel(filepath) %>% 
             mutate(across(everything(), as.character), # for merging
                    subid = as.numeric(subid)) 
      return(contacts)
    }
}
```

### Get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```

### Read in data and glimpse
```{r}
contacts <- map_df(subids$subid, ~read_contacts(.)) %>% 
  glimpse()
```


<br>


### Clean data from log
cleaning function
```{r}
clean_contacts <- function(d, log){
  # recode_one log entries
  log_recode_one <- dplyr::filter(log, log_action == "recode_one")

  for (i in seq_along(log_recode_one$index)){

    log_subid <- pluck(log_recode_one, "subid", i)
    log_var_name <- pluck(log_recode_one, "var_name", i)
    log_new_value <- pluck(log_recode_one, "new_value", i)
    log_old_value <- pluck(log_recode_one, "old_value", i)

    # pull out row id
    if (is.na(log_old_value)) {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(is.na(get(log_var_name))) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    } else {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    }
    
    # check that only one matching data row
    if (length(row_id) != 1) {
      stop("Rows matching subid: ", log_subid, " does not equal 1")
    }

    # make change to rowid
    if (is.numeric(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.numeric(log_new_value)
    if (is_character(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.character(log_new_value)
    if (is.POSIXt(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as_datetime(log_new_value)

  }

  # recode_all log entries
  # Involves changing recurrent typo patterns in variable response labels
  log_recode_all <- dplyr::filter(log, log_action == "recode_all")

  for (i in seq_along(log_recode_all$index)){

    log_var_name <- pluck(log_recode_all, "var_name", i)
    log_new_value <- pluck(log_recode_all, "new_value", i)
    log_old_value <- pluck(log_recode_all, "old_value", i)

    # pull out row ids that need to be recoded
    row_ids <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)

    for (i in seq_along(row_ids)) {

      if (is.numeric(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.numeric(log_new_value)
      if (is_character(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.character(log_new_value)
      if (is.POSIXt(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as_datetime(log_new_value)
    }
  }
  
  # remove log entries
  # match on subid, utc, var_name and remove_on values
  log_remove <- dplyr::filter(log, log_action == "remove")

  for (i in seq_along(log_remove$index)){

    log_subid <- pluck(log_remove, "subid", i)
    log_utc <- pluck(log_remove, "utc", i)
    log_var_1_name <- pluck(log_remove, "var_name", i)
    log_var_1_value <- pluck(log_remove, "old_value", i)
    log_var_2_name <- pluck(log_remove, "remove_on", i)
    log_var_2_value <- pluck(log_remove, "remove_on_value", i)
    

    # pull out row_id
     if (is.na(log_var_1_value) && is.na(log_var_2_value)) {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(UTC == log_utc) %>%
      dplyr::filter(is.na(get(log_var_1_name)) & is.na(get(log_var_2_name))) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    } else if (is.na(log_var_1_value) && !is.na(log_var_2_value)) {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(UTC == log_utc) %>%
      dplyr::filter(is.na(get(log_var_1_name)) & get(log_var_2_name) == log_var_2_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    } else if (!is.na(log_var_1_value) && is.na(log_var_2_value)) {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(UTC == log_utc) %>%
      dplyr::filter(is.na(get(log_var_2_name)) & get(log_var_1_name) == log_var_1_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    } else {
      row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(UTC == log_utc) %>%
      dplyr::filter(get(log_var_1_name) == log_var_1_value) %>%
      dplyr::filter(get(log_var_2_name) == log_var_2_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    }
    
    # check that only one matching data row
    if (length(row_id) != 1) {
      stop("Rows matching subid: ", log_subid, " does not equal 1")
    }

    # filter out row id
    d <- d %>% 
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(row_number != row_id) %>% 
      select(-row_number)
  }
  
  return(d)
}
```

read in log and summarize
```{r}
log <- read_csv(here(path_log, "log_contacts.csv"), col_types = cols()) %>%
  rowid_to_column("index") %>%
  glimpse()

# view log actions
table(log$log_action)

# print remove entries
log %>%
  dplyr::filter(log_action == "remove") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed"))

# print note entries
log %>%
  dplyr::filter(log_action == "note") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed"))
```

clean data
```{r}
contacts <- contacts %>%
  clean_contacts(., log) %>%
  glimpse()
```


### tidy data
Tidy variable names
```{r}
contacts <- contacts %>%
  clean_names() %>%
  glimpse()
```


Check for any context entries with no associated numbers
```{r}
contacts %>%
  dplyr::filter(is.na(home_phone) & is.na(cell_phone) & is.na(other_phone1) & is.na(other_phone2)) 
```

Check how many entries have more than one number
```{r}
contacts_wide <- contacts

n_numbers <- contacts %>% 
  mutate(home = if_else(is.na(home_phone), 0, 1),
         cell = if_else(is.na(cell_phone), 0, 1),
         other = if_else(is.na(other_phone1), 0, 1),
         other_2 = if_else(is.na(other_phone2), 0, 1)) %>% 
  rowwise() %>% 
  mutate(n_numbers = sum(home, cell, other, other_2)) %>% 
  select(home_phone:other_phone2, n_numbers)

n_numbers %>% 
  dplyr::filter(n_numbers != 1) %>% 
  print(n = Inf)
```

pivot longer and reorder variables   
We expect to have an additional `r sum(n_numbers$n_numbers) - nrow(contacts_wide)` rows added to the data frame, which is the total sum of numbers (`r sum(n_numbers$n_numbers)`) minus the number of contacts/rows in wide tibble (`r nrow(contacts_wide)`).
```{r}
contacts <- contacts %>%
  pivot_longer(home_phone:other_phone2, names_to = "phone_type", values_to = "phone_number") %>%
  dplyr::filter(!is.na(phone_number)) %>%
  select(subid, utc, contact_type = type, phone_type, phone_number, contact_drank_past:state, utc) %>%
  glimpse()
```

`r nrow(contacts) - nrow(contacts_wide)` new rows added   

<br>


### EDA

#### Check for missing contact files

Read in visit dates
```{r}
visit_dates <- read_csv(file.path(path_shared, "visit_dates.csv"), col_types = cols()) %>% 
  glimpse()
```

**170 participants completed intake visit**
```{r}
visit_dates %>% 
  dplyr::filter(!is.na(intake))
```

**We have contact information for `r length(unique(contacts$subid))` subids.**     

**Subids 8 and 235 completed intake but do not have a contacts file**     
```{r}
notes <- read_csv(file.path(path_raw, "raw_notes.csv"), col_types = cols()) %>%
  select(subid, notes_general)

visit_dates %>%
  dplyr::filter(!is.na(intake)) %>%
  dplyr::filter(!subid %in% as.numeric(contacts$subid))

notes %>%
  dplyr::filter(subid %in% c(8, 235)) %>%
  kbl() %>%
  kable_styling()
```


**Subid 67 has contacts but never completed intake/started study** (leaving contacts in because they will be filtered out at the study-level depending on final sample)
```{r}
intake <- visit_dates %>%
  dplyr::filter(!is.na(intake))
contacts %>%
  dplyr::filter(!as.numeric(subid) %in% intake$subid)

visit_dates %>%
  dplyr::filter(subid == 67)

notes %>%
  dplyr::filter(subid == 67) %>%
  kbl() %>%
  kable_styling()
```


#### Check for duplicate entries
9 entries were identical on every variable except UTC - these are filtered out
```{r}
glimpse(contacts)

# filter out identical entries
contacts <- contacts %>%
  distinct(across(-utc), .keep_all = TRUE) %>% 
  glimpse()
```

Duplicate numbers and discrepancies still exist.  
```{r}
# count duplicate numbers listed for each subid
duplicates <- contacts %>%
  group_by(subid, phone_number) %>%
  summarise(n = n(), .groups = "drop") %>%
  dplyr::filter(n > 1)
```

`r nrow(duplicates)` subid/phone_number duplicates   
```{r}
print(duplicates, n = Inf)
```

Some duplicates represent errors in data/poor data quality (2 entries on same date with discrepant answers) and some are not errors (updating address, home phone number belongs to 2 parents, etc.)     

FIX: Need to handle at study-level
```{r}
contacts %>%
  dplyr::filter(phone_number %in% duplicates$phone_number & subid %in% duplicates$subid) %>%
  arrange(subid, phone_number) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  scroll_box(width = "100%", height = "500px")
```


<br>

#### Missing data

Convert text string NA's to NA
```{r}
contacts <- contacts %>% 
  naniar::replace_with_na_if(.predicate = is.character, condition = ~.x == "NA")
```

```{r}
naniar::miss_var_summary(contacts)
```

1 Missing phone number noted in cleaning log
```{r}
log %>% 
  dplyr::filter(subid == 81, log_action == "note") %>% 
  select(subid, log_action, notes) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%")
```


<br>


3 missing contact type values, despite full context information available
```{r}
contacts %>%
  dplyr::filter(is.na(contact_type)) %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  column_spec(3, color = "red") %>%
  scroll_box(width = "100%")
```

Check if numbers with missing contact type have duplicate entries   
Only one entry for each number
```{r}
missing_type <- contacts %>%
  dplyr::filter(is.na(contact_type)) %>% 
  select(phone_number) %>% 
  unlist(use.names = FALSE)

contacts %>% 
  dplyr::filter(phone_number %in% missing_type) %>% 
  group_by(subid, phone_number) %>% 
  summarise(n = n(), .groups = "drop")
```


Most missing context variables are self, other or spam entries - still a considerable amount of missing values for co-workers and family-other
```{r}
contacts %>%
  dplyr::filter(is.na(recovery)) %>%
  dplyr::filter(contact_type != "Self" & contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  scroll_box(width = "100%", height = "500px")
```

Check if duplicate entries for these numbers exist  
No duplicates exist
```{r}
missing_context <- contacts %>%
  dplyr::filter(is.na(recovery)) %>%
  dplyr::filter(contact_type != "Self" & contact_type != "Irrelevant/Spam" & contact_type != "Other") %>%
  select(phone_number) %>% 
  unlist(use.names = FALSE)

contacts %>% 
  dplyr::filter(phone_number %in% missing_context) %>% 
  group_by(subid, phone_number) %>% 
  summarise(n = n(), .groups = "drop")
```


<br>

#### contact type

```{r}
contacts %>%
  tabyl(contact_type)
```

<br>

#### Phone numbers

Raw number format
```{r}
contacts %>%
  dplyr::filter(!is.na(phone_number)) %>%
  select(phone_number) %>%
  print(n = Inf)
```

Check for non-numeric characters
```{r}
contacts %>%
  dplyr::filter(str_detect(phone_number, "[[:space:][:punct:][:alpha:]]")) %>%
  select(phone_number)
```

Numbers not 10 digits
```{r}
contacts %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  print(n = Inf)
```

Filter out short codes
```{r}
contacts %>%
  select(subid, phone_number, contact_type) %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  dplyr::filter(str_length(phone_number) != 5 & str_length(phone_number) != 6) %>%
  print(n = Inf)
```

Check country code on these numbers
```{r}
numbers <- contacts %>%
  dplyr::filter(str_length(phone_number) != 10) %>%
  dplyr::filter(str_length(phone_number) != 5 & str_length(phone_number) != 6) %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)

valid_country_code <- NULL

for (i in 1:length(numbers)) {
  if(check_country_code(numbers[i])) {
     valid_country_code <- append(valid_country_code, numbers[i])
  }
}

valid_country_code
```
**All known contacts (i.e., not irrelevant/spam) are valid international numbers**   
- 57 = columbia   
- 91 = India   
- 800050001020 is a health insurance scammer according to Google 

Check area code for all 10 digit numbers
Print numbers without valid area code
```{r}
numbers <- contacts %>%
  dplyr::filter(str_length(phone_number) == 10) %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)

not_valid_area_code <- NULL

for (i in 1:length(numbers)) {
  if(!check_area_code(numbers[i])) {
     not_valid_area_code <- append(not_valid_area_code, numbers[i])
  }
}
```

`r length(not_valid_area_code)` out of `r length(numbers)` 10 digit numbers don't have a valid North American area code.
```{r}
contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  select(subid, phone_number, contact_type) %>%
  print(n = Inf)

# filter out spam and irrelevant/spam numbers
numbers <- contacts %>%
  dplyr::filter(phone_number %in% not_valid_area_code) %>%
  dplyr::filter(contact_type != "Irrelevant/Spam") %>%
  select(phone_number) %>%
  unlist(use.names = FALSE)
```


`r length(numbers)` are known contacts
```{r}
contacts %>%
  dplyr::filter(phone_number %in% numbers) %>%
  select(subid, phone_number, contact_type) %>%
  print(n = Inf)
```


Check if any are international numbers
```{r}
valid_country_code <- NULL

for (i in 1:length(not_valid_area_code)) {
  if(check_country_code(not_valid_area_code[i])) {
     valid_country_code <- append(valid_country_code, not_valid_area_code[i])
  }
}

valid_country_code
```

Since 47 number is a 10 digit number check to see if it appears in logs
```{r}
# read in voice and SMS logs
voice_logs <- read_csv(file.path(path_shared, "voice_android.csv"), col_types = "icnTccccTT") 
sms_logs <- read_csv(file.path(path_shared, "sms_android.csv"), col_types = "icicTiccccciiicccTT") 

logs_76 <- voice_logs %>% 
  dplyr::filter(subid == 76) %>% 
  select(number) %>% 
  bind_rows(sms_logs %>% 
              dplyr::filter(subid == 76) %>% 
              select(number = address)) %>% 
  group_by(number) %>% 
  slice(1) %>% 
  ungroup()

logs_76$number_formatted <- purrr::map_chr(logs_76$number, extract_number)

logs_76 %>% 
  dplyr::filter(str_detect(number, "4745227703"))
```

* 47 number is in logs and passed country code check as a valid number for Norway      
* 49 is the country code for Germany but there are too few digits 

subid 87 never made it to followup 1 so no logs to check the 49 number
```{r}
visit_dates %>% 
  dplyr::filter(subid == 87)
```

<br>

#### Monthly visit
NOTE: monthly visit means participant visits home of contact at least monthly
```{r}
contacts %>%
  tabyl(monthly_visit)
```

Should have been gathering addresses when monthly_visit = yes
We have addresses for all but 11 of the contacts who participants visited monthly
```{r}
contacts %>%
  dplyr::filter(monthly_visit == "Yes") %>%
  count(!is.na(street_address))

contacts %>%
  dplyr::filter(monthly_visit == "Yes") %>%
  dplyr::filter(!is.na(street_address)) %>%
  select(subid, contact_type, street_address, city, state) %>%
  print(n = Inf)
```

Locations for other contacts
We only have 6 address for contacts that don't have monthly_visit as yes
```{r}
contacts %>%
  dplyr::filter(monthly_visit == "No" | is.na(monthly_visit)) %>%
  count(!is.na(street_address))
```

<br>

#### Context variables

```{r}
contacts %>%
  tabyl(contact_drank_past)

contacts %>%
  tabyl(drink_status)

contacts %>%
  tabyl(contact_drink_future)

contacts %>%
  tabyl(recovery)

contacts %>%
  tabyl(support_status)

contacts %>%
  tabyl(contact_experience)
```

FIX: unpleasant/mixed is not a valid response option - error, but not enough info to resolve? (note entry in log)
```{r}
contacts %>%
  dplyr::filter(contact_experience == "Unpleasant/mixed") %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("condensed", "striped")) %>%
  column_spec(11, color = "red") %>%
  scroll_box(width = "100%")
```

<br>

#### Other Distributions

Number of contacts per subid
NOTE: this should be interpreted as number of unique phone numbers per participant since this plot is not accounting for the fact that contacts could have more than one number (e.g., home, cell, work)
```{r message = FALSE}
contacts %>%
  group_by(subid) %>%
  summarise(n_contacts = length(unique(phone_number))) %>%
  ggplot(aes(x = n_contacts)) +
  geom_histogram(color = "black", fill = "light grey", bins = 20) +
  labs(title = "Number of contacts per participant") +
  geom_vline(aes(xintercept = mean(n_contacts)), contacts %>%
               group_by(subid) %>%
               summarise(n_contacts = length(unique(phone_number))), linetype = "dashed")
```

Min, max, and average number of contacts per subid
```{r}
contacts %>%
  group_by(subid) %>%
  summarise(n_contacts = length(unique(phone_number))) %>%
  summarise(min = min(n_contacts),
            max = max(n_contacts),
            mean = mean(n_contacts))
```

Number of contacts per subid faceted by spam vs not spam
```{r message = FALSE}
contacts %>%
  mutate(spam = case_when(contact_type == "Irrelevant/Spam" ~ "spam",
                          TRUE ~ "known contact")) %>%
  group_by(subid, spam) %>%
  summarise(n_contacts = length(unique(phone_number)), .groups = "drop") %>%
  ggplot(aes(x = n_contacts)) +
  geom_histogram(color = "black", fill = "light grey", bins = 20) +
  facet_wrap(~ spam) +
  labs(title = "Number of contacts per participant",
       x = "Number of contacts",
       y = "Number of participants") +
  geom_vline(aes(xintercept = mean(n_contacts)), contacts %>%
               mutate(spam = case_when(contact_type == "Irrelevant/Spam" ~ "spam",
                          TRUE ~ "known contact")) %>%
               group_by(subid, spam) %>%
               summarise(n_contacts = length(unique(phone_number)), .groups = "drop"), linetype = "dashed")
```


<br>

### Write CSV
```{r}
write_csv(contacts, file.path(path_shared, "contacts.csv")) %>%
  glimpse()
```

<br>
