---
title: "IOS/Voice Logs"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

### Notes
Purpose: This script contains code to open and merge all voice log files in sql and csv format from participants raw data folders. This is a study-level clean script so cleaning is minimal. Errors that don't have an obvious solution are highlighted in this clean script but are not corrected for. These will need to be corrected during pre-processing at the study-level.   

Inputs:   
[subid]_Voice_1.sql  
[subid]_Voice_2.sql  
[subid]_Voice_3.sql  
etc. for as many voice sql logs in the subid's folder  


### Setup
```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths 
```{r}
path_raw <- "Z:/studydata/risk/data_raw"
path_out <- "Z:/studydata/risk/data_processed/shared"
```

Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(RSQLite)
library(lubridate)
library(janitor)

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


### Read in data 

#### Create function to read in subid logs

```{r}
read_sql <- function(subid) {
    logs <- tibble(subid = character(),
                   message = character())
    log_files <- list.files(file.path(path_raw, subid), pattern = "Voice", include.dirs = FALSE)
    # subids 1-15 have a RawSMSVoice folder in addition to SQL logs - not including this folder 
    log_files <- discard(log_files, log_files == "RawSMSVoice")
    if(length(log_files) > 0) {
      for(file in log_files) {
        if(str_detect(file,'.sql')) {
          path <- file.path(path_raw, subid, file)
          log_db <- dbConnect(RSQLite::SQLite(), path)
          
          log <- dbGetQuery(log_db,'select * from ZCALLRECORD')
          
          # Add subid and log information to dataframe
          log <- log %>% 
            mutate(subid = subid,
                   log_file = file,
                   created = file.info(path)$ctime,
                   modified = file.info(path)$mtime)
          
          # Update ZAddress to text instead of blob SQL object
          address <-  dbGetQuery(log_db,'select cast(ZADDRESS as text) from ZCALLRECORD')
          log <- log %>% 
            mutate(ZADDRESS = unlist(address)) %>% 
            # converting disconnected and face_time variable to character
            # most logs are all numeric but at least one log has a character string in column
            mutate(ZDISCONNECTED_CAUSE = as.character(ZDISCONNECTED_CAUSE),
                   ZFACE_TIME_DATA = as.character(ZFACE_TIME_DATA))
          
            # convert binary objects for new variables in more recent SQL files to character
            if("ZLOCALPARTICIPANTUUID" %in% names(log)) {
              ZLOCALPARTICIPANTUUID_2 <-  
                dbGetQuery(log_db,'select cast(ZLOCALPARTICIPANTUUID as text) from ZCALLRECORD') %>% 
                unlist()
              ZOUTGOINGLOCALPARTICIPANTUUID_2 <-  
                dbGetQuery(log_db,'select cast(ZOUTGOINGLOCALPARTICIPANTUUID as text) from ZCALLRECORD') %>%
                unlist()
              ZLOCAL_ADDRESS_2 <-  dbGetQuery(log_db,'select cast(ZLOCAL_ADDRESS as text) from ZCALLRECORD') %>%
                unlist()
              log <- log %>% 
                mutate(ZLOCALPARTICIPANTUUID = ZLOCALPARTICIPANTUUID_2,
                       ZOUTGOINGLOCALPARTICIPANTUUID = ZOUTGOINGLOCALPARTICIPANTUUID_2,
                       ZLOCAL_ADDRESS = ZLOCAL_ADDRESS_2)
            }
          
          #close the db connection
          dbDisconnect(log_db)
    
                  
           # Join log files
          logs <- logs %>% 
            full_join(log)
          
        }
         
        if(nrow(logs) == 0) {
          extension <- str_extract(log_files[1], "[^.]*$")
          logs <- logs %>% add_row(subid = subid, message = str_c("Log files in ", extension, " format"))
        }
      }
      return(logs)
    } else if(length(log_files) == 0){
        logs <- logs %>% add_row(subid = subid, message = "No log files found")
        return(logs)
    }
}
```

#### get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```


#### read in sql logs
```{r message = FALSE}
all_logs <- tibble(subid = character())
all_logs <- map_df(subids$subid, ~read_sql(.)) %>% 
  glimpse()
```

FIX: Warning message explains that it is coercing a mixed type variable containing integers to string. I can cast this column as a character during SQL query but it gets complicated because then I can't just select all (*) and I might miss a newly appearing variable. Keeping this with warning until better fix is determined. Will carefully check ZFACE_TIME_DATA variable during EDA below.   
FIX: New binary objects appearing in more recent SQL files (ZLOCALPARTICIPANTUUID, ZOUTGOINGLOCALPARTICIPANTUUID, ZLOCAL_ADDRESS). 100% are missing values for ZLOCAL_ADDRESS and UUID variables do not seem to contain relevant info. Keeping variables for closer inspection with EDA. Also found 2 new tables in later SQL files - need to look more into these tables. They don't seem notably important from first looks.     


#### Separate logs and messages
```{r}
log_messages <- all_logs %>% 
  filter(!is.na(message)) %>% 
  select(subid, message)
table(log_messages$message)

logs_ios <- all_logs %>% 
  filter(is.na(message)) %>% 
  # removing my temp message variable for documenting subids without SQL logs
  select(-message) %>% 
  glimpse()
```


### Read in CSV logs (IOS 13+)

```{r}
read_csv <- function(subid) {
    logs <- tibble(subid = character())
    log_files <- list.files(file.path(path_raw, subid), pattern = "Voice", include.dirs = FALSE)
    # subids 1-15 have a RawSMSVoice folder in addition to SQL logs - not including this folder 
    log_files <- discard(log_files, log_files == "RawSMSVoice")
    if(length(log_files) > 0) {
      for(file in log_files) {
        if(str_detect(file,'.xls')) {
          path <- file.path(path_raw, subid, file)
          log <- readxl::read_excel(file.path(path)) %>% 
            mutate(subid = subid,
                   # convert to character for merging
                   Number = as.character(Number),
                   log_file = file,
                   created = file.info(path)$ctime,
                   modified = file.info(path)$mtime) 
        
           # Join log files
          logs <- logs %>% 
            full_join(log)
        }
        if(nrow(logs) > 0) {
        return(logs)
        }
      }
    }
}
```

#### Read in csv logs
```{r message = FALSE}
csv_logs <- tibble(subid = character())
csv_logs <- map_df(subids$subid, ~read_csv(.)) %>% 
  glimpse()
```


CSV logs don't have many of the variables that SQL has.   


### Join csv and sql files

Update SQL logs for merge
```{r}
glimpse(logs_ios)

logs_ios <- logs_ios %>%
  # convert date to utc date time object
  mutate(ZDATE = ZDATE + 978307200,
         ZDATE = as_datetime(ZDATE, tz = "UTC")) %>% 
  # recode variables as strings to match csv
  mutate(ZCALLTYPE = case_when(ZCALLTYPE == 8 ~ "FaceTime Audio",
                               ZCALLTYPE == 16 ~ "FaceTime Video",
                               ZCALLTYPE == 1 ~ "Phone",
                               TRUE ~ as.character(ZCALLTYPE)),
         ZORIGINATED = case_when(ZORIGINATED == 0 ~ "Incoming",
                                 ZORIGINATED == 1 ~ "Outgoing",
                                 TRUE ~ as.character(ZORIGINATED))) %>% 
  select(subid, ZDATE, everything()) %>% 
  glimpse()
```

Prepare CSV logs for merge
```{r}
csv_logs <- csv_logs %>% 
  rename(ZDATE = Date,
         ZADDRESS = Number,
         ZLOCATION = Location,
         ZCALLTYPE = Service,
         ZDURATION = Duration,
         ZNAME = Contact,
         ZORIGINATED = `Call type`) %>% 
  mutate(# fix format of duration to seconds 
         ZDURATION = as.numeric(ZDURATION - as_datetime("1899-12-31 00:00:00"))) %>% 
  glimpse()
```

Join
```{r}
logs_ios <- logs_ios %>% 
  full_join(csv_logs,  by = c("subid", "ZDATE", "ZCALLTYPE", "ZORIGINATED", "ZDURATION", 
                              "ZLOCATION", "ZNAME", "ZADDRESS", "log_file", "created", 
                              "modified")) %>% 
  glimpse()
```


#### Replace blank character cells with NA
```{r}
logs_ios <- logs_ios %>% 
  mutate(across(where(is.character), ~na_if(., ""))) %>% 
  glimpse()
```

#### Remove duplicates
Match on everything except log related info (file name, created/modified date)
```{r}
logs_ios <- logs_ios %>% 
  distinct(across(-c(log_file, created, modified, ZLOCALPARTICIPANTUUID, ZOUTGOINGLOCALPARTICIPANTUUID,
                     Z_OPT, Z_PK)), .keep_all = TRUE) %>% 
  glimpse()
```



### EDA

`r length(unique(logs_ios$subid))` subids had SQL/CSV voice data logs read in.   
`r nrow(subset(log_messages, message == "No log files found"))` subids did not have logs.  
`r nrow(subset(log_messages, message != "No log files found"))` subids had logs but not in SQL format.    

This accounts for a total of 216 participants.  

#### missing data
```{r}
logs_ios %>% 
  naniar::miss_var_summary() %>% 
  print(n = Inf)
```

100% missing values for 3 variables - remove them  
```{r}
logs_ios <- logs_ios %>% 
  select(-c(ZDISCONNECTED_CAUSE, ZDEVICE_ID, ZLOCAL_ADDRESS))
```

Variables with 1040 missing values are all due to csv files not having these variables.   


#### Dates

Dates range from `r min(logs_ios$ZDATE)` to `r max(logs_ios$ZDATE)`

FIX: 2 dates are out of study range (2024) - not sure why 
```{r}
logs_ios %>% 
  arrange(desc(ZDATE)) %>% 
  head(50)
```

Both are from same participant on their first log  
```{r}
logs_ios %>% 
  arrange(desc(ZDATE)) %>% 
  slice(1:2) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed")) %>% 
  scroll_box(width = "100%")
```


look at raw log entries - date incorrectly encoded (UTC begins with 7 instead of 5) so no way to recover actual date.
```{r message = FALSE}
logs_163 <- read_sql("163")

logs_163 %>% 
  filter(log_file == "163_Voice_1.sql") %>% 
  arrange(desc(ZDATE)) %>% 
  select(subid, ZDATE, everything()) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px", width = "100%")
```



#### Phone number (ZADDRESS)

Missing phone numbers by subid
```{r}
logs_ios %>% 
  filter(is.na(ZADDRESS)) %>% 
  count(subid) %>% 
  arrange(desc(n)) %>% 
  print(n = Inf)
```

raw numbers 
```{r}
logs_ios %>% 
  select(ZADDRESS) %>% 
  print(n = Inf)
```


#### ZNUMBER_AVAILABILITY

Note: Looks like when number_availability = 1 or 2 then there is no phone number (blocked and unknown numbers). Need to confirm which is which     


0 = number known   
1 =   
2 =   


```{r}
logs_ios %>% 
  filter(is.na(ZADDRESS)) %>% 
  tabyl(ZNUMBER_AVAILABILITY)

logs_ios %>% 
  filter(!is.na(ZADDRESS)) %>% 
  tabyl(ZNUMBER_AVAILABILITY)
```


#### Country code
Missing ISO country codes are from csv logs which didn't have this as a variable.     
be = belgium; ca = canada; de = germany; mx = mexico; nz = new zealand; pe = peru; tr = turkey   
Source: https://www.nationsonline.org/oneworld/country_code_list.htm   
```{r}
tabyl(logs_ios$ZISO_COUNTRY_CODE)
```

NOTE: some non-us country codes are paired with us numbers - may indicate traveling?  
```{r}
logs_ios %>% 
  select(ZADDRESS, ZADDRESS, ZISO_COUNTRY_CODE) %>% 
  filter(ZISO_COUNTRY_CODE != "us") %>% 
  print(n = Inf)
```


#### ZLOCATION
```{r}
tabyl(all_logs$ZLOCATION) %>% 
  select(1:2) 
```


#### Z_ENT
```{r}
tabyl(logs_ios$Z_ENT)
```
NAs due to missing variable in CSV files   
Z_ENT is the identifier of the SQL table - all log info is coming from table ZCALLRECORD (table 2) so can remove this variable
```{r}
logs_ios <- logs_ios %>% 
  select(-Z_ENT)
```


#### Z_OPT
```{r}
tabyl(logs_ios$Z_OPT)
```

Z_OPT indicates the number of times an entity has been changed (starting with 1 when it is initially added to the database)

#### call type (ZCALLTYPE)
```{r}
tabyl(logs_ios$ZCALLTYPE)
```

0 = third party app call
```{r}
logs_ios %>% 
  filter(ZCALLTYPE == 0) %>% 
  tabyl(ZSERVICE_PROVIDER)

logs_ios <- logs_ios %>% 
  mutate(ZCALLTYPE = case_when(ZCALLTYPE == "0" ~ "Third Party App",
                               TRUE ~ ZCALLTYPE))

tabyl(logs_ios$ZCALLTYPE)
```



#### Facetime info (ZFACE_TIME_DATA)
```{r}
logs_ios %>% 
  filter(!is.na(ZFACE_TIME_DATA)) %>% 
  select(ZFACE_TIME_DATA, ZCALLTYPE, ZADDRESS)
```

Not sure what these data are yet, but matches onto FACETIME call type (8/16)   
**NOTE: 0 is not blank - should not be removed**  

#### answered vs rejected calls (ZANSWERED)
```{r}
tabyl(logs_ios$ZANSWERED)

logs_ios %>% 
  filter(ZANSWERED == 1) %>% 
  select(ZADDRESS, ZANSWERED, ZDURATION, ZORIGINATED)

logs_ios %>% 
  filter(ZANSWERED == 0) %>% 
  select(ZADDRESS, ZANSWERED, ZDURATION, ZORIGINATED)
```

0 = not answered (includes outgoing, missed, and rejected calls)   
1 = answered  
Missing values from csv files

```{r}
logs_ios <- logs_ios %>% 
  mutate(ZANSWERED = case_when(ZANSWERED == 1 ~ "Answered",
                               ZANSWERED == 0 ~ "Not Answered",
                               TRUE ~ as.character(ZANSWERED)))

tabyl(logs_ios$ZANSWERED)
```


#### incoming vs outgoing calls (ZORIGINATED)
```{r}
tabyl(logs_ios$ZORIGINATED)
```


#### duration of call in seconds (ZDURATION)
```{r}
psych::describe(logs_ios$ZDURATION)

logs_ios %>% 
  filter(ZDURATION == 0) %>% 
  tabyl(ZANSWERED)
```

FIX: Not sure how some calls that were incoming and answered have a duration of 0 seconds
```{r}
logs_ios %>% 
  filter(ZDURATION == 0) %>% 
  filter(ZANSWERED == "Answered") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


#### call read
```{r}
tabyl(logs_ios$ZREAD)
```


Calls that are not read are missed incoming calls
```{r}
logs_ios %>% 
  filter(ZREAD == 0) %>% 
  tabyl(ZANSWERED)

logs_ios %>% 
  filter(ZREAD == 0) %>% 
  tabyl(ZORIGINATED)

logs_ios %>% 
  filter(ZREAD == 0) %>% 
  tabyl(Z_OPT)
```

```{r}
logs_ios <- logs_ios %>% 
  mutate(ZREAD = case_when(ZREAD == 1 ~ "Read",
                           ZREAD == 0 ~ "Not Read",
                           TRUE ~ as.character(ZREAD)))

tabyl(logs_ios$ZREAD)
```

Missing values due to CSV files not containing this variable


#### call category
```{r}
logs_ios %>% 
  tabyl(ZCALL_CATEGORY)
```

Not yet sure what this one is    
```{r}
logs_ios %>% 
  filter(ZCALL_CATEGORY == 2) %>% 
  tabyl(ZCALLTYPE)

logs_ios %>% 
  filter(ZCALL_CATEGORY == 1) %>% 
  tabyl(ZCALLTYPE)
```


1 = ?  
2 = ?  


#### handle type
```{r}
logs_ios %>% 
  tabyl(ZHANDLE_TYPE)
```

0 seems to be related to missing number   
Handle type appears to be related to type of call and platform used. Likely not relevant.
```{r}
logs_ios %>% 
  filter(is.na(ZADDRESS)) %>% 
  tabyl(ZHANDLE_TYPE)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 1) %>% 
  tabyl(ZCALLTYPE)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 1) %>% 
  tabyl(ZSERVICE_PROVIDER)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 2) %>% 
  tabyl(ZCALLTYPE)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 2) %>% 
  tabyl(ZSERVICE_PROVIDER)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 3) %>% 
  tabyl(ZCALLTYPE)

logs_ios %>% 
  filter(ZHANDLE_TYPE == 3) %>% 
  tabyl(ZSERVICE_PROVIDER)
```


0 =   
1 =   
2 =   
3 =   

#### name
Name of contacts? Includes scam likely so may be display name or combination.
```{r}
logs_ios %>% 
  group_by(ZNAME) %>% 
  summarise(n = n()) %>% 
  print(n = Inf)
```

Not sure why some names are numbers. Number as name appears to be same as raw number.
```{r}
logs_ios %>% 
  filter(!is.na(ZNAME)) %>% 
  select(ZADDRESS, ZNAME) %>% 
  print(n = Inf)
```


#### service provider
Almost all calls through Apple - also some Facebook messenger calls
```{r}
logs_ios %>% 
  tabyl(ZSERVICE_PROVIDER)
```


#### unique id 
The unique ID tracks the entry, but we may have duplicates if someone listens to a voicemail after their first data download or views call log to see missed call. 
```{r}
logs_ios %>% 
  group_by(ZUNIQUE_ID) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) %>% 
  arrange(desc(n)) 
```

For example the read variable here changes       
```{r}
logs_ios %>% 
  filter(ZUNIQUE_ID == "0255BA8B-DF83-4827-A529-B3AFA3671796") %>% 
  kbl() %>% 
  kable_styling()
```

FIX: keep the first entry or have duplicate with different read value



#### Primary key
Not sure what value this has (seems to be more for SQL matching) - started investigating if it was a unique identifier (It is not). Not going to dig more into this right now.   

4 subids are missing primary keys because they had csv files where this variable did not exist
```{r}
logs_ios %>% 
  filter(is.na(Z_PK)) %>% 
  count(subid)
```

Check for duplicate keys within subid
```{r}
(dup_keys <- logs_ios %>% 
  count(subid, Z_PK) %>% 
  filter(n > 1)) %>% 
  print(n = Inf)
```

`r nrow(dup_keys)` duplicate keys.  
`r length(unique(dup_keys$subid))` subids have duplicate keys.   


FIX: Subid 37 looks problematic - They have 6 duplicate keys and date, location, uniqueID, and phone number all different   
**These are not repeated entries**
```{r}
logs_ios %>% 
  filter(subid == "037" & Z_PK == 3745) %>% 
  arrange(subid, Z_PK) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")

logs_ios %>% 
  filter(subid == "037" & Z_PK == 3765) %>% 
  arrange(subid, Z_PK) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```

Subid 100 also has 1 duplicate key with completely different entries
```{r}
logs_ios %>% 
  filter(subid == "100" & Z_PK == 39) %>% 
  arrange(subid, Z_PK) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(width = "100%")
```

<br>

#### UUID variables 
No idea what these are yet but do not seem relevant and there are only 42 unique entries.    

ZLOCALPARTICIPANTUUID         
```{r}
logs_ios %>% 
  group_by(ZLOCALPARTICIPANTUUID) %>% 
  summarise(n = n()) %>% 
  print(n = Inf)
```

ZOUTGOINGLOCALPARTICIPANTUUID 
```{r}
logs_ios %>% 
  group_by(ZOUTGOINGLOCALPARTICIPANTUUID) %>% 
  summarise(n = n()) %>% 
  print(n = Inf)
```

NOTE: removing for UUIDs for now
```{r}
logs_ios <- logs_ios %>% 
  select(-c(ZLOCALPARTICIPANTUUID, ZOUTGOINGLOCALPARTICIPANTUUID))
```



### Write CSV
```{r}
# Tidy variable names
logs_ios <- logs_ios %>% 
  janitor::clean_names()

write_csv(logs_ios, file.path(path_out, "voice_ios.csv")) %>% 
  glimpse()
```

Note: date saved as UTC

