---
title: "Clean and process location data from interviews"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/gps", 
      "/Volumes/private/studydata/risk/knits/gps")
    )
  })
---
### Code status

This script should use the cleaning log if needed
This script still needs improved EDA


### Notes

This script opens the individual raw excel files for frequent locations in the 
individual subject folders, merges them, and then does EDA.   Final clean, merged
file is saved in shared folder

### Set up Environment



Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Absolute paths
```{r, paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_processed/gps"
          path_shared <- "/Volumes/private/studydata/data_raw"
          path_lab_support <- "/Volumes/toolboxes/lab_support"}
        )
```

Relative Paths 
```{r}
path_log <- "shared/notes"
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}

# for data wrangling
library(tidyverse)  # always need this
library(janitor)
library(purrr)
library(readxl)

source(here("shared", "fun_risk.R"))  # for merge_excel_files()
```


### Import locations files
Import
```{r}
locations <- merge_excel_files("Locations", path_raw) %>% 
  relocate(subid) %>% 
  glimpse()
```

### EDA

TO DO


### Save final locations file

```{r}
locations %>% 
  write_csv(here(path_shared, "locations.csv"))
```
