---
title: "Clean and process location data from interviews"
author: "Hannah Moshontz & John Curtin"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
  toc: true 
  toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Code status

Under construction


### Notes

Purpose: This file does cleaning and basic processing of interview data.

Inputs:  Opens data files in path_raw

* subid_Locations.xlsx

Also opens log files in path_log

* log_locations.csv

Outputs: 

Next steps:
- need to apply any existing log files / corrections
- eda 
- update logs
- eda

### Setup

Functions
```{r}
import_w_subid <- function(xlsxfile){
  read_excel(xlsxfile) %>% 
    mutate(subid = str_extract(xlsxfile, "\\d\\d\\d"))
}

merge_raw_files <- function(file_suffix) {
  list.files(file.path(path_raw), 
           recursive = TRUE,
           pattern = paste0("\\d\\d\\d_", file_suffix, ".xlsx"),
           full.names = TRUE) %>% 
  as.list() %>% 
  set_names(str_extract(., "\\d\\d\\d")) %>% 
  map_df(~import_w_subid(.x) %>% 
           clean_names() %>% 
           mutate(across(everything(), as.character)))
}
```


Paths 
```{r}
path_raw <- "P:/studydata/risk/data_raw" 
path_log <- "./shared/notes"
path_processed <- "P:/studydata/risk/data_processed" 
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(purrr)
library(readxl)
```

### Import locations files
Import
```{r}
known_locations <- merge_raw_files("Locations") %>% 
  glimpse()
```




### Save final shared file

# FIX: This is a temp save b/c JJC needs this file.   We still need to do EDA before trusting these data!
```{r}
# known_locations %>% 
#   select(subid, utc, street_address, city, state, type, drank, alcohol, emotion, risk, avoid, vacation, lat, long) %>%   #added by JJC b.c of prob with extra columns
#   write_csv(file.path(path_shared, "locations.csv"))
```
