---
title: "Clean Audio Metadata"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Status

To do:

* merge the audio file meta data created here with the transcripts


To check:

* Not clear why there are duplicate entries on a single date. Possibly they thought the audio was not sending. Will investigate more at a later date. (see below)

To (possibly) improve:

* there are a lot of join messages.  Can that code be written to avoid those?
* Code runs REALLY slow.  Need to use future_map or foreach loops to speed it up but I have not figured out how to do this yet.  

### Notes
Purpose: This script gets metadata info regarding daily check in, such as number of days with audio, file names, and duration of audio clip.   

**Can add audio transcripts to this script at a later date**   


Inputs:  

* raw audio files


### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_out <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_out <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(lubridate)
library(av)
```


### Read in audio files

#### Function

```{r message = FALSE}
read_audio <- function(subid) {
  
  audio_log <- tibble(subid = character(), message = character())
  audio_files <- list.files(here(path_raw, subid, "Audio"))
  if(length(audio_files) > 0) {
    for(file in audio_files) {
      path <- here(path_raw, subid, "Audio", file)
      extension <- str_extract(path, "[^.]*$")
      
      # filter out non-audio files
      if(extension != "db" & extension != "lnk") {
        
        log <- tibble(subid = subid,
               audio_file_name = file,
               created = file.info(path)$ctime,
               modified = file.info(path)$mtime,
               
               # estimated duration of audio clip from bitrate
               duration = av_media_info(path)$duration) %>% 
          
               # extract date from file name
               mutate(date = str_trunc(audio_file_name, 13, "right", ellipsis = ""),
               date = str_trunc(date, 9, "left", ellipsis = ""),
               date = str_replace(date, "_", ""),
               date = ymd(date))

        audio_log <- audio_log %>%
          full_join(log) 
      } 
    }
    
  return(audio_log)
    
  } else if(length(audio_files) == 0) {
    audio_log <- audio_log %>% 
      add_row(subid = subid, message = "No audio files found")
    return(audio_log)
  }
}
```

#### Get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```


#### Read in all audio files
```{r message = FALSE}
all_audio <- tibble(subid = character())
all_audio <- map_df(subids$subid, ~read_audio(.)) %>% 
  glimpse()
```


### EDA 

```{r}
table(all_audio$message)

audio <- all_audio %>% 
  filter(is.na(message)) %>% 
  select(subid, date, duration, everything(), -message) %>% 
  glimpse()

no_audio <- all_audio %>% 
  filter(message == "No audio files found") %>% 
  select(subid, message) %>% 
  glimpse()
```

`r nrow(audio)` sleep observations from `r length(unique(audio$subid))` subids.  
`r length(unique(no_audio$subid))` subids have no audio files.   
*Subids with no audio were manually confirmed by checking raw data folders*   

Audio data ranges from `r min(audio$date)` to `r max(audio$date)`  


#### audio files per subid

```{r}
audio %>% 
  count(subid) %>% 
  ggplot(aes(x = n)) +
  geom_histogram(color = "black", fill = "light grey", bins = 20) +
  theme_classic() +
  labs(title = "Histogram of audio files per subid",
       x = "Number of audio files",
       y = "Number of subids")
```

more than 90 days worth of audio files
```{r, attr.output='style="max-height: 300px;"'}
audio %>% 
  count(subid) %>% 
  filter(n > 90)
```


#### check for duplicate dates

```{r, attr.output='style="max-height: 300px;"'}
audio %>% 
  count(subid, date) %>% 
  filter(n > 1) %>% 
  arrange(desc(n))
```

```{r, attr.output='style="max-height: 300px;"'}
audio %>% 
  filter(subid == 128) %>% 
  select(subid, date, duration) %>% 
  print(n = Inf)
```

FIX: Not clear why there are duplicate entries on a single date. Possibly they thought the audio was not sending. Will investigate more at a later date.  



#### Duration

Audio files range from `r min(audio$duration)` to `r max(audio$duration)` seconds in duration.    

```{r}
audio %>% 
  mutate(duration = case_when(duration > 120 ~ 120,
                              TRUE ~ duration)) %>% 
  ggplot(aes(x = duration)) +
  geom_histogram(color = "black", fill = "light grey", bins = 20) +
  theme_classic() +
  labs(title = "Histogram of length of audio files",
       x = "Duration (in seconds)",
       y = "Number of files")
```

files less than 5 seconds long
```{r}
short_audio <- audio %>% 
  filter(duration < 5) %>% 
  select(subid, date, duration) 
```

There are `r nrow(short_audio)` short audio files (less than 5 seconds long), but there is a clear pattern among subids.  
`r length(unique(short_audio$subid))` subids make up all the short audio clips.    
```{r, attr.output='style="max-height: 300px;"'}
print(short_audio, n = Inf)
```


### Write csv
```{r, attr.output='style="max-height: 300px;"'}
write_csv(audio, here(path_out, "audio_.csv")) %>% 
  glimpse()
```