---
title: "Clean and process raw data from interviews"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
  toc: true 
  toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Code Status
THIS FILE WILL BE PARSED INTO SEPARARE FILES FOR EACH DATA SOURCE WITH 
EDA ADDED FOR EACH FILE.  JJC HAS BEGUN TO DO THIS WITH THE LOCATIONS DATA SOURCE.

Kendra has completed contacts.   Much of the rest of this parsing still needs to be 
completed as we finalize cleaning of the RISK data

This fill will eventually be deleted

### Notes
Purpose: This file does cleaning and basic processing of interview data.

Inputs:  Opens data files in path_raw

* subid_Vacations.xlsx
* subid_Times.xlsx
* subid_Dates.xlsx
* subid_Locations.xlsx
* subid_Contacts.xlsx

Also opens log files in path_log

* log_vacations.csv
* log_times.csv
* log_dates.csv
* log_locations.csv
* log_contacts.csv

Outputs: 

Next steps:
- need to apply any existing log files / corrections
- eda 
- update logs
- eda

### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "hold",  message = FALSE)
```


Functions
```{r}
import_w_subid <- function(xlsxfile){
  read_excel(xlsxfile) %>% 
    mutate(subid = str_extract(xlsxfile, "\\d\\d\\d"))
}

merge_raw_files <- function(file_suffix) {
  list.files(file.path(path_raw), 
           recursive = TRUE,
           pattern = paste0("\\d\\d\\d_", file_suffix, ".xlsx"),
           full.names = TRUE) %>% 
  as.list() %>% 
  set_names(str_extract(., "\\d\\d\\d")) %>% 
  map_df(~import_w_subid(.x) %>% 
           clean_names() %>% 
           mutate(across(everything(), as.character)))
}
```


Paths 
```{r}
path_raw <- "./raw_data"
path_log <- "./analysis/shared/notes"
path_shared <- "./analysis/shared/data"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(purrr)
library(readxl)
```

### Reported Vacations

Import
```{r}
vacations <- merge_raw_files("Vacations") %>% 
  glimpse()
```

### Risky and protective times
Import
```{r}
times <- merge_raw_files("Times") %>% 
  glimpse()
```

Clearly an issue with the way that times were recorded. Will need to convert these to dttm.

### Risky and protective dates
Import
```{r}
dates <- merge_raw_files("Dates") %>% 
  glimpse()
```

### Known locations
Import
```{r}
known_locations <- merge_raw_files("Locations") %>% 
  glimpse()


# FIX: This is a temp save b/c JJC needs this file.   We still need to do EDA before trusting these data!
# known_locations %>% 
#   select(subid, utc, street_address, city, state, type, drank, alcohol, emotion, risk, avoid, vacation, lat, long) %>%   #added by JJC b.c of prob with extra columns
#   write_csv(file.path(path_shared, "locations.csv"))
```

### Known contacts 
Import
```{r}
known_contacts <- merge_raw_files("Contacts") %>% 
  glimpse()
```
