---
title: "Andriod/Voice Logs"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 2
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/shared", 
      "/Volumes/private/studydata/risk/knits/shared")
    )
  })
---

### Code Status

This script fully cleans the android voice logs with EDA.   

Outstanding issue to fix at study level:   
* One voice call has duration of -4 (invalid duration)   
* 8 subids have invalid type values. Online forums suggest that “some flavours of Android return haphazard integers.”     


### Notes
Purpose: This script contains code to open and merge all voice log files in xml format from participants raw data folders. This is a study-level clean script so cleaning is minimal. Errors that don't have an obvious solution are highlighted in this clean script but are not corrected for. These will need to be corrected during pre-processing at the study-level.     
 

Inputs:   
[subid]_Voice_1.xml  
[subid]_Voice_2.xml   
[subid]_Voice_3.xml  
etc. for as many voice xml logs in the subid's folder  


### Setup
Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"},
        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"})
```


Relative Paths
```{r}
path_log <- "shared/notes"
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(lubridate)
library(XML)
library(xml2)
```


### Android Voice Logs (XML) 

#### Create function to read in subid logs

```{r}
read_xml <- function(subid) {
    logs <- tibble(subid = character(),
                   message = character())
    log_files <- list.files(here(path_raw, subid), pattern = "Voice", include.dirs = FALSE)
    # subids 1-15 have a RawSMSVoice folder in addition to SQL logs - not including this folder 
    log_files <- discard(log_files, log_files == "RawSMSVoice")
    if(length(log_files) > 0) {
      for(file in log_files) {
        if(str_detect(file,'.xml')) {
          path <- here(path_raw, subid, file)
          
          # xml code adapted from Susan's fun_database script
          # use read_html instead of read_xml to avoid problem with emojis in contacts
          xml <- xml_children(read_html(here(path)))
 
          # fix for problem with nested list after switching to read_html()
          while (length(xml) == 1) {
            xml <- xml_children(xml) #loop to find lower level of xml children 
          }    

          log <- data.frame(
            number = xml_attr(xml,'number'),
            duration = xml_attr(xml,'duration'),
            date = xml_attr(xml,'date'),
            type = xml_attr(xml,'type'),
            presentation = xml_attr(xml,'presentation'),
            readable_date = xml_attr(xml,'readable_date'),
            contact_name = xml_attr(xml,'contact_name'),
            stringsAsFactors = FALSE)
          
          # Add subid and log information to dataframe
          log <- log %>% 
            mutate(subid = subid,
                   log_file = file,
                   created = file.info(path)$ctime,
                   modified = file.info(path)$mtime)
          
          # Join log files
          logs <- logs %>% 
            full_join(log)
        }
        if(nrow(logs) == 0) {
          extension <- str_extract(log_files[1], "[^.]*$")
          logs <- logs %>% add_row(subid = subid, message = str_c("Log files in ", extension, " format"))
        }
      }
      return(logs)
    } else if(length(log_files) == 0){
        logs <- logs %>% add_row(subid = subid, message = "No log files found")
        return(logs)
    }
}
```

#### get subids
```{r}
subids <- list.dirs(path_raw, recursive = FALSE, full.names = FALSE) %>% 
  keep(~ str_detect(.x, "([0-2][0-9][0-9])")) %>% 
  enframe(name = NULL, value = "subid")
```


#### read in all logs
```{r message = FALSE}
all_logs <- tibble(subid = character())
all_logs <- map_df(subids$subid, ~read_xml(.)) %>% 
  glimpse()
```

#### Separate logs and messages
```{r}
log_messages <- all_logs %>% 
  filter(!is.na(message)) %>% 
  select(subid, message)

table(log_messages$message)

all_logs <- all_logs %>% 
  filter(is.na(message)) %>%
  # removing my temp message variable for documenting subids without XML logs
  select(-message) %>% 
  glimpse()
```

#### Remove duplicates
```{r}
logs_android <- all_logs %>% 
  distinct(across(c(subid, number, duration, date, type, presentation)), .keep_all = TRUE) %>% 
  glimpse()
```

Check no unique log entries in all_logs missing from logs_android
```{r}
all_logs %>% 
  anti_join(logs_android, by = c("subid", "number", "duration", "date", "type", "presentation"))
```

Look at duplicates as a check      
*Only showing preview in knitted file because pandoc crashes with full table*
```{r}
dups <- all_logs %>% 
  add_count(subid, number, duration, date, type, presentation) %>% 
  filter(n > 1) %>% 
  select(-c(log_file, created, modified, n))

all_logs %>% 
  semi_join(dups, by = c("subid", "number", "duration", "date", "type", "presentation")) %>% 
  arrange(subid, number, duration, date, type, presentation) %>%
  head(n = 500) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Clean with cleaning log
cleaning function
```{r}
clean_logs <- function(d, log){
  # recode_one log entries
  log_recode_one <- dplyr::filter(log, log_action == "recode_one")

  for (i in seq_along(log_recode_one$index)){

    log_subid <- pluck(log_recode_one, "subid", i)
    log_date <- pluck(log_recode_one, "date", i)
    log_number <- pluck(log_recode_one, "number", i)
    log_var_name <- pluck(log_recode_one, "var_name", i)
    log_new_value <- pluck(log_recode_one, "new_value", i)
    log_old_value <- pluck(log_recode_one, "old_value", i)

    # pull out row id
    row_id <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      # match on subid, date, phone number, and old value
      dplyr::filter(subid == log_subid) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      dplyr::filter(date == log_date) %>%
      dplyr::filter(number == log_number) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)
    
    # check that only one matching data row
    if (length(row_id) != 1) {
      stop("Rows matching subid: ", log_subid, " does not equal 1")
    }

    # make change to rowid
    if (is.numeric(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.numeric(log_new_value)
    if (is_character(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as.character(log_new_value)
    if (is.POSIXt(d[[row_id, log_var_name]])) d[[row_id, log_var_name]] <- as_datetime(log_new_value)

  }
  
  # recode_all entries
  log_recode_all <- dplyr::filter(log, log_action == "recode_all")

  for (i in seq_along(log_recode_all$index)){

    log_var_name <- pluck(log_recode_all, "var_name", i)
    log_new_value <- pluck(log_recode_all, "new_value", i)
    log_old_value <- pluck(log_recode_all, "old_value", i)

    # pull out row ids that need to be recoded
    row_ids <- d %>%
      mutate(row_number = as.numeric(rownames(d))) %>%
      dplyr::filter(get(log_var_name) == log_old_value) %>%
      select(row_number) %>%
      unlist(use.names = FALSE)

    for (i in seq_along(row_ids)) {

      if (is.numeric(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.numeric(log_new_value)
      if (is_character(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as.character(log_new_value)
      if (is.POSIXt(d[[row_ids[i], log_var_name]])) d[[row_ids[i], log_var_name]] <- as_datetime(log_new_value)
    }
  }
  
  return(d)
}
```

read in log and summarize
```{r}
log <- vroom::vroom(here(path_log, "log_voice_android.csv"), col_types = "ccccccccc") %>%
  rowid_to_column("index") %>%
  glimpse()

# view log actions
table(log$log_action)
```

clean data
```{r}
logs_android <- logs_android %>%
  clean_logs(., log) %>%
  glimpse()
```



#### Convert utc to date time     
Check all dates encoded as 13 digit utc in milliseconds  
```{r}
logs_android %>% 
  filter(!nchar(date) == 13)
```

Check no missing date values
```{r}
logs_android %>% 
  filter(is.na(date))
```

Convert to date time object
```{r}
logs_android <- logs_android %>% 
  mutate(date = round(as.numeric(date)/1000, 0), 
         date = as_datetime(date, tz = "utc"))
```


#### Other data updates for eda

Check classes
```{r}
logs_android %>% 
  glimpse()
```

Convert int columns to numeric
```{r}
# check variables contain only integers
logs_android %>% 
  count(duration) %>% 
  print(n = Inf)
logs_android %>% 
  count(type)
logs_android %>% 
  count(presentation)

# convert to int class
logs_android <- logs_android %>% 
  mutate(duration = as.numeric(duration),
         type = as.numeric(type),
         presentation = as.numeric(presentation)) 
```

replace empty character cells with NA
```{r}
logs_android <- logs_android %>% 
  mutate(across(where(is.character), ~na_if(., "")))
```

Final glimpse
```{r}
logs_android %>% 
  glimpse()
```

<br>

### EDA

`r length(unique(logs_android$subid))` subids had xml voice data logs read in.   
`r nrow(subset(log_messages, message == "No log files found"))` subids did not have logs.  
`r nrow(subset(log_messages, message != "No log files found"))` subids had logs but not in XML format.    

This accounts for a total of 216 participants.  


#### missing data
```{r}
logs_android %>% 
  naniar::miss_var_summary()
```

<br>

#### dates
date ranges from `r min(logs_android$date)` to `r max(logs_android$date)`   

Check dates against readable_date variable   
```{r}
logs_android %>% 
  # convert readable date to date time object
  mutate(date_str = as_datetime(readable_date, tz = "America/Chicago", 
                                                   format = "%b %e, %Y %I:%M:%S %p")) %>% 
  # convert utc date to central time
  mutate(date = with_tz(date, tzone = "America/Chicago")) %>% 
  select(date, date_str)
```

Compare two date entries for discrepancies
```{r}
logs_android %>% 
  mutate(date_str = as_datetime(readable_date, tz = "America/Chicago", 
                                                   format = "%b %e, %Y %I:%M:%S %p"),
         date = with_tz(date, tzone = "America/Chicago"),
         diff = round(difftime(date, date_str, units = "mins"), 0)) %>%
  filter(diff != 0)
```

Date and times match. No longer need readable date.
```{r}
logs_android <- logs_android %>% 
  select(-readable_date) %>% 
  glimpse()
```

<br>

#### phone number

`r nrow(subset(logs_android, is.na(number)))` missing phone numbers   
All numbers correctly show the number was blocked (presentation = 2) or unknown by network (presentation = 3).   
```{r}
logs_android %>% 
  filter(is.na(number)) %>% 
  janitor::tabyl(presentation)
```

Seems like some subids get more blocked calls than others - all belong to 30 subids   
```{r}
logs_android %>% 
  filter(is.na(number)) %>% 
  count(subid) %>% 
  arrange(desc(n)) %>% 
  print(n = Inf)
```

Raw number format
```{r}
logs_android %>% 
  filter(!is.na(number)) %>% 
  select(number) %>% 
  print(n = Inf)
```

<br>



Non-US country codes 
```{r}
logs_android %>% 
  # remove spaces and dashes for count
  mutate(number = str_replace(number, "[[:space:]]", ""),
         number = str_replace_all(number, "-", "")) %>% 
  # remove us country codes
   mutate(number = case_when(str_detect(number, "\\+1") & nchar(number) == 12 ~ 
                               str_replace(number, "\\+1", ""),
                             TRUE ~ number)) %>% 
  filter(str_detect(number, "^\\+\\d*")) %>% 
  filter(nchar(number) > 11) %>% 
  select(number) %>% 
  print(n = Inf)
```


https://countrycode.org/   
91 = India  
32 = Belgium  
33 = France  
233 = Ghana  
60 = Malaysia   
47 = Norway  

<br>

numbers with less than 7 characters     
* 86 - calls voicemail for verizon phones   
```{r}
logs_android %>% 
  #exclude blocked numbers
  filter(number != "-1" & number != "-2") %>% 
  filter(str_length(number) < 7) %>% 
  count(number) %>% 
  arrange(desc(n)) %>% 
  print(n = Inf)
```


#### duration

Fix: one call duration is -4 seconds
```{r}
psych::describe(logs_android$duration)

logs_android %>% 
  filter(duration < 0) %>%
  kbl() %>% 
  kable_styling() %>% 
  column_spec(3, color = "red")
```

Calls with 0 seconds duration
```{r}
logs_android %>% 
  filter(duration == 0) %>% 
  janitor::tabyl(type)
```

```{r}
hist(logs_android$duration)
```


#### type
```{r}
janitor::tabyl(logs_android$type)
```
https://developer.android.com/reference/android/provider/CallLog.Calls#TYPE   
1 = incoming   
2 = outgoing   
3 = missed   
4 = voicemail
5 = rejected   
6 = blocked (automatically - block list)     
7 = answered externally (different device)   

FIX: it seems like these 7 are the only documented types and online forums suggest that "some flavours of Android return haphazard integers."    
**It looks like all 556 log entries with incorrect type integers belong to 8 subids**
```{r}
logs_android %>% 
  filter(type > 7) %>% 
  group_by(subid) %>% 
  summarise(n = n())
```

Add categorical labels
```{r}
logs_android <- logs_android %>% 
  mutate(type = case_when(type == 1 ~ "Incoming",
                          type == 2 ~ "Outgoing",
                          type == 3 ~ "Missed",
                          type == 4 ~ "Voicemail",
                          type == 5 ~ "Rejected",
                          type == 6 ~ "Blocked",
                          type == 7 ~ "Answered Externally",
                          TRUE ~ as.character(type)))
```



#### presentation
```{r}
table(logs_android$presentation)
```
https://developer.android.com/reference/android/provider/CallLog.Calls#PRESENTATION_ALLOWED  
1 = number displayed (presentation allowed)  
2 = number is blocked by user   
3 = number is not specified or unknown by network   
4 = payphone  

blocked numbers   
Number displayed as -2 or NA for blocked calls.   
```{r}
logs_android %>% 
  filter(presentation == 2) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")
```

Number displayed as -1 or NA for calls that are unknown by network.   
```{r}
logs_android %>% 
  filter(presentation == 3) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(height = "500px")
```

Add categorical labels
```{r}
logs_android <- logs_android %>% 
  mutate(presentation = case_when(presentation == 1 ~ "Displayed",
                                  presentation == 2 ~ "Blocked",
                                  presentation == 3 ~ "Unknown",
                                  presentation == 4 ~ "Payphone",
                                  TRUE ~ as.character(presentation)))
```



#### contact name
```{r}
logs_android %>% 
  group_by(contact_name) %>% 
  slice(1) %>% 
  select(contact_name) %>% 
  kbl() %>% 
  kable_styling() %>% 
  scroll_box(width = "50%", height = "500px")
```


#### log files
more than 3 logs
```{r}
logs_android %>% 
  group_by(subid) %>% 
  summarise(n_logs = length(unique(log_file))) %>% 
  filter(n_logs > 3)

logs_android %>% 
  filter(subid == "032") %>% 
  janitor::tabyl(log_file)

logs_android %>% 
  filter(subid == "052") %>% 
  janitor::tabyl(log_file)
```

subid 32 bought a new phone in the first month of the study and so we collected call/sms logs from both phones at Follow Up 1.  
subid 52 got a new phone while on study - likely explains extra log.   


log creation dates range from `r min(logs_android$created)` to `r max(logs_android$created)`.      
log modification dates range from `r min(logs_android$modified)` to `r max(logs_android$modified)`.   

Note: almost all of the logs have modification dates that precede the creation date. Not sure why this is.
```{r}
logs_android %>% 
  filter(modified < created)
```


### Write csv
```{r}
write_csv(logs_android, here(path_shared, "voice_android.csv")) %>% 
  glimpse()
```



