---
title: "Characterize best `r params$data_type` model for `r params$window` and lead = `r params$lead` and `r params$version`"
author: "John Curtin & Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
params:
  study: "ema"
  data_type: "all"
  cv: "kfold"
  window: "1week"
  lead: 0
  version: "v4"
---

### Code Status

In use with iterative improvement

### Notes
This is a generic script that reproduces the CV metrics for the best model configuration, calculates various performance metrics from that resampling, makes plots, and then fits the best config to the final sample to do feature importance.

This script is called by various studies, passing in the data_type, window, lead, and version.


### Set Up Environment

```{r}
study <- params$study
data_type <- params$data_type
cv <- params$cv
window <- params$window
lead <- params$lead 
version <- params$version
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("slice", "dplyr")
conflict_prefer("spec", "yardstick")
conflicts_prefer(ggplot2::`%+%`)
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(forcats)
# library(SHAPforxgboost)
#library(rstanarm)
library(tidyposterior)
library(tidyverse)
library(tidymodels)

theme_set(theme_classic()) 
```

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_input <- str_c("P:/studydata/risk/chtc/", study)
          path_processed <- str_c("P:/studydata/risk/data_processed/", study)
          path_models <- str_c("P:/studydata/risk/models/", study)},

        # IOS paths
        Darwin = {
          path_input <- str_c("/Volumes/private/studydata/risk/chtc/", study)
          path_processed <- str_c("/Volumes/private/studydata/risk/data_processed/", study)
          path_models <- str_c("/Volumes/private/studydata/risk/models/", study)}
        )
```


Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


Source training controls 
```{r source}
# EDA
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

# CHTC support functions
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/chtc/static_files/fun_chtc.R?raw=true")

# ML functions
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")

```


### Read in preds and metrics for best model

```{r load_preds_metrics}
preds_best <- readRDS(file.path(path_models, str_c("resample_preds_best_", data_type, "_", window, "_", lead, "_", version, 
                                              "_", cv, ".rds")))
metrics_best <- readRDS(file.path(path_models, str_c("resample_metrics_best_", data_type, "_", window, "_", lead, "_", version,
                                                "_", cv, ".rds")))
```


### Model Performance Metrics

#### 10x10 resamples
Look at performance within folds
```{r}
  metrics_best %>% 
    print_kbl()
```

```{r model_metrics}
config_best <- metrics_best %>% 
  group_by(algorithm, feature_set, hp1, hp2, hp3, resample) %>% 
  summarise(across(accuracy:roc_auc, ~mean(.x)), .groups = "drop")

config_best %>% glimpse
```

Confusion matrix using .5 threshold
```{r default_cm}
(cm <- preds_best %>% 
  conf_mat(truth, estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# save plot for presentations
# ggsave(file.choose(), width = 7.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```


### Probability Histograms
Histograms with free Y
```{r prob_plot_free}
preds_best %>% 
  mutate(truth = if_else(truth == "no_lapse", "No lapse", "Lapse"),
         estimate = if_else(estimate == "no_lapse", "No lapse", "Lapse")) %>% 
  ggplot(data = ., aes(x = prob)) + 
   geom_histogram(bins = 15, fill = "white", col = "black") +
   facet_wrap(~truth, nrow = 2, scales = "free_y") +
   xlab("Pr(Lapse)") +
  theme(axis.text = element_text(size = rel(1.00)), 
        axis.title.x = element_text(size = rel(1.25)),
        strip.text = element_text(size = rel(1.75)))

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```

Histograms with fixed Y
```{r prob_plot_fixed}
preds_best %>% 
  mutate(truth = if_else(truth == "no_lapse", "No lapse", "Lapse"),
         estimate = if_else(estimate == "no_lapse", "No lapse", "Lapse")) %>% 
  ggplot(data = ., aes(x = prob)) + 
   geom_histogram(bins = 15, fill = "white", col = "black") +
   facet_wrap(~truth, nrow = 2) +
   xlab("Pr(Lapse)") +
  theme(axis.text = element_text(size = rel(1.00)), 
        axis.title.x = element_text(size = rel(1.25)),
        strip.text = element_text(size = rel(1.75)))

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```

### ROC curve
file.path is single ROC by concatenating all folds.
Could consider reporting this AUC though likely average of resample AUCs is more appropriate?
Could also plot ROC by fold but maybe too confusing?
How about Bayesian posterior for AUC instead?
```{r roc_info}
preds_best %>%
  roc_auc(prob, truth = truth)

roc_data <- preds_best %>% 
  roc_curve(prob, truth = truth)
  
roc_data %>% 
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path() +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "Specificity",
       y = "Sensitivity") +
  scale_x_continuous(breaks = seq(0,1,.25),
    labels = sprintf("%.2f", seq(1,0,-.25))) +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```

### Posterior probabibilites for AUC

```{r}
resamples <- metrics_best %>% 
  select(id, id2, roc_auc) %>% 
  print(n = 5)
```

```{r}
resamples %>% 
  slice(1:30) %>%   # 3x 10-fold
  ggplot() + 
  geom_histogram(aes(x = roc_auc), bins = 10)
```


```{r}
set.seed(101)
pp <- resamples %>% 
  slice(1:30) %>%   # 3x 10-fold
  perf_mod(    formula = statistic ~ 1 + (1 | id2/id),
               iter = 5000, chains = 4,  
               transform = tidyposterior::logit_trans,  # for skewed & bounded AUC
               family = gaussian, 
               adapt_delta = .9999999)  

pp %>%  saveRDS(file.path(path_models, str_c("posteriors_", data_type, "_", window, 
                                             "_", lead, "_", version, "_", cv, 
                                             ".rds")))
```

```{r}
# get shinystan package
# launch_shinystan(pp$stan)
pp$stan

rstanarm::prior_summary(pp$stan)
```


```{r}
pp %>% 
  tidy(seed = 123) %>% 
  ggplot() + 
  geom_density(aes(x = posterior))
```



### PR Curve
file.path is precision/recall by concatenating all folds
Same approach as above for ROC
```{r pr_info}
preds_best %>%
  pr_auc(prob, truth = truth)

pr_data <- preds_best %>% 
  pr_curve(prob, truth = truth)

pr_data %>% 
  ggplot(aes(x = recall, y = precision)) +
  geom_path() +
  geom_hline(lty = 3, yintercept = mean(preds_best$truth == "lapse")) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "Recall (Sensitivity)",
       y = "Precision (PPV)")

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```


### Feature Importance

Read in best model fit (chosen with kfold)
```{r load_best_model}
model_fit_best <- readRDS(file.path(path_models, str_c("best_model_fit_", 
                                                    data_type, "_", window, "_", 
                                                    lead, "_", version, ".rds")))

```

get data
```{r get_data}
path_best <- file.path(path_input, 
                  str_c("train_", data_type, "_", window, "_", lead, "_", 
                        version, "_xgboost_", cv), "input")
source(file.path(path_best, "training_controls.R"))

chunks <- str_split_fixed(data_trn, "\\.", n = Inf) # parse name from extensions
if (length(chunks) == 2) {
  fn <- str_c("data_trn.", chunks[[2]])
} else {
  fn <- str_c("data_trn.", chunks[[2]], ".", chunks[[3]])
}

# open based on file type
if (str_detect(fn, "csv")) {
  d <- read_delim(file.path(path_best, fn), delim = "\t",
                  show_col_types = FALSE) 
} else {
  d <- readRDS(file.path(path_best, fn))
}

d <- d %>% 
  rename(y = {{y_col_name}})
    
# build recipe
config_best <- readRDS(file.path(path_models, 
                            str_c("resample_metrics_best_", data_type, "_", 
                                  window, "_", lead, "_", version,
                                  "_kfold", ".rds"))) %>% 
  group_by(algorithm, feature_set, hp1, hp2, hp3, resample) %>% 
  summarise(across(accuracy:roc_auc, ~mean(.x)), .groups = "drop")

rec <- build_recipe(d = d, job = config_best)

features_test <- rec %>% 
  prep(training = d, strings_as_factors = FALSE) %>%
  bake(new_data = d) #  get test data (no resampling) by setting new_data = d

x <- features_test %>% select(-y)  # x features
y <- features_test %>% pull(y)

mean_y <- features_test %>% 
  tab(y) %>% 
  filter(y == "yes") %>% 
  pull(prop)
```



#### Permutation Feature Importance

make  predictor function that returns lapse (yes) probabilities
```{r}
predictor <- function(model, x){
  predict(model, x, type = "prob") %>% 
    pull(.pred_yes)
}
```

```{r calc_perm}
if(file.exists(file.path(path_models, str_c("imp_permute_", data_type, "_", 
                                  window, "_", lead, "_", version, 
                                  ".rds")))){
  
  message("Loading previously computed Permutation Variable Importance")
  imp_perm  <- readRDS(file.path(path_models, str_c("imp_permute_", data_type, "_", 
                                  window, "_", lead, "_", version, 
                                  ".rds")))
} else {
  message("Calculating Permutation Variable Importance")
  var_strings <- c(".lapse", str_c("ema_", 2:10), "count.ema", "day", "age", 
                   "hour", "sex", "educ", "marital", "race")
  
  set.seed(12345)
  imp_perm <- var_strings %>% 
    map(\(var_string) get_vip(model = model_fit_best, 
                              x = x, y = y,
                              var_string = var_string,
                              fun_pred = predictor, 
                              fun_metric = yardstick::roc_auc_vec,
                              n_reps = 20)) %>% 
    list_rbind()
  
  imp_perm  %>% 
    saveRDS(file.path(path_models, str_c("imp_permute_", data_type, "_", 
                                    window, "_", lead, "_", version, 
                                    ".rds")))
}
```

```{r perm_plot}
imp_perm %>%   
  mutate(importance = metric_median) %>% 
  arrange(abs(importance)) %>% 
  mutate(feature = factor(var_string),
         feature = forcats::fct_inorder(feature)) %>% 
  ggplot(mapping = aes(x = feature, y = importance)) +
  geom_point(size = 2, color = "red") +
  geom_segment(aes(x = feature, y = importance, xend = feature), 
               yend = 0, colour = "grey50")  +
  ylab("Variable Importance (AUC difference") +
  coord_flip()

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```


#### Shapley Value Feature Importance

Using SHAPforxgboost package
  

```{r calc_shaps}

if(file.exists(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
                                  window, "_", lead, "_", version, 
                                  ".rds")))){
  
  message("Loading previously calculated raw SHAPS")
  shap_raw <- readRDS(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
                                              window, "_", lead, "_", version, 
                                              ".rds")))
} else {
  message("Calculating raw SHAPS")
  
shap_raw <- SHAPforxgboost::shap.prep(xgb_model = extract_fit_engine(model_fit_best),
                     X_train = x %>% as.matrix())

clean_feature_names <- function(feat_name){
  new_name <- gsub(".l0", "", feat_name)
  new_name <- gsub("rratecount.count", "raw_count", new_name)
  new_name <- gsub("dratecount.count", "diff_count", new_name)
  new_name <- gsub("drecent_response", "diff_recent", new_name)
  new_name <- gsub("rrecent_response", "raw_recent", new_name)
  new_name <- gsub("dmin_response", "diff_min", new_name)
  new_name <- gsub("rmin_response", "raw_min", new_name)
  new_name <- gsub("dmax_response", "diff_max", new_name)
  new_name <- gsub("rmax_response", "raw_max", new_name)
  new_name <- gsub("dmedian_response", "diff_median", new_name)
  new_name <- gsub("rmedian_response", "raw_median", new_name)
  new_name <- gsub("label_", "", new_name)
  new_name <- gsub("demo_", "", new_name)
  new_name <- gsub("High.school.or.less", "high.school", new_name)
  new_name <- gsub("Some.college", "some.college", new_name)
  new_name <- gsub("Mon", "mon", new_name)
  new_name <- gsub("Tue", "tue", new_name)
  new_name <- gsub("Wed", "wed", new_name)
  new_name <- gsub("Thu", "thu", new_name)
  new_name <- gsub("Fri", "fri", new_name)
  new_name <- gsub("Sat", "sat", new_name)
  new_name <- gsub("Sun", "sun", new_name)
  new_name <- gsub("Never.Married", "never.married", new_name)
  new_name <- gsub("Never.Other", "never.other", new_name)
  new_name <- gsub("White.Caucasian", "caucasian", new_name)
  new_name <- gsub("Male", "male", new_name)
  new_name <- gsub("p12.raw_count.lapse", "lapse.p12.raw_count", new_name)
  new_name <- gsub("p24.raw_count.lapse", "lapse.p24.raw_count", new_name)
  new_name <- gsub("p48.raw_count.lapse", "lapse.p48.raw_count", new_name)
  new_name <- gsub("p72.raw_count.lapse", "lapse.p72.raw_count", new_name)
  new_name <- gsub("p168.raw_count.lapse", "lapse.p168.raw_count", new_name)
  new_name <- gsub("p12.diff_count.lapse", "lapse.p12.diff_count", new_name)
  new_name <- gsub("p24.diff_count.lapse", "lapse.p24.diff_count", new_name)
  new_name <- gsub("p48.diff_count.lapse", "lapse.p48.diff_count", new_name)
  new_name <- gsub("p72.diff_count.lapse", "lapse.p72.diff_count", new_name)
  new_name <- gsub("p168.diff_count.lapse", "lapse.p168.diff_count", new_name)
  new_name <- gsub("p12.raw_count.ema", "missing.p12.raw_count", new_name)
  new_name <- gsub("p24.raw_count.ema", "missing.p24.raw_count", new_name)
  new_name <- gsub("p48.raw_count.ema", "missing.p48.raw_count", new_name)
  new_name <- gsub("p72.raw_count.ema", "missing.p72.raw_count", new_name)
  new_name <- gsub("p168.raw_count.ema", "missing.p168.raw_count", new_name)
  new_name <- gsub("p12.diff_count.ema", "missing.p12.diff_count", new_name)
  new_name <- gsub("p24.diff_count.ema", "missing.p24.diff_count", new_name)
  new_name <- gsub("p48.diff_count.ema", "missing.p48.diff_count", new_name)
  new_name <- gsub("p72.diff_count.ema", "missing.p72.diff_count", new_name)
  new_name <- gsub("p168.diff_count.ema", "missing.p168.diff_count", new_name)
  return(new_name) 
}
shap_raw <- shap_raw %>% 
  mutate(variable = fct_relabel(variable, clean_feature_names))

shap_raw %>% saveRDS(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
                                              window, "_", lead, "_", version, 
                                              ".rds")))
}
```

Now group SHAPs
```{r calc_grouped_shaps}
if(file.exists(file.path(path_models, str_c("imp_shap_grouped_", data_type, "_", 
                                  window, "_", lead, "_", version, 
                                  ".rds")))){
  message("Loading previously calculated grouped SHAPs")
  shap_grouped <- readRDS(file.path(path_models, str_c("imp_shap_grouped_",
                                                       data_type, "_", 
                                                       window, "_", lead, "_",
                                                       version, ".rds")))
} else {
  
  message("Calculating grouped SHAPs")
  
  shap_grouped <- shap_raw %>% 
    mutate(group = if_else(str_detect(variable, "lapse."), 
                           "past use (EMA item)", 
                           variable),
           group = if_else(str_detect(group, "ema_2"), 
                           "craving (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_3"), 
                           "past risky situation (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_4"), 
                           "past stressful event (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_5"), 
                           "past pleasant event (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_6"), 
                           "valence (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_7"), 
                           "arousal (EMA item)", 
                           group),
           group = if_else(str_detect(group, "ema_8"), 
                           "future risky situation (EMA item)",
                           group),
           group = if_else(str_detect(group, "ema_9"), 
                           "future stressful event (EMA item)",
                           group),
           group = if_else(str_detect(group, "ema_10"), 
                           "future efficacy (EMA item)", 
                           group),
           group = if_else(str_detect(group, "missing."), 
                           "missing surveys (other)", 
                           group),
           group = if_else(str_detect(group, "day"), 
                           "lapse day (other)", 
                           group),
           group = if_else(str_detect(group, "hour"), 
                           "lapse hour (other)", 
                           group),
           group = if_else(str_detect(group, "age"), 
                           "age (demographic)", 
                           group),
           group = if_else(str_detect(group, "sex"), 
                           "sex (demographic)", 
                           group),
           group = if_else(str_detect(group, "marital"), 
                           "marital (demographic)", 
                           group),
           group = if_else(str_detect(group, "race"), 
                           "race (demographic)", 
                           group),
           group = if_else(str_detect(group, "educ"), 
                           "education (demographic)", 
                           group)) %>%
    mutate(group = factor(group)) %>% 
    group_by(ID, group) %>% 
    summarize(shap = sum(value))
  
  shap_grouped %>% saveRDS(file.path(path_models, str_c("imp_shap_grouped_",
                                                         data_type, "_", 
                                                         window, "_", lead, "_",
                                                         version, ".rds")))
}
```


Global importance Shap plot for raw features
```{r shap_raw_plot}
shap_raw %>% 
  group_by(variable) %>% 
  slice(1) %>%   # mean for each variable is same for all rows for that variable
  ungroup() %>% 
  arrange(mean_value) %>% 
  slice_tail(n = 50) %>%
  mutate(variable = factor(variable),
         variable = forcats::fct_inorder(variable)) %>% 
  ggplot(mapping = aes(x = variable, y = mean_value)) +
  geom_point(size = 2, color = "red") +
  geom_segment(aes(x = variable, y = mean_value, xend = variable), 
               yend = 0, colour = "grey50")  +
  ylab("Mean |SHAP| value") +
  coord_flip()

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)
```

Global importance Shap plot for grouped features
```{r shap_grouped_plot}
shap_grouped %>% 
  group_by(group) %>% 
  summarize(mean_value = mean(abs(shap)), .groups = "drop") %>% 
  arrange(mean_value) %>% 
  mutate(group = factor(group),
         group = forcats::fct_inorder(group)) %>% 
  ggplot(mapping = aes(x = group, y = mean_value)) +
  geom_point(size = 2, color = "red") +
  geom_segment(aes(x = group, y = mean_value, xend = group), 
               yend = 0, colour = "grey50")  +
  ylab("Mean |SHAP| value") +
  coord_flip()

# save plot for presentations
# ggsave(file.choose(), width = 6.5, height = 6.5, units = "in", device = "png",  dpi = 100)

# shaps <- shap.values(xgb_model = extract_fit_engine(model_fit_best),
#                      X_train = x %>% as.matrix())

 
# shap.plot.summary.wrap1(extract_fit_engine(model_fit_best), x %>% as.matrix(), 
#                         top_n = 20, dilute = 10)
```


### Alternative SHAP code

```{r}
# Using shapr package.  However, only currently supports 30 features.

# might be able to  use groups to reduce "features" but not implemented in current package version
# group_list <- list(lapse = colnames(x)[str_detect(colnames(x), ".lapse")],
#                    ema_2 = colnames(x)[str_detect(colnames(x), "ema_2")],
#                    ema_3 = colnames(x)[str_detect(colnames(x), "ema_3")],
#                    ema_4 = colnames(x)[str_detect(colnames(x), "ema_4")],
#                    ema_5 = colnames(x)[str_detect(colnames(x), "ema_5")],
#                    ema_6 = colnames(x)[str_detect(colnames(x), "ema_6")],
#                    ema_7 = colnames(x)[str_detect(colnames(x), "ema_7")],
#                    ema_8 = colnames(x)[str_detect(colnames(x), "ema_8")],
#                    ema_9 = colnames(x)[str_detect(colnames(x), "ema_9")],
#                    ema_10 = colnames(x)[str_detect(colnames(x), "ema_10")],
#                    age = colnames(x)[str_detect(colnames(x), "age")],
#                    educ = colnames(x)[str_detect(colnames(x), "educ")],
#                    marital = colnames(x)[str_detect(colnames(x), "marital")],
#                    race = colnames(x)[str_detect(colnames(x), "race")],
#                    day = colnames(x)[str_detect(colnames(x), "day")],
#                    hour = colnames(x)[str_detect(colnames(x), "hour")])
# 
# 
# if(file.exists(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
#                                   window, "_", lead, "_", version, 
#                                   ".rds")))){
#   
#   message("Loading previously calculated raw SHAPS")
#   shap_raw <- readRDS(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
#                                               window, "_", lead, "_", version, 
#                                               ".rds")))
# } else {
#   message("Calculating raw SHAPS")
#   
#   explainer <- shapr::shapr(x, model_fit_best$fit)
# 
#   shap_raw <- shapr::explain(x, approach = "empirical", explainer = explainer,
#                              prediction_zero = mean_y) %>%     
#     pull(dt)
#   
# shap_raw <- shap.prep(xgb_model = extract_fit_engine(model_fit_best),
#                      X_train = x %>% as.matrix())
# 
# clean_feature_names <- function(feat_name){
#   new_name <- gsub(".l0", "", feat_name)
#   new_name <- gsub("rratecount.count", "raw_count", new_name)
#   new_name <- gsub("dratecount.count", "diff_count", new_name)
#   new_name <- gsub("drecent_response", "diff_recent", new_name)
#   new_name <- gsub("rrecent_response", "raw_recent", new_name)
#   new_name <- gsub("dmin_response", "diff_min", new_name)
#   new_name <- gsub("rmin_response", "raw_min", new_name)
#   new_name <- gsub("dmax_response", "diff_max", new_name)
#   new_name <- gsub("rmax_response", "raw_max", new_name)
#   new_name <- gsub("dmedian_response", "diff_median", new_name)
#   new_name <- gsub("rmedian_response", "raw_median", new_name)
#   new_name <- gsub("label_", "", new_name)
#   new_name <- gsub("demo_", "", new_name)
#   new_name <- gsub("High.school.or.less", "high.school", new_name)
#   new_name <- gsub("Some.college", "some.college", new_name)
#   new_name <- gsub("Mon", "mon", new_name)
#   new_name <- gsub("Tue", "tue", new_name)
#   new_name <- gsub("Wed", "wed", new_name)
#   new_name <- gsub("Thu", "thu", new_name)
#   new_name <- gsub("Fri", "fri", new_name)
#   new_name <- gsub("Sat", "sat", new_name)
#   new_name <- gsub("Sun", "sun", new_name)
#   new_name <- gsub("Never.Married", "never.married", new_name)
#   new_name <- gsub("Never.Other", "never.other", new_name)
#   new_name <- gsub("White.Caucasian", "caucasian", new_name)
#   new_name <- gsub("Male", "male", new_name)
#   new_name <- gsub("p12.raw_count.lapse", "lapse.p12.raw_count", new_name)
#   new_name <- gsub("p24.raw_count.lapse", "lapse.p24.raw_count", new_name)
#   new_name <- gsub("p48.raw_count.lapse", "lapse.p48.raw_count", new_name)
#   new_name <- gsub("p72.raw_count.lapse", "lapse.p72.raw_count", new_name)
#   new_name <- gsub("p168.raw_count.lapse", "lapse.p168.raw_count", new_name)
#   new_name <- gsub("p12.diff_count.lapse", "lapse.p12.diff_count", new_name)
#   new_name <- gsub("p24.diff_count.lapse", "lapse.p24.diff_count", new_name)
#   new_name <- gsub("p48.diff_count.lapse", "lapse.p48.diff_count", new_name)
#   new_name <- gsub("p72.diff_count.lapse", "lapse.p72.diff_count", new_name)
#   new_name <- gsub("p168.diff_count.lapse", "lapse.p168.diff_count", new_name)
#   new_name <- gsub("p12.raw_count.ema", "missing.p12.raw_count", new_name)
#   new_name <- gsub("p24.raw_count.ema", "missing.p24.raw_count", new_name)
#   new_name <- gsub("p48.raw_count.ema", "missing.p48.raw_count", new_name)
#   new_name <- gsub("p72.raw_count.ema", "missing.p72.raw_count", new_name)
#   new_name <- gsub("p168.raw_count.ema", "missing.p168.raw_count", new_name)
#   new_name <- gsub("p12.diff_count.ema", "missing.p12.diff_count", new_name)
#   new_name <- gsub("p24.diff_count.ema", "missing.p24.diff_count", new_name)
#   new_name <- gsub("p48.diff_count.ema", "missing.p48.diff_count", new_name)
#   new_name <- gsub("p72.diff_count.ema", "missing.p72.diff_count", new_name)
#   new_name <- gsub("p168.diff_count.ema", "missing.p168.diff_count", new_name)
#   return(new_name) 
# }
# shap_raw <- shap_raw %>% 
#   mutate(variable = fct_relabel(variable, clean_feature_names))
# 
# shap_raw %>% saveRDS(file.path(path_models, str_c("imp_shap_raw_", data_type, "_", 
#                                               window, "_", lead, "_", version, 
#                                               ".rds")))
# }
# 
# if(file.exists(file.path(path_models, str_c("imp_shap_grouped_", data_type, "_", 
#                                   window, "_", lead, "_", version, 
#                                   ".rds")))){
#   message("Loading previously calculated grouped SHAPs")
#   shap_grouped <- readRDS(file.path(path_models, str_c("imp_shap_grouped_",
#                                                        data_type, "_", 
#                                                        window, "_", lead, "_",
#                                                        version, ".rds")))
# } else {
#   
#   message("Calculating grouped SHAPs")
#   
#   shap_grouped <- shap_raw %>% 
#     mutate(group = if_else(str_detect(variable, "lapse."), 
#                            "past use (EMA item)", 
#                            variable),
#            group = if_else(str_detect(group, "ema_2"), 
#                            "craving (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_3"), 
#                            "past risky situation (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_4"), 
#                            "past stressful event (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_5"), 
#                            "past pleasant event (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_6"), 
#                            "valence (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_7"), 
#                            "arousal (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "ema_8"), 
#                            "future risky situation (EMA item)",
#                            group),
#            group = if_else(str_detect(group, "ema_9"), 
#                            "future stressful event (EMA item)",
#                            group),
#            group = if_else(str_detect(group, "ema_10"), 
#                            "future efficacy (EMA item)", 
#                            group),
#            group = if_else(str_detect(group, "missing."), 
#                            "missing surveys (other)", 
#                            group),
#            group = if_else(str_detect(group, "day"), 
#                            "lapse day (other)", 
#                            group),
#            group = if_else(str_detect(group, "hour"), 
#                            "lapse hour (other)", 
#                            group),
#            group = if_else(str_detect(group, "age"), 
#                            "age (demographic)", 
#                            group),
#            group = if_else(str_detect(group, "sex"), 
#                            "sex (demographic)", 
#                            group),
#            group = if_else(str_detect(group, "marital"), 
#                            "marital (demographic)", 
#                            group),
#            group = if_else(str_detect(group, "race"), 
#                            "race (demographic)", 
#                            group),
#            group = if_else(str_detect(group, "educ"), 
#                            "education (demographic)", 
#                            group)) %>%
#     mutate(group = factor(group)) %>% 
#     group_by(ID, group) %>% 
#     summarize(shap = sum(value))
#   
#   shap_grouped %>% saveRDS(file.path(path_models, str_c("imp_shap_grouped_",
#                                                          data_type, "_", 
#                                                          window, "_", lead, "_",
#                                                          version, ".rds")))
# }
```

```{r}
# Using iml package

# predict_wrapper <- function(model, newdata) {
#   predict(model, newdata, type = "prob") %>%  # set type = "prob" for probabilities
#     dplyr::select(yes = .pred_yes, no = .pred_no)
#   
# }
# 
# iml_predictor <- iml::Predictor$new(model = model_fit_best, 
#                            data = x, 
#                            y = y,
#                            predict.fun = predict_wrapper)  


# get_shapley_values <- function(df1, predictor){
#   iml::Shapley$new(iml_predictor, x.interest = df1)$results %>%
#     separate_wider_delim(feature.value, delim = "=",
#                          names = c("tmp", "feature_value")) %>%
#     mutate(feature_value = as.numeric(feature_value)) %>%
#     select(feature, feature_value, phi)
# }

# x1 <- slice(x, 1:2)
# local_shaps <- x1 %>%
#   dplyr::mutate(id = row_number()) %>%
#   nest(.by = id, .key = "dfs") %>%  # nest a dataframe for each observation
#   dplyr::mutate(shapleys = map(dfs, \(df1) get_shapley_values(df1, predictor))) %>%
#   dplyr::select(-dfs) %>%
#   unnest(shapleys) 
# 
# local_shaps %>% head
```

