---
title: "Checking Audio Data"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
 
This script checks data from RISK participants' transcribed audio check-ins by computing 
descriptives and checking for missingness and potential errors. 
  

### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths 
```{r}
path_data <- "./analysis/shared/data"
```

Packages
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
library(psych)
library(tidytext)
library(tm)
library(textclean)
library(textrecipes)
```


### Import Data and glimpse 

Audio data
```{r}
audio <- read_rds(file.path(path_data, "ds_audio.rds"))  
audio <- audio %>%
  clean_names() %>% 
  rename("subid" = "sub_id") %>% 
  mutate(date_central = date(as_datetime(utc, tz = 'America/Chicago'))) %>%
  glimpse()
```

`r length(unique(audio$subid))` participants contribute to a total of `r nrow(audio)` audio recordings.    
The earliest audio recording is from `r min(audio$date_central)` and the last is from `r max(audio$date_central)`.  
This is because there is only `r length(unique(audio$utc))` unique utc for entire utc column.  
As a result this script only will be checking message text characteristics and descriptives overall and by subid.  

Final dataset
```{r}
audio <- audio %>%
  select(subid, text) %>% 
  glimpse()
```

Missing (NA) values
```{r}
if(any(is.na(audio))){
  missing <- audio %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There is `r sum(is.na(audio))` missing value (NA) from the dataset. The observation is below
however, it is difficult to say why this value is missing because we only have the subid.

```{r}
audio %>% 
  filter(is.na(text)) %>% 
   kable(caption = "Observation with missing data",
        table.attr = "style = 'width:40%;'") %>% 
  kable_styling(position = "left")
```

Blank or notably short audio recordings
```{r}
audio_short <- audio %>%
  filter(nchar(text) <= 15)

audio_short %>% 
  kable(caption = "Audio recordings less than 15 characters in length",
         table.attr = "style = 'width:40%;'") %>% 
  kable_styling(position = "left")
```

Inaudible messages
```{r}
contains_inaudible <- audio %>% 
  filter(str_detect(tolower(text), "inaudible"))

inaudible_short <- audio %>% 
  filter(str_detect(tolower(text), "inaudible")) %>% 
  filter(nchar(text) < 100) 

inaud_short_bysubid <- inaudible_short %>% 
  group_by(subid) %>% 
  summarise(n_obs = n())

inaudible_short %>%   
  kable(caption = "Shorter audio recordings inaudible for transcription") %>% 
  kable_styling(position = "left")

contains_inaudible_total <- contains_inaudible %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  filter(n_obs > 20) 

contains_inaudible_total %>%   
  kable(caption = "Participants with more than 20 messages containing inaudible in entire dataset",
        table.attr = "style = 'width:50%;'") %>% 
  kable_styling(position = "left")
```

`r nrow(contains_inaudible)` audio recordings have "inaudible" in transcription.  However only 
`r nrow(inaudible_short)` are short enough (less than 100 characters) for it to likely be a
problem. Of these shorter inaudible messages, subid 242 makes up `r max(inaud_short_bysubid$n_obs)` 
(`r round(max(inaud_short_bysubid$n_obs)/nrow(inaudible_short), 3)*100`%) of them.  
Of the entire dataset subid 242 has a total of `r contains_inaudible_total$n_obs` messages containing 
inaudible transcription in them.  


### Descriptives

#### overall descriptives

Number of audio messages per participant
```{r}
audio %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  summarise(mean = round(mean(n_obs), 2),
            sd = round(sd(n_obs), 2),
            min = min(n_obs),
            max = max(n_obs)) %>% 
  kable(caption = "Average audio messages per participant",
        table.attr = "style = 'width:40%;'") %>% 
  kable_styling(position = "left")

audio %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 12) +
  xlab("number of audio recordings") +
  ggtitle("Histogram of number of audio recordings per participant") +
  theme_classic()
```

Character length of all audio messages per participant
```{r}
audio %>% 
  mutate(char_length = nchar(text)) %>% 
  group_by(subid) %>% 
  summarise(total_char = sum(char_length)) %>%  
  summarise(mean = round(mean(total_char, na.rm = TRUE), 2),
            sd = round(sd(total_char, na.rm = TRUE), 2),
            min = min(total_char, na.rm = TRUE),
            max = max(total_char, na.rm = TRUE)) %>% 
  kable(caption = "Average character length and range of all audio messages per participant",
        table.attr = "style = 'width:70%;'") %>% 
  kable_styling(position = "left")

audio %>% 
  mutate(char_length = nchar(text)) %>% 
  group_by(subid) %>% 
  summarise(total_char = sum(char_length)) %>% 
  ggplot(aes(x = total_char)) +
  geom_histogram(bins = 15) +
  xlab("length of all audio recordings") +
  ggtitle("Histogram of length of all audio recordings combined per participant") +
  theme_classic()
```

Average character length of each audio message per participant
```{r}
audio %>% 
  mutate(char_length = nchar(text)) %>% 
  summarise(mean = round(mean(char_length, na.rm = TRUE), 2),
            sd = round(sd(char_length, na.rm = TRUE), 2),
            min = min(char_length, na.rm = TRUE),
            max = max(char_length, na.rm = TRUE)) %>% 
  kable(caption = "Average character length and range of each audio message",
        table.attr = "style = 'width:70%;'") %>% 
  kable_styling(position = "left")

audio %>% 
  mutate(char_length = nchar(text)) %>% 
  group_by(subid) %>% 
  summarise(char_length = nchar(text)) %>% 
  ggplot(aes(x = char_length)) +
  geom_histogram(bins = 15) +
  xlab("length of audio recordings") +
  ggtitle("Histogram of average length of audio recordings per participant") +
  theme_classic()
```

#### text analyses

Clean text
```{r}
audio_tidy <- audio %>% 
      mutate(text = removeNumbers(text)) %>%
      mutate(text = tolower(text))%>% 
      mutate(text = removePunctuation(text)) %>% 
      mutate(text = replace_symbol(text)) %>% 
      mutate(text = stripWhitespace(text)) # condenses whitespace into a single space

# Remove new blank text tokens for word count statistics
audio_tidy <- audio_tidy %>% 
  filter(!text == " " & !text == "") 
```

Tokenize text data (tidy text)
```{r}
audio_tidy <- audio_tidy %>% 
  unnest_tokens(word, text) %>% 
  glimpse()
```

Get ML features
```{r}
audio_features <- audio_tidy %>%
  anti_join(get_stopwords(), by = "word") %>%
  count(subid, word) %>%
  bind_tf_idf(word, subid, n) %>%
  glimpse()

audio_features %>%
  cast_dtm(subid, word, tf_idf)
```

Number of unique words per participant
```{r}
unique_words <- audio_tidy %>%
  group_by(subid) %>%
  summarize(n_unique_words = n_distinct(word)) 

describe(unique_words$n_unique_words) %>%
  kable(caption = "Number of unique words per participant") %>%
  kable_styling()

unique_words %>%
  ggplot(aes(x = n_unique_words)) +
  geom_histogram(bins = 15) +
  xlab("number of unique words per participant") +
  ggtitle("Histogram of participants' number of unique words in audio recordings") +
  theme_classic()
```

Top words (common/relevant)
```{r}
audio_words <- audio_tidy %>% 
  count(subid, word, sort = TRUE) %>% 
  bind_tf_idf(word, subid, n)

audio_words %>% 
  arrange(desc(n)) %>%
  head(n = 20) %>%
  kable(caption = "Most common words by frequency (n)") %>% 
  kable_styling(full_width = FALSE, position = "left")

audio_words %>%
  arrange(desc(tf_idf)) %>%
  head(n = 20) %>%
  kable(caption = "Most relevant words by tf_idf") %>% 
  kable_styling(full_width = FALSE, position = "left")

audio_words %>%
  arrange(desc(tf_idf)) %>%
  top_n(25) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  ggplot(aes(word, tf_idf, fill = subid)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Twenty-five most relevant words by tf_idf") +
  coord_flip() +
  theme_classic()
```

Example of top ten words (tf-idf) from a single participant
```{r}
audio %>% 
  mutate(char_length = nchar(text)) %>% 
  group_by(subid) %>% 
  summarise(mean = round(mean(char_length, na.rm = TRUE), 2),
            sd = round(sd(char_length, na.rm = TRUE), 2),
            min = min(char_length, na.rm = TRUE),
            max = max(char_length, na.rm = TRUE)) %>% 
  arrange(desc(mean)) %>% 
  head(n = 3) %>% 
  kable(caption = "Top 3 subids with highest mean character length of audio recordings",
        table.attr = "style = 'width:70%;'") %>% 
  kable_styling(position = "left")

audio_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 192) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 192 top words (tf-idf)") %>% 
  kable_styling(full_width = FALSE, position = "left")

audio_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 236) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 236 top words (tf-idf)") %>% 
  kable_styling(full_width = FALSE, position = "left")

audio_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 131) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 131 top words (tf-idf)") %>% 
  kable_styling(full_width = FALSE, position = "left")
```
