---
title: "Checking Locations Report"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

### Notes
 
This script checks data from RISK participants' locations reports by computing descriptives and 
checking for missingness and potential errors.  

Thoughts for discussion:  
1. Time of visit refers to study visit when location was identified. How can we link to gps data
with time of location visit?  
2. Location_type "other" was 2nd most common choice. Locate paper files to analyze what these 
locations are.  
3. Not much variability in yes and no questions. Ex: Less than 4% answered "yes" to vacationing 
at location question.
  

### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths 
```{r}
getwd()
path_data <- "./analysis/shared/data"
```

Packages
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
```


### Import Data and glimpse 

Locations data
```{r}
locations <- read_rds(file.path(path_data, "ds_locations_report.rds")) 

locations <- locations %>%
  mutate(time_central = as_datetime(utc, tz = 'America/Chicago')) %>%
  select(-utc) %>%
  glimpse() 
```

`r length(unique(locations$subid))` participants contribute to a total of `r nrow(locations)` locations.    
The earliest recorded location is from `r min(date(locations$time_central))` and the last is from `r max(date(locations$time_central))`. 

Check for being at different locations at the same time
```{r}
locations %>% 
  select(subid, street_address, type, time_central) %>% 
  head(n = 20) %>% 
  kable(caption = "Sample of locations and corresponding times", table.attr = "style='width:80%;'") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed")
```

UTCs appear to not be accurate as to time sub visited the location but instead of when they reported 
the location to research staff (confirmed by checking with notes log/visit dates).

Check for missing values
```{r}
if(any(is.na(locations))){
  missing <- locations %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There are `r sum(is.na(locations))` missing values (NA) from `r length(missing$var)` unique 
variables in the entire dataset.

View location with missing city
```{r}
locations %>% 
  filter(is.na(city)) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "condensed")
```

A google map search of 1222 East Washington Avenue, WI confirms city should be Madison. Will add city.  

Add city to city variable and full_address variable
```{r}
locations_137 <- locations %>% 
  filter(subid == 137 & street_address == "1222 East Washington Avenue") %>% 
  mutate(city = "Madison",
         full_address = str_glue("{street_address}, {city}, {state}"))
locations <- locations %>%
  filter(!(subid == 137 & street_address == "1222 East Washington Avenue"))
locations <- locations %>% 
  rbind(locations_137)
# check  
locations %>%
  filter(subid == 137 & street_address == "1222 East Washington Avenue") %>%
  kable() %>% 
  kable_styling(bootstrap_options = "condensed")
```

Check missing values again
```{r}
if(any(is.na(locations))){
  missing <- locations %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There are now `r sum(is.na(locations))` missing values (NA) from `r length(missing$var)` unique 
variables in the entire dataset.

### Descriptives

Locations outside Madison (city)
```{r}
locations %>% 
  select(city) %>%
  mutate(city = case_when(
    city == "Madison" ~ "Madison",
    TRUE ~ "Outside Madison")) %>% 
  tabyl(city, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Average number of places participants reported each visit
```{r}
mean_avg_location_per_day <- locations %>%                                                          
  group_by(subid, date(time_central)) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_locations_per_day = mean(n_obs)) %>% 
  .$avg_locations_per_day %>% 
  mean()

max_location_per_day <- locations %>% 
  group_by(subid, date(time_central)) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(max = max(n_obs)) %>% 
  .$max %>% max()

locations %>% 
  group_by(subid, date(time_central)) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_locations_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_locations_per_day)) +
  geom_histogram(bins = 12) +
  xlab("avg locations participants reported per visit") +
  ggtitle("Histogram of average locations reported per day (visit)") +
  theme_classic()
```

On average, participants reported an average of `r round(mean_avg_location_per_day, 2)` places visisted at their 
intake/followup visits (max = `r max_location_per_day`).


COMMENT KW 2020-08-11: The goal would be to use the above script to report the places participants visited each 
day if we can combine these locations with GPS data. Currently it probably does not tell us much because we would 
expect participants reported more locations at intake and fewer at followups.


Type of location (type)
```{r}
locations %>%
  mutate(type = tolower(type),
         type = fct_infreq(factor(type))) %>% 
  tabyl(type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Type of location", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

locations %>%
  mutate(type = tolower(type),
         type = fct_infreq(factor(type))) %>%
  ggplot(aes (x = type)) +
  geom_bar() +
  xlab("location type") +
  ggtitle("Frequency plot of types of locations visited") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Location as a function of risk level
```{r}
locations %>%
  mutate(type = tolower(type),
         type = fct_infreq(factor(type))) %>%
  mutate(risk = tolower(risk),
         risk = fct_relevel(factor(risk, c("high", "medium", "low", "no", "NA")))) %>% 
  ggplot(aes (x = type, fill = risk)) +
  geom_bar() +
  xlab("location type") +
  ggtitle("Frequency plot of types of locations visited by risk level") +
  theme_classic() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "BuPu", direction = -1, na.value = "light grey")
```

Drank alcohol at location in past (drank)
```{r}
locations %>%
  mutate(drank = tolower(drank),
         drank = fct_infreq(factor(drank))) %>% 
  tabyl(drank, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Drank alcohol at location in past", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Alcohol is available at location (alcohol)
```{r}
locations %>%
  mutate(alcohol = tolower(alcohol),
         alcohol = fct_infreq(factor(alcohol))) %>% 
  tabyl(alcohol, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Alcohol is available at location", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Emotion associated with location (emotion)
```{r}
locations %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", "mixed", "neutral")))) %>% 
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Emotion associated with location", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")

locations %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", "mixed", "neutral", "NA")))) %>% 
  ggplot(aes (x = emotion)) +
  geom_bar() +
  xlab("emotion from location") +
  ggtitle("Frequency plot of type of emotion from location") +
  theme_classic()
```

Risk level for drinking (risk)
```{r}
locations %>%
  mutate(risk = tolower(risk),
         risk = fct_relevel(factor(risk, c("high", "medium", "low", "no")))) %>% 
  tabyl(risk, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Risk level for drinking at location", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")

locations %>%
  mutate(risk = tolower(risk),
         risk = fct_relevel(factor(risk, c("high", "medium", "low", "no", "NA")))) %>% 
  ggplot(aes (x = risk)) +
  geom_bar() +
  xlab("risk level") +
  ggtitle("Frequency plot of risk level for drinking at location") +
  theme_classic()
```

Avoiding location (avoid)
```{r}
locations %>%
  mutate(avoid = tolower(avoid)) %>% 
  tabyl(avoid, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Location participant avoids", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Vacation location (vacation)
```{r}
locations %>%
  mutate(vacation = tolower(vacation)) %>% 
  tabyl(vacation, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Location participant vacations at", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

