---
title: "Creating datasets to share with the Huang lab"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
Purpose: This script creates and describes the datasets we are sharing with Dr. Huang's lab.

Inputs:

* analysis/shared/data/ds_gps.rds
* analysis/shared/data/ds_locations_report.rds
* raw_data/locations/locations_abby REAL.csv
* raw_data/locations/locations_connie.csv
* analysis/shared/data/ds_intake.csv

Outputs

* analysis/gps/data/to_share/gps.csv
* analysis/gps/data/to_share/locations_report.csv
* analysis/gps/data/to_share/other_locations_report_a.csv
* analysis/gps/data/to_share/other_locations_report_c.csv
* analysis/gps/data/to_share/demographics.csv
* analysis/gps/data/to_share/codebook_demographics.csv

### Setup
```{r setup, include = FALSE}
knitr::opts_chunk$set(message = TRUE, warning = TRUE)
# You want to set each of these to TRUE OR FALSE in the above setting for the entire script
# depending on the nature of the code in the script.  Default is TRUE so you can 
# delete this code chunk if you dont plan to suppress messages or warnings for
# the entire Rmd.

# You can also add results = "hold" if you want all results from a code chunk to
# display together without interleaving 
```

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
  # all codeblocks bigger than 500 px will be scrollable - can adjust as needed
  # all codeblocks wider then 100% will be scollable - can make narrower with max-width: 50% or similar
}
```

Paths 
```{r}
path_data <- "analysis/shared/data"
path_other_codes <- "raw_data/locations"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(gt)
```

### analysis/gps/data/to_share/gps.csv

```{r}
gps <- read_rds(file.path(path_data, "ds_gps.rds")) %>% 
  select(subid, time_central, lat, long, app_source, data_type) %>% 
  glimpse()

write_csv(gps, "analysis/gps/data/to_share/gps.csv")
```

### analysis/gps/data/to_share/locations_report.csv

```{r}
locations_report <- read_rds(file.path(path_data, "ds_locations_report.rds")) %>% 
  glimpse()

write_csv(locations_report, "analysis/gps/data/to_share/locations_report.csv")
```

### analysis/gps/data/to_share/other_locations_report_a.csv

A's codes
```{r}
other_locations_a <- read_csv(file.path(path_other_codes, "locations_abby REAL.csv")) %>% 
  mutate(coder = "a") %>% 
  glimpse()

write_csv(other_locations_a, "analysis/gps/data/to_share/other_locations_report_a.csv")
```

### analysis/gps/data/to_share/other_locations_report_c.csv

C's codes
```{r}
other_locations_c <- read_csv(file.path(path_other_codes, "locations_connie.csv")) %>% 
  mutate(coder = "c") %>% 
  glimpse()

write_csv(other_locations_c, "analysis/gps/data/to_share/other_locations_report_c.csv")
```


### analysis/gps/data/to_share/demographics.csv

```{r}
demographics <- read_csv(file.path(path_data, "ds_screen.csv")) %>% 
  select(subid, starts_with("dem")) %>% 
  glimpse()

demographic_variables <- names(demographics)

write_csv(demographics, "analysis/gps/data/to_share/demographics.csv")
```

create the codebook for the demographics

```{r}
read_csv("./analysis/shared/codebooks/codebook_ds_id.csv") %>% 
  filter(name %in% demographic_variables) %>% 
  write_csv("analysis/gps/data/to_share/codebook_demographics.csv")
```

