---
title: "make demographic summary for features"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---

### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

library(here)  
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)

theme_set(theme_classic()) 
```

### ID Demographic Features and Snapshot Screening Data

Read in logs
```{r}
logs_all <- screen <- vroom::vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) 
```


Read in screening data
```{r}
screen <- vroom::vroom(here(path_shared, "screen.csv"), col_types = vroom::cols()) %>%
  filter(subid %in% logs_all$subid)
```

Select variables of interest
```{r}
screen_select <- screen %>%
  # only 6 participants are Hispanic - consider removing
  mutate(id_hispanic = if_else(dem_4 == "No, I am not of Hispanic, Latino, or Spanish origin",
                            "no", "yes"),
         id_employment = if_else(dem_6 == "Employed", dem_6_1, dem_6),
         id_tx_long_term_residential = if_else(!is.na(auh_6_1), "yes", "no"),
         id_tx_short_term_residential = if_else(!is.na(auh_6_2), "yes", "no"),
         id_tx_outpatient = if_else(!is.na(auh_6_3), "yes", "no"),
         id_tx_indiv_counseling = if_else(!is.na(auh_6_4), "yes", "no"),
         id_tx_group_counseling = if_else(!is.na(auh_6_5), "yes", "no"),
         id_tx_aa_or_na = if_else(!is.na(auh_6_6), "yes", "no"),
         id_tx_other = if_else(!is.na(auh_6_7), "yes", "no"),
         id_quit_date = as_datetime(str_c(screen$auh_8_month, " ",  screen$auh_8_day, " ", screen$auh_8_year),
                                 tz = "america/Chicago", format = "%B %d %Y"),
         across(dsm5_1:dsm5_11, ~if_else(.x == "Yes", 1, 0)),
         across(assist_1_1:assist_1_8, ~if_else(.x == "Yes", 1, 0))) %>%
  rowwise() %>%
  mutate(id_dsm5_total = sum(c_across(dsm5_1:dsm5_11)),
         id_lifetime_n_drugs_endorsed = sum(c_across(assist_1_1:assist_1_8))) %>%
  ungroup() %>%
  select(subid,
         id_age = dem_1,
         id_gender = dem_2,
         id_race = dem_3,
         id_hispanic,
         id_education = dem_5,
         id_employment,
         id_income = dem_7,
         id_marrital_status = dem_8,
         id_age_first_drank = auh_1,
         id_age_drank_regularly = auh_2,
         id_age_believed_drinking_was_problem = auh_3,
         id_age_first_quit_drinking = auh_4,
         id_number_quit_attempts = auh_5,
         id_tx_long_term_residential,
         id_tx_short_term_residential,
         id_tx_outpatient,
         id_tx_indiv_counseling,
         id_tx_group_counseling,
         id_tx_aa_or_na,
         id_tx_other,
         id_aud_medication = auh_7,
         id_quit_date,
         id_days_per_week_drank_6_mos_before_quit = auh_9,
         id_days_per_week_drank_heavily_6_mos_before_quit = auh_10,
         id_avg_drinks_per_day_6_mos_before_quit = auh_11,
         id_days_per_week_drank_6_mos_heaviest = auh_12,
         id_days_per_week_drank_heavily_6_mos_heaviest = auh_13,
         id_avg_drinks_per_day_6_mos_heaviest = auh_14,
         id_lifetime_use_tobacco = assist_1_1,
         id_lifetime_use_cannabis = assist_1_2,
         id_lifetime_use_cocaine = assist_1_3,
         id_lifetime_use_amphetamine = assist_1_4,
         id_lifetime_use_inhalant = assist_1_5,
         id_lifetime_use_sedative = assist_1_6,
         id_lifetime_use_hallucinogen = assist_1_7,
         id_lifetime_use_opioid = assist_1_8,
         id_lifetime_n_drugs_endorsed,
         id_past_3_mo_freq_tobacco = assist_2_1, # 3 months prior to screen date
         id_past_3_mo_freq_cannabis = assist_2_2,
         id_past_3_mo_freq_cocaine = assist_2_3,
         id_past_3_mo_freq_amphetamine = assist_2_4,
         id_past_3_mo_freq_inhalant = assist_2_5,
         id_past_3_mo_freq_sedative = assist_2_6,
         id_past_3_mo_freq_hallucinogen = assist_2_7,
         id_past_3_mo_freq_opioid = assist_2_8,
         id_past_3_mo_urge_tobacco = assist_3_1,
         id_past_3_mo_urge_cannabis = assist_3_2,
         id_past_3_mo_urge_cocaine = assist_3_3,
         id_past_3_mo_urge_amphetamine = assist_3_4,
         id_past_3_mo_urge_inhalant = assist_3_5,
         id_past_3_mo_urge_sedative = assist_3_6,
         id_past_3_mo_urge_hallucinogen = assist_3_7,
         id_past_3_mo_urge_opioid = assist_3_8,
         id_past_3_mo_problem_tobacco = assist_4_1,
         id_past_3_mo_problem_cannabis = assist_4_2,
         id_past_3_mo_problem_cocaine = assist_4_3,
         id_past_3_mo_problem_amphetamine = assist_4_4,
         id_past_3_mo_problem_inhalant = assist_4_5,
         id_past_3_mo_problem_sedative = assist_4_6,
         id_past_3_mo_problem_hallucinogen = assist_4_7,
         id_past_3_mo_problem_opioid = assist_4_8,
         id_past_3_mo_fail_expect_tobacco = assist_5_1,
         id_past_3_mo_fail_expect_cannabis = assist_5_2,
         id_past_3_mo_fail_expect_cocaine = assist_5_3,
         id_past_3_mo_fail_expect_amphetamine = assist_5_4,
         id_past_3_mo_fail_expect_inhalant = assist_5_5,
         id_past_3_mo_fail_expect_sedative = assist_5_6,
         id_past_3_mo_fail_expect_hallucinogen = assist_5_7,
         id_past_3_mo_fail_expect_opioid = assist_5_8,
         id_lifetime_concern_tobacco = assist_6_1,
         id_lifetime_concern_cannabis = assist_6_2,
         id_lifetime_concern_cocaine = assist_6_3,
         id_lifetime_concern_amphetamine = assist_6_4,
         id_lifetime_concern_inhalant = assist_6_5,
         id_lifetime_concern_sedative = assist_6_6,
         id_lifetime_concern_hallucinogen = assist_6_7,
         id_lifetime_concern_opioid = assist_6_8,
         id_lifetime_cutback_tobacco = assist_7_1,
         id_lifetime_cutback_cannabis = assist_7_2,
         id_lifetime_cutback_cocaine = assist_7_3,
         id_lifetime_cutback_amphetamine = assist_7_4,
         id_lifetime_cutback_inhalant = assist_7_5,
         id_lifetime_cutback_sedative = assist_7_6,
         id_lifetime_cutback_hallucinogen = assist_7_7,
         id_lifetime_cutback_opioid = assist_7_8,
         id_lifetime_drug_injection = assist_8,
         id_dsm5_total)
```

Impute WHO-Assist NA values
```{r}
naniar::miss_var_summary(screen_select)

screen_select <- screen_select %>% 
  mutate(across(c(id_past_3_mo_freq_tobacco, id_past_3_mo_urge_tobacco, id_past_3_mo_problem_tobacco, 
                  id_past_3_mo_fail_expect_tobacco, id_lifetime_concern_tobacco, id_lifetime_cutback_tobacco), 
                ~ if_else(is.na(.x) & id_lifetime_use_tobacco == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_cannabis, id_past_3_mo_urge_cannabis, id_past_3_mo_problem_cannabis, 
                  id_past_3_mo_fail_expect_cannabis, id_lifetime_concern_cannabis, id_lifetime_cutback_cannabis), 
                ~ if_else(is.na(.x) & id_lifetime_use_cannabis == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_cocaine, id_past_3_mo_urge_cocaine, id_past_3_mo_problem_cocaine, 
                  id_past_3_mo_fail_expect_cocaine, id_lifetime_concern_cocaine, id_lifetime_cutback_cocaine), 
                ~ if_else(is.na(.x) & id_lifetime_use_cocaine == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_amphetamine, id_past_3_mo_urge_amphetamine, id_past_3_mo_problem_amphetamine, 
                  id_past_3_mo_fail_expect_amphetamine, id_lifetime_concern_amphetamine, 
                  id_lifetime_cutback_amphetamine), 
                ~ if_else(is.na(.x) & id_lifetime_use_amphetamine == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_inhalant, id_past_3_mo_urge_inhalant, id_past_3_mo_problem_inhalant, 
                  id_past_3_mo_fail_expect_inhalant, id_lifetime_concern_inhalant, id_lifetime_cutback_inhalant), 
                ~ if_else(is.na(.x) & id_lifetime_use_inhalant == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_sedative, id_past_3_mo_urge_sedative, id_past_3_mo_problem_sedative, 
                  id_past_3_mo_fail_expect_sedative, id_lifetime_concern_sedative, id_lifetime_cutback_sedative), 
                ~ if_else(is.na(.x) & id_lifetime_use_sedative == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_hallucinogen, id_past_3_mo_urge_hallucinogen, id_past_3_mo_problem_hallucinogen, 
                  id_past_3_mo_fail_expect_hallucinogen, id_lifetime_concern_hallucinogen, 
                  id_lifetime_cutback_hallucinogen), 
                ~ if_else(is.na(.x) & id_lifetime_use_hallucinogen == 0, "Never", .x)),
         across(c(id_past_3_mo_freq_opioid, id_past_3_mo_urge_opioid, id_past_3_mo_problem_opioid, 
                  id_past_3_mo_fail_expect_opioid, id_lifetime_concern_opioid, id_lifetime_cutback_opioid), 
                ~ if_else(is.na(.x) & id_lifetime_use_opioid == 0, "Never", .x)))
```


Score and add YAP
```{r}
yap_life <- screen %>%
  select(subid, yap_1:yap_27) %>%
  mutate(across(yap_1:yap_27, ~ if_else(.x == "No, never", 0, 1))) %>%
  rowwise() %>%
  mutate(id_yap_lifetime = sum(c_across(yap_1:yap_27))) %>%
  select(subid, id_yap_lifetime)

yap_past_year <- screen %>%
  select(subid, yap_1:yap_27) %>%
  mutate(across(yap_1:yap_27, ~ case_when(.x == "No, never" ~ 0,
                                          .x == "Yes, but not in the past year" ~ 0,
                                          TRUE ~ 1))) %>%
  rowwise() %>%
  mutate(id_yap_past_year = sum(c_across(yap_1:yap_27))) %>%
  select(subid, id_yap_past_year)


# add to screen_select
screen_select <- screen_select %>%
  full_join(yap_life, by = "subid") %>%
  full_join(yap_past_year, by = "subid")
```

Score and add SCL-90
```{r}
scl_90 <- screen %>%
  select(subid, contains("scl90")) %>%
  mutate(across(scl90_1:scl90_90, ~ dplyr::recode(.x,
                                                  "Not At All" = 0,
                                                  "A Little Bit" = 1,
                                                  "Moderately" = 2,
                                                  "Quite A Bit" = 3,
                                                  "Extremely" = 4))) %>%
  rowwise() %>%
  mutate(id_scl90_total = (sum(c_across(scl90_1:scl90_90)) - 90) / 90,
         id_scl90_somatization = (sum(scl90_1, scl90_4, scl90_12, scl90_27, scl90_40,
                                  scl90_42, scl90_48, scl90_49, scl90_52, scl90_53,
                                  scl90_56, scl90_58) - 12) / 12,
         id_scl90_obsess_compuls = (sum(scl90_3, scl90_9, scl90_10, scl90_28, scl90_38,
                                     scl90_45, scl90_46, scl90_51, scl90_55, scl90_65) - 10) / 10,
         id_scl90_interpers_sensibility = (sum(scl90_6, scl90_21, scl90_34, scl90_36,
                                            scl90_37, scl90_41, scl90_61, scl90_69,
                                            scl90_73) - 9) / 9,
         id_scl90_depression = (sum(scl90_5, scl90_14, scl90_20, scl90_22, scl90_26,
                                 scl90_29, scl90_30, scl90_31, scl90_32, scl90_54,
                                 scl90_71, scl90_79) - 12) / 12,
         id_scl90_anxiety = (sum(scl90_17, scl90_23, scl90_33, scl90_39, scl90_57,
                              scl90_72, scl90_78, scl90_80, scl90_86) - 9) / 9,
         id_scl90_anger_hostility = (sum(scl90_11, scl90_24, scl90_63, scl90_67,
                                      scl90_74, scl90_81) - 6) / 6,
         id_scl90_phobic_anxiety = (sum(scl90_13, scl90_25, scl90_47, scl90_50, scl90_70,
                                     scl90_75, scl90_82) - 7) / 7,
         id_scl90_paranoid = (sum(scl90_8, scl90_18, scl90_43, scl90_68, scl90_76,
                               scl90_83) - 6) / 6,
         id_scl90_psychoticism = (sum(scl90_7, scl90_16, scl90_35, scl90_62, scl90_77,
                                   scl90_84, scl90_85, scl90_87, scl90_88, scl90_90) - 10) / 10) %>%
  round(2) %>%
  select(-c(scl90_1:scl90_90))

screen_select <- screen_select %>%
  full_join(scl_90, by = "subid")
```


Score and add IUS
```{r}
ius <- screen %>%
  select(subid, contains("ius")) %>%
  mutate(across(ius_1:ius_27, ~ dplyr::recode(.x,
                                              "Very untrue of me" = 1,
                                              "Somewhat untrue of me" = 2,
                                              "Neutral" = 3,
                                              "Somewhat true of me" = 4,
                                              "Very true of me" = 5))) %>%
  rowwise() %>%
  mutate(id_ius_total = sum(c_across(ius_1:ius_27))) %>%
  select(-c(ius_1:ius_27))

screen_select <- screen_select %>%
  full_join(ius, by = "subid")
```


Score and add ASI-3
```{r}
asi3 <- screen %>%
  select(subid, contains("asi3")) %>%
  mutate(across(asi3_1:asi3_18, ~ dplyr::recode(.x,
                                              "Very untrue of me" = 0,
                                              "Somewhat untrue of me" = 1,
                                              "Neutral" = 2,
                                              "Somewhat true of me" = 3,
                                              "Very true of me" = 4))) %>%
  rowwise() %>%
  mutate(id_asi3_total = sum(c_across(asi3_1:asi3_18)) - 18,
         id_asi3_phys_concerns = sum(asi3_4, asi3_12, asi3_8, asi3_7, asi3_15, asi3_3) - 6,
         id_asi3_cog_concerns = sum(asi3_14, asi3_18, asi3_10, asi3_16, asi3_2, asi3_5) - 6,
         id_asi3_soc_concerns = sum(asi3_9, asi3_6, asi3_11, asi3_13, asi3_17, asi3_1) - 6) %>%
  select(-c(asi3_1:asi3_18))

screen_select <- screen_select %>%
  full_join(asi3, by = "subid")
```


Score and add DTS
```{r}
dts <- screen %>%
  select(subid, contains("dts")) %>%
  mutate(across(dts_1:dts_15, ~ dplyr::recode(.x,
                                              "Very untrue of me" = 1,
                                              "Somewhat untrue of me" = 2,
                                              "Neutral" = 3,
                                              "Somewhat true of me" = 4,
                                              "Very true of me" = 5)),
         # item 6 is reverse coded
         dts_6 = dplyr::recode(dts_6, "1" = 5, "2" = 4, "3" = 3, "4" = 2, "5" = 1)) %>%
  rowwise() %>%
  mutate(id_dts_total = sum(c_across(dts_1:dts_15)) / 15,
         id_dts_tolerance = sum(dts_1, dts_3, dts_5) / 3,
         id_dts_absorption = sum(dts_2, dts_4, dts_15) / 3,
         id_dts_appraisal = sum(dts_6, dts_7, dts_9, dts_10, dts_11, dts_12) / 6,
         id_dts_regulation = sum(dts_8, dts_13, dts_14) / 3) %>%
  round(2) %>%
  select(-c(dts_1:dts_15))

screen_select <- screen_select %>%
  full_join(dts, by = "subid")
```

Score and add FAD
```{r}
fad <- screen %>%
  select(subid, contains("fad")) %>%
  mutate(across(fad_1:fad_60, ~ dplyr::recode(.x,
                                              "Strongly Disagree" = 1,
                                              "Disagree" = 2,
                                              "Agree" = 3,
                                              "Strongly Agree" = 4)),
         # reverse coded items
         across(c(fad_14, fad_22, fad_35, fad_52, fad_4, fad_8, fad_15, fad_23,
                  fad_34, fad_45, fad_53, fad_58, fad_9, fad_19, fad_28, fad_39,
                  fad_5, fad_13, fad_25, fad_33, fad_37, fad_42, fad_54, fad_7,
                  fad_17, fad_27, fad_44, fad_47, fad_48, fad_1, fad_11, fad_21,
                  fad_31, fad_41, fad_51), ~ dplyr::recode(.x,
                                                           "1" = 4,
                                                           "2" = 3,
                                                           "3" = 2,
                                                           "4" = 1))) %>%
  rowwise() %>%
  mutate(id_fad_prob_solving = sum(fad_2, fad_12, fad_24, fad_38, fad_50, fad_60),
         id_fad_communication = sum(fad_3, fad_18, fad_29, fad_43, fad_59, fad_14,
                                 fad_22, fad_35, fad_52),
         id_fad_roles = sum(fad_10, fad_30, fad_40, fad_4, fad_8, fad_15, fad_23,
                         fad_34, fad_45, fad_53, fad_58),
         id_fad_affective_resp = sum(fad_49, fad_57, fad_9, fad_19, fad_28, fad_39),
         id_fad_affective_involv = sum(fad_5, fad_13, fad_25, fad_33, fad_37, fad_42, fad_54),
         id_fad_behavior_control = sum(fad_20, fad_32, fad_55, fad_7, fad_17, fad_27, fad_44,
                                    fad_47, fad_48),
         id_fad_gen_functioning = sum(fad_6, fad_16, fad_26, fad_36, fad_46, fad_56,
                                   fad_1, fad_11, fad_21, fad_31, fad_41, fad_51)) %>%
  select(-c(fad_1:fad_60))

screen_select <- screen_select %>%
  full_join(fad, by = "subid")
```

Score and add MPS
```{r}
mps <- screen %>%
  select(subid, contains("mps")) %>%
  mutate(across(where(is.logical), ~ as.numeric(.x) + 1)) %>%
  # recode character strings
  mutate(mps_17 = if_else(mps_17 == "I tend to seek the company of a friend.", 1, 2),
         mps_34 = if_else(mps_34 == "Having a pilot announce that the plane has engine trouble and it may be necessary to make an emergency landing.", 1, 2),
         mps_57 = if_else(mps_57 == "Having to walk around all day on a blistered foot,", 1, 2),
         mps_69 = if_else(mps_69 == "Being out on a sailboat during a great storm at sea,", 1, 2),
         mps_70 = if_else(mps_70 == "Stricter observance of major religious holidays", 1, 2),
         mps_81 = if_else(mps_81 == "Being at the circus when two lions suddenly get loose down in the ring,", 1, 2),
         mps_93 = if_else(mps_93 == "Riding a long stretch of rapids in a canoe,", 1, 2),
         mps_105 = if_else(mps_105 == 'Being chosen as the "target" for a knife-throwing act,', 1, 2),
         mps_129 = if_else(mps_129 == "Being in a flood", 1, 2),
         mps_141 = if_else(mps_141 == "Being seasick every day for a week while on an ocean voyage", 1, 2)) %>%
  # reverse coded items
  mutate(across(c(mps_63, mps_98, mps_122, mps_134, mps_145, mps_64, mps_99, mps_17,
                mps_28, mps_65, mps_89, mps_100, mps_124, mps_136, mps_148, mps_79,
                mps_21, mps_33, mps_80, mps_152, mps_11, mps_22, mps_34, mps_46,
                mps_69, mps_81, mps_93, mps_105, mps_129, mps_153, mps_47, mps_70,
                mps_118, mps_4, mps_14, mps_37, mps_61, mps_84, mps_108, mps_131),
                ~dplyr::recode(.x, "1" = 2, "2" = 1))) %>%
  rowwise() %>%
  mutate(id_mps_wellbeing = sum(mps_1, mps_26, mps_38, mps_50, mps_62, mps_74, mps_85,
                             mps_97, mps_109, mps_121, mps_133, mps_144) - 12,
         id_mps_social_potency = sum(mps_2, mps_15, mps_39, mps_51, mps_75, mps_87,
                                  mps_110, mps_63, mps_98, mps_122, mps_134, mps_145) - 12,
         id_mps_achievement = sum(mps_64, mps_99, mps_3, mps_16, mps_27, mps_52, mps_76,
                               mps_88, mps_111, mps_123, mps_135, mps_146) - 12,
         id_mps_social_closeness = sum(mps_17, mps_28, mps_65, mps_89, mps_100, mps_124,
                                    mps_136, mps_148, mps_5, mps_40, mps_77, mps_112) - 12,
         id_mps_stress_reaction = sum(mps_6, mps_18, mps_29, mps_41, mps_53, mps_78,
                                   mps_90, mps_101, mps_113, mps_125, mps_137, mps_149) - 12,
         id_mps_alienation = sum(mps_7, mps_19, mps_30, mps_42, mps_54, mps_66, mps_91,
                              mps_102, mps_114, mps_126, mps_138, mps_150) - 12,
         id_mps_aggression = sum(mps_8, mps_20, mps_31, mps_43, mps_55, mps_67, mps_103,
                              mps_115, mps_127, mps_139, mps_151, mps_79) - 12,
         id_mps_control = sum(mps_9, mps_44, mps_56, mps_68, mps_92, mps_116, mps_128,
                           mps_140, mps_21, mps_33, mps_80, mps_152) - 12,
         id_mps_harm_avoidance = sum(mps_57, mps_141, mps_11, mps_22, mps_34, mps_46,
                                  mps_69, mps_81, mps_93, mps_105, mps_129, mps_153) - 12,
         id_mps_traditionalism = sum(mps_12, mps_23, mps_35, mps_58, mps_82, mps_94,
                                  mps_106, mps_142, mps_154, mps_47, mps_70, mps_118) - 12,
         id_mps_absorption = sum(mps_13, mps_24, mps_36, mps_48, mps_59, mps_71, mps_83,
                              mps_95, mps_107, mps_119, mps_130, mps_155) - 12,
         id_mps_unlikely_virtues = sum(mps_25, mps_49, mps_72, mps_96, mps_120, mps_143,
                                    mps_147, mps_4, mps_14, mps_37, mps_61, mps_84,
                                    mps_108, mps_131) - 14) %>%
  select(-c(mps_1:mps_155))

screen_select <- screen_select %>%
  full_join(mps, by = "subid")
```


```{r}
screen_select %>% 
  write_csv(here(path_meta, "static_features.csv")) %>% 
  glimpse()
```

```{r}
screen_select %>% 
  write_rds(here(path_meta, "static_features.rds"))
```

