---
title: "Make Meta Logs"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---


### Code Status

Code is almost fully complete. Data in output can be trusted but more exploration on numbers should be done to ensure we are not missing any contact/log entry pairings.    


### Conclusions

* Still need to print warnings with extract number function and look for any missed patterns for cleaning. Purpose would be to make sure we match all instances of known contacts in logs to context variables.   
* More work could be done to understand what duplicates mean in SMS files. This shouldn't affect meta project though.     
* The extract number function takes a long time to run (several hours). I have code chunks with this function set to cache = TRUE.         
  

### Notes
Purpose: This script does further cleaning and pre-processing on the voice and SMS logs specifically for meta study. It outputs a single clean log file joined with the cleaned contact variables ready for feature engineering in the meta project.    

Preprocessing steps:   

1. Handle any identified errors/anomalies in clean scripts    
2. Join logs on common variables    
3. Filter down to analysis sample (N = 154; participants who completed followup 1)    
4. Format numbers to match contacts and join with context variables   
5. EDA on numbers/variables and check for contacts not in logs     


Inputs:  

- voice_ios.csv    
- voice_android.csv   
- sms_ios.csv   
- sms_android.csv  
- contacts.csv    


Output:   

- meta_logs.csv   

### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Absolute Paths 
```{r}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_lab_support <- "P:/toolboxes/lab_support"},
        # IOS paths
        Darwin = {
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"})
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
# Detect and warn about function conflicts
library(conflicted) 
conflict_prefer("filter", "dplyr")

# establish project directory consistently as working directory
library(here)  
```

Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(readxl)
library(lubridate)
library(janitor)

source(here(path_lab_support, "fun_phone_numbers.R"))
```

Global Settings
```{r}
theme_set(theme_classic())
options(tibble.print_max = Inf)
options(tibble.width = Inf)
```


## Voice IOS logs

### Read in Data
Read in voice IOS data and filter down to variables for meta
```{r}
voice_ios <- vroom::vroom(here(path_shared, "voice_ios.csv"), col_types = vroom::cols()) %>%
  select(subid, zdate, zaddress, zduration, zanswered, zoriginated, zunique_id) %>% 
  glimpse()
```

### Clean errors identified in clean script EDA

Filter out log entries with missing dates
```{r}
voice_ios %>% 
  filter(is.na(zdate))

voice_ios <- voice_ios %>% 
  filter(!is.na(zdate))
```


Numbers with a wait (;)       
A wait tells the phone to wait for action by the user (tapping a button) before dialing the next sequence of numbers. A wait in a phone number is denoted by a semi-colon ; for example: 222-222-2222;12345.    
```{r}
voice_ios %>% 
  filter(str_detect(zaddress, ";")) %>% 
  select(subid, zaddress)
```

Keeping US number before semicolon as number.
```{r}
voice_ios <- voice_ios %>% 
  mutate(zaddress = case_when(zaddress == "608-663-3926;206" ~ "608-663-3926",
                              zaddress == "+12623678600;114" ~ "+12623678600",
                              zaddress == "6082561901;15045" ~ "6082561901",
                              zaddress == "+86566;n" ~ "+86566",
                              zaddress == "6082332100;2024" ~ "6082332100",
                              zaddress == "6086615437;116" ~ "6086615437",
                              zaddress == "8444176626;5618" ~ "8444176626",
                              zaddress == "18774155164;5077085016597013" ~ "18774155164",
                              TRUE ~ zaddress))
```



### Filter out duplicates

`r nrow(voice_ios) - nrow(distinct(voice_ios))` duplicates remain in dataset due to updates made to log entries between visits (e.g., read status).   

Note: there is no read variable for android voice logs so we cannot use this variable.   

Check all duplicates    
All duplicates have an update to z_opt variable suggesting something happened in between log downloads. Does not appear relevant for meta project so can filter out duplicates.   
```{r}
voice_ios_full <- vroom::vroom(here(path_shared, "voice_ios.csv"), col_types = vroom::cols())

dup_voice_ios <- voice_ios %>% 
  count(across(subid:zunique_id)) %>% 
  filter(n > 1)

voice_ios_full %>% 
  left_join(dup_voice_ios, by = c("subid", "zdate", "zaddress", "zduration", "zanswered", "zoriginated", "zunique_id")) %>% 
  filter(!is.na(n)) %>% 
  arrange(subid, zdate) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


Remove duplicates
```{r}
voice_ios <- voice_ios %>% 
  distinct()
```


### Clean numbers

Clean numbers with function
```{r cache = TRUE}
voice_ios$number_formatted <- map_chr(voice_ios$zaddress, extract_number)
```


## Voice Android logs

### Read in data
```{r}
voice_android <- vroom::vroom(here(path_shared, "voice_android.csv"), col_types = vroom::cols()) %>% 
  select(subid, number, duration, date, type) %>% 
  glimpse()
```

### Clean errors identified in clean script EDA

Remove number after semicolon (wait indicator)
```{r}
voice_android %>% 
  filter(str_detect(number, ";")) %>% 
  select(subid, number)

voice_android <- voice_android %>% 
  mutate(number = case_when(number == "+1-385-262-3849;418173518#" ~ "3852623849",
                            TRUE ~ number))
```
  

invalid duration value of -4   
Duration cannot be negative; changing to NA since no way of knowing actual duration
```{r}
voice_android <- voice_android %>% 
  mutate(duration = case_when(duration == -4 ~ as.numeric(NA),
                              TRUE ~ duration))
```

invalid type values   
8 subids produced invalid numbers for type variable. Changing these numbers to NA since 
we have no way of determining correct value.
```{r}
voice_android <- voice_android %>% 
  mutate(type = case_when(type %in% c(8, 9, 10, 101, 1000, 1001, 1002, 6503) ~ as.character(NA),
                          TRUE ~ as.character(type)))
```

### Check duplicates   

No duplicates
```{r}
voice_android %>% 
  count(across(subid:type)) %>% 
  filter(n > 1)
```


### Clean numbers

Clean numbers with function
```{r cache = TRUE}
voice_android$number_formatted <- map_chr(voice_android$number, extract_number)
```


## Join voice logs

### Common voice log variables relevant to meta project

- subid - participant identifier   
- dttm_obs - date and time of log entry    
- number - raw phone number of other party   
- formatted_number - number formatted to match contacts   
- originated - incoming or outgoing    
- call_duration - duration of call  
- call_answered - answered or not answered     


### tidy android variables for merge
```{r}
voice_android %>% 
  glimpse()
```

Create new variables to match IOS
```{r}
voice_android <- voice_android %>% 
  rename(call_duration = duration,
         dttm_obs = date) %>% 
  mutate(originated = case_when( type == "Missed" ~ "incoming",
                                 type == "Voicemail" ~ "incoming",
                                 type == "Rejected" ~ "incoming",
                                 type == "Blocked" ~ "incoming",
                                 type == "Answered Externally" ~ "incoming",
                                 type == "Incoming" ~ "incoming",
                                 type == "Outgoing" ~ "outgoing",
                                 TRUE ~ type),
         is_answered = case_when(type == "incoming" ~ "yes",
                              is.na(type) ~ as.character(NA),
                              TRUE ~ "no")) %>% 
  select(-type) %>% 
  glimpse()
```


### tidy ios variables for merge
```{r}
voice_ios %>% 
  glimpse()

voice_ios <- voice_ios %>% 
  select(c(subid,
           dttm_obs = zdate,
           originated = zoriginated,
           call_answered = zanswered,
           call_duration = zduration,
           number = zaddress,
           number_formatted)) %>%
  mutate(originated = case_when(originated == "Incoming" ~ "incoming",
                                originated == "Outgoing" ~ "outgoing",
                                TRUE ~ originated)) %>% 
  mutate(is_answered = case_when(call_answered == "Not Answered" ~ "no",
                                   call_answered == "Answered" ~ "yes",
                                   TRUE ~ call_answered)) %>% 
  select(-call_answered) %>% 
  glimpse()
```


### Join

join voice logs
```{r}
logs_voice <- voice_android %>% 
  full_join(voice_ios,  by = c("subid", "number", "call_duration", "dttm_obs", "originated", 
                               "is_answered", "number_formatted")) %>% 
  # add new variable to mark these are voice logs
  mutate(log_type = "voice") %>% 
  glimpse()
```



## SMS IOS logs

### Read in data
```{r}
sms_ios <- vroom::vroom(here(path_shared, "sms_ios.csv"), col_types = vroom::cols()) %>% 
  # temporarily keeping text and log_file to filter out duplicates
  select(subid, phone_number, date, is_delivered, is_from_me, is_sent, is_read, 
         is_prepared, n_people_in_chat, text, chat_id, log_file) %>% 
  glimpse()
```


### Filter out duplicates

`r nrow(sms_ios) - nrow(distinct(sms_ios %>% select(-log_file)))` duplicates exist in dataset.  

Check all duplicates    
```{r}
sms_ios_full <- vroom::vroom(here(path_shared, "sms_ios.csv"), col_types = cols())

dup_sms_ios <- sms_ios %>% 
  select(-log_file) %>% 
  count(across(subid:chat_id)) %>% 
  filter(n > 1)

dup_sms_ios <- sms_ios_full %>% 
  left_join(dup_sms_ios, by = c("subid", "phone_number", "date", "is_delivered", 
                                "is_from_me", "is_sent", "is_read", "is_prepared",
                                "n_people_in_chat", "text", "chat_id")) %>% 
  filter(!is.na(n)) %>% 
  arrange(subid, date)
```

Duplicates not related to group messages    
Many of these are on the same log so I am unclear as to why there are duplicates with different message_id and guid's. For purposes of meta project these are identical on the relevant variables. So I will not investigate further at the moment.   
```{r}
dup_sms_ios %>% 
  filter(n_people_in_chat == 1) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Some duplicates appear to exist due to how group messages are handled. Same date, text, number but message_id, guid, other_handle, and other unique message identifiers seem to differ. These variables are not relevant for meta.  
```{r}
dup_sms_ios %>% 
  filter(n_people_in_chat > 1) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Most duplicates are missing a chat_id but they appear to have the same pattern seen with duplicates related to group messages.    
```{r}
dup_sms_ios %>% 
  filter(is.na(n_people_in_chat)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Remove duplicates
```{r}
sms_ios <- sms_ios %>% 
  distinct(across(-log_file), .keep_all = TRUE)
```


### Handle non-identical duplicates do to changes in read status

Both ios and android have a read variable for sms logs. Will retain this variable for meta study.   

Keep 2nd entry for read discrepancies
```{r}
sms_ios <- sms_ios %>% 
  group_by(subid, phone_number, date, is_delivered, is_from_me, is_sent, is_prepared,
           n_people_in_chat, text, chat_id) %>% 
  arrange(desc(log_file)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  # remove log_file variable
  select(-log_file)
```


### Group Messages

create group message variable    
log entries with missing chat_id will have to be set to NA since there was no way to count number of phone numbers associated with a chat.
```{r}
sms_ios <- sms_ios %>% 
  mutate(message_is_group = case_when(n_people_in_chat > 1 ~ "yes",
                                      n_people_in_chat == 1 ~ "no",
                                      TRUE ~ as.character(NA))) %>% 
  glimpse()
```



Note: IOS outgoing text messages have NA as the number if sent to more than one person.


check new variable
```{r}
tabyl(sms_ios$message_is_group)
```

### Clean numbers

Clean numbers with function
```{r cache = TRUE}
sms_ios$number_formatted <- map_chr(sms_ios$phone_number, extract_number)
```


## SMS Android logs

### Read in data
```{r}
sms_android <- vroom::vroom(here(path_shared, "sms_android.csv"), col_types = vroom::cols()) %>% 
  # keep text message content and log_file in for filtering out duplicates
  select(subid, address, date, type, text = body, read, log_file) %>% 
  glimpse()
```


### Filter out Duplicates    

`r nrow(sms_android) - nrow(distinct(sms_android %>% select(-log_file)))` duplicates exist in dataset.  

Check all duplicates    
Not clear what caused duplicate but they are identical on all meta relevant variables so not going to investigate further at the moment. 
```{r}
sms_android_full <- vroom::vroom(here(path_shared, "sms_android.csv"), col_types = vroom::cols()) %>% 
  rename(text = body)

dup_sms_android <- sms_android %>% 
  count(across(subid:read)) %>% 
  filter(n > 1)

sms_android_full %>% 
  left_join(dup_sms_android, by = c("subid", "address", "date", "type", "text", "read")) %>% 
  filter(!is.na(n)) %>% 
  arrange(subid, date) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```


Remove duplicates
```{r}
sms_android <- sms_android %>% 
  distinct(across(-log_file), .keep_all = TRUE) 
```



### Handle non-identical duplicates do to changes in read status

Keep 2nd entry 
```{r}
sms_android <- sms_android %>% 
  group_by(subid, address, date, type, text) %>% 
  arrange(desc(log_file)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  # remove log_file variable
  select(-log_file)
```


### Group Messages

Identify group messages 
```{r}
sms_android %>% 
  filter(str_detect(address, "~")) %>% 
  select(address)
```

count number of people in group messages (# of ~ + 1) 
```{r}
sms_android <- sms_android %>% 
  mutate(message_n_people = str_count(address, "~") + 1) %>% 
  glimpse()
```


Add group variable
```{r}
sms_android <- sms_android %>% 
  mutate(message_is_group = case_when(str_detect(address, "~") ~ "yes",
                                      !str_detect(address, "~") ~ "no",
                                      TRUE ~ as.character(NA))) %>% 
  glimpse()

tabyl(sms_android$message_is_group)
```


### Clean numbers

Clean numbers with function
```{r cache = TRUE}
sms_android$number_formatted <- map_chr(sms_android$address, extract_number)
```



## Join SMS variables

### Common voice log variables relevant to meta project  

- subid - participant identifier   
- dttm_obs - date and time of log entry    
- number - raw phone number of other party   
- formatted_number - number formatted to match contacts    
- message_read = yes if sent or read status on incoming message   
- message_failed = yes if outgoing message not delivered    
- originated = outgoing if from_me else incoming (type is NA for android group messages)    
- message_is_group = yes if group message   
- message_n_people = number of people in message thread  


### tidy android variables for merge
```{r}
sms_android <- sms_android %>% 
  rename(number = address,
         message_read = read,
         dttm_obs = date) %>% 
  mutate(message_failed = if_else(type == "failed", "yes", "no"),
         originated = case_when(type == "sent" ~ "outgoing",
                                  type == "draft" ~ "outgoing",
                                  type == "failed" ~ "outgoing",
                                  type == "inbox" ~ "incoming")) %>% 
  select(-c(text, type)) %>% 
  glimpse()
```


### tidy IOS variables for merge

```{r}
sms_ios <- sms_ios %>% 
  rename(number = phone_number, 
         message_n_people = n_people_in_chat,
         dttm_obs = date) %>% 
  mutate(message_read = case_when(is_read == 1 ~ "yes",
                               is_from_me == 1 ~ "yes",
                               TRUE ~ "no"),
         message_failed = case_when(is_sent == 0 & is_from_me == 1 ~ "yes",
                                    TRUE ~ "no"),
         originated = case_when(is_sent == 1 ~ "outgoing",
                                  is_from_me == 1 ~ "outgoing",
                                  TRUE ~ "incoming")) %>% 
  select(-c(is_delivered, is_from_me, is_sent, is_read, is_prepared, chat_id, text)) %>% 
  glimpse()
```


### Join

```{r}
logs_sms <- sms_android %>%
  full_join(sms_ios, by = c("subid", "number", "dttm_obs", "message_read", "message_failed", 
                            "originated", "message_is_group", "message_n_people", "number_formatted")) %>%
  # add new variable to mark these are sms logs
  mutate(log_type = "sms") %>%
  glimpse()
```




## Join SMS and Voice logs

```{r}
logs <- logs_voice %>%  
  full_join(logs_sms, by = c("subid", "dttm_obs", "number", "log_type", "originated", "number_formatted")) %>%
  select(subid, dttm_obs, number, log_type, originated, everything()) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  glimpse()
```



Filter down to analysis sample (N = 154)   

Read in visit dates
```{r}
visit_dates <- vroom::vroom(here(path_shared, "visit_dates.csv"), col_types = vroom::cols()) 

study_sample <- visit_dates %>% 
  filter(!is.na(followup_1)) %>% 
  glimpse()
```

Filter log data
```{r}
logs <- logs %>% 
  filter(subid %in% study_sample$subid)
```





## Contacts

### Read in Data
```{r}
contacts <- vroom::vroom(here(path_shared, "contacts.csv"), col_types = "icccccccccccccc") %>% 
  glimpse()
```

Filter contacts down to analysis sample
```{r}
contacts <- contacts %>% 
  filter(subid %in% study_sample$subid)
```

### Clean errors identified in clean script EDA

Invalid response (unpleasant/mixed) for "How would you describe your typical experience 
with this person?"   

Recode as mixed  
```{r}
contacts <- contacts %>% 
  mutate(contact_experience = case_when(contact_experience == "Unpleasant/mixed" ~ "Mixed",
                                        TRUE ~ contact_experience))
```

Remove entry with missing number
```{r}
contacts %>% 
  filter(is.na(phone_number))

contacts <- contacts %>% 
  filter(!is.na(phone_number))
```




### Handle duplicate numbers 

```{r}
# Duplicate subid/phone number pairs
dup_contacts <- contacts %>%
  group_by(subid, phone_number) %>%
  summarise(n = n(), .groups = "drop") %>%
  dplyr::filter(n > 1)

print(dup_contacts, n = Inf)
```

`r nrow(dup_contacts)` duplicates to handle    
```{r}
dup_contacts <- contacts %>%
  left_join(dup_contacts, by = c("subid", "phone_number")) %>%
  arrange(subid, phone_number) %>% 
  filter(n == 2) 
```



Duplicate 1: Subid 86
Differs on two context variable and address   
Keep first entry but with updated address
```{r}
dup_contacts %>%
  slice(1:2)

contacts <- contacts %>% 
  mutate(street_address = case_when(subid == 86 & utc == "1531924200" & phone_number == "6304275562" ~ 
                                      "642 State Street",
                                    TRUE ~ street_address),
         city = case_when(subid == 86 & utc == "1531924200" & phone_number == "6304275562" ~ 
                                      "Madison",
                                    TRUE ~ city),
         state = case_when(subid == 86 & utc == "1531924200" & phone_number == "6304275562" ~ 
                                      "WI",
                                    TRUE ~ state)) %>% 
  filter(!(subid == 86 & utc == 1534779600 & phone_number == 6304275562))
```


Duplicate 2: Subid 104  
This is an interesting one because it looks like they stopped frequently visiting a family member (monthly visit variable).   
Keep first entry
```{r} 
dup_contacts %>%
  slice(3:4)

contacts <- contacts %>% 
  filter(!(subid == 104 & utc == 1537991280 & phone_number == 6084693159))
```

Duplicate 3: Subid 109  
Keep first entry 
```{r}
dup_contacts %>%
  slice(5:6)

contacts <- contacts %>% 
  filter(!(subid == 109 & utc == 1537819200 & phone_number == 6305611375))
```

Duplicate 4: Subid 110  
Keep 2nd entry - Both entries completed on same day.   
```{r}
dup_contacts %>%
  slice(7:8)

contacts <- contacts %>% 
  filter(!(subid == 110 & utc == 1534531200 & phone_number == 4148819604))
```

Duplicate 5-6: Subid 117   
These 2 are really conflicting - removing context entries since we can discern which is correct
```{r}
dup_contacts %>%
  slice(9:10)

dup_contacts %>%
  slice(11:12)

contacts <- contacts %>% 
  filter(!(subid == 117 & phone_number == 6085987543)) %>% 
  filter(!(subid == 117 & phone_number == 919811021816))
```


Duplicate 7: Subid 240   
Only change is updated address   
Keep first entry since this was address 2/3 months on study   
```{r}
dup_contacts %>%
  slice(13:14)

contacts <- contacts %>% 
  filter(!(subid == 240 & utc == 1566831600 & phone_number == 9204509643))
```

Duplicate 8-11: Subid 248  
8 differs on only one variable - keep 1st entry  
```{r}
dup_contacts %>%
  slice(15:16)

contacts <- contacts %>% 
  filter(!(subid == 248 & utc == 1568314800 & phone_number == 6084452342))
```

9 differs on three variables some are probably important (drinker vs. nondrinker)   
Keep first entry 
```{r}
dup_contacts %>%
  slice(17:18)

contacts <- contacts %>% 
  filter(!(subid == 248 & utc == 1568314800 & phone_number == 6086695757))
```

10 differs on only one variable - keep 1st entry  
```{r}
dup_contacts %>%
  slice(19:20)

contacts <- contacts %>% 
  filter(!(subid == 248 & utc == 1568314800 & phone_number == 6088432572))
```

11 differs on 3 variables   
Keep first entry
```{r}
dup_contacts %>%
  slice(21:22)

contacts <- contacts %>% 
  filter(!(subid == 248 & utc == 1568314800 & phone_number == 9062815847))
```

Duplicate 12: Subid 269   
Keep first entry
```{r}
dup_contacts %>%
  slice(23:24)

contacts <- contacts %>% 
  filter(!(subid == 269 & utc == 1575567600 & phone_number == 6309131339))
```




### Use contacts to find area codes for 7 digit numbers in logs
```{r message = FALSE}
numbers_7_digits <- logs %>% 
  filter(str_detect(number, "^[1-9]") & nchar(number) == 7) %>% 
  select(number) %>% 
  unlist(use.names = FALSE)

contacts_7_digits <- tibble(subid = as.numeric())

for (i in seq_along(numbers_7_digits)) {
  match <- contacts %>% 
    filter(str_detect(phone_number, numbers_7_digits[i])) %>% 
    mutate(pattern = numbers_7_digits[i])
  if(nrow(match) != 0) {  
    contacts_7_digits <- contacts_7_digits %>% full_join(match)
  }
}

contacts_7_digits %>% 
  select(subid, phone_number, pattern, contact_type) %>% 
  group_by(subid, phone_number, pattern) %>% 
  slice(1) %>% 
  print(n = Inf) 
```

Area code is 608 for most but not all 7-digit number matches
```{r}
contacts_7_digits %>% 
  mutate(area_code = str_sub(phone_number, 1, 3)) %>% 
  tabyl(area_code)
```

Join numbers with log entries on number and subid and replace formatted number with contact number    
```{r}
logs <- logs %>% 
  mutate(subid = as.numeric(subid)) %>% 
  left_join(contacts_7_digits %>% 
              select(subid, contact_number = phone_number, number = pattern), 
            by = c("subid", "number")) %>% 
  mutate(number_formatted = case_when(!is.na(contact_number) ~ as.character(contact_number),
                                      TRUE ~ number_formatted)) %>% 
  glimpse()
```

7-digit Log entries with contact matches
```{r}
logs %>% 
  filter(!is.na(contact_number)) %>% 
  select(subid, number, contact_number, dttm_obs) %>% 
  print(n = Inf)
```

remove contact number variable
```{r}
logs <- logs %>% 
  select(-contact_number)
```




## Join logs with contacts on formatted number
```{r}
glimpse(contacts)
glimpse(logs)

logs <- logs %>% 
  left_join(contacts %>% 
              select(-utc) %>% 
              mutate(phone_number = as.character(phone_number)), 
              by = c("subid", "number_formatted" = "phone_number")) %>% 
  glimpse()
```



## Contacts without log entries

```{r}
contacts %>% 
  filter(!phone_number %in% logs$number_formatted)
```



## Check unknown patterns for matches to contacts   

HANDLE: print warnings and look for possible missed matches to contacts    



## Other EDA

`r length(unique(logs$subid))` subids have voice and/or sms logs.   

Missing data    
```{r}
logs %>%
  naniar::miss_var_summary()
```

Removing addresses since too many missing data
```{r}
logs <- logs %>% 
  select(-c(street_address, city, state)) %>% 
  glimpse()
```

High percentage of missing call answered and duration variables due to the majority of the logs being text message logs.   
log type
```{r}
tabyl(logs$log_type)
```

originated
```{r}
tabyl(logs$originated)
```

call duration
```{r}
logs %>% 
  filter(log_type == "voice") %>% 
  summarise(min = min(call_duration, na.rm = TRUE),
            mean = mean(call_duration, na.rm = TRUE),
            max = max(call_duration, na.rm = TRUE))
```

call answered
```{r}
logs %>% 
  filter(log_type == "voice") %>% 
  tabyl(is_answered)
```

message read
```{r}
logs %>% 
  filter(log_type == "sms") %>% 
  tabyl(message_read)
```

message is group
```{r}
logs %>% 
  filter(log_type == "sms") %>% 
  tabyl(message_is_group)
```

Number of people in message thread
```{r}
logs %>% 
  filter(log_type == "sms") %>% 
  summarise(min = min(message_n_people, na.rm = TRUE),
            mean = mean(message_n_people, na.rm = TRUE),
            max = max(message_n_people, na.rm = TRUE))
```

message failed   
```{r}
logs %>% 
  filter(log_type == "sms") %>% 
  tabyl(message_failed)
```

contact type
```{r}
tabyl(logs$contact_type)
```

contact has drinken with subid in past
```{r}
tabyl(logs$contact_drank_past)
```

Contact drinking status
```{r}
tabyl(logs$drink_status)
```

Contact would drink in front of subid in future
```{r}
tabyl(logs$contact_drink_future)
```

Contact is in recovery
```{r}
tabyl(logs$recovery)
```

Contact is supportive of participant's recovery
```{r}
tabyl(logs$support_status)
```

Level of pleasantness or unpleasantness of interactions with this contact
```{r}
tabyl(logs$contact_experience)
```

Whether participant visits this contact's home monthly
```{r}
tabyl(logs$monthly_visit)
```

## Clean variable names
```{r}
logs <- logs %>% 
  rename(drank_with_in_past = contact_drank_past,
         is_drinker = drink_status,
         will_drink_in_presence = contact_drink_future,
         in_recovery = recovery,
         supportiveness = support_status,
         experience = contact_experience,
         visits_monthly = monthly_visit) %>% 
  mutate(contact_type = case_when(contact_type == "Aunt/Uncle" ~ "aunt_uncle",
                                  contact_type == "Child" ~ "child",
                                  contact_type == "Co-Worker/Business Contact" ~ "coworker",
                                  contact_type == "Counselor" ~ "counselor",
                                  contact_type == "Cousin" ~ "cousin",
                                  contact_type == "Family-Other" ~ "family_other",
                                  contact_type == "Friend" ~ "friend",
                                  contact_type == "Grandparent" ~ "grandparent",
                                  contact_type == "Irrelevant/Spam" ~ "irrelevant",
                                  contact_type == "Other" ~ "other",
                                  contact_type == "Parent" ~ "parent",
                                  contact_type == "Self" ~ "self",
                                  contact_type == "Sibling" ~ "sibling",
                                  contact_type == "Social Worker/Case Manager" ~ "social_worker",
                                  contact_type == "Spouse/Significant Other" ~ "significant_other",
                                  TRUE ~ contact_type),
         drank_with_in_past = case_when(drank_with_in_past == "Almost Always/Always" ~ "always_almost_always",
                                        drank_with_in_past == "Never/Almost Never" ~ "never_almost_never",
                                        drank_with_in_past == "Occasionally" ~ "occasionally",
                                        TRUE ~ drank_with_in_past),
         is_drinker = case_when(is_drinker == "Dont Know" ~ "dont_know",
                                is_drinker == "Drinker" ~ "yes",
                                is_drinker == "NonDrinker" ~ "no",
                                TRUE ~ is_drinker),
         will_drink_in_presence = case_when(will_drink_in_presence == "No" ~ "no",
                                            will_drink_in_presence == "Uncertain" ~ "uncertain",
                                            will_drink_in_presence == "Yes" ~ "yes",
                                            TRUE ~ will_drink_in_presence),
         in_recovery = case_when(in_recovery == "Dont Know" ~ "dont_know",
                                 in_recovery == "No" ~ "no",
                                 in_recovery == "Yes" ~ "yes",
                                 TRUE ~ in_recovery),
         supportiveness = case_when(supportiveness == "Dont Know" ~ "dont_know",
                                    supportiveness == "Mixed" ~ "mixed",
                                    supportiveness == "Neutral" ~ "neutral",
                                    supportiveness == "Supportive" ~ "supportive",
                                    supportiveness == "Unsupportive" ~ "unsupportive",
                                    TRUE ~ supportiveness),
         experience = case_when(experience == "Mixed" ~ "mixed",
                                experience == "Neutral" ~ "neutral",
                                experience == "Pleasant" ~ "pleasant",
                                experience == "Unpleasant" ~ "unpleasant",
                                TRUE ~ experience),
         visits_monthly = case_when(visits_monthly == "No" ~ "no",
                                    visits_monthly == "Yes" ~ "yes",
                                    TRUE ~ visits_monthly))
```

## Write csv
```{r}
write_csv(logs, here(path_meta, "meta_logs.csv")) %>% 
  glimpse() 
```



