---
title: "Make samples"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---

### Code Status

This code is complete.      



### Conclusions   

- This script marks subids to be held out as a test sample or eyeball sample. It 
returns a dataframe of subids (one row per subid).   

- 30% of subids with lapses and 30% of subids without lapses are marked as the held 
out test (`test = TRUE`).    

- The remaining 70% (`test = FALSE`) make up the train set.      

- 20% of subids with lapses and 20% of subids without lapses in the training set 
are marked as an eyeball sample for EDA (`eyeball = TRUE`).     


### Set Up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_lab_support <- "/Volumes/private/toolboxes/lab_support"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)
library(vroom)
library(janitor)
library(lubridate)

theme_set(theme_classic())
```


Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_lab_support, "print_kbl.R"))
source(here("shared/fun_risk.R"))
```

### Read in data

Get lapses
```{r}
lapses <- vroom::vroom(here(path_shared, "lapses.csv"), col_types = vroom::cols()) %>% 
  # put all date times in Central time
  mutate(lapse_start = with_tz(lapse_start, "America/Chicago"),
         lapse_end = with_tz(lapse_end, "America/Chicago"),
         ema_end = with_tz(ema_end, "America/Chicago")) %>% 
  # keep only valid lapses
  filter(!exclude) %>% 
  glimpse()
```

Get all subids from labels
```{r}
subids <- vroom::vroom(here(path_meta, "labels_all.csv"), col_types = vroom::cols()) %>% 
  select(subid) %>% 
  unique()
```


### Create two groups of subids

`r length(unique(lapses$subid))` subids with lapses
```{r}
subs_lapses <- lapses %>% 
  count(subid) %>% 
  rename(n_lapses = n)

subs_lapses %>% 
  arrange(desc(n_lapses))
```


`r length(unique(subset(subids, !subid %in% subs_lapses$subid)$subid))` subids without any lapses
```{r}
subs_no_lapses <- subids %>% 
  filter(!subid %in% subs_lapses$subid) %>% 
  mutate(n_lapses = 0)
  
subs_no_lapses %>% 
  arrange(subid)
```

### Create test set

set seed
```{r}
set.seed(102030)
```

Select random sample of 30% of subids with lapses and 30% of subids without lapses  
30% of 84 subids with lapses = `r round(84 * .3)`   
30% of 67 subids with no lapses = `r round(67 * .3)`   
```{r}
subs_test <- slice_sample(subs_lapses, n = 25) %>% 
  bind_rows(slice_sample(subs_no_lapses, n = 20)) %>% 
  mutate(test = TRUE)
```

`r nrow(subs_test)` subids in held out test set     
45/151 = `r round(45/151, 2)`
```{r}
subs_test
```


### Create eyeball sample

Select random sample of 20% of subids with lapses and of those only not in test set and 20% without lapses    
20% of 84 subids with lapses = `r round(84 * .2)`   
20% of 67 subids with no lapses = `r round(67 * .2)`   
```{r}
subs_eyeball <- slice_sample(subs_lapses %>% filter(!subid %in% subs_test$subid), 
                             n = 17) %>% 
  bind_rows(slice_sample(subs_no_lapses %>% filter(!subid %in% subs_test$subid),
                         n = 13)) %>% 
  mutate(eyeball = TRUE)
```

`r nrow(subs_eyeball)` subids in eyeball set     
30/151 = `r round(30/151, 2)`  
```{r}
subs_eyeball
```



### Create final `samples` dataframe

Bind subids with lapses and without lapses
```{r}
samples <- subs_lapses %>% 
  bind_rows(subs_no_lapses) %>% 
  glimpse()
```

Add `test` and `eyeball`
```{r}
samples <- samples %>%
  mutate(eyeball = if_else(subid %in% subs_eyeball$subid, TRUE, FALSE),
         test = if_else(subid %in% subs_test$subid, TRUE, FALSE)) %>% 
  glimpse()
```

Check subids are not in both test and eyeball sample
```{r}
samples %>% 
  tabyl(eyeball, test)
```



### Eyeball Sample EDA

Join samples df to lapses    
```{r}
lapses <- lapses %>% 
  left_join(samples, by = "subid")
```

`r nrow(subset(lapses, eyeball))` lapses in eyeball set.   


Visualize lapse days and times     

Hours
```{r}
lapses %>% 
  filter(eyeball) %>% 
  rowwise() %>% 
  mutate(hours = str_split(lapse_start, pattern = " ")[[1]][2],
         hours = str_split(hours, pattern = ":")[[1]][1],
         hours = factor(as.numeric(hours), levels = c(1:24), ordered = TRUE)) %>% 
  ggplot(aes(x = hours)) +
  geom_bar(aes(y = ..count../sum(..count..))) +
  ylab("proportion") +
  scale_x_discrete(drop = FALSE)
```


Days
```{r}
lapses %>% 
  filter(eyeball) %>% 
  mutate(day = wday(lapse_start, label = TRUE)) %>% 
  ggplot(aes(x = day)) +
  geom_bar(aes(y = ..count../sum(..count..))) +
  ylab("proportion")
```



Hours and Days

```{r fig.width = 10}
lapses %>% 
  filter(eyeball) %>% 
  rowwise() %>% 
  mutate(hours = str_split(lapse_start, pattern = " ")[[1]][2],
         hours = str_split(hours, pattern = ":")[[1]][1],
         hours = factor(as.numeric(hours), levels = c(1:24), ordered = TRUE)) %>% 
  mutate(day = wday(lapse_start, label = TRUE)) %>% 
  tabyl(day, hours) %>% 
  pivot_longer(cols = c(2:25), names_to = "hour") %>% 
  mutate(day_hour = str_c(as.character(day), hour, sep = " ")) %>% 
  mutate(day_hour = factor(day_hour, levels = day_hour, ordered = TRUE)) %>% 
  ggplot(aes(x = day_hour, y = value/nrow(subset(lapses, eyeball)))) +
  geom_bar(stat = "identity") +
  scale_x_discrete(drop = FALSE) +
  ylab("proportion") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 7))
```

```{r fig.height = 7}
lapses %>% 
  filter(eyeball) %>% 
  rowwise() %>% 
  mutate(hours = str_split(lapse_start, pattern = " ")[[1]][2],
         hours = str_split(hours, pattern = ":")[[1]][1],
         hours = factor(as.numeric(hours), levels = c(1:24), ordered = TRUE)) %>% 
  mutate(day = wday(lapse_start, label = TRUE)) %>% 
  ggplot(aes(x = hours)) +
  geom_bar(aes(y = ..count../sum(..count..))) +
  facet_wrap(~ day, ncol = 2) +
  ylab("proportion") +
  scale_x_discrete(drop = FALSE) 
```



### Save samples

```{r}
samples %>% 
  write_csv(here(path_meta, "samples.csv")) %>% 
  glimpse()
```

