---
title: "Feature Engineering"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    )
    rmarkdown::render(
      input,
      "/Volumes/private/studydata/risk/knits/meta")
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
---

### Code status

First run at making features for meta project. Still working on implementation of features for dates, numbers, and combined features.   

Discuss with JC:   
- Writing functions to manipulate dates   
- Writing more complex functions using multiple columns (i.e., n incoming calls from supportive contacts)    
- Add general descriptives about social network based on all logs with static/snapshot screening variables   


### Conclusions

These features will be further broken down into different feature sets:     

- feat_baseline_id - Only static/ID features    
- feat_baseline_temporal - Only features derived from temporal features about label      
- feat_all - All features.   
- feat_all_passive - All features except those derived from context information.     
- feat_logs - Only features derived from log and context info     


### Notes

This script returns a dataframe of features to be used as inputs into a machine learning model and the output label.      

Input:   

- meta_logs.csv (path_meta)   
- labels_05.csv (path_shared)   
- screen.csv (path_shared)


### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```

Relative paths
```{r}
path_fun_risk <- "shared"
path_lab_support <- "../lab_support"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)  # always need this
library(janitor) # cleaning and EDA
library(lubridate)
library(purrr)
library(vroom)

# for plots and tables
library(ggplot2)
theme_set(theme_bw()) # or theme_set(theme_classic())
library(kableExtra)
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_fun_risk, "fun_risk.R"))
source(here(path_lab_support, "print_kbl.R"))
```

### Read in Data

Meta logs dataframe  
```{r}
logs <- vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tzone = "America/Chicago")) %>% 
  glimpse()

logs_sms <- logs %>% 
  filter(log_type == "sms") %>% 
  glimpse()
```

Lapse labels dataframe
```{r}
labels_05 <- vroom(here(path_meta, "labels_05.csv"), col_types = vroom::cols()) %>% 
  mutate(dttm_label = with_tz(dttm_label, tzone = "America/Chicago")) %>% 
  glimpse()
```


### Make Features

### New function demo

Set period duration and lead hours   

*Using 48 hours for now to shorten time to knit*
```{r}
period_duration_hours <- 48
lead_hours <-  0 
```

Read in study start date (for now using this to get relative rate)

FIX: Need to update this to be min of first observation or first day on study
```{r}
data_start <- vroom::vroom(here(path_shared, "visit_dates.csv"), col_types = vroom::cols()) %>% 
  select(subid, start_study) %>% 
  mutate(start_study = with_tz(start_study, tz = "America/Chicago"))
```

Slice out test set of labels
```{r}
set.seed(102030)
labels_test <- slice_sample(labels_05, n = 20)
```



Call function     

*Note 0 log entries for a duration period will return a rate of 0*
```{r}
map2_dfr(labels_test$subid,
                          labels_test$dttm_label,
                          score_ratecount_value,
                              x_all  = logs_sms,
                              period_durations = c(24, 48),
                              lead = 0, 
                              data_start = data_start, 
                              col_name = "originated", 
                              value = "incoming", 
                              data_type = "sms",
                              context = "all") %>% 
  glimpse()
```

```{r}
features <- map2_dfr(labels_test$subid,
                          labels_test$dttm_label,
                          score_ratecount_value,
                              x_all  = logs_sms,
                              period_duration = c(24, 48),
                              lead = 0, 
                              data_start = data_start, 
                              col_name = "originated", 
                              value = "incoming", 
                              data_type = "sms")

features <- features %>% 
  full_join(map2_dfr(labels_test$subid,
                          labels_test$dttm_label,
                          score_ratecount_value,
                              x_all  = logs_sms,
                              period_duration = c(24, 48),
                              lead = 0, 
                              data_start = data_start, 
                              col_name = "originated", 
                              value = "outgoing", 
                              data_type = "sms"),
            by = c("subid", "dttm_label"))
```

