---
title: "Feature Engineering"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---

### Code status

This script is in progress. It makes features for meta project.    

Still need to do:   
- Write functions to manipulate dates    
- Feature engineer numbers (blocked, out of country)   
- Add more combinations of features    
- Possibly add general descriptives about social network based on all logs with static/snapshot screening variables   


### Conclusions

These features will be further broken down into different feature sets:     

- feat_baseline_id - Only static/ID features    
- feat_baseline_temporal - Only features derived from temporal features about label      
- feat_all - All features.   
- feat_all_passive - All features except those derived from context information.     
- feat_logs - Only features derived from log and context info     


### Notes

This script returns a dataframe of features to be used as inputs into a machine learning 
model and the yes/no outcome label (lapse).      

Input:   

- meta_logs.csv (path_meta)   
- labels_05.csv (path_shared)   
- screen.csv (path_shared)


### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
# detect and warn of conflicts
library(conflicted) 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

# set working directory to project
library(here)
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# data wrangling
library(tidyverse)  
library(janitor) 
library(lubridate)
library(purrr)
library(vroom)

# plots and tables
library(ggplot2)
theme_set(theme_classic()) 
library(kableExtra)
```

Source scripts
```{r, source_script, message=FALSE, warning=FALSE}
source(here("shared/fun_risk.R"))
source(here("../lab_support/print_kbl.R"))
```

### Read in Data

Meta logs dataframe  
```{r}
logs_all <- vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tzone = "America/Chicago")) %>% 
  glimpse()

logs_sms <- logs_all %>% 
  filter(log_type == "sms") 
logs_voice <- logs_all %>% 
  filter(log_type == "voice") 
```

Lapse labels dataframe
```{r}
labels_05 <- vroom(here(path_meta, "labels_05.csv"), col_types = vroom::cols()) %>% 
  mutate(dttm_label = with_tz(dttm_label, tzone = "America/Chicago")) %>% 
  glimpse()
```

Read in study specific start dates
```{r}
data_start <- vroom::vroom(here(path_meta, "study_dates.csv"), col_types = vroom::cols()) %>% 
  select(subid, study_start, comm_start, data_start) %>% 
  mutate(across(study_start:data_start), with_tz(., tz = "America/Chicago")) %>% 
  glimpse()
```



*Slice out test set of labels*    
FIX: Remove this code block when ready to run script on all labels
```{r}
set.seed(102030)
labels_05 <- slice_sample(labels_05, n = 10)
```



### Initialize values for period duration and lead hours

Period duration should be a vector containing 1+ values in hours
```{r}
period_durations <- c(24, 48) 
```

Lead should be a single value in hours
```{r}
lead <-  0 
```



### Rates and Proportions

Incoming/Outgoing calls 
```{r}
meta_features <- map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_ratecount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            data_start = data_start, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_types = c("all", "sms", "voice"),
            context = "all") %>% 
  full_join(map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_propcount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_types = c("all", "sms", "voice"),
            context = "all"), by = c("subid", "dttm_label"))
  
```

Incoming/Outcoming calls from Drinkers and NonDrinkers
```{r}
meta_features <- meta_features %>% 
  full_join(map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_ratecount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            data_start = data_start, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_type = c("all", "sms", "voice"),
            context = "drink_status",
            context_values = c("Drinker", "NonDrinker")), by = c("subid", "dttm_label")) %>% 
  full_join(map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_propcount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_types = c("all", "sms", "voice"),
            context = "drink_status",
            context_values = c("Drinker", "NonDrinker")), by = c("subid", "dttm_label"))
```


Incoming/Outcoming calls from Supportive, NonSupportive, and Mixed Contacts
```{r}
meta_features <- meta_features %>% 
  full_join(map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_ratecount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            data_start = data_start, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_type = c("all", "sms", "voice"),
            context = "support_status",
            context_values = c("Supportive", "Unsupportive", "Mixed")), by = c("subid", "dttm_label")) %>% 
  full_join(map2_dfr(labels_05$subid, 
         labels_05$dttm_label,
         score_propcount_value,
            x_all  = logs_all,
            period_durations = period_durations,
            lead = lead, 
            col_name = "originated", 
            values = c("incoming", "outgoing"), 
            data_types = c("all", "sms", "voice"),
            context = "support_status",
            context_values = c("Supportive", "Unsupportive", "Mixed")), by = c("subid", "dttm_label"))
```





```{r}
glimpse(meta_features)

meta_features %>% 
  print_kbl()
```


```{r}

```



