---
title: "Post-CHTC Processing"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
---

### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")
 conflict_prefer("spec", "yardstick")

library(here)  
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)

theme_set(theme_classic()) 
```

Set additional paths
```{r}
path_job <- here("P:/studydata/risk/chtc/meta/jobs/features/test")
path_output <- here(path_job, "output/output")
path_features <-  here(path_job, "output/features")
path_error <-  here(path_job, "output/error")
```

Source function scripts from lab support
```{r  source_script, message=FALSE, warning=FALSE}
source(here("../lab_support/print_kbl.R"))
```


### Notes
This script aggregates all CHTC features for the job `r name_job`. It runs checks for 
missing jobs, plots hyperparameters, and summarizes model performance across all folds.    
  

Inputs:  

Returned CHTC files   

- output.zip  
- features.zip    
- output.zip   

Jobs input file   

- jobs.csv   

Output:   

- features_aggregate.csv   

### Unzip and check jobs

unzip chtc folders
```{r}
unzip(zipfile = file.path(path_job, "output/output.zip"), exdir = file.path(path_job, "output"))
unzip(zipfile = file.path(path_job, "output/features.zip"), exdir = file.path(path_job, "output"))
unzip(zipfile = file.path(path_job, "output/error.zip"), exdir = file.path(path_job, "output"))
```

Read in jobs
```{r}
jobs <- read_lines(here(path_job, "input/jobs.csv")) %>% 
    as.numeric() %>%
    enframe(., value = "label_num", name = NULL) %>% 
  glimpse()
```



check all error files are blank (0 kb)    
Note: error files also contain warnings
```{r}
err_files <- map_df(list.files(path_error, full.names = TRUE), file.info)
tabyl(err_files$size)
```

Pull error messages and jobs if error files are not all blank
```{r}
if (nrow(subset(err_files, size > 0)) > 0) {
  err_paths <- err_files %>% 
    filter(size > 0) %>% 
    rownames_to_column("path") %>% 
    pull(path) 
  for (i in err_paths) {
    err_i <- read_csv(i, col_types = readr::cols()) %>% 
      mutate(job_num = as.numeric(str_remove(str_split(str_split(i, "/")[[1]][10], "_")[[1]][2], ".err"))) %>% 
      relocate(job_num)
    errs <- if (i == err_paths[1]) {
      err_i
    } else rbind(errs, err_i)
  }
  
  # print error messages
  print_kbl(errs, align = "l")
}
```


Job rows with error messages
```{r}
if (nrow(subset(err_files, size > 0)) > 0) {
  # print jobs
 jobs %>%
    inner_join(errs, by = c("label_num" = "job_num")) %>%
    print_kbl(align = "l")
} else print("no errors or warnings")
```


check all output files are blank (0 kb)
```{r}
out_files <- map_df(list.files(path_output, full.names = TRUE), file.info)
tabyl(out_files$size)
```

### Aggregate all result CSVs

read in all result CSVs
```{r}
feat_files <- list.files(path_features, full.names = TRUE)
features <- map_df(feat_files, ~read_rds(.x)) %>% 
  glimpse()
```


check for missing jobs
```{r}
missing_job_nums <- enframe(seq(1:nrow(jobs)), name = NULL, value = "job_num") %>% 
  filter(!job_num %in% features$label_num)
```

`r nrow(features)` results from `r nrow(jobs)` jobs.      

```{r}
if (nrow(missing_job_nums) > 0) {
  print(str_c("missing jobs: ", str_c(as.character(missing_job_nums$job_num), collapse=", ")))
  } else print("No missing jobs")
```


### Print features

```{r}
features %>% 
  glimpse()

print_kbl(features)
```



### Write out aggregated features


```{r}
write_csv(features, here(path_job, "output/features_aggregate.csv")) %>% 
  glimpse()
```

