---
title: "Demo of get_label_windows"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---


### Set Up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_raw <- "P:/studydata/risk/data_raw"
          path_processed <- "P:/studydata/risk/data_processed/shared"
          path_meta <- "P:/studydata/risk/data_processed/meta"},

        # IOS paths
        Darwin = {
          path_raw <- "/Volumes/private/studydata/risk/data_raw"
          path_processed <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)
library(vroom)
library(janitor)
library(lubridate)
```


Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here("../lab_support/print_kbl.R"))
source(here("shared/fun_local.R"))
```

### Read in data
Lapses
```{r}
lapses <- vroom::vroom(here(path_processed, "lapses.csv"), col_types = vroom::cols()) %>% 
  mutate(across(c(lapse_start, lapse_end, ema_end)), with_tz(., "America/Chicago")) %>% 
  glimpse()
```

Read in dates from study level folder
```{r}
dates <- vroom::vroom(here(path_meta, "study_dates.csv"), col_types = vroom::cols()) %>%
  mutate(across(study_start:ema_end), with_tz(., tz = "America/Chicago")) %>% 
  glimpse()
```



### get label windows (1 hour)

get label windows (uses default buffer_start and window_dur)
```{r}
label_windows <- dates %>% 
    select(subid, study_start, study_end, ema_end) %>% 
    pmap_dfr(~get_label_windows(..1, ..2, ..3, ..4))

glimpse(label_windows)
```

Check one subid's windows
```{r}
label_windows %>% 
  filter(subid == 1) 
```

recalculate study end time
```{r}
study_end_times <- dates %>% 
  rowwise() %>% 
  mutate(study_end = study_end + (hours(23)),
         ema_end = floor_date(ema_end, unit = "hours"),
         end_time = min(study_end, ema_end)) %>% 
  ungroup() %>% 
  select(subid, end_time)
```

Last observation does not include study_end
```{r}
label_windows %>% 
  left_join(study_end_times, by = "subid") %>% 
  group_by(subid) %>% 
  slice_tail(n = 1)
```

### get label windows (1 day)

get label windows (specify window_dur)
```{r}
label_windows <- dates %>% 
    select(subid, study_start, study_end, ema_end) %>% 
    mutate(buffer_start = 0,
           window_dur = 86400) %>% 
    pmap_dfr(~get_label_windows(..1, ..2, ..3, ..4, ..5, ..6))
```

Look at one subid's dttm's at a time  
```{r}
label_windows %>% 
  filter(subid == 1) 
```

```{r}
label_windows %>% 
  filter(subid == 10) 
```

```{r}
label_windows %>% 
  filter(subid == 18) 
```

Last observation does not include study_end
```{r}
label_windows %>% 
  left_join(study_end_times, by = "subid") %>% 
  group_by(subid) %>% 
  slice_tail(n = 1)
```



### get label windows (3 days)

get label windows (specify window_dur)
```{r}
label_windows <- dates %>% 
    select(subid, study_start, study_end, ema_end) %>% 
    mutate(buffer_start = 0,
           window_dur = 259200) %>% 
    pmap_dfr(~get_label_windows(..1, ..2, ..3, ..4, ..5, ..6))
```

Look at one subid's dttm's at a time
```{r}
label_windows %>% 
  filter(subid == 1) 
```

Last observation does not include study_end
```{r}
label_windows %>% 
  left_join(study_end_times, by = "subid") %>% 
  group_by(subid) %>% 
  slice_tail(n = 1)
```


### get lapse labels
subset of lapses
```{r}
set.seed(1234)

lapse_subset <- lapses %>% 
  slice_sample(n = 5)
```

```{r}
# default parameters
get_lapse_labels(lapse_subset, dates) %>% 
  head(30)

# specify duration window to 3 days
get_lapse_labels(lapse_subset, dates, window_dur = 259200) %>% 
  head(100)
```

FIX: still need to update exclusions/checks



