---
title: "Meta EDA"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---

### Code Status

- add apple/android variable
- check all variables
- check known contacts with no log matches (were they reported at screen)
- count how many contacts reported at each visit
- check to see if calls to self is voicemail check (outgoing? Remove from counts?)
- see if can extract or determine number for emails and *86

### Notes
This script performs more EDA on meta dataset (logs and contacts).

- John and Kendra have decided to drop subid 104's data for the following reasons:   
  - They had lapses every day on study except one day.    
  - Only had 75 surveys where a lapse was not reported.   
  - Viewing their lapse times it appears they were drinking constantly (morning and 
  night).   
  - They consistently report being uncertain that their goal is to be abstinent 
  (uncertain on 125 of 137 lapses. They also report they are uncertain in this goal 
  at followup 1 and 2.    
  - They are ultimately discontinued since they were struggling to gain sobriety.   
  - Unfortunately this drops 109 valid lapses.    


- John and Kendra have decided to drop subid 269's data for the following reasons:       
  - They completed 10-15 surveys on many days on study (avg number of surveys per 
  day is 6.76).  
  - Their responses indicate careless responding - they were filling 2-4 surveys out 
  within an hour of each other and the responses to the questions were completely different.     
  - They have questionable no lapse labels - they reported no lapses while on study but 
  according to notes left two messages for study staff where they admitted to drinking 
  over the weekend.   
  

- John and Kendra have decided to drop subid 204's data for the following reasons:    
  - Subid 204 had extremely poor compliance. 33 out of 89 study days had an EMA completed. 
  They only did a total of 5 surveys between followup 2 and 3.    
  - We don't trust their lapse labels - They report several lapses during their interviews 
  but times appear questionable (same time every night). They only report 1 lapse with EMA.
  - From notes - "Participant did not do many surveys during their second month of participation. 
  At their Follow-up 2 visit they reported several lapses that were not documented in their 
  EMAs - estimated lapse days/times in subid's raw data log."  
  - JC note: "There are issues with 204. They are missing lapses reported by interview. But they  
  also stopped doing any ema by 5/17 even though their study end date was 6/13. Probably need to 
  drop them for lapse analyses for anything after 5/17.  Probably also need to add in their 
  reported lapses at follow-up 2. OR we drop them at the end of follow-up 1 or wherever their 
  ema gets sketchy"  

### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
path_meta <- "P:/studydata/risk/data_processed/meta"
path_shared <- "P:/studydata/risk/data_processed/shared"
```

Relative paths
```{r}
path_lab_support <- "../lab_support"
```



Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

library(here)  
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)

theme_set(theme_classic()) 
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_lab_support, "print_kbl.R"))
```




### Read in Data

```{r}
study_dates <- vroom::vroom(here(path_meta, "study_dates.csv"), col_types = vroom::cols()) %>% 
  select(subid, study_start, comm_start, data_start) %>% 
  mutate(across(study_start:data_start), with_tz(., tz = "America/Chicago")) %>% 
  glimpse()

meta <- vroom::vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) %>% 
  filter(subid %in% study_dates$subid) %>% # need to rerun mak_logs to filter out excluded subids
  mutate(dttm_obs = with_tz(dttm_obs, tzone = "America/Chicago")) %>% 
  glimpse()

contacts_all <- vroom::vroom(here(path_shared, "contacts.csv"), col_types = vroom::cols()) %>% 
  filter(subid %in% study_dates$subid) %>% # remove excluded subids
  glimpse()
```


### Check self contact type

In logs       

- `r length(unique(meta$subid))` unique subids in meta project
- 87 subids have a self contact_type in their log communications   
- 5 subids have more than 1 self type (77, 150, 187, 236, 252) 
```{r}
meta %>% 
  filter(contact_type == "self") %>% 
  group_by(subid, number_formatted) %>% 
  slice(1) %>% 
  ungroup() %>% 
  count(subid) 

meta %>% 
  filter(contact_type == "self") %>% 
  group_by(subid, number_formatted) %>% 
  slice(1) %>% 
  ungroup() %>% 
  count(subid) %>% 
  filter(n > 1)
```


In full contacts file  

- all 151 subids have a self contact_type   
- 12 list more than 1 number (home and cell, cell and other)
```{r}
contacts_all %>% 
  filter(contact_type == "Self") %>% 
  group_by(subid, phone_number) %>% 
  slice(1) %>% 
  ungroup() %>% 
  count(subid) 

(dup_subs <- contacts_all %>% 
  filter(contact_type == "Self") %>% 
  group_by(subid, phone_number) %>% 
  slice(1) %>% 
  ungroup() %>% 
  count(subid) %>% 
  filter(n > 1))

contacts_all %>% 
  filter(contact_type == "Self") %>% 
  filter(subid %in% dup_subs$subid) %>% 
  select(subid, utc, contact_type, phone_type, phone_number)
```

Contact info on subids with more than 1 self number in logs
```{r}
contacts_all %>% 
  filter(contact_type == "Self" & subid %in% c(77, 150, 187, 236, 252)) %>% 
  select(subid, utc, contact_type, phone_type, phone_number)
```


Number of calls to self
```{r}
meta %>% 
  filter(contact_type == "self") %>% 
  count(subid, number_formatted, phone_type) %>% 
  arrange(desc(n))
```

Type of calls to self    

- Includes SMS messages     
- Includes outgoing messages    
```{r}
meta %>% 
  filter(contact_type == "self") %>% 
  tabyl(log_type)

meta %>% 
  filter(contact_type == "self" & log_type == "sms") %>% 
  glimpse()

meta %>% 
  filter(contact_type == "self" & log_type == "sms") %>% 
  tabyl(org)

meta %>% 
  filter(contact_type == "self") %>% 
  tabyl(org)

meta %>% 
  filter(contact_type == "self" & org == "incoming") %>% 
  glimpse()
```

It appears it is possible to text yourself - should have incoming and outgoing text with 
same time stamp (few seconds off okay)
```{r}
meta %>% 
  filter(contact_type == "self" & log_type == "sms") %>% 
  select(subid, number_formatted, dttm_obs, org) 

meta %>% 
  filter(contact_type == "self" & log_type == "sms") %>% 
  mutate(dttm_round_min = round_date(dttm_obs, unit = "minute")) %>% 
  count(subid, number_formatted, dttm_round_min) %>% 
  filter(n != 2)
```



### Date reported contacts
```{r}
contacts_all %>% 
  count(subid, utc)
```


### Unmatched contacts

- 310 unmatched contacts (60 unmatched self contacts)   
- from 94 subids   
- 8 subids have 10 or more unmatched contacts
```{r}
contacts_all %>% 
  filter(!phone_number %in% meta$number_formatted) %>% 
  glimpse()

contacts_all %>% 
  filter(!phone_number %in% meta$number_formatted) %>% 
  tabyl(contact_type)

contacts_all %>% 
  filter(!phone_number %in% meta$number_formatted) %>% 
  # filter out self contact_type
  filter(contact_type != "Self") %>% 
  select(subid, contact_type, phone_number)

contacts_all %>% 
  filter(!phone_number %in% meta$number_formatted & contact_type != "Self") %>% 
  count(subid) %>% 
  arrange(desc(n))
```

Check numbers are valid   


Check if unmatched contacts were reported at first visit  

- 117 has a lot of unmatched contacts not reported at first visit
```{r}
contacts_all %>% 
  filter(!phone_number %in% meta$number_formatted & contact_type != "Self") %>% 
  count(subid, utc) %>% 
  left_join(contacts_all %>% 
              count(subid, utc) %>% 
              arrange(subid, utc) %>% 
              ungroup() %>% 
              group_by(subid) %>% 
              slice(1) %>% 
              select(c(subid, utc)) %>% 
              mutate(first_report = "yes"), by = c("subid", "utc"))
```


