---
title: "Summary of text message data"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/", 
      "/Volumes/private/studydata/risk/knits")
    )
  })
---

### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
path_meta <- "P:/studydata/risk/data_processed/meta"
path_shared <- "P:/studydata/risk/data_processed/shared"
```


Packages
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)
library(here)
library(vroom)

theme_set(theme_classic()) 
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here("../lab_support/print_kbl.R"))
```



### Text Message Data

Read in clean logs
```{r}
logs <- vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) 
```

Filter out voice calls
```{r}
logs_sms <- logs %>% 
  filter(log_type == "sms") %>% 
  glimpse()
```


### Summary of Data

There are a total of `r nrow(logs_sms)` text messages from `r length(unique(logs_sms$subid))` participants.  

Note: no SMS messages for subid 9 - from notes: "Subject's SMS files are empty because the subject deleted all text messages before their study visit; They also did not text much."
```{r}
dates <- vroom(here(path_shared, "visit_dates.csv"), col_types = vroom::cols()) %>% 
  filter(!is.na(followup_1)) 

dates %>% 
  filter(!subid %in% logs_sms$subid)
```

Messages per subid   
Below is min, max, and mean for the number of messages per person
```{r}
logs_sms %>% 
  count(subid) %>% 
  summarise(min = min(n),
            max = max(n),
            mean = mean(n))
```


Distribution of messages per person
```{r}
logs_sms %>% 
  count(subid) %>% 
  ggplot(aes(x = n)) +
  geom_histogram(bins = 30, color = "black", fill = "light grey") +
  geom_vline(aes(xintercept = mean), logs_sms %>% 
               count(subid) %>% 
               summarise(mean = mean(n)), color = "red3")
```




