---
title: "Comparing GPS and vacation file data"
author: "John Curtin"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

### Notes
This script will read in data fomr GPS as well as individual vacation files to determine how well vacation files capture data needed for lapses


### Setup

Paths 
```{r}
path_raw_data <- "P:/StudyData/RISK/raw_data"
path_gps <-
path_plots <- "P:/StudyData/RISK/analysis/shared/scripts_chk/chk_gps_plots"
path_shared_data <- "P:/StudyData/RISK/analysis/shared/data"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(xlsx)
library(purrr)
library(pdftools)
library(lmSupport)

```

## Vacation files
First we will get a list of individuals who have vacation files
```{r}
subs <- list.files(path_raw_data)
subs <- subs[str_length(subs)==3] #select down to just subject directories

#Save a vector of subjects who have a vacation file
vac_subs <- character()
novac_subs <- character()
for(a_sub in subs){
  files <- list.files(file.path(path_raw_data,a_sub))
    if(str_c(a_sub,"_Vacations.xlsx") %in% files){a_sub
    vac_subs <- c(vac_subs,a_sub)
    }else{novac_subs <- c(novac_subs,a_sub)}
}

length(novac_subs) #10 people do not have vacation files


```

Look at people who do not have vacation files gps to see if we would miss timezone info by not looking at this data
```{r}
#see which subjects have maps generated, get 3 character vector of subs
map_subs <- list.files(path_plots)
map_subs <- gsub("gps_plot_", "", map_subs)
map_subs <- varPadString(gsub(".pdf","",map_subs),3)

novac_subs[novac_subs %in% map_subs == FALSE]
#Subjects 77, 169, 181, and 269 do not have vacation files or gps graphs.
#Its not clear from the chk_gps codes why these indiviuals do not have maps

#For those that do have maps----------
novac_map_subs <- novac_subs[novac_subs %in% map_subs]
novac_map_subs = as.numeric(novac_map_subs)
novac_maps <- paste(path_plots, "/gps_plot_",novac_map_subs,".pdf", sep = "")

pdf_combine(c(novac_maps), output = "C:/Users/sjkit/Desktop/joined.pdf")

#Maybe subject 7 went somewhere?
subid = "180"
database_file <- str_c("P:/StudyData/RISK/database/", subid, "/", subid, "_GPS.rds")

gps<- read_rds(database_file) %>% 
  mutate(subid = subid) %>% 
  select(subid, long, lat, time, app_source) %>% 
  arrange(time) %>% 
  mutate(timezone = tz_lookup_coords(lat,long))



```

DS_ema has not been created since 5/27, but lets see if we can do a quick scan
```{r}
full_gps <- read_rds(file.path(path_shared_data, "ds_gps.rds")) %>% 
  select(c(subid, utc, lat, long, time, next_time)) %>% 
  mutate(timezone = tz_lookup_coords(lat, long)) %>% 
  glimpse()

unique(full_gps$timezone)

new_tz <- full_gps %>% 
  filter(timezone != "America/Chicago")

length(unique(new_tz$subid))
unique(new_tz$subid)

#Check to see these subs vacation files
subid = 6
sub = varPadString(subid,3)

vacations<- read.xlsx(file.path(path_raw_data,sub,str_c(sub,"_Vacations.xlsx")),1)
View(vacations)

new_tz %>% filter(subid == subid) %>% View()

#So the gps files will allow us to better see traveling instead of just final destination for lapses. Only use vacation files if gps is missing

#loading full ema file for by subject comparisons
ema <- read_rds(file.path(path_shared_data,"ds_ema.rds"))
```

Load all relevant files for a subject
```{r}
sub = 128
sub_s = varPadString(sub,3)

vacations<- read.xlsx(file.path(path_raw_data,sub_s,str_c(sub_s,"_Vacations.xlsx")),1)
View(vacations)

timezone<- new_tz %>% filter(subid == sub)
View(timezone)


lapses<- ema %>% filter(subid==sub) %>%filter(ema_1==2) 
View(lapses)

```

Start with the EMA
make file with all reported lapses across all participants
start date, start time, end date, end time, future goals
Open gps file take all coordinate from gps file and convert to time zone
go to lapses, look up every lapse date and time of lapse and figure out where they were
6th column lapse data frame for timezone

check gps before and after lapse see if they match
new variable for length between last gps and lapse.
Look at distribution
if no gps for a long time before and after, look into it
Also total number of gps observations per participant