---
title: "Lapse Report Lengths"
author: "Sarah"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE, fig.pos = "H")
```
### Description / Notes
This is a short snippet of the chk_lapses file that specifically looks at EMA report lengths (extracted for easier viewing).We are starting with an intermediate lapses file saved within chk_lapses.rmd

```{r Packages and paths, echo =FALSE}
# Packages
library(tidyverse)
library(knitr)
library(lubridate)
library(kableExtra)
library(psych)
```
```{r}
lapses <- read_rds("P:/StudyData/RISK/analysis/shared/scripts_chk/chk_lapses/intermediate_lapses.rds")
```


These data have gone through the following processes:

  1. **Basic cleaning:** Date formatting, removing unfinished surveys
  2. **Participant reported lapse corrections**: taken from the RISK data cleaning log, these are corrections verbally confirmed participants at a follow-up visit/phone call
  3. **Assigning lapse timezones**: using closest gps point to lapse (required to get true distance between ema report and lapse)

**Lapse report length** (EMA survey start time - lapse start time) does not include lapses reported outside of EMA surveys. I provide descriptives of three versions of lapse report length below:
  1. **Raw** EMA lapse report lengths
  2. The **absolute value** of EMA lapse report lengths
  3. Only **positive** EMA lapse report lengths (report length >=0, since negative reports are impossible)
  
I also display **Non-EMA** report lengths (between lapses and the date they were reported at followup/in audio messages) for comparison.


### EMA report lengths

```{r Report length descriptives, echo=FALSE}

report_lengths <- lapses %>% 
  filter(!ema_type == "non ema") %>% 
  mutate(abs_report_length = 
           abs(report_length),
         positive_report_length =
           if_else((report_length >= 0), 
                   report_length, NA_real_)) %>%
  select(report_length, abs_report_length, positive_report_length)

describe(report_lengths) %>% 
  kable(., caption = "EMA Lapse Report Length (Hours): Raw vs Absolute Value vs Only positive lengths") %>% 
   kable_styling(full_width=F)

```

```{r Histogram raw report length, echo = FALSE, fig.show="hold"}
#raw lapse report
lapses %>% 
  filter(!ema_type=="non ema") %>% 
  filter(report_length< 75) %>% 
  ggplot(aes(x = report_length)) +
  geom_histogram(bins = 14) +
  xlab("Raw report length (hours)") +
  xlim(-75, 75) +
  ggtitle("EMA lapse report length - Raw (Truncated at + 75 hours)") +
  theme_classic()

#Absolute value of lapse report
lapses %>% 
  filter(!ema_type=="non ema") %>% 
  filter(abs(abs(report_length))< 75) %>% 
  ggplot(aes(x = abs(report_length))) +
  geom_histogram(bins = 14) +
  xlab("Abs value of report length (hours)") +
  xlim(0, 75) +
  ggtitle(" EMA lapse report length - Absolute value (Truncated at 75 hours)") +
  theme_classic()

#only positive reports
lapses %>% 
  filter(!ema_type=="non ema") %>% 
  filter(report_length< 75 & report_length >=0) %>% 
  ggplot(aes(x = report_length)) +
  geom_histogram(bins = 14) +
  xlab("Report length (hours), positive cases only") +
  xlim(0, 75) +
  ggtitle("EMA lapse report length - Positive cases only (Truncated at 75 hours)") +
  theme_classic()


```


### Non-EMA report lengths
For comparison

```{r nonema, echo = FALSE}
#Non EMA report lengths
non_ema_rl <- lapses %>% 
  filter(ema_type == "non ema") %>% 
  mutate(abs_report_length = abs(report_length)) %>% 
  select(report_length,abs_report_length)

describe(non_ema_rl) %>% 
  kable(., caption = "Non-EMA Lapse Report Length (Hours): Raw vs Absolute value lengths") %>% 
   kable_styling(
    bootstrap_options = "condensed", 
    full_width = FALSE, 
    position = "left")
```

```{r hist non ema, echo=FALSE}
#Non-EMA lapses

lapses %>% 
  filter(ema_type=="non ema") %>% 
  filter(report_length< 800) %>% 
  ggplot(aes(x = report_length)) +
  geom_histogram(bins = 30) +
  xlab("Raw non-EMA report lengths (hours)") +
  xlim(0, 800) +
  ggtitle("Non-EMA lapse report length - Raw (Truncated at 800 hrs)") +
  theme_classic()

```

