---
title: "Make comment csv files"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

### Notes
 
This script makes the csv files of the participants comments on each measure. Does not include wristband comments.  


### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths 
```{r}
path_data <- "./database"
```

Packages
```{r}
library(tidyverse)
library(lubridate)
library(textclean)
```


### Import Data and glimpse 
All updates to data frame are documented in eda_burden.rmd

Burden data
```{r}
burden <- read_rds(file.path(path_data, "burden.rds")) 

burden <- burden %>%
  mutate(date_central = as_datetime(as.integer(utc), 
                                    tz = 'America/Chicago')) %>%
  mutate(date_central = date(date_central)) %>% 
  select(subid,
         utc,
         date_central,
         sleep_interfere = rbm_5,
         sleep_dislike = rbm_6,
         sleep_1year = rbm_7,
         sleep_text = rbm_8,
         daily_survey_interfere = rbm_9,
         daily_survey_dislike = rbm_10,
         daily_survey_4_1year = rbm_11,
         daily_survey_1_1year = rbm_12,
         daily_survey_text = rbm_13,
         audio_checkin_interfere = rbm_14,
         audio_checkin_dislike = rbm_15,
         audio_checkin_1year = rbm_16,
         audio_checkin_text = rbm_17,
         location_dislike = rbm_22,
         location_1year = rbm_23,
         location_text = rbm_24,
         sms_logs_dislike = rbm_25,
         sms_logs_1year = rbm_26,
         sms_content_dislike = rbm_27,
         sms_content_1year = rbm_28,
         phone_logs_dislike = rbm_29,
         phone_logs_1year = rbm_30,
         phone_text = rbm_31) %>%
  mutate(across(-c(contains("_text"),
                  subid,
                  utc,
                  date_central),
                ~as.numeric(.))) %>%
  mutate(across(c(contains("_1year")),
                ~recode(., "5" = 1, "4" = 2, "3" = 3, "2" = 4, "1" = 5))) %>% 
  glimpse()
```

text encoding corrections
```{r}
burden <- burden %>% 
  mutate_if(is.character, iconv, from = "UTF-8", to = "Windows-1252") %>% 
  mutate_if(is.character, str_replace_all, pattern = "\\\\", replacement = "") %>% 
  mutate_if(is.character, str_replace_all, pattern = '\\"', replacement = "") %>% 
  mutate_if(is.character, replace_symbol)
```

Create df of last observation
```{r}
# pull out most recent survey for each subid
burden_last <- burden %>% 
  group_by(subid) %>% 
  arrange(desc(date_central)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  glimpse()
```


### Extract Text Comments on Measures

```{r}
comments_sleep <- burden_last %>% 
  select(subid,
         text = sleep_text) %>% 
  mutate("+ inform" = "",
         "+ uninform" = "",
         "- inform" = "",
         "- uninform" = "",
         "exclude" = "") %>%  
  na.omit()

comments_survey <- burden_last %>% 
  select(subid, 
         text = daily_survey_text) %>% 
  mutate("+ inform" = "",
         "+ uninform" = "",
         "- inform" = "",
         "- uninform" = "",
         "exclude" = "") %>% 
  na.omit()

comments_audio <- burden_last %>% 
  select(subid,
         text = audio_checkin_text) %>% 
  mutate("+ inform" = "",
         "+ uninform" = "",
         "- inform" = "",
         "- uninform" = "",
         "exclude" = "") %>% 
  na.omit()

comments_location <- burden_last %>% 
  select(subid,
         text = location_text) %>% 
  mutate("+ inform" = "",
         "+ uninform" = "",
         "- inform" = "",
         "- uninform" = "",
         "exclude" = "") %>% 
  na.omit()

comments_phone <- burden_last %>% 
  select(subid,
         text = phone_text) %>% 
  mutate("+ inform" = "",
         "+ uninform" = "",
         "- inform" = "",
         "- uninform" = "",
         "exclude" = "") %>% 
  na.omit()
```

Save as csv files
```{r}
write_csv(comments_sleep, "./analysis/burden/data/comments_sleep.csv")
write_csv(comments_survey, "./analysis/burden/data/comments_survey.csv")
write_csv(comments_audio, "./analysis/burden/data/comments_audio.csv")
write_csv(comments_location, "./analysis/burden/data/comments_location.csv")
write_csv(comments_phone, "./analysis/burden/data/comments_phone.csv")
```


Check all comments from an individual subid
```{r}
burden %>% 
  filter(subid == "079") %>% 
  select(subid, contains("text")) %>% 
  kable() %>% 
  kable_styling()
```

