---
title: "Check EMA"
author: "Hannah and Sarah"
date: "4/3/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, message = FALSE}
Sys.time()
data_path <- "P:/StudyData/RISK/analysis/shared/data"

library(tidyverse) 
library(janitor)
library(lmSupport)
library(knitr)
library(mice)
```
##Read in data

```{r}
ema <- read_rds(file.path(data_path, "ds_ema.rds")) %>% 
  glimpse()

lapses <- read_rds(file.path(data_path, "ds_lapses.rds")) %>% 
  glimpse()

id <- read_rds(file.path(data_path, "ds_id.rds")) %>% 
  glimpse()

#previously also loaded in Xday (X) and yday (y)
```

## ema survey data from qualtrics (ema feature source)

```{r, warning=FALSE, echo = FALSE}
#converting the unix time to actual time
ema$date <- ema$utc %>% #converting into human readable form
  as.numeric %>% 
  as.POSIXct(tz='America/Chicago', origin="1970-01-01")
ema$utc_date <- ema$date #saving this to compare to start_date

#converting Start and End dates to chicago
attributes(ema$start_date)$tzone <- "America/Chicago"
attributes(ema$end_date)$tzone <- "America/Chicago"

ema <- ema %>% #making columns for day and time
  separate(date, into = c("day", "time"), sep = " ")

ema_lapse <- ema %>% 
  filter(ema_1==2) %>% 
  select(c(utc,subid, start_date, end_date, type, day, time, utc_date))

#converting the unix time to actual time
ema_lapse$s_date <- ema_lapse$start_date %>% #converting into human readable form
  as.numeric %>% 
  as.POSIXct(tz='America/Chicago', origin="1970-01-01")

#converting the unix time to actual time
ema_lapse$e_date <- ema_lapse$end_date %>% #converting into human readable form
  as.numeric %>% 
  as.POSIXct(tz='America/Chicago', origin="1970-01-01")

ema_lapse <- ema_lapse %>% #making columns for day and time
  separate(s_date, into = c("s_day", "s_time"), sep = " ")

ema_lapse <- ema_lapse %>% #making columns for day and time
  separate(e_date, into = c("e_day", "e_time"), sep = " ")

glimpse(ema_lapse)

ema_lapse <- ema_lapse %>% 
  select(c(utc,subid, start_date,s_day, s_time, end_date, e_day,e_time,utc_date,day,time,everything()))

#before doing math on times, which lapses spanned days
length(which(ema_lapse$s_day!=ema_lapse$e_day))
e2<- ema_lapse %>% 
  filter(s_day != e_day) 

ema_lapse <- ema_lapse %>% 
 mutate(lapse_length = end_date - start_date) %>% 
  mutate(lapse_length = lapse_length/3600) %>% 
  mutate(lapse_length = as.numeric(lapse_length))

summary(ema_lapse$lapse_length)

```

##Basic descriptives and properties 


```{r warning=FALSE, echo = FALSE}
# observations per person and number of obs
counts <- ema %>% group_by(subid) %>% 
  summarize(n = n()) %>% 
  varDescribe()  %>% 
  filter(vars == 2) 

```

There are `r nrow(ema)` rows from `r counts$n` subjects, who contributed an average of
`r counts$mean` observations (range `r counts$min` - `r counts$max`).

```{r echo = FALSE}
#windows()
ema %>% group_by(subid) %>% 
  summarize(n = n()) %>% .$n %>% hist(main = 'Observations per Subject')
```

```{r warning=FALSE, echo = FALSE}
#Observations per person by type
#type = 1 (morning)
counts_am <- ema %>% group_by(subid) %>%
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  select(subid, n) %>% 
  varDescribe() %>% 
  filter(vars == 2) 

#per day
counts_am_perday <- ema %>% group_by(subid, day) %>%
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  select(subid, n) %>% 
  varDescribe() %>% 
  filter(vars == 2) 

```
`r counts_am$n` subjects contributed an average of `r counts_am$mean` total morning observations 
(range `r counts_am$min` - `r counts_am$max`) and an average of `r counts_am_perday$mean` morning surveys per day
(range `r counts_am_perday$min` - `r counts_am_perday$max`).  

```{r echo = FALSE}

ema %>% group_by(subid) %>% 
  filter(type == 1) %>% 
  summarize(n = n()) %>% .$n %>% hist(main = 'Morning Observations per Subject')

ema %>% group_by(subid, day) %>% 
  filter(type ==1) %>% 
  summarize(n = n()) %>% .$n %>% hist(main = 'Morning Observations per day per Subject')
```


```{r warning=FALSE, echo = FALSE}
#Observations per person by type
#type = 2 (afternoon)
counts_pm <- ema %>% group_by(subid) %>%
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  select(subid, n) %>% 
  varDescribe() %>% 
  filter(vars == 2) 
#perday
counts_pm_perday <- ema %>% group_by(subid, day) %>%
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  select(subid, n) %>% 
  varDescribe() %>% 
  filter(vars == 2) 

```
`r counts_pm$n` subjects contributed an average of `r counts_pm$mean` total day observations 
(range `r counts_pm$min` - `r counts_pm$max`) and an average of `r counts_pm_perday$mean` day surveys per day
(range `r counts_pm_perday$min` - `r counts_pm_perday$max`).  

```{r echo = FALSE}
ema %>% group_by(subid) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% .$n %>% hist(main = 'day Observations per Subject')

ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% .$n %>% hist(main = 'day Observations per day per Subject')
```



### Understanding sources of duplicate surveys per day 

``` {r warning=FALSE, echo = FALSE}

#Ruled out sources of duplicates are:
# 1. Exact identical observations (all are unique)
n_duplicated <-  ema %>% filter(duplicated(ema) == TRUE) %>% nrow()
# 2. People triggering the survey but not completing them or people not finishing one survey, then restarting?
#(no - these are removed unless there is a lapse)
n_incomplete <- ema %>% group_by(subid, day) %>% 
  filter(type == 1) %>% 
  mutate(am_count = cumsum(type)) %>% 
  filter(am_count > 1) %>% 
  mutate(missing = is.na(ema_10)) %>% 
  filter(missing > 0) %>% nrow()
#4. utc coding lapse date rather than survey date
#no -- this never happens, utc is pulled from QT
#However, there are people where utc and start are not the same
n_startisnotutc <- ema %>% filter(start_date != utc_date) %>% nrow()
n_startdayisnotutcday <- ema %>% filter(substr(start_date, 1, 10) != substr(utc_date, 1, 10)) %>% nrow()


``` 

Looking at the data and speaking to project staff, we determined that the following reasons **do** **not** explain many surveys per day:  
1. Duplicate surveys (number of duplicates is `r n_duplicated`)  
2. People starting but not finishing (no, removed in clearning; number of incompletes is `r n_incomplete`)  
3. utc indicates an incorrect date? no, as on 4/24/2019, utc is the Qulatrics start time, which is different for `r n_startisnotutc` people. Looking just at the dates (not the time), only `r n_startdayisnotutcday` are different for utc and start date.

```{r warning=FALSE, echo = FALSE}
#Sources of duplicates are:
# 1. People taking multiple surveys in the 6 hour window
# e.g., taking many in a row

# 2. A few cases of people with a lot of duplicate surveys for known reasons
# LOOK AT DATA LOG In RAW DATA

# 5. Partial finishes that were recoded as complete if they answered lapse Qs
# yes (see patterns of missingness)
n_lapsedataonly <- ema %>% filter(ema_1 != 'NA' & ema_3 == 'NA') %>%  nrow()

```


Looking at the data and speaking to project staff, we determined that the following reasons **do** explain many surveys per day:  
1. Several people early on the in study who are documented to have completed surveys under a different survey distribution system  
2. A few individual instances of people who had multiple responses for other reasons (e.g., a participant who was completing surveys 'for' someone else, who got data reassigned to them), as described in the data log  
3. Partial finishes that were recorded as complete if they answered the lapse Qs (clear in the patterns of missingness). Currently, the number of obs this describes is `r n_lapsedataonly`.  
4. People taking multiple surveys during the 6 hour window when the link was active.  


#### Looking closely at people with many *morning* surveys per day 

```{r warning=FALSE, echo = FALSE}
#ordering dates first
ema <- select(ema, utc_date, start_date, end_date, everything())

#who had 5 per day?
id_5inaday <- ema %>% group_by(subid, day) %>% 
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  filter(n == 5) %>% .$subid
```

Subject `r id_5inaday` had 5 morning surveys one day, giving many similar responses in a short span.

```{r warning=FALSE, echo = FALSE}
ema %>% filter(subid == 79, day == "2018-08-16", type == 1) %>% 
  select(subid, day, time, ema_1, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7, ema_8, ema_9, ema_10) %>% 
  kable()
```

```{r warning=FALSE, echo = FALSE}
#who had 4?
id_4inaday <- ema %>% group_by(subid, day) %>% 
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  filter(n == 4)

##SARAH didnt work
#Subject `r id_4inaday` had 4 morning surveys one day, giving many similar #responses in a short span.
```



```{r warning=FALSE, echo = FALSE}
ema %>% filter(subid == 30, day == "2017-12-24", type == 1) %>% select(subid, day, time, ema_1, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7, ema_8, ema_9, ema_10) %>% kable()
```


```{r warning=FALSE, echo = FALSE}
#how many people had 3?
n_3inaday <- ema %>% group_by(subid, day) %>% 
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  filter(n == 3) %>% arrange(subid) %>% group_by(subid) %>% summarize(n = n()) %>% nrow()
#several people had multiple instances
id_3inaday <- ema %>% group_by(subid, day) %>% 
  filter(type == 1) %>% 
  summarize(n = n()) %>% 
  filter(n == 3) %>% arrange(subid) %>% group_by(subid) %>% summarize(n = n()) %>% filter(n > 1) 
#10 people -- with subjects 78, 85, 185 having lots of instances
```

`r n_3inaday` people had three morning surveys in one day, and some of these people had three morning surveys multiple days (subjects`r print(id_3inaday$subid)`).

```{r warning=FALSE, results = FALSE, echo = FALSE}
#Looking at these people
#subj 52 on 2018-04-15
ema %>% filter(subid == 52, day == "2018-04-15", type ==1) 
# spaced out responses throughout the day

#subj 65 on 2018-06-27
ema %>% filter(subid == 65, day == "2018-06-27", type ==1) 
#similar duplicates all in a row

#subj 74 on 2018-06-08
ema %>% filter(subid == 74, day == "2018-06-08", type ==1)
#similar duplicates all in a row

# subj 85 on 2018-07-28, 2018-08-08, 2018-08-15, 2018-08-21, 
# 2018-09-03, 2018-09-07, 2018-09-13
ema %>% filter(subid == 85, 
               day == "2018-07-28" | 
                 day == "2018-08-08"| 
                 day == "2018-08-15"|
                 day == "2018-08-21"|
                 day == "2018-09-03"|
                 day == "2018-09-07"| 
                 day == "2018-09-13",
               type ==1) 
#none of these are lapses
#giving the same responses to 8, 9, and 10
#looking at all data from this person
ema %>%  filter(subid == 85) %>%  .$ema_8 %>% table()
#I guess this is plausible? almost always said 7 but sometimes 6 and twice 4
ema %>%  filter(subid == 85) %>%  .$ema_9 %>% table()
#less plausible, said 11 every time and 7 once
ema %>%  filter(subid == 85) %>%  .$ema_10 %>% table()
#said 1 every time. I guess plausible.

# subj 78 on seveal days
ema %>% filter(subid == 78, 
               day == "2018-08-17" |
                 day == "2018-08-19" | 
                 day == "2018-08-24" | 
                 day == "2018-08-30",
               type ==1)
#seems fine

# subj 190 on 2019-03-03  
ema %>% filter(subid == 190, day == "2019-03-03", type ==1) 
#several in a row, seems fine

#subj 185 on several days
ema %>% filter(subid == 185, 
               day == "2019-03-04" |   
                 day == "2019-03-05" |   
                 day == "2019-03-22" |   
                 day == "2019-03-31" ,
               type ==1)
#Lots of duplicates on the same day in a row

# subj 138 on 2018-12-23  
ema %>% filter(subid == 138 , day == "2018-12-23", type ==1)
#ditto

# subj 117 on 2018-10-19   
ema %>% filter(subid == 117 , day == "2018-10-19", type ==1)
#same

# subj 98 on 2018-08-27    
ema %>% filter(subid == 98, day == "2018-08-27", type ==1) 
#seems fine also
```

We looked at these cases and found nothing clearly wrong. Here is a representative example of one day from one subject who often completed many surveys per day:

```{r echo = FALSE}
ema %>% filter(subid == 185, 
               day == "2019-03-04",
               type ==1) %>% 
  select(subid, day, time, num_range("ema_", 1:10)) %>% 
  kable

```

#### Looking closely at people with many *day* surveys per day 

```{r warning=FALSE, echo = FALSE}
#how many had more than 3 per day?
n_3inaday_pm <- ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(n == 3) %>% arrange(subid) %>% group_by(subid) %>% summarize(n = n()) %>% nrow()

#who had 10 per day
id_10inaday <- ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(n == 10) %>% .$subid

#subj 66 on 2018-05-23
#looking at one person with 10 in a day
Data_10inaday_pm <- ema %>% filter(subid == 66, day == "2018-05-23", type == 2) %>% select(time, ema_1, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7)

```

`r n_3inaday_pm` subjects had more than 3 surveys per day, with some having as many as 10! (Subjects `r id_10inaday`). Responses seem a little odd (going from 2 to 10 and back to 2 for ema_7 within a 10 minute span).


We looked at these cases and found nothing clearly wrong. Here is a representative example of one day from someone who often completed many surveys per day:

```{r echo = FALSE}
ema %>% filter(subid == 53, 
               day == "2018-03-30",
               type ==2) %>% 
  select(subid, day, time, num_range("ema_", 1:7)) %>% 
  kable

```


```{r warning=FALSE, results = FALSE, echo=FALSE}
#Multiple day surveys
ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(n > 5) %>% arrange(subid)

# subj   7 on 2017-07-02 completed  6 surveys
# subj   7 on 2017-08-16 completed  6 surveys
ema %>% filter(subid == 7, day == "2017-07-02" | day == "2017-08-16", type == 2)
#a lot spaced out throughout the day

# subj  25 on 2018-02-12 completed  6 surveys
ema %>% filter(subid == 25, day == "2018-02-12", type == 2) 
#many in a row but seems okay

# subj  53 on 2018-03-30 completed  6 surveys
# subj  53 on 2018-03-31 completed  6 surveys
# subj  53 on 2018-04-06 completed  6 surveys
# subj  53 on 2018-05-12 completed  6 surveys
ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(subid == 53) %>% arrange(-n)
#they also completed 5 and 4 on other days 
ema %>% filter(subid == 53, day == "2018-03-30", type == 2) 
#responses inconsistent but spaced 
ema %>% filter(subid == 53, day == "2018-03-31", type == 2) 
#I think this person just likes reporting when things happen

# subj  65 on 2018-06-19 completed  6 surveys
ema %>% filter(subid == 65, day == "2018-06-19", type == 2) 

#checking people with 10 in one day and those who have lots of high repeat days

# subj  66 on 2018-05-23 completed 10 surveys
ema %>% filter(subid == 66, day == "2018-05-23", type == 2) %>% 
  View()
#responses don't look totally normal... checking to see if they have lots of
#other high survey days
ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(subid == 66) %>% arrange(-n)
#not a lot,,, 2 with 5, 5 with four

# subj  79 on 2018-06-25 completed  7 surveys
# subj  79 on 2018-06-28 completed  6 surveys
# subj  79 on 2018-06-30 completed  6 surveys
# subj  79 on 2018-07-15 completed  6 surveys
ema %>% group_by(subid, day) %>% 
  filter(type == 2) %>% 
  summarize(n = n()) %>% 
  filter(subid == 79) %>% arrange(-n)
#they had multiple surveys on most days
ema %>% filter(subid == 79, day == "2018-06-30", type == 2) 
#not sure. seems okay.


# subj  84 on 2018-07-26 completed  7 surveys
# subj  84 on 2018-08-21 completed 10 surveys
# subj  84 on 2018-08-24 completed 10 surveys
# subj  84 on 2018-08-25 completed  6 surveys
# subj  84 on 2018-08-28 completed  7 surveys
# subj  84 on 2018-08-29 completed  8 surveys
# subj  84 on 2018-08-30 completed  8 surveys
# subj  84 on 2018-09-03 completed  8 surveys
# subj  84 on 2018-09-05 completed  7 surveys
# subj  84 on 2018-09-21 completed  6 surveys
# subj  84 on 2018-09-25 completed  6 surveys
# subj  84 on 2018-09-28 completed  6 surveys
ema %>% filter(subid == 84, day == "2018-08-21", type == 2) 
#a bunch within a short window

#Subjects with odd data: 84, 79, 66, 85
```

### Characterizing the data

```{r warning=FALSE, echo = FALSE}

#Basic descriptives ------------------------------------------------------------
# Descriptives - mins and maxes, distributions
ema %>% select(-type, -subid, -utc, -end_date, -day, -time, -start_date, -ema_1_1, -ema_1_3, -utc_date) %>% 
  varDescribe(2) %>% select(-vars) %>% kable()
#11 point scales, people using the full range of the scale
#some milk skewness and kurtosis

ema %>% .$ema_2 %>% hist(main = 'Greatest Urge Histogram') #greatest urge is really zero inf
#does that make sense?
#I suppose if people are filling out a lot of surveys per day there isn't time for urges.
ema %>% .$ema_3 %>% hist(main = 'Risks Histogram') #risks also really zero inflated
#are people not perceiving risks that are there?
ema %>% .$ema_4 %>% hist(main = 'Hassles Histogram') #hassles also zero inflated
#also this is surprising to me!
ema %>% .$ema_5 %>% hist(main = 'Positive Events') #same with positive events

#What about distributions within people?
#For example, greatest urge
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            urge_mean = mean(ema_2)) %>%   
  .$urge_mean %>% 
  hist(main = 'Urge Within-Person Mean')
#max urge
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            urge_max = max(ema_2)) %>%   
  .$urge_max %>% 
  hist(main = 'Urge Within-Person Max')
#for most people this was 12, but for a surprisingly large number, it was lower
#suggests that lapses might be more of a choice than failures to resist temptations
# (or they are impulses)

#and for min?
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            urge_min = min(ema_2)) %>%   
  .$urge_min %>% 
  hist(main = 'Urge Within-Person Min')
#almost everyone used the full range of the scale

#how about for risks?
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            risks_mean = mean(ema_3)) %>%   
  .$risks_mean %>% 
  hist(main = 'Risks Within-Person Mean')
#surprisingly skew
#max?
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            risks_max = max(ema_3)) %>%   
  .$risks_max %>% 
  hist(main = 'Risks Within-Person Mean')
#more people reporting max of 12
ema %>% group_by(subid) %>% 
  summarize(n = n(),
            risks_min = min(ema_3)) %>%   
  .$risks_min %>% 
  hist(main = 'Risks Within-Person Min')
#people using the full lower range of the scale
```

###Missing data

Table shows the number of observations with a particular pattern and the pattern (i.e., the presence/absence of each item). The bottom row shows the number of observations missing each item.
```{r echo = FALSE, warning= FALSE}

missing <- ema %>%  select(-type, -subid, -utc, -end_date, -day, -time, -start_date, -ema_1_1, -ema_1_3, -ema_1_5, -utc_date) %>% md.pattern(plot = FALSE) 

missing %>%  as_tibble() %>% mutate(nmissing = V11, n = row.names(missing)) %>% select(-V11, -nmissing) %>% select(n, everything()) %>%  kable() 

```

### Checking for errors with survey completion

```{r echo = FALSE}
#did conditional display of questions 1_1, 1_3, 1_5 work as it should?
n_missedlapse_qs <- ema %>% filter(ema_1 == 2 & is.na(ema_1_1) & is.na(ema_1_3) & is.na(ema_1_5)) %>% nrow()
#nobody answered yes that they drank but has all three follow-ups NA

n_bonuslapse_qs <- ema %>% filter(ema_1 == 1 & (!is.na(ema_1_1) | !is.na(ema_1_3) | !is.na(ema_1_5))) %>% nrow()
#nobody answered no that they didn't drink but has any response to a follow-up Q
#so, yes, conditional display of these questions worked

#some follow up questions are missing from this dataframe (ema 1_2, 1_4)
#these were collapsed into other items

#did morning and evening surveys have what they should?
n_missingmorning_qs <- ema %>% filter(type == 1 & is.na(ema_8) & is.na(ema_9) & is.na(ema_10)) %>% nrow()
#6 people have NAs for all these questions
#but they have NAs for all the other questions, too... how many are filled in lapses
n_missingmorning_qs_lapsed <- ema %>% filter(type == 1 & is.na(ema_8) & is.na(ema_9) & is.na(ema_10)) %>% filter(ema_1 == 2) %>% nrow()

#did evening surveys not have what they shouldn't?
n_bonusmorning_qs <-  ema %>% filter(type == 2 & (!is.na(ema_8) | !is.na(ema_9) | !is.na(ema_10))) %>% nrow()
#yes
```

There is one apparent error with the survey display:  

* The number of people who did not report a lapse but have responses for questions about the lapse is `r n_bonuslapse_qs`.  

```{r echo = FALSE}
ema %>%filter(ema_1 == 1 & (!is.na(ema_1_1) | !is.na(ema_1_3) | !is.na(ema_1_5))) %>% 
  select(subid, day, ema_1, ema_1_1, ema_1_3, ema_1_5, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7, ema_8) %>% kable()
```

Other errors checked for:  

* The number of people who reported a lapse but have no responses for the lapse questions is `r n_missedlapse_qs`.  
* The number of morning surveys that don't have responses to questions 8, 9, and 10 is `r n_missingmorning_qs`.     
    + Of these, `r n_missingmorning_qs_lapsed` were lapses, and were probably filled in based on in-lab information.  
* The number of evening surveys that have responses to questions 8, 9, and 10 is `r n_bonusmorning_qs`.  

### Checking survey completion times

```{r echo = FALSE}
survey_duration_summary <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  select(subid, survey_duration_mins) %>% 
  varDescribe() %>% filter(vars == 2)

n_under3mins <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  filter(survey_duration_mins < 3) %>% nrow()

n_morethan1hr <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration_hours >1) %>% nrow()

n_morethan3hr <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration_hours >3) %>% nrow()

n_morethan5hr <-ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration_hours >5) %>% nrow()

n_slowseveraltimes <-  ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_mins, subid, everything()) %>% 
  filter(survey_duration_mins > 3) %>% group_by(subid) %>% 
  summarise(n = n()) %>% filter(n > 1) %>% nrow()

n_slowalot <-  ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_mins, subid, everything()) %>% 
  filter(survey_duration_mins > 3) %>% group_by(subid) %>% 
  summarise(n = n()) %>% filter(n > 5) %>% nrow()

n_slowtoomuch <-  ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_mins, subid, everything()) %>% 
  filter(survey_duration_mins > 3) %>% group_by(subid) %>% 
  summarise(n = n()) %>% filter(n > 10) %>% nrow()

```

Of `r survey_duration_summary$n` observations, the average time it took to complete the survey was `r survey_duration_summary$mean` minutes (range `r round(survey_duration_summary$min, 0)` - `r round(survey_duration_summary$max, 0)`). Survey duration is exteremely kurtotic `r survey_duration_summary$kurtosis`.

Most surveys (`r n_under3mins`) were completed in under 3 minutes. Among surveys that took less than three minutes, distribution is more normal, though right skewed.

```{r echo = FALSE}
ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  filter(survey_duration_mins < 3) %>% 
  .$survey_duration_mins %>% hist(main = 'Survey Completion time in Minutes, Obs < 3 mins')
```

Some surveys were completed exteremly slowly:

* `r n_morethan1hr` surveys took more than an hour
* `r n_morethan3hr` surveys took more than three hours
* `r n_morethan5hr` surveys took more than five hours 

Many of the surveys that look a long time were lapses:
```{r echo = FALSE}
ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(subid, day, survey_duration_hours, type, ema_1, ema_1_5, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7) %>% 
  filter(survey_duration_hours >5) %>% kable()
```

Some people were especially slow:

* `r n_slowseveraltimes` people took more than 3 minutes more than once.
* `r n_slowalot` people took more than 3 minutes more than five times.
* `r n_slowtoomuch` people took more than 3 minutes more than ten times 

A few people regularly took more than 10 minutes.
```{r echo = FALSE}
ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_mins = as.numeric(survey_duration / 60)) %>% 
  select(survey_duration, survey_duration_mins, subid, everything()) %>% 
  filter(survey_duration_mins > 10) %>% group_by(subid) %>% 
  summarise(n_morethan10minutes = n()) %>% filter(n_morethan10minutes > 5) %>% kable()
```


```{r echo = FALSE}

n_lessthan15secs <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  select(survey_duration_secs,subid, everything()) %>% 
  filter(survey_duration_secs < 15) %>% nrow()

n_lessthan13secs <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  select(survey_duration_secs,subid, everything()) %>% 
  filter(survey_duration_secs < 13) %>% nrow()

n_lessthan11secs <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  select(survey_duration_secs,subid, everything()) %>% 
  filter(survey_duration_secs < 11) %>% nrow()


n_fastseveraltimes <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration < 13) %>% group_by(subid) %>% 
  summarize(n = n()) %>% filter(n > 1) %>% nrow()
#34 people took less than 15 seconds more than once

n_fastalot <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration < 13) %>% group_by(subid) %>% 
  summarize(n = n()) %>% filter(n > 5) %>% nrow()

n_fasttoomuch <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_hours = as.numeric(survey_duration / 60 / 60)) %>% 
  arrange(-survey_duration) %>% 
  select(survey_duration, survey_duration_hours, subid, everything()) %>% 
  filter(survey_duration < 13) %>% group_by(subid) %>% 
  summarize(n = n()) %>% filter(n > 10) %>% nrow()

n_fast_lapses <- ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  select(subid, day, survey_duration_secs, type, ema_1, ema_1_5, ema_2, ema_3, ema_4, ema_5, ema_6, ema_7) %>% 
  filter(survey_duration_secs < 15) %>% filter(ema_1 == 2) %>% nrow()

```

Other surveys were completed very quickly.

* `r n_lessthan15secs` surveys took more than 15 seconds
* `r n_lessthan13secs` surveys took more than 13 seconds
* `r n_lessthan11secs` surveys took more than 11 seconds 

`r n_fast_lapses` of the surveys that were completed in under 15 seconds were lapses.

```{r echo = FALSE}
ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  filter(survey_duration_secs < 15) %>% 
  .$survey_duration_secs %>% hist(main = 'Survey Completion time in Seconds, Obs < 15 secs', breaks = 5)
```

Some people were especially fast:

* `r n_fastseveraltimes` people took less than 13 minutes more than once.
* `r n_fastalot` people took less than 13 minutes more than five times.
* `r n_fasttoomuch` people took less than 13 minutes more than ten times 

A few people regularly took 10 seconds or less.
```{r echo = FALSE}
ema %>% mutate(survey_duration = end_date - start_date) %>% 
  mutate(survey_duration_secs = as.numeric(survey_duration)) %>% 
  select(survey_duration, survey_duration_secs, subid, everything()) %>% 
  filter(survey_duration_secs <= 10) %>% group_by(subid) %>% 
  summarise(n_lessthan10secs = n()) %>% filter(n_lessthan10secs > 2) %>% kable()
```

## Looking at lapses (y)

```{r echo = FALSE}
#note: all data included are from the day before the day they were recorded as drinking.
# (not much here)

lapses_ema <- ema %>% filter(ema_1 == 2) %>% nrow()
lapses_y <- lapses%>% filter(lapse == 1) %>% nrow() 

```

There are `r lapses_ema` lapses in the ema dataset and `r lapses_y` lapses in the lapse dataset.

```{r echo = FALSE, warning=FALSE}

#Looking at lapses per day in ema
lapses_per_day_ema <- ema %>% group_by(subid, day) %>% 
  filter(ema_1 == 2) %>% 
  summarize(n = n()) %>% varDescribe() %>% filter(vars == 3)

```

In the ema dataset, most people have just one lapse per day, with an average of `r lapses_per_day_ema$mean` (range `r lapses_per_day_ema$min` - `r lapses_per_day_ema$max`).

```{r}
#in y lapses
lapses$day <- lapses$utc %>% #converting into human readable form
  as.numeric %>% 
  as.POSIXct(tz='America/Chicago', origin="1970-01-01")
#note, the time has been removed

##SARAH where did this come from?
y_TooManylapses_per_dayy <- lapses %>% group_by(subid, day) %>% 
  filter(lapse == 1) %>% 
  summarize(n = n()) %>% filter(n > 1) %>% nrow()

lapsesPerPerson <- lapses%>% group_by(subid) %>% 
  filter(lapse == 1) %>% 
  summarize(n = n()) %>% 
  summarize(mean_nlapses = mean(n),
            max_nlapses = max(n),
            min_nlapses = min(n))
```

In the y dataset, there are `r` lapses. `r y_TooManylapses_per_dayy` had more than one lapse per day. Among lapses, some came from the same people. Among those who lapsed, the average number of lapses was `r lapsesPerPerson$mean_nlapses` (range `r lapsesPerPerson$min_nlapses` = `r lapsesPerPerson$max_nlapses`).

## Looking at ema Features (X, looking at id and ema variables)
##SARAH we no longer have a features file?

```{r} 
#Do the X dataset and y dataset have the same number of observations? `r nrow(X) #== nrow(lapses)`
```

```{r echo = FALSE}
 
# #subsetting just to ema and General
# X_ema <- X %>% as_tibble() %>% 
#   select(subid, utc, contains("ema"), contains("Gen")) 
# 
# #converting dates
# #these have alreay been standardized to just the day
# X_ema$Date <- X_ema$utc %>% #converting into human readable form
#   as.numeric %>% 
#   as.POSIXct(tz='America/Chicago', origin="1970-01-01") %>% 
#   substr(1, 10)
# 
# #looks normal
# nrow(X_ema)
# ncol(X_ema)
# #there are 206 features
# #and 9108 observations
# 
# #checking the number that are exact duplicates ()
# duplicated(X_ema) %>% table()
# #there are zero
# 
# #check that the values here are all possible
# #ema_2 as an example
# X_ema %>% select(contains("ema_2")) %>% varDescribe()
# #two are extremely kurtotic
# #MeanWeekvB
# X_ema %>% select(contains("MeanWeekvB")) %>% varDescribe()
# #Mean3dayvB
# X_ema %>% select(contains("Mean3dayvB")) %>% varDescribe()
# #MeandayvB
# X_ema %>% select(contains("MeandayvB")) %>% varDescribe()
# #these look correct
```

# Looking at the id dataset 
```{r}
# ##SARAH doesnt work
# #reloading just in case?
# id <- read_rds(file.path(data_path, "ds_id.rds")) %>% 
#   glimpse()
# dim(id)
# #154 rows
# 
# id %>% group_by(subid) %>% 
#   summarize(n = n()) %>% nrow()
# #154 people
# 
# #vs for ema
# ema %>% group_by(subid) %>% 
#   summarize(n = n()) %>% nrow()
# #also 154
# 
# #looking at demographics
# id %>% select(contains("dem")) %>% varDescribe()
# #some missing values on Dem2_4, 6, 8
# #also where are Dem 2_1, 3, 5, 7?
# #dem_7 must be income
# ##SARAH error might be here?
# #hist(id$dem_7)
# 
# #looking at alcohol use history
# id %>% select(contains("auh")) %>% varDescribe()
# #no missing 
# 
# #looking at assist
# id %>% select(contains("assist")) %>% varDescribe()
# #no missing 
# #some insane kurtosis and skew for the self-efficacy
# 
# #DSM
# id %>% .$scale_dtm5_tot %>% hist()
# #left skew but not too bad
# 
# #DTS
# id %>% select(contains("dts")) %>% varDescribe()
# #looks good
# 
# #FAD
# id %>% select(contains("fad")) %>% varDescribe()
# #why are the maxes here all over the place? what was the scale?
# #otherwise no problems
# 
# #ASI
# id %>% select(contains("asi")) %>% varDescribe()
# #looks good
# 
# #SCL
# id %>% select(contains("scl")) %>% varDescribe()
# #mostly normal excelt Pho and Ang are kurtotic
# #most people scored very low on both
# 
# #MPS
# id %>% select(contains("mps")) %>% varDescribe()
# #looks normal
# 
# #else
# id %>% select(-contains("mps"), -contains("scl"), -contains("asi"),
#               -contains("fad"), -contains("dts"), -contains("assist"),
#               -contains("auh"), -contains("dsm"), -contains("dem"),
#               -contains("sub"), -contains("utc")) %>% varDescribe()
# #all good

```

- age is ok
- gender is ok
- trait level time 0 is ok as just intercept
- trait level time 0 is a source of interaction, too
- id is the id labels, includes things like the DSM-5 checklist, demographics
- SR is self-report varying

Clinical story is to build a model to predict from self-report
Theory ema story is to expand on static person-level variables
- by adding time-varying components
- and then interactions

next ... we will do a nested CV just using ema to get a starting point. Maybe use lasso to figure out 
what features are best and most useful. To help us with the theory-driven questions.
would like to interact features -- maybe not all features, but some subset (e.g.,
holiday, person-level variables, ...)

#thinking about pre-registering this project
- there is 1 way that we can still be cherry-picking:
- specifically, any decisions made outside of CV
- is still subject to cherry picking
- specifically the DV and inclusion/exclusion
- and inclusion/exclusion of the ema data (e.g., because of odd behavior)
- including for sparseness / missing data within the ema

# goals of this would be:
1. to do analyses we are comfortable with
2. to do analyses that others are comfortable with / confident in?

#To - do:
- check for missingness in the ema ...
- do a little lit search using risk 2 citations as starting point
