---
title: "Make Final GPS samples"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/gps", 
      "/Volumes/private/studydata/risk/knits/gps")
    )
  })
---

### Code Status

in development



### Notes   

The final sample starts with the N = 151 participants who completed through at 
least follow-up 1 and who had valid lapse data.   More details on these decisions
are available in the cleaning of EMA and lapses and in the mak_study_dates.Rmd
scripts

This script checks the GPS data of the N=151 and finalizes an overall sample 
and identifies an eyeball sample.

it is also relevant to consider the mak_rset script for how the full sample is 
divided up in the train/validate resamples




### Set Up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_processed <- "P:/studydata/risk/data_processed/shared"
          path_gps <- "P:/studydata/risk/data_processed/gps"},

        # IOS paths
        Darwin = {
          path_processed <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_gps <- "/Volumes/private/studydata/risk/data_processed/gps"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
  conflict_prefer("filter", "dplyr")
  conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)
library(vroom)
library(janitor)
library(lubridate)
```


Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here("../lab_support/print_kbl.R"))
```


### Begin Main Code

```{r}
study_dates <- vroom(here(path_gps, "study_dates.csv")) %>% 
  glimpse()
```

