---
title: "make RSET object for gps train and test per GA tech splits"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/gps", 
      "/Volumes/private/studydata/risk/knits/gps")
    )
  })
---
### Updates Needed
It still needs to have X added to the data at some point.  Right now the splits are
done only on the labels

### Notes

This script makes and saves an RSET object that includes train/test splits
defined by GA Tech for use across our labs. It saves this rset in the gps study 
data folder on the server for use with this study


### Set up Environment

Absolute paths
```{r, paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_gps <- "P:/studydata/risk/data_processed/gps"
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_lab_support <- "P:/toolboxes/lab_support"},

        # IOS paths
        Darwin = {
          path_gps <- "/Volumes/private/studydata/risk/data_processed/gps"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_lab_support <- "/Volumes/toolboxes/lab_support"}
        )
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}

# for data wrangling
library(tidyverse)  # always need this
library(rsample)
library(janitor)

source(here("gps", "fun_gps.R"))  # for make_rset()
```


### Make RSET

Get labels and subids for splits. 

* subids for train sets in separate columns of train_ids
* d contains both X and Y for entire sample

FIX: Need to update to add raw X to d
```{r}
d <- read_csv(here(path_gps, "labels_05.csv")) %>% 
  glimpse()


train_ids <- read_csv(here(path_gps, "train_ids.csv"), col_names = FALSE, 
                      col_types = cols()) %>% 
  glimpse()
```

Make rset
```{r}
rset <- make_rset(train_ids, d)
```

### Some EDA
```{r}
rset
```

Split 1
```{r}
rset$splits[[1]]

analysis(rset$splits[[1]]) %>% 
  glimpse()

assessment(rset$splits[[1]]) %>% 
  glimpse()

subid_in_1 <- analysis(rset$splits[[1]]) %>% 
  pull(subid) %>% 
  unique() %>% 
  print()
  
subid_out_1 <- assessment(rset$splits[[1]]) %>% 
  pull(subid) %>% 
  unique() %>% 
  print()

length(subid_in_1)
length(subid_out_1)
any(subid_in_1 %in% subid_out_1)
any(subid_out_1 %in% subid_in_1)


```

Split 2
```{r}
rset$splits[[2]]
subid_in_2 <- analysis(rset$splits[[2]]) %>% 
  pull(subid) %>% 
  unique() %>% 
  print()
  
subid_out_2 <- assessment(rset$splits[[2]]) %>% 
  pull(subid) %>% 
  unique() %>% 
  print()

length(subid_in_2)
length(subid_out_2)
any(subid_in_2 %in% subid_out_2)
any(subid_out_2 %in% subid_in_2)
```

Compare test for splits 1 and 2.  Should not be fully overlapping but some 
overlap is expected b/c this is NOT k-fold
```{r}
sum(subid_out_1 %in% subid_out_2)
```

### Save RSET
```{r}
rset %>% 
  glimpse() %>% 
  write_rds(here(path_gps, "rset.rds"))
```