---
title: "Phone screen"
output: html_document
---

## Notes
This script pull info about participants screened out of risk during phone screen for burden manuscript.

```{r}
library(tidyverse)
library(kableExtra)
```

```{r}
path_in <- "Z:/studydata/risk/data_raw/qualtrics"
```

### Read in data and join relevant columns

```{r}
screen_1 <- read_csv(file.path(path_in, "phone_screen_v1.csv"), col_types = cols()) %>% 
  select(-Q6) %>% 
  rename(Q6 = Q5) %>% 
  select(-Q10) %>% 
  rename(Q10 = Q9) %>% 
  rename(Q9 = Q8) %>% 
  select(-Q18) %>% 
  rename(Q18 = Q17) %>% 
  glimpse()

screen_2 <- read_csv(file.path(path_in, "phone_screen_v2.csv"), col_types = cols()) %>% 
  glimpse()

screen_3 <- read_csv(file.path(path_in, "phone_screen_v3.csv"), col_types = cols()) %>% 
  glimpse()

screen_4 <- read_csv(file.path(path_in, "phone_screen_v4.csv"), col_types = cols()) %>% 
  rename(Q2 = DataType,
         Q32 = CallType,
         Q18 = Phone_11,
         Q38 = Phone_12,
         Q19 = Phone_13) %>% 
  mutate(Q10 = ifelse(Phone_7 == "Participant did not have time to be screened (skip to end of survey)", 
                     "No, participant does not have time now", "Yes, participant has time now"),
         Q9 = ifelse(Phone_7 == "Participant was not interested in the study (skip to end of survey)",
                     "Participant is no longer interested", "Participant is interested"),
         Q2 = ifelse(Q2 == "Real", "Real data", "Fake data")) %>% 
  glimpse()
```



```{r}
screen <- screen_1 %>% 
  select(Q2, Q6, Q9, Q10, Q18) %>% 
  full_join(screen_2 %>% 
              select(Q2, Q6, Q9, Q10, Q18, Q19, Q32)) %>% 
  full_join(screen_3 %>% 
              select(Q2, Q6, Q9, Q10, Q18, Q19, Q32, Q38)) %>% 
  full_join(screen_4 %>% 
              select(Q2, Q9, Q10, Q18, Q19, Q32, Q38)) %>% 
  glimpse()
```









### Version 1
```{r}
tabyl(screen_1$Q10)
```


### Version 2
```{r}
screen_2 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Interest in study after hearing about it
```{r}
screen_2 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q9)
```

Interested but does not have time to complete screen now
```{r}
screen_2 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q10)
```


Able and willing to use own phone
Interest in study after hearing about it
```{r}
screen_2 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q18)
```


Primary number is internet based service
Interest in study after hearing about it
```{r}
screen_2 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q19)
```

### Version 3
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Interest in study after hearing about it
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q9)
```

Interested but does not have time to complete screen now
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q10)
```


Able and willing to use own phone
Interest in study after hearing about it
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q18)
```


Primary number is internet based service
Interest in study after hearing about it
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q19)
```

Phone model   
Samsung galaxy s7 or older = ineligible
```{r}
screen_3 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>%
  filter(Q19 == "No") %>% 
  tabyl(Q38)
```

### Version 4
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  # filter(Q6 == "Yes, participant has time now") %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
  scroll_box(width = "100%", height = "500px")
```

Interest in study after hearing about it
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  # filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q9)
```

Interested but does not have time to complete screen now
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q9 == "Participant is interested") %>% 
  # filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q10)
```


Able and willing to use own phone
Interest in study after hearing about it
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q18)
```


Primary number is internet based service
Interest in study after hearing about it
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>% 
  tabyl(Q19)
```

Phone model   
Samsung galaxy s7 or older = ineligible
```{r}
screen_4 %>%
  filter(Q2 == "Real data") %>% 
  filter(Q32 == "Screen") %>% 
  filter(Q6 == "Yes, participant has time now") %>%
  filter(Q19 == "No") %>% 
  tabyl(Q38)
```
