---
title: "Compliance"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---

### Notes
Purpose: This script calculates all measures of compliance cited in *Acceptability of Personal Sensing among People with Alcohol Use Disorder*.     

Inputs:  
* visit_dates.csv   
* audio.csv   
* ema_morning.csv  
* ema_later.csv  
* voice_android.csv  
* voice_ios.csv  
* sms_android.csv  
* sms_ios.csv  
* gps.rds  
   


### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths 
```{r}
path_shared <- "P:/studydata/risk/data_processed/shared"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(ggtext)
library(janitor)
library(lubridate)
library(cowplot)
library(data.table)
library(patchwork)
```


### Read in Data

```{r}
visit_dates <- read_csv(file.path(path_shared, "visit_dates.csv"), col_types = cols())
ema_m <- read_csv(file.path(path_shared, "ema_morning.csv"), col_types = cols())
ema_l <- read_csv(file.path(path_shared, "ema_later.csv"), col_types = cols())
audio <- read_csv(file.path(path_shared, "audio.csv"), col_types = cols())
gps <- read_rds(file.path(path_shared, "gps.rds"))

# using vroom for large csv files
sms_android <- vroom::vroom(file.path(path_shared, "sms_android.csv"), col_types = cols()) 
sms_ios <- vroom::vroom(file.path(path_shared, "sms_ios.csv"), col_types = cols())  
voice_android <- vroom::vroom(file.path(path_shared, "voice_android.csv"), col_types = cols())
voice_ios <- vroom::vroom(file.path(path_shared, "voice_ios.csv"), col_types = cols())
```

Filter visit dates down to enrolled participants (N = 169). Study start and end dates will be used to filter data streams down to when participants were officially on study for compliance proportions.
```{r}
visit_dates <- visit_dates %>% 
  filter(!is.na(start_study)) %>% 
  # filter out subid who started and ended study on same day - not considered enrolled
  filter(subid != 235) 
```

<br>


### Compliance for Passive Data Streams 

Check if data exists for every passive data stream for all participants. This will be used to 
judge whether participants opted-in to passive data streams at least at some point during the study.    


#### GPS

`r nrow(gps %>% count(subid))` (`r round(nrow(gps %>% count(subid))/nrow(visit_dates)*100, 2)`%) of the enrolled subids (N = 169) have gps data   

Enrolled subids with no gps data
```{r}
visit_dates %>% 
  filter(!subid %in% gps$subid) 
```

<br>


#### Cellular communication logs 

Cellular communication logs could only be downloaded in person so the first opportunity to download logs was at follow-up 1.    
Subset to subids who completed follow-up 1    

`r nrow(visit_dates %>% filter(!is.na(followup_1)))` participants completed follow-up 1.  

```{r}
fu_1 <- visit_dates %>% 
  filter(!is.na(followup_1))
```

<br>


**Voice Logs**

Get subids from IOS and android voice logs
```{r}
voice <- voice_android %>% 
  mutate(subid = as.numeric(subid)) %>% 
  select(subid) %>% 
  full_join(voice_ios %>% mutate(subid = as.numeric(subid)) %>% select(subid), by = "subid")
```

`r nrow(voice %>% count(subid))` subids have voice call data.    

* We have voice logs for 1 subid who never completed their follow-up 1 visit      
According to notes: Subid 237 arrived to Follow-up 1 but asked to be discontinued before data was collected. They needed to leave shortly after their visit time started so unreported contacts locations and ID Battery were NOT collected. Call and SMS logs were collected at FU1 but numbers were not gone over with participant.

<br>

`r nrow(subset(voice, subid %in% fu_1$subid) %>% count(subid))` (`r round(nrow(subset(voice, subid %in% fu_1$subid) %>% count(subid))/(nrow(fu_1 %>% count(subid)))*100, 2)`%) of the subids who completed follow-up 1 (N = 154) have voice log data.



<br>

**SMS Logs**
 
Get subids from IOS and android SMS logs
```{r}
sms <- sms_android %>% 
  mutate(subid = as.numeric(subid)) %>% 
  select(subid) %>% 
  full_join(sms_ios %>% mutate(subid = as.numeric(subid)) %>% select(subid), by = "subid") 
```


`r nrow(sms %>% count(subid))` subids have sms data.   

* We have SMS logs for subid 237 but they never completed their follow-up 1 visit.

<br>

`r nrow(subset(sms, subid %in% fu_1$subid) %>% count(subid))` (`r round(nrow(subset(sms, subid %in% fu_1$subid) %>% count(subid))/(nrow(fu_1 %>% count(subid)))*100, 2)`%) of the subids who completed follow-up 1 (N = 154) have SMS data.

<br>

Missing SMS logs for 1 subid    
According to Notes: Subject's SMS files are empty because the subject deleted all text messages before their study visit; They also did not text much.  
```{r}
fu_1 %>% 
  filter(!subid %in% sms$subid)
```



<br>

### Compliance for Active Data Streams

Enrolled subids (N = 169) serves as the denominator for all compliance measures unless otherwise noted.

#### Audio  

`r nrow(audio %>% count(subid))` (`r round(nrow(audio %>% count(subid))/nrow(visit_dates)*100, 2)`%) subids have audio data   

Enrolled subids with no audio data
```{r}
visit_dates %>% 
  filter(!subid %in% as.numeric(audio$subid)) 
```


Remove duplicate audio check ins on same day and filter by start end date
```{r}
audio <- audio %>% 
  group_by(subid, date) %>% 
  slice(1) %>% 
  ungroup() %>% 
  mutate(subid = as.numeric(subid)) %>% 
  select(subid, date)

audio <- audio %>% 
  full_join(visit_dates, by = "subid") %>% 
  # truncate by start and end date
  filter(date >= start_study & date < end_study)
```

calculate proportion days with audio
```{r}
# days with audio
audio_days <- audio %>% 
  group_by(subid) %>% 
  summarise(days_audio = n()) %>% 
  ungroup()

# days on study
audio_days <- visit_dates %>% 
  mutate(days_study = as.numeric(end_study - start_study)) %>% 
  full_join(audio_days, by = "subid") %>% 
  mutate(days_audio = case_when(is.na(days_audio) ~ 0,
                                TRUE ~ as.numeric(days_audio)),
         days_study = case_when(days_study == 0 ~ as.numeric(NA), # to prevent errors from dividing by 0 denominator
                                TRUE ~ days_study))
```

Calculate mean compliance
```{r}
mean_audio <- audio_days %>% 
  summarise(proportion_days = days_audio/days_study) %>% 
  summarise(mean = mean(proportion_days, na.rm = TRUE))
```

<br>

On average participants (N = 169) completed `r round(mean_audio$mean, 2)` audio checkins each day they were on study. That is their overall compliance for a once daily audio check-in was `r round(mean_audio$mean, 2)*100`%.

<br>

Histogram
```{r}
audio_days %>% 
  summarise(proportion_days = days_audio/days_study) %>% 
  ggplot(aes(x = proportion_days)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .05) +
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0)) +
  labs(y = "Frequency", x = "Proportion of study days with an audio check-in",
       subtitle = "Audio Check-in") +
  geom_vline(aes(xintercept = mean_audio$mean), size = .4) +
  theme_classic() +
  theme(text = element_text()) 
```

<br>

#### EMA

Join morning and evening EMA datasets
```{r}
ema <- ema_m %>% 
  select(subid, start_date) %>% 
  full_join(ema_l %>% select(subid, start_date), by = c("subid", "start_date")) %>% 
  mutate(start_date = date(start_date),
         subid = as.numeric(subid)) %>% 
  # Subid 55 re-enrolled as subid 61. These observations should not be considered. 
  filter(subid != 55)
```

`r nrow(ema %>% count(subid))` (`r round(nrow(ema %>% count(subid))/nrow(visit_dates)*100, 2)`%) subids have ema data   

<br>

**Days with at least 1 EMA**
```{r message = FALSE}
ema_one_daily <- ema %>% 
  group_by(subid, start_date) %>% 
  slice(1)  %>% 
  full_join(visit_dates, by = "subid") %>% 
  # truncate by start and end date
  filter(start_date >= start_study & start_date < end_study)
```

calculate proportion days with 1 ema
```{r}
# days with 1 ema
ema_days <- ema_one_daily %>% 
  group_by(subid) %>% 
  summarise(days_ema = n()) %>% 
  ungroup()

# days on study
ema_days <- visit_dates %>% 
  mutate(days_study = as.numeric(end_study - start_study)) %>% 
  full_join(ema_days, by = "subid") %>% 
  mutate(days_ema = case_when(is.na(days_ema) ~ 0,
                                TRUE ~ as.numeric(days_ema)),
         days_study = case_when(days_study == 0 ~ as.numeric(NA), # to prevent errors from dividing by 0 denominator (1 subid)
                                TRUE ~ days_study))
```

Calculate Mean Proportion
```{r}
mean_ema_days <- ema_days %>% 
  summarise(proportion_days = days_ema/days_study) %>% 
  summarise(mean = mean(proportion_days, na.rm = TRUE))
```

<br>

On average participants (N = 169) complied with at least one daily EMA on `r round(mean_ema_days$mean, 2)*100`% of study days.

<br>

Histogram
```{r warning = FALSE}
ema_days %>% 
  summarise(proportion_days = days_ema/days_study) %>% 
  ggplot(aes(x = proportion_days)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .05) +
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0), limits = c(0, 1.05)) +
  labs(y = "Frequency", x = "Proportion of study days with at least one EMA completed",
       subtitle = "1 Time Daily EMA Compliance") +
  geom_vline(aes(xintercept = mean_ema_days$mean), size = .4) +
  theme_classic()
```


<br>

**Overall proportion of EMAs completed while on study**

```{r message = FALSE}
ema_total <- ema_m %>% 
  select(subid, start_date) %>% 
  full_join(ema_l %>% select(subid, start_date)) %>% 
  mutate(start_date = date(start_date),
         subid = as.numeric(subid)) %>% 
  full_join(visit_dates, by = "subid") %>% 
  # truncate by start and end date
  filter(start_date >= start_study & start_date < end_study)
```

calculate proportion of total emas completed
```{r}
# total emas
ema_total <- ema_total %>% 
  group_by(subid, start_date) %>% 
  summarise(num_emas = n(), .groups = "drop") %>% 
  ungroup() %>% 
  mutate(num_emas = case_when(num_emas > 4 ~ 4,
                              TRUE ~ as.numeric(num_emas))) %>% 
  group_by(subid) %>% 
  summarise(total_ema = sum(num_emas))

# days on study
ema_total <- visit_dates %>% 
  mutate(days_study = as.numeric(end_study - start_study)) %>% 
  full_join(ema_total, by = "subid") %>% 
  mutate(total_ema = case_when(is.na(total_ema) ~ 0,
                                TRUE ~ as.numeric(total_ema)),
         days_study = case_when(days_study == 0 ~ as.numeric(NA), # to prevent errors from dividing by 0 denominator (1 subid)
                                TRUE ~ days_study))
```

Calculate average overall compliance
```{r}
mean_ema <- ema_total %>% 
  summarise(proportion_ema = total_ema/days_study) %>% 
  summarise(mean = mean(proportion_ema, na.rm = TRUE))

mean_ema_total <- ema_total %>% 
  summarise(proportion_ema = total_ema/(days_study * 4)) %>% 
  summarise(mean = mean(proportion_ema, na.rm = TRUE))
```

<br>

Participants on average completed `r round(mean_ema, 2)` EMAs per day with an overall compliance of `r round(mean_ema_total, 2)*100`%.  

<br>


Histogram of proportion of total EMAs completed
```{r warning = FALSE}
ema_total %>% 
  summarise(proportion_ema = total_ema/(days_study * 4)) %>% 
  ggplot(aes(x = proportion_ema)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .05) +
  scale_x_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.0), limits = c(0, 1.05)) +
  labs(y = "Frequency", x = "Proportion of total EMA's completed while on study (max = 4 x's per day)",
       subtitle = "Total EMA Compliance") +
  geom_vline(aes(xintercept = mean_ema_total$mean), size = .4) +
  theme_classic()
```


<br>
