---
title: "Compliance"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---

### Notes
Purpose: This script calculates all measures of compliance cited in *Acceptability of Personal Sensing among People with Alcohol Use Disorder*.     

Inputs:  
* visit_dates.csv   
* audio.csv   
* ema_morning.csv  
* ema_later.csv  
* voice_android.csv  
* voice_ios.csv  
* sms_android.csv  
* sms_ios.csv  
* gps.rds  
   


### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths 
```{r}
path_shared <- "P:/studydata/risk/data_processed/shared"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(ggtext)
library(janitor)
library(lubridate)
library(cowplot)
library(data.table)
library(patchwork)
library(vroom)
```


### Read in Data

```{r}
visit_dates <- read_csv(file.path(path_shared, "visit_dates.csv"), col_types = cols())
ema_m <- vroom(file.path(path_shared, "ema_morning.csv"), col_types = vroom::cols()) %>% 
  mutate(start_date = with_tz(start_date, tzone = "America/Chicago"),
         subid = as.numeric(subid))
ema_l <- vroom(file.path(path_shared, "ema_later.csv"), col_types = vroom::cols()) %>% 
  mutate(start_date = with_tz(start_date, tzone = "America/Chicago"),
         subid = as.numeric(subid))
audio <- vroom(file.path(path_shared, "audio.csv"), col_types = vroom::cols()) %>% 
  mutate(subid = as.numeric(subid))



# passive - update dates if daily compliance calculated
gps <- read_rds(file.path(path_shared, "gps.rds"))
sms_android <- vroom::vroom(file.path(path_shared, "sms_android.csv"), col_types = cols())
sms_ios <- vroom::vroom(file.path(path_shared, "sms_ios.csv"), col_types = cols())
voice_android <- vroom::vroom(file.path(path_shared, "voice_android.csv"), col_types = cols())
voice_ios <- vroom::vroom(file.path(path_shared, "voice_ios.csv"), col_types = cols())
```


### Compliance for Passive Data Streams 

Check if data exists for every passive data stream for all participants.  


Use enrolled participants (N = 169) since they opt in at time of enrollment:   
Filter visit dates down to enrolled participants
```{r}
visit_dates <- visit_dates %>%
  filter(!is.na(start_study)) %>%
  # filter out subid who started and ended study on same day - not considered enrolled
  filter(subid != 235)
```

#### GPS

`r nrow(gps %>% count(subid))` (`r round(nrow(gps %>% count(subid))/nrow(visit_dates)*100, 2)`%) of the enrolled subids (N = 169) have gps data   
 
Enrolled subids with no gps data     
No notes as to why
```{r}
visit_dates %>% 
  filter(!subid %in% gps$subid) 
```



#### Cellular communication logs 

Cellular communication logs could only be downloaded in person so the first opportunity to download logs was at follow-up 1.    
Subset to subids who completed follow-up 1    

`r nrow(visit_dates %>% filter(!is.na(followup_1)))` participants completed follow-up 1.  

```{r}
fu_1 <- visit_dates %>% 
  filter(!is.na(followup_1))
```



**Voice Logs**

Get subids from IOS and android voice logs
```{r}
voice <- voice_android %>% 
  mutate(subid = as.numeric(subid)) %>% 
  select(subid) %>% 
  full_join(voice_ios %>% mutate(subid = as.numeric(subid)) %>% select(subid), by = "subid")
```

`r nrow(voice %>% count(subid))` subids have voice call data.    

* We have voice logs for 1 subid who never completed their follow-up 1 visit      
According to notes: Subid 237 arrived to Follow-up 1 but asked to be discontinued before data was collected. They needed to leave shortly after their visit time started so unreported contacts locations and ID Battery were NOT collected. Call and SMS logs were collected at FU1 but numbers were not gone over with participant.    



`r nrow(subset(voice, subid %in% fu_1$subid) %>% count(subid))` (`r round(nrow(subset(voice, subid %in% fu_1$subid) %>% count(subid))/(nrow(fu_1 %>% count(subid)))*100, 2)`%) of the subids who completed follow-up 1 (N = 154) have voice log data.     


**SMS Logs**
 
Get subids from IOS and android SMS logs
```{r}
sms <- sms_android %>% 
  mutate(subid = as.numeric(subid)) %>% 
  select(subid) %>% 
  full_join(sms_ios %>% mutate(subid = as.numeric(subid)) %>% select(subid), by = "subid") 
```


`r nrow(sms %>% count(subid))` subids have sms data.    

* We have SMS logs for subid 237 but they never completed their follow-up 1 visit.    


`r nrow(subset(sms, subid %in% fu_1$subid) %>% count(subid))` (`r round(nrow(subset(sms, subid %in% fu_1$subid) %>% count(subid))/(nrow(fu_1 %>% count(subid)))*100, 2)`%) of the subids who completed follow-up 1 (N = 154) have SMS data.     



Missing SMS logs for 1 subid         
According to Notes: Subject's SMS files are empty because the subject deleted all text messages before their study visit; They also did not text much.      
```{r}
fu_1 %>% 
  filter(!subid %in% sms$subid)
```


### Compliance for Active Data Streams

Analysis sample (N = 154) serves as the denominator for all compliance measures below unless otherwise noted.   

#### Audio  

```{r}
audio <- audio %>% 
  filter(subid %in% fu_1$subid)
```

`r nrow(audio %>% count(subid))` (`r round(nrow(audio %>% count(subid))/nrow(fu_1)*100, 2)`%) subids have audio data   

Enrolled subids with no audio data
```{r}
fu_1 %>% 
  filter(!subid %in% as.numeric(audio$subid)) 
```


Get all study days for each subid
```{r}
# function to map over
get_study_days <- function(the_subid, dates) {
  start_study <- dates %>% filter(subid == the_subid) %>% pull(start_study)
  end_study <- dates %>% filter(subid == the_subid) %>% pull(end_study)
  study_days <- tibble(subid = the_subid, study_day = seq(start_study, end_study - days(1), by = "day")) 
  return(study_days)
}

subids <- fu_1$subid
dates <- fu_1 %>% 
  select(subid, start_study, end_study)

study_dates <- subids %>% 
  map_dfr(~get_study_days(.x, dates))
```

Count audios per study day
```{r}
# count audio surveys per day
audio_count <- audio %>%  
  count(subid, date) %>%
  mutate(n = if_else(n > 1, 1, as.numeric(n)))

# left join with study dates
audio_study_dates <- study_dates %>% 
  left_join(audio_count, by = c("subid", "study_day" = "date")) %>% 
  mutate(n = if_else(is.na(n), 0, n)) %>% 
  mutate(n_prompts = 1)
```

calculate mean compliance
```{r}
mean_audio <- audio_study_dates %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(mean = n_total/prompt_total)
```



On average participants (N = 154) completed `r round(mean_audio$mean, 2)` audio checkins each day they were on study. That is their overall compliance for a once daily audio check-in was `r round(mean_audio$mean, 2)*100`%.    

Hist of overall compliance by subid
```{r}
audio_study_dates %>% 
  group_by(subid) %>% 
  summarise(n_total = sum(n),
            n_prompts = sum(n_prompts)) %>% 
  mutate(compliance = n_total/n_prompts) %>% 
  ggplot(aes(x = compliance)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .2, center = .5) +
  scale_x_continuous(breaks = c(0, 0.20, 0.40, 0.60, 0.80, 1.0)) +
  labs(y = "Frequency", x = "Proportion of audio check-in's completed",
       subtitle = "Audio Check-in (N = 154)") +
  geom_vline(aes(xintercept = mean_audio$mean), size = .3) +
  theme_classic()

audio_study_dates %>% 
  group_by(subid) %>% 
  summarise(n_total = sum(n),
            n_prompts = sum(n_prompts)) %>% 
  mutate(compliance = n_total/n_prompts) %>% 
  ggplot(aes(x = compliance)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .1, center = .55) +
  scale_x_continuous(breaks = c(0, 0.10, 0.20, 0.30, 0.40, 0.50, 0.60, 0.70, 0.80, 0.90, 1.0)) +
  labs(y = "Frequency", x = "Proportion of audio check-in's completed",
       subtitle = "Audio Check-in (N = 154)") +
  geom_vline(aes(xintercept = mean_audio$mean), size = .3) +
  theme_classic()


audio_study_dates %>%
  group_by(subid) %>%
  summarise(n_total = sum(n),
            n_prompts = sum(n_prompts)) %>%
  mutate(compliance = n_total/n_prompts) %>%
  ggplot(aes(x = compliance)) +
  geom_histogram(color = "black", fill = "#FFDEDE", binwidth = .15, center = .5) +
  scale_x_continuous(breaks = c(0, 0.15, 0.30, 0.45, 0.60, 0.75, 0.90, 1)) +
  labs(y = "Frequency", x = "Proportion of audio check-in's completed",
       subtitle = "Audio Check-in (N = 154)") +
  geom_vline(aes(xintercept = mean_audio$mean), size = .3) +
  theme_classic()
```



**Compliance over time**

Slice into 7 day bins 
```{r}
audio_study_weeks <- audio_study_dates %>% 
  group_by(subid) %>% 
  slice(1:7) %>% 
  mutate(week = 1) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(8:14) %>% 
    mutate(week = 2)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(15:21) %>% 
    mutate(week = 3)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(22:28) %>% 
    mutate(week = 4)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(29:35) %>% 
    mutate(week = 5)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(36:42) %>% 
    mutate(week = 6)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(43:49) %>% 
    mutate(week = 7)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(50:56) %>% 
    mutate(week = 8)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(57:63) %>% 
    mutate(week = 9)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(64:70) %>% 
    mutate(week = 10)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(71:77) %>% 
    mutate(week = 11)) %>% 
  bind_rows(audio_study_dates %>% 
    group_by(subid) %>% 
    slice(78:84) %>% 
    mutate(week = 12)) %>% 
  ungroup()
```


Get individual compliance scores 
```{r}
audio_week_compliance <- audio_study_weeks %>% 
  group_by(subid, week) %>% 
  summarize(sum_n = sum(n), sum_prompts = sum(n_prompts), .groups = "rowwise") %>% 
  mutate(compliance = sum_n/sum_prompts) %>% 
  ungroup()
```

Summarize total compliance
```{r}
audio_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) 
```

Plot compliance by week
```{r}
audio_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  ggplot(aes(x = week, y = mean_compliance)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  labs(title = "Audio compliance over time",
       caption = "<i>Note:</i>  Average participant compliance (N = 154) for audio surveys each week <br>on study. Dashed line represents overall mean compliance.") +
  theme(legend.title = element_blank(),
        legend.text = element_markdown(),
        plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1.25),
        text = element_text(),
        plot.title = element_markdown(),
        plot.subtitle = element_markdown(size = 12, lineheight = 1.25)) +
  geom_hline(aes(yintercept = mean(mean_compliance)), linetype = "dashed", size = .3)
```

#### EMA

Join morning and evening EMA datasets
```{r}
ema <- ema_m %>% 
  select(subid, start_date) %>% 
  full_join(ema_l %>% select(subid, start_date), by = c("subid", "start_date")) %>% 
  mutate(start_date = date(start_date),
         subid = as.numeric(subid)) %>% 
  filter(subid %in% fu_1$subid)
```

`r nrow(ema %>% count(subid))` (`r round(nrow(ema %>% count(subid))/nrow(fu_1)*100, 2)`%) subids have ema data   



**Days with at least 1 EMA**

Count EMAs per study day
```{r}
# count EMAs per day
ema_1_count <- ema %>%  
  count(subid, start_date) %>%
  mutate(n = if_else(n > 1, 1, as.numeric(n)))

# left join with study dates
ema_1_study_dates <- study_dates %>% 
  left_join(ema_1_count, by = c("subid", "study_day" = "start_date")) %>% 
  mutate(n = if_else(is.na(n), 0, n)) %>% 
  mutate(n_prompts = 1)
```


calculate mean compliance
```{r}
mean_ema_1 <- ema_1_study_dates %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(mean = n_total/prompt_total)
```

mean compliance for one daily survey is `r mean_ema_1$mean`




**Overall proportion of EMAs completed while on study**

Count EMAs per study day
```{r}
# count EMAs per day
ema_count <- ema %>%  
  count(subid, start_date) %>%
  mutate(n = if_else(n > 4, 4, as.numeric(n)))

# left join with study dates
ema_study_dates <- study_dates %>% 
  left_join(ema_count, by = c("subid", "study_day" = "start_date")) %>% 
  mutate(n = if_else(is.na(n), 0, n)) %>% 
  mutate(n_prompts = 4)
```

calculate mean compliance
```{r}
mean_ema_4 <- ema_study_dates %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(mean = n_total/prompt_total)
```

compliance = `r mean_ema_4$mean`   

avg emas = `r mean(ema_study_dates$n)`



**Compliance over time**

Slice into 7 day bins 
```{r}
ema_study_weeks <- ema_study_dates %>% 
  group_by(subid) %>% 
  slice(1:7) %>% 
  mutate(week = 1) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(8:14) %>% 
    mutate(week = 2)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(15:21) %>% 
    mutate(week = 3)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(22:28) %>% 
    mutate(week = 4)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(29:35) %>% 
    mutate(week = 5)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(36:42) %>% 
    mutate(week = 6)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(43:49) %>% 
    mutate(week = 7)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(50:56) %>% 
    mutate(week = 8)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(57:63) %>% 
    mutate(week = 9)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(64:70) %>% 
    mutate(week = 10)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(71:77) %>% 
    mutate(week = 11)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(78:84) %>% 
    mutate(week = 12)) %>% 
  ungroup()
```


Get individual compliance scores - N EMAs/possible EMAs
```{r}
ema_week_compliance <- ema_study_weeks %>% 
  group_by(subid, week) %>% 
  summarize(sum_n = sum(n), sum_prompts = sum(n_prompts), .groups = "rowwise") %>% 
  mutate(compliance = sum_n/sum_prompts) %>% 
  ungroup()
```

Summarize total compliance
```{r}
ema_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) 
```

Plot compliance by week
```{r}
ema_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  ggplot(aes(x = week, y = mean_compliance)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  labs(title = "Compliance over time",
       caption = "<i>Note:</i>  Average participant compliance (N = 154) for EMA each week on study. <br>Dashed line represents overall mean compliance.") +
  theme(legend.title = element_blank(),
        legend.text = element_markdown(),
        plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1.25),
        text = element_text(),
        plot.title = element_markdown(),
        plot.subtitle = element_markdown(size = 12, lineheight = 1.25)) +
  geom_hline(aes(yintercept = mean(mean_compliance)), linetype = "dashed", size = .3)
```



**Compliance - at least 1 EMA per day**

Get individual compliance scores 
```{r}
ema_1_week_compliance <- ema_study_weeks %>%
  mutate(n = if_else(n > 1, 1, n),
         n_prompts = 1) %>% 
  group_by(subid, week) %>% 
  summarize(sum_n = sum(n), sum_prompts = sum(n_prompts), .groups = "rowwise") %>% 
  mutate(compliance = sum_n/sum_prompts) %>% 
  ungroup()
```

Summarize total compliance
```{r}
ema_1_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) 
```


```{r}
ema_1_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  ggplot(aes(x = week, y = mean_compliance)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  labs(title = "Compliance over time",
       caption = "<i>Note:</i>  Average participant compliance (N = 154) for completing at least 1 EMA <br>each week on study. Dashed line represents overall mean compliance.") +
  theme(legend.title = element_blank(),
        legend.text = element_markdown(),
        plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1.25),
        text = element_text(),
        plot.title = element_markdown(),
        plot.subtitle = element_markdown(size = 12, lineheight = 1.25)) +
  geom_hline(aes(yintercept = mean(mean_compliance)), linetype = "dashed", size = .3)
```


#### Combined plot
```{r}
week_compliance_all <- audio_week_compliance %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  mutate(signal = "Audio Check-in") %>% 
  bind_rows(ema_week_compliance %>% 
              group_by(week) %>% 
              summarize(mean_compliance = mean(compliance)) %>% 
              mutate(signal = "EMA (4x Daily)")) %>% 
  bind_rows(ema_1_week_compliance %>% 
              group_by(week) %>% 
              summarize(mean_compliance = mean(compliance)) %>% 
              mutate(signal = "EMA (1x Daily)"))


week_compliance_all %>% 
  mutate(signal = factor(signal, levels = c("EMA (1x Daily)", "EMA (4x Daily)", "Audio Check-in"))) %>% 
  group_by(week, signal) %>% 
  ggplot(aes(x = week, y = mean_compliance, group = signal, color = signal)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_color_manual(values = c("dodgerblue4", "skyblue3", "thistle3")) +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  geom_hline(aes(yintercept = mean_compliance), week_compliance_all %>% 
               group_by(signal) %>% 
               summarize(mean_compliance = mean(mean_compliance)),
             linetype = "dashed", size = .3) +
    labs(title = "Compliance over time",
       caption = "<i>Note:</i>  Average participant compliance (N = 154) for audio check-in, EMA (1x daily), and EMA (4x daily) <br>by week on study. Dashed line represents overall mean compliance for each signal.") +
  theme(legend.title = element_blank(),
        legend.text = element_markdown(),
        plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1.25),
        text = element_text(),
        plot.title = element_markdown(),
        plot.subtitle = element_markdown(size = 12, lineheight = 1.25)) 
```

