---
title: "Additional Analyses Following Burden Meeting"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---



### Setup

Paths
```{r}
path_data <- "P:/studydata/risk/data_processed/burden"
path_shared <- "P:/studydata/risk/data_processed/shared"
```

Packages and Sources
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(ggtext)
library(cowplot)
library(patchwork)
library(rstatix)
library(janitor)
library(here)
library(vroom)

theme_set(theme_classic())
options(knitr.kable.NA = '')
```


### Read in data
```{r}
# self-report acceptability data
# data <- vroom(here(path_data, "acceptability.csv"), col_types = vroom::cols())

# disposition status for burden project
disp <- vroom(here(path_data, "disposition.csv"), col_types = vroom::cols())

# Monthly survey data 
fu_12 <- vroom(here(path_shared, "followup_12.csv"), col_types = vroom::cols())
screen <- vroom(here(path_shared, "screen.csv"), col_types = vroom::cols())
```

Get subids for analysis sample (N = 154)
```{r}
ana_subids <- disp %>% 
  filter(last_visit != "screen" & last_visit != "intake")
```


### Past Month Drug Use

Any past month drug use reported (at fu 1 or 2)
```{r}
assist_fu_1 <- fu_12 %>% 
  filter(subid %in% ana_subids$subid) %>% 
  group_by(subid) %>% 
  slice(1) %>% 
  select(subid,
         tobacco_fu1 = assist_2_1,
         cannabis_fu1 = assist_2_2,
         cocaine_fu1 = assist_2_3,
         amphetamine_fu1 = assist_2_4,
         inhalants_fu1 = assist_2_5,
         sedatives_fu1 = assist_2_6,
         hallucinogens_fu1 = assist_2_7,
         opioids_fu1 = assist_2_8,
         other_fu1 = assist_2_9) %>% 
  ungroup()

assist_fu_2 <- fu_12 %>% 
  filter(subid %in% subset(ana_subids, last_visit != "followup_1")$subid) %>% 
  group_by(subid) %>%
  arrange(desc(start_date)) %>% 
  slice(1) %>% 
  select(subid,
         tobacco_fu2 = assist_2_1,
         cannabis_fu2 = assist_2_2,
         cocaine_fu2 = assist_2_3,
         amphetamine_fu2 = assist_2_4,
         inhalants_fu2 = assist_2_5,
         sedatives_fu2 = assist_2_6,
         hallucinogens_fu2 = assist_2_7,
         opioids_fu2 = assist_2_8,
         other_fu2 = assist_2_9) %>% 
  ungroup()


assist <- assist_fu_1 %>% 
  left_join(assist_fu_2, by = "subid") %>%
  mutate(across(tobacco_fu1:other_fu2, ~if_else(.x == "Never" | is.na(.x), 0, 1)),
         tobacco = if_else(tobacco_fu1 == 1 | tobacco_fu2 == 1, "yes", "no"),
         cannabis = if_else(cannabis_fu1 == 1 | cannabis_fu2 == 1, "yes", "no"),
         cocaine = if_else(cocaine_fu1 == 1 | cocaine_fu2 == 1, "yes", "no"),
         amphetamine = if_else(amphetamine_fu1 == 1 | amphetamine_fu2 == 1, "yes", "no"),
         inhalants = if_else(inhalants_fu1 == 1 | inhalants_fu2 == 1, "yes", "no"),
         sedatives = if_else(sedatives_fu1 == 1 | sedatives_fu2 == 1, "yes", "no"),
         hallucinogens = if_else(hallucinogens_fu1 == 1 | hallucinogens_fu2 == 1, "yes", "no"),
         opioids = if_else(opioids_fu1 == 1 | opioids_fu2 == 1, "yes", "no"),
         other = if_else(other_fu1 == 1 | other_fu2 == 1, "yes", "no")) %>% 
  select(subid, tobacco:other)
```


Number of drugs endorsed (including tobacco)
69.5% of participants reported past month drug use (at followup 1 or 2)   
```{r}
assist %>% 
  mutate(across(tobacco:other, ~if_else(.x == "no" | is.na(.x), 0, 1))) %>%
  rowwise() %>%
  mutate(total = sum(across(tobacco:other))) %>%
  tabyl(total)
```


Number of drugs endorsed (not including tobacco)
49% of participants reported past month illicit drug use (at followup 1 or 2)   
```{r}
assist %>% 
  mutate(across(cannabis:other, ~if_else(.x == "no" | is.na(.x), 0, 1))) %>%
  rowwise() %>%
  mutate(total = sum(across(cannabis:other))) %>%
  tabyl(total)
```


### Personal Income

Question on screener: Please indicate your approximate total personal gross income (prior to deducting taxes) in dollars per year. Do not include a dollar sign ($).    


Mean income = $34,233    
11% report income <= $1000
25% below federal poverty line ($12880)

```{r}
screen %>% 
  filter(subid %in% ana_subids$subid) %>% 
  ggplot(aes(x = dem_7)) +
  geom_histogram(bins = 40, color = "black", fill = "light grey") +
  geom_vline(aes(xintercept = mean), screen %>% 
               filter(subid %in% ana_subids$subid) %>% 
               summarize(mean = mean(dem_7)), color = "dark red")

screen %>% 
  filter(subid %in% ana_subids$subid) %>% 
  tabyl(dem_7)

screen %>% 
  filter(subid %in% ana_subids$subid) %>% 
  filter(dem_7 <= 12880)
```

