---
title: "Demographic Characteristics"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---


<br>

Purpose: This script creates the participant descriptive tables for the manuscript *Acceptability of Personal Sensing among People with Alcohol Use Disorder*.    


### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths
```{r}
path_shared <- "P:/studydata/risk/data_processed/shared"
path_burden <- "P:/studydata/risk/data_processed/burden"
```

Packages
```{r message = FALSE}
library(tidyverse)
library(kableExtra)
library(janitor)

options(knitr.kable.NA = '')
```



### Read in Data

```{r}
screen <- read_csv(file.path(path_shared, "screen.csv"), col_types = cols()) 
visit_dates <- read_csv(file.path(path_shared,"visit_dates.csv"), col_types = cols())

# include only participants used in analyses (n = 154) - use visit dates to determine
sample_fu1 <- visit_dates %>% 
  filter(!(is.na(followup_1)))
screen <- screen %>% 
  filter(subid %in% sample_fu1$subid)

# read in notes on incomplete participants
notes_incomplete <- read_csv(file.path(path_burden, "notes_discontinue.csv"), col_types = cols()) %>% 
  filter(screen != "cancelled" & screen != "no show")
```

<br>

### Create Table 1

Table 1 contains the demographics of our final analysis sample.   

```{r message = FALSE}
# Join demographics as tibble
dem <- screen %>% 
  summarise(mean = as.character(round(mean(dem_1, na.rm = TRUE), 1)),
            SD = as.character(round(sd(dem_1, na.rm = TRUE), 1))) %>% 
  mutate(var = "Age",
         n = as.numeric(""),
         perc = as.numeric("")) %>% 
  select(var, n, perc, everything()) %>% 
  full_join(screen %>% 
  select(var = dem_2) %>% 
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  select(var = dem_3) %>% 
  mutate(var = fct_relevel(factor(var, 
                         c("American Indian/Alaska Native", "Asian", "Black/African American",
                           "White/Caucasian", "Other/Multiracial")))) %>%
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  select(var = dem_4) %>% 
  mutate(var = case_when(var == "No, I am not of Hispanic, Latino, or Spanish origin" ~ "No",
                         TRUE ~ "Yes"),
         var = fct_relevel(factor(var, c("Yes", "No")))) %>% 
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  select(var = dem_5) %>% 
  mutate(var = fct_relevel(factor(var, 
                         c("Less than high school or GED degree", "High school or GED", 
                           "Some college", "2-Year degree", "College degree", "Advanced degree")))) %>%
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  select(var = dem_6, dem_6_1) %>% 
  mutate(var = case_when(dem_6_1 == "Full-time" ~ "Employed full-time",
                         dem_6_1 == "Part-time" ~ "Employed part-time",
                         TRUE ~ var)) %>% 
  mutate(var = fct_relevel(factor(var, 
                         c("Employed full-time", "Employed part-time", "Full-time student",
                           "Homemaker", "Disabled", "Retired", "Unemployed", 
                           "Temporarily laid off, sick leave, or maternity leave",
                           "Other, not otherwise specified")))) %>%
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  summarise(mean = as.character(round(mean(dem_7, na.rm = TRUE), 0)),
            SD = as.character(round(sd(dem_7, na.rm = TRUE), 0))) %>% 
  mutate(var = "Income",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  select(var = dem_8) %>% 
  mutate(var = case_when(var == "Never Married" ~ "Never married",
                         TRUE ~ var)) %>% 
  mutate(var = fct_relevel(factor(var, 
                         c("Never married", "Married", "Divorced", "Separated",
                           "Widowed")))) %>%
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100))

# display and format table
dem %>% 
  kbl(col.names = c("", "<i>n</i>", "%", "<i>M</i>", "<i>SD</i>"),
      digits = 1,
      align = c("l", "c", "c", "c", "c"),
      caption = "<b>Table 1<br><br>Demographics</b>",
      table.attr = "style='width:60%;'",
      escape = FALSE) %>% 
  row_spec(row = 0, align = "c") %>% 
  kable_classic(html_font = "Times New Roman", position = "left") %>% 
  pack_rows("Sex", 2, 3, bold = FALSE) %>% 
  pack_rows("Race", 4, 8, bold = FALSE) %>% 
  pack_rows("Hispanic, Latino, or Spanish Origin", 9, 10, bold = FALSE) %>% 
  pack_rows("Education", 11, 16, bold = FALSE) %>% 
  pack_rows("Employment", 17, 25, bold = FALSE) %>% 
  pack_rows("Marital Status", 27, 31, bold = FALSE) %>% 
  footnote("N = 154")
```

-----

<br>

### Create Table 2

Table 2 contains descriptives of participants' alcohol use history and alcohol use disorder severity.  

```{r message = FALSE}
# combine AUH variables as tibble
auh <- screen %>% 
  summarise(mean = mean(auh_1, na.rm = TRUE),
            SD = sd(auh_1, na.rm = TRUE)) %>% 
  mutate(var = "Age of first drink",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything()) %>% 
  full_join(screen %>% 
  summarise(mean = mean(auh_2, na.rm = TRUE),
            SD = sd(auh_2, na.rm = TRUE)) %>% 
  mutate(var = "Age of regular drinking",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  summarise(mean = mean(auh_3, na.rm = TRUE),
            SD = sd(auh_3, na.rm = TRUE)) %>% 
  mutate(var = "Age at which drinking became problematic",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  summarise(mean = mean(auh_4, na.rm = TRUE),
            SD = sd(auh_4, na.rm = TRUE)) %>% 
  mutate(var = "Age of first quit attempt",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  summarise(mean = mean(auh_5, na.rm = TRUE),
            SD = sd(auh_5, na.rm = TRUE)) %>% 
  mutate(var = "Number of Quit Attempts",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  select(var = auh_6_1) %>%
  mutate(var = case_when(var == "Long-Term Residential Treatment (more than 6 months)" ~ "Long-term residential (6+ mos.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_2) %>%
  mutate(var = case_when(var == "Short-Term Residential Treatment (less than 6 months)" ~ "Short-term residential (< 6 mos.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_3) %>%
  mutate(var = case_when(var == "Outpatient Treatment" ~ "Outpatient",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_4) %>%
  mutate(var = case_when(var == "Individual Counseling" ~ "Individual counseling",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_5) %>%
  mutate(var = case_when(var == "Group Counseling" ~ "Group counseling",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_6) %>%
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_6_7) %>%
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = auh_7) %>% 
  mutate(var = fct_relevel(factor(var, c("Yes", "No")))) %>%
  group_by(var) %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / sum(n)) * 100)) %>% 
  full_join(screen %>% 
  mutate(across(dsm5_1:dsm5_11, ~ recode(., "No" = 0, "Yes" = 1))) %>% 
  rowwise() %>% 
  # calculate dsm5 score by adding up dsm5_1 through dsm5_11
  mutate(dsm5_total = sum(c(dsm5_1, dsm5_2, dsm5_3, dsm5_4, dsm5_5, dsm5_6, dsm5_7, 
                            dsm5_8, dsm5_9, dsm5_10, dsm5_11))) %>% 
  ungroup() %>% 
  summarise(mean = mean(dsm5_total),
            SD = sd(dsm5_total)) %>% 
  mutate(var = "AUD DSM-5 Symptom Count*",
        n = as.numeric(""),
        perc = as.numeric("")) %>% 
  select(var, n, perc, everything())) %>% 
  full_join(screen %>% 
  select(var = assist_1_1) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Tobacco products (cigarettes, chewing tobacco, cigars, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_2) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Cannabis (marijuana, pot, grass, hash, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_3) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Cocaine (coke, crack, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_4) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Amphetamine type stimulants (speed, diet pills, ecstasy, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_5) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Inhalants (nitrous, glue, petrol, paint thinner, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_6) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Sedatives or sleeping pills (Valium, Serepax, Rohypnol, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_7) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Hallucinogens (LSD, acid, mushrooms, PCP, Special K, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) %>% 
  full_join(screen %>% 
  select(var = assist_1_8) %>%
  filter(var == "Yes") %>% 
  mutate(var = case_when(var == "Yes" ~ "Opioids (heroin, morphine, methadone, codeine, etc.)",
                         TRUE ~ var)) %>% 
  group_by(var) %>% 
  drop_na() %>% 
  summarise(n = n()) %>% 
  mutate(perc = (n / 154) * 100)) 

# display and format table
auh %>%
  kbl(col.names = c("", "<i>n</i>", "%", "<i>M</i>", "<i>SD</i>"),
      digits = 1,
      align = c("l", "c", "c", "c", "c"),
      caption = "<b>Table 2<br><br>Alcohol Related Information</b>",
      table.attr = "style='width:70%;'",
      escape = FALSE) %>% 
  row_spec(row = 0, align = "c") %>% 
  kable_classic(html_font = "Times New Roman", position = "left") %>% 
  pack_rows("AUD Milestones", 1, 4, bold = FALSE) %>% 
  pack_rows("Types of Treatment (Can choose more than 1)", 6, 12, bold = FALSE) %>% 
  pack_rows("Received Medication for AUD", 13, 14, bold = FALSE) %>% 
  pack_rows("Lifetime Drug Use", 16, 23, bold = FALSE) %>% 
  footnote("N = 154")
```


-----

<br>

### Create Table 3

Table 3 provides a breakdown of why participants discontinued prior to the first month followup   

```{r}
notes_incomplete <- notes_incomplete %>%
  filter(screen != "no consent") %>%
  mutate(characterize = case_when(characterize == "no_transportation" ~ "No longer has transportation",
                                  characterize == "not_sober" ~ "No longer sober or no longer wishes to abstain from alcohol",
                                  characterize == "rescheduled" ~ "Rescheduled multiple times before cancelling/no showing",
                                  characterize == "treatment" ~ "No longer sober or no longer wishes to abstain from alcohol",
                                  characterize == "compliance" ~ "Noncompliance with providing data",
                                  characterize == "lapse" ~ "No longer sober or no longer wishes to abstain from alcohol",
                                  characterize == "cell_service" ~ "Cell service shut off",
                                  characterize == "move" ~ "Moved out of state",
                                  characterize == "study_demands" ~ "Cited study demands as too burdensome",
                                  characterize == "Unreachable" ~ "Unknown",
                                  characterize == "Unspecified concerns from staff" ~ "Staff concerns",
                                  characterize == "inappropriate behavior" ~ "Staff concerns",
                                  characterize == "mental health" ~ "Mental health concerns",
                                  characterize == "no aud" ~ "Does not meet criteria for moderate or severe AUD",
                                  characterize == "phone" ~ "Ineligible phone",
                                  is.na(characterize) ~ "Unknown",
                                  TRUE ~ characterize))
notes_incomplete %>% 
  filter(screen != "ineligible") %>% 
  filter(intake != "complete" | is.na(intake)) %>% 
  filter(intake != "ineligible" | is.na(intake)) %>% 
  group_by(characterize) %>% 
  summarise(n = n()) %>% 
  mutate(percent = n/sum(n)) %>% 
  adorn_totals("row") %>% 
  kbl(col.names = c("", "<i>n</i>", "%"), 
      caption = "<b>Table 3<br><br>A</b><br><i>Characterization of eligible and consented participants who discontinued prior to completing enrollment</i>",
      digits = 2, table.attr = "style='width:60%;'", escape = FALSE) %>% 
  kable_classic(position = "left", html_font = "Arial") %>% 
  footnote("These participants are noted as 'Not Enrolled' in Figure 1.")
notes_incomplete %>% 
  filter(screen != "ineligible") %>% 
  filter(completed_1month == "no") %>% 
  filter(intake == "complete") %>% 
  group_by(characterize) %>% 
  summarise(n = n()) %>% 
  mutate(percent = n/sum(n)) %>% 
  adorn_totals("row") %>% 
  kbl(col.names = c("", "<i>n</i>", "%"), 
      caption = "<b>B</b><br><i>Characterization of enrolled participants who discontinued prior to first month follow-up</i>",
      digits = 2, table.attr = "style='width:60%;'", escape = FALSE) %>% 
  kable_classic(position = "left", html_font = "Arial") %>% 
  footnote("These participants are noted as 'Discontinued' in Figure 1.")
notes_incomplete %>% 
  filter(screen != "ineligible") %>% 
  filter(completed_1month == "yes") %>% 
  group_by(characterize) %>% 
  summarise(n = n()) %>% 
  mutate(percent = n/sum(n)) %>% 
  adorn_totals("row") %>% 
  kbl(col.names = c("", "<i>n</i>", "%"), 
      caption = "<b>C</b><br><i>Characterization of enrolled participants who discontinued after the first month follow-up</i>",
      digits = 2, table.attr = "style='width:60%;'", escape = FALSE) %>% 
  kable_classic(position = "left", html_font = "Arial") %>% 
  footnote("These participants are noted as 'Participated through 1st month follow-up' or 'Participated through 2nd month follow-up' in Figure 1.")
```



