---
title: "Disposition Flowchart Figure"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 3
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---

<br>
 
Purpose: This script examines disposition status throughout the study by creating a flowchart from participant data.  


### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths
```{r}
path_data <- "P:/studydata/risk/data_processed/burden"
```

Packages
```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(psych)
library(kableExtra)
library(DiagrammeR) # for flowchart
```



### Read in Data

```{r}
disposition <- read_csv(file.path(path_data, "disposition.csv"), col_types = cols())
```

<br>

### Disposition Status  

Last completed visits
```{r}
tabyl(disposition$last_visit)
```

The following numbers are confirmed:   
`r nrow(subset(disposition, last_visit == "followup_3")) + nrow(subset(disposition, last_visit == "followup_2")) + nrow(subset(disposition, last_visit == "followup_1")) + nrow(subset(disposition, last_visit == "intake")) ` participants completed the intake (i.e., enrolled).   
`r nrow(subset(disposition, last_visit == "followup_3")) + nrow(subset(disposition, last_visit == "followup_2")) + nrow(subset(disposition, last_visit == "followup_1"))` participants completed followup 1   
`r nrow(subset(disposition, last_visit == "followup_3")) + nrow(subset(disposition, last_visit == "followup_2"))` participants made it to followup 2  
`r nrow(subset(disposition, last_visit == "followup_3"))` participants completed followup 3    

<br>

Discontinued participants
```{r}
disposition %>% 
  filter(last_visit == "screen" | is.na(last_visit)) %>% 
  tabyl(reason_no_intake)
```

<br>


### Calculate Flowchart Branches

```{r}
disposition_summary <- disposition %>% 
  group_by(last_visit, reason_no_intake) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  mutate(group = case_when(reason_no_intake == "ineligible" ~ "ineligible",
                           reason_no_intake == "no_consent" ~ "no_consent",
                           reason_no_intake == "not_interested" ~ "discontinued",
                           TRUE ~ last_visit)) %>% 
  group_by(group) %>% 
  summarise(n = sum(n))

disposition_summary
```

Remove ineligible participants since not including in flow chart
```{r}
disposition <- disposition %>% 
  filter(reason_no_intake != "ineligible" | is.na(reason_no_intake))
```

One participant discontinued same day as starting study - moving participant to not enrolled since no data collected
```{r}
not_enrolled <- disposition_summary %>% filter(group == "discontinued") %>% select(n) %>% unlist(use.names = FALSE) + 1
```

create separate branch variables
```{r}
starting_sample <- disposition %>% nrow()
no_consent <- disposition_summary %>% filter(group == "no_consent") %>% select(n) %>% unlist(use.names = FALSE)
consented <- starting_sample - no_consent 
enrolled <- consented - not_enrolled
followup_3 <- disposition_summary %>% filter(group == "followup_3") %>% select(n) %>% unlist(use.names = FALSE)
followup_2 <- disposition_summary %>% filter(group == "followup_2") %>% select(n) %>% unlist(use.names = FALSE) + followup_3
followup_1 <- disposition_summary %>% filter(group == "followup_1") %>% select(n) %>% unlist(use.names = FALSE) + followup_2
discontinued <- enrolled - followup_1
```

<br>

### Create Flowchart

Note that the flowchart in the manuscript (Figure 1) was created in R and then edited in PowerPoint. In PowerPoint a piechart was created and overlayed over the flowchart where the dashed circle is present. Additional notes were also added to annote the figure with information about reasons for participant discontinuation.   

The code below creates the flowchart used as the base for Figure 1. Code is also presented to create a Pie Chart in R that depicts participant disposition status at each one month follow-up.     


Flowchart 
```{r}
DiagrammeR::grViz("
  digraph {
  
  node [fontname = 'Arial', shape = rectangle, fixedsize = true, width = 1.7, height = .6]
  a [label = '@@1']
  b1 [label = '@@2']
  b2 [label = '@@3', color = crimson]
  c1 [label = '@@4']
  c2 [label = '@@5', color = crimson]
  
  node [fontname = 'Arial', shape = circle, style = dotted]
  d1 [label = '@@6']

  node [fontname = 'Arial', shape = rectangle, fixedsize = true, width = 1.7, height = .6, style = solid]
  d2 [label = '@@7', color = crimson]
  
  a -> b1
  a -> b2
  b1 -> c1
  b1 -> c2
  c1 -> d1
  c1 -> d2
  }
  
  [1]: str_c('Eligible Sample\\n', 'N = ', starting_sample)
  [2]: str_c('Consented\\n', 'n = ', consented) 
  [3]: str_c('Not Consented\\n', 'n = ', no_consent)
  [4]: str_c('Enrolled\\n', 'n = ', enrolled)
  [5]: str_c('Not Enrolled\\n', 'n = ', not_enrolled)
  [6]: str_c('n = 154')
  [7]: str_c('Discontinued\\n', 'n = ', discontinued)
  ", width = "600px") 
```

Piechart
```{r}
month_3 <- followup_3
month_2 <- followup_2 - followup_3
month_1 <- followup_1 - followup_2

lbls <- c("3 mos data", "2 mos data", "1 mo data")

slices <- c(month_3, month_2, month_1)
pct <- round(slices/sum(slices)*100)
n <- slices
lbls <- str_c(lbls, '\n', pct, '% (n = ', n, ')')
pie(slices, lbls, col = c("lavender", "lightgrey", "lightblue"),
   main="Participants with at least 1 month of data (N = 154)") 
```

<br>
