---
title: "EMA Adherence"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

### Notes


### Setup

Paths 
```{r}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_ema <- "P:/studydata/risk/data_processed/ema"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_ema <- "/Volumes/private/studydata/risk/data_processed/ema"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"},
        
        # Linux paths
        Linux = {
          path_ema <- "~/mnt/private/studydata/risk/data_processed/ema"
          path_shared <- "~/mnt/private/studydata/risk/data_processed/shared"}
        )
```


Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
```


### Read in Data

```{r}
disposition <- read_csv(file.path(path_ema, "disposition.csv"), col_types = cols()) %>% 
  filter(analysis == "yes")
ema_m <- read_csv(file.path(path_shared, "ema_morning.csv"), col_types = cols()) %>% 
  mutate(read_csv = with_tz(start_date, tzone = "America/Chicago"),
         subid = as.numeric(subid))
ema_l <- read_csv(file.path(path_shared, "ema_later.csv"), col_types = cols()) %>% 
  mutate(start_date = with_tz(start_date, tzone = "America/Chicago"),
         subid = as.numeric(subid))
```

Join morning and evening EMA datasets and filter down to analysis sample (n = 151)
```{r}
ema <- ema_m %>% 
  select(subid, start_date) %>% 
  full_join(ema_l %>% select(subid, start_date), by = c("subid", "start_date")) %>% 
  mutate(start_date = date(start_date),
         subid = as.numeric(subid)) %>% 
  filter(subid %in% disposition$subid)
```

`r nrow(ema %>% count(subid))` (`r round(nrow(ema %>% count(subid))/nrow(disposition)*100, 2)`%) subids have ema data   


Get all study days for each subid
```{r}
# function to map over
get_study_days <- function(the_subid, dates) {
  start_study <- dates %>% filter(subid == the_subid) %>% pull(start_study)
  end_study <- dates %>% filter(subid == the_subid) %>% pull(end_study)
  study_days <- tibble(subid = the_subid, study_day = seq(start_study, end_study - days(1), by = "day")) 
  return(study_days)
}

study_dates <- disposition$subid %>% 
  map_dfr(~get_study_days(.x, disposition %>% 
                            select(subid, start_study, end_study)))
```

### Overall compliance (4x daily)

Count EMAs per study day
```{r}
# count EMAs per day
ema_count_4x <- ema %>%  
  count(subid, start_date) %>%
  mutate(n = if_else(n > 4, 4, as.numeric(n)))

# left join with study dates
ema_study_dates <- study_dates %>% 
  left_join(ema_count_4x, by = c("subid", "study_day" = "start_date")) %>% 
  mutate(n = if_else(is.na(n), 0, n)) %>% 
  mutate(n_prompts = 4)
```

calculate unweighted mean compliance
```{r}
mean_ema_4x <- ema_study_dates %>% 
  group_by(subid) %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(compliance = n_total/prompt_total,
         mean_n_emas = n_total/(prompt_total/4)) %>% 
  ungroup() %>% 
  summarize(compliance = mean(compliance),
         mean_emas = mean(mean_n_emas),
         sd_emas = sd(mean_n_emas))

mean_ema_4x

```

compliance = `r mean_ema_4x$compliance`   

avg emas = `r mean_ema_4x$mean_n_emas`  



### 4x Daily Compliance over time

Slice into 7 day bins 
```{r}
ema_study_weeks <- ema_study_dates %>% 
  group_by(subid) %>% 
  slice(1:7) %>% 
  mutate(week = 1) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(8:14) %>% 
    mutate(week = 2)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(15:21) %>% 
    mutate(week = 3)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(22:28) %>% 
    mutate(week = 4)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(29:35) %>% 
    mutate(week = 5)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(36:42) %>% 
    mutate(week = 6)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(43:49) %>% 
    mutate(week = 7)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(50:56) %>% 
    mutate(week = 8)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(57:63) %>% 
    mutate(week = 9)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(64:70) %>% 
    mutate(week = 10)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(71:77) %>% 
    mutate(week = 11)) %>% 
  bind_rows(ema_study_dates %>% 
    group_by(subid) %>% 
    slice(78:84) %>% 
    mutate(week = 12)) %>% 
  ungroup()
```


Get individual compliance scores - N EMAs/possible EMAs
```{r}
ema_week_compliance_4x <- ema_study_weeks %>% 
  group_by(subid, week) %>% 
  summarize(sum_n = sum(n), sum_prompts = sum(n_prompts), .groups = "rowwise") %>% 
  mutate(compliance = sum_n/sum_prompts) %>% 
  ungroup()
```

Summarize total compliance
```{r}
ema_week_compliance_4x %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) 
```

Plot compliance by week
```{r}
ema_week_compliance_4x %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  ggplot(aes(x = week, y = mean_compliance)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  labs(title = "Compliance over time (4x Daily)") +
  theme(legend.title = element_blank()) +
  geom_hline(aes(yintercept = mean(mean_compliance)), linetype = "dashed", linewidth = .3)
```

### Days with at least 1 EMA

Count EMAs per study day
```{r}
# count EMAs per day
ema_count_1x <- ema %>%  
  count(subid, start_date) %>%
  mutate(n = if_else(n > 1, 1, as.numeric(n)))

# left join with study dates
ema_study_dates_1x <- study_dates %>% 
  left_join(ema_count_1x, by = c("subid", "study_day" = "start_date")) %>% 
  mutate(n = if_else(is.na(n), 0, n)) %>% 
  mutate(n_prompts = 1)
```


calculate unweighted mean compliance
```{r}
mean_ema_1x <- ema_study_dates_1x %>% 
  group_by(subid) %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(mean_1ema = n_total/prompt_total) %>% 
  ungroup %>% 
  summarize(mean = mean(mean_1ema),
            sd = sd(mean_1ema))

mean_ema_1x
```

mean compliance for one daily survey is `r mean_ema_1x$mean`


```{r}
ema_perfect_compliance_1x <- ema_study_dates_1x %>% 
  group_by(subid) %>% 
  summarize(n_total = sum(n), prompt_total = sum(n_prompts)) %>% 
  mutate(mean = n_total/prompt_total) %>% 
  filter(mean == 1)
```

`r nrow(ema_perfect_compliance_1x)` participants (`r nrow(ema_perfect_compliance_1x)/nrow(disposition)`%) completed an EMA every day on study.


### 1x Daily Compliance over time   

Get individual compliance scores 
```{r}
ema_week_compliance_1x <- ema_study_weeks %>%
  mutate(n = if_else(n > 1, 1, n),
         n_prompts = 1) %>% 
  group_by(subid, week) %>% 
  summarize(sum_n = sum(n), sum_prompts = sum(n_prompts), .groups = "rowwise") %>% 
  mutate(compliance = sum_n/sum_prompts) %>% 
  ungroup()
```

Summarize total compliance
```{r}
ema_week_compliance_1x %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) 
```


```{r}
ema_week_compliance_1x %>% 
  group_by(week) %>% 
  summarize(mean_compliance = mean(compliance)) %>% 
  ggplot(aes(x = week, y = mean_compliance)) +
  geom_point() +
  geom_line() +
  theme_classic() +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  labs(title = "Compliance over time (1x Daily)") +
  theme(legend.title = element_blank()) +
  geom_hline(aes(yintercept = mean(mean_compliance)), linetype = "dashed", linewidth = .3)
```


### Combined plot
```{r}
week_compliance_all <- ema_week_compliance_4x %>% 
              group_by(week) %>% 
              summarize(mean_compliance = mean(compliance),
                        n = n(),
                        sd = sd(compliance)) %>% 
              mutate(se = sd/sqrt(n),
                     signal = "EMA (4x Daily)") %>% 
  bind_rows(ema_week_compliance_1x %>% 
              group_by(week) %>% 
              summarize(mean_compliance = mean(compliance),
                        n = n(),
                        sd = sd(compliance)) %>% 
              mutate(se = sd/sqrt(n),
                     signal = "EMA (1x Daily)"))


week_compliance_all %>% 
  mutate(signal = factor(signal, levels = c("EMA (1x Daily)", "EMA (4x Daily)"))) %>% 
  group_by(week, signal) %>% 
  ggplot(aes(x = week, y = mean_compliance, group = signal, shape = signal)) +
  geom_point(size = 2) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_compliance - se, ymax = mean_compliance + se), 
                width = .3, linewidth = .3) +
  theme_classic() +
  scale_shape_manual(values = c(19, 1, 17)) +
  scale_x_continuous(name = "Week", 
                     breaks = seq(1, 12, 1)) +
  scale_y_continuous(name = "Compliance", 
                     breaks = seq(0, 1, .1), 
                     limits = c(0, 1)) +
  geom_hline(aes(yintercept = mean_compliance), week_compliance_all %>% 
               group_by(signal) %>% 
               summarize(mean_compliance = mean(mean_compliance)),
             linetype = "dashed", linewidth = .3) +
    labs(title = "Compliance over time") +
  theme(legend.title = element_blank(),
        legend.position = "bottom")
```

