---
title: "Clean and process location data from interviews"
author: "Hannah Moshontz & John Curtin"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
  toc: true 
  toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Code status

Under construction


### Notes

Purpose: This file summarizes the location labels supplied by participants for the Liu et al. GPS project. In that project, place labels (supplied by participants) are predicted by geospatial and temporal features of people's GPS data in the risk project. In this markdown, I aim to:
1. Recommend what data to exclude on the basis of: multiple homes, multiple workplaces.
2. Understand meaningful, risk-related clusters of labels. We want these labels to be useful for inclusion in models like the kind we are creating for the primary aims of the risk and risk2 projects.
3. Identify any "other" labels that fit existing factor levels. The goal is for these labels to be as accurate as possible, since they serve as ground truth.

Inputs:  Opens data files in path_raw

* locations.csv

### Setup

Paths 
```{r}
path_processed <- "P:/studydata/risk/data_processed" 
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(purrr)
library(kableExtra)
library(geosphere)
```

### Import locations files

```{r}
locations <- read_csv(file.path(path_processed, "locations.csv")) %>% 
  mutate(across(where(is_character), str_to_lower),
         across(
           c("type", 
             "drank",
             "alcohol",
             "emotion",
             "risk",
             "avoid",
             "vacation"),
           as_factor),
         date_of_observation = as_datetime(utc, tz = "America/Chicago")) %>% 
  select(-utc) %>% 
  glimpse()
```


### EDA

#### 1. Recommend what data to exclude on the basis of: multiple homes, multiple workplaces.

##### Multiple homes

```{r}
locations %>% 
  filter(type == "home") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  kable(caption = "Multiple homes", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Investigating when homes were added and how far away they are (as they may be the same place, but different lat and long).

```{r}
subs_with_mult_homes <- locations %>% 
  filter(type == "home") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  pull(subid)

locations %>% 
  filter(type == "home") %>% 
  filter(subid %in% subs_with_mult_homes) %>% 
  group_by(subid) %>% 
  mutate( #adding readable month
    month_of_obs = month(date_of_observation, label = TRUE),
    next_lat = lead(lat),
    next_long = lead(long)) %>% 
  arrange(month_of_obs) %>% 
  rowwise() %>% 
  mutate(
    miles_to_next_home = distm(c(long, lat), c(next_long, next_lat))*0.000621371) %>% 
  group_by(subid, type, month_of_obs) %>% 
  summarize(
    n = n(),
    miles_to_next_home = first(miles_to_next_home)) %>% 
  ungroup() %>% 
  kable(caption = "Multiple homes", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Some of these places were added later, and some appear to be the same place with different lat/long.

##### Multiple workplaces
```{r}
subs_with_mult_works <- locations %>% 
  filter(type == "work") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  pull(subid)

locations %>% 
  filter(type == "work") %>% 
  filter(subid %in% subs_with_mult_works) %>% 
  group_by(subid) %>% 
  mutate( #adding readable month
    month_of_obs = month(date_of_observation, label = TRUE),
    next_lat = lead(lat),
    next_long = lead(long)) %>% 
  arrange(month_of_obs) %>% 
  rowwise() %>% 
  mutate(
    miles_to_next_work = distm(c(long, lat), c(next_long, next_lat))*0.000621371) %>% 
  group_by(subid, type, month_of_obs) %>% 
  summarize(
    n = n(),
    miles_to_next_work = first(miles_to_next_home)) %>% 
  ungroup() %>% 
  kable(caption = "Multiple works", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Similar pattern to homes; most appear to be truly different places.


#### 2. Understand meaningful, risk-related clusters of labels. We want these labels to be useful for inclusion in models like the kind we are creating for the primary aims of the risk and risk2 projects.


```{r}
locations %>% 
  tabyl(type, drank) %>% 
  tibble() %>% 
  mutate(drink_majority = (yes > no)) %>% 
  arrange(desc(drink_majority)) %>% 
  kable(caption = "Place type by drank", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, alcohol) %>% 
  tibble() %>% 
  mutate(alcohol_majority = (yes > no)) %>% 
  arrange(desc(alcohol_majority)) %>% 
  kable(caption = "Place type by alcohol", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, avoid) %>% 
  tibble() %>% 
  mutate(avoid_majority = (yes > no)) %>% 
  arrange(desc(avoid_majority)) %>% 
  kable(caption = "Place type by avoid", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  glimpse()
```

3. Identify any "other" labels that fit existing factor levels. The goal is for these labels to be as accurate as possible, since they serve as ground truth.


```{r}

```

