---
title: "EDA on location data for context project"
author: "Hannah Moshontz"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "P:/studydata/risk/knits/context")
  })
---


### Notes

Purpose: This file summarizes the location labels supplied by participants for the Liu et al. GPS project. In that project, place labels (supplied by participants) are predicted by geospatial and temporal features of people's GPS data in the risk project. In this markdown, I aim to:

1. Recommend what data to exclude on the basis of: multiple homes, multiple workplaces.

2. Understand meaningful, risk-related clusters of labels. We want these labels to be useful for inclusion in models like the kind we are creating for the primary aims of the risk and risk2 projects.

3. Identify any "other" labels that fit existing factor levels. The goal is for these labels to be as accurate as possible, since they serve as ground truth.

Inputs:  Opens data files in path_raw

* locations.csv

### Summary / recommendations

Categories could be:

* others' homes -- home of family, home of friend, (some from "other" fit here)

* own home

* liquor store

* public drinking spaces -- bar, restaurant - w/ alcohol (some from "other" fit here), coffee shop/cafe - w/ alochol

* public community spaces -- coffee shop/cafe - w/o alochol, restaurant - w/o alochol, church, park, volunteer (from "other", library)

* recovery and health -- aa/recovery meeting, health care, gym/fitness center

* work/school (if single places)

* airports

Drop:

* errands

* distributed work places

* travel stop (many from "other" fit here: bus stop)

There are duplicate rows in the locations data. Need to reduce to unique rows.

In the locations data, rows may refer to the same place despite having different lat/long. However, unique lat/long are useful so you should not reduce to unique rows for analysis (but should when making exclusions based on multiple homes/work places).

Some people may have moved during the study. Consider closely evaluating people's GPS movement patterns to determine if they moved.

Many people seem to travel in-town for work (e.g., perhaps domestic work or grocery/food delivery). Would be good if a model could allow for this.

We should impute type labels for one "NA" and for several "others"


### Setup

Paths 
```{r}
path_processed <- "P:/studydata/risk/data_processed" 
path_raw <- "P:/studydata/risk/data_raw" 
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(janitor)
library(purrr)
library(kableExtra)
library(geosphere)
library(here)
```

### Import locations files

```{r}
other_codes <- list.files(file.path(path_raw, "locations"), full.names = TRUE) 

locations <- other_codes %>% 
  keep(str_detect(., "REAL") | str_detect(., "connie")) %>% 
  map(~read_csv(.x) %>% 
           mutate(subid = str_pad(subid, 3, side = "left", pad = "0")) %>% 
           select(subid, utc, lat, long, description) %>% 
        unique() %>% 
        filter(!is.na(description))) %>% #they did not code every 'other'
  reduce(left_join, by = c("subid", "utc", "lat", "long")) %>% 
  #note that there were duplicate rows in the raw locations data
  mutate(across(starts_with("description"), str_to_lower)) %>% 
  left_join(read_csv(file.path(path_processed, "locations.csv")), ., 
            by = c("subid", "utc", "lat", "long")) %>% 
  mutate(across(where(is_character), str_to_lower),
         across(
           c("type", 
             "drank",
             "alcohol",
             "avoid",
             "vacation"),
           as_factor),
         risk = factor(risk, 
                       levels = c("no", "low", "medium", "high"), 
                       ordered = TRUE),
         emotion = factor(emotion,
                          levels = c("unpleasant", "mixed", "neutral", "pleasant"),
                          ordered = TRUE),
         date_of_observation = as_datetime(utc, tz = "America/Chicago")) %>% 
  select(-utc) %>% 
  glimpse()



```


### EDA

#### 1. Recommend what data to exclude on the basis of: multiple homes, multiple workplaces.

##### Multiple homes

```{r}
locations %>% 
  filter(type == "home") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  kable(caption = "Multiple homes", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Investigating when homes were added and how far away they are (as they may be the same place, but different lat and long).

```{r}
subs_with_mult_homes <- locations %>% 
  filter(type == "home") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  pull(subid)

locations %>% 
  filter(type == "home") %>% 
  filter(subid %in% subs_with_mult_homes) %>% 
  group_by(subid) %>% 
  mutate( #adding readable month
    month_of_obs = month(date_of_observation, label = TRUE),
    next_lat = lead(lat),
    next_long = lead(long)) %>% 
  arrange(month_of_obs) %>% 
  rowwise() %>% 
  mutate(
    miles_to_next_home = distm(c(long, lat), c(next_long, next_lat))*0.000621371) %>% 
  group_by(subid, type, month_of_obs) %>% 
  summarize(
    n = n(),
    miles_to_next_home = first(miles_to_next_home)) %>% 
  ungroup() %>% 
  kable(caption = "Multiple homes", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Some of these places were added later, and some appear to be the same place with different lat/long.

##### Multiple workplaces
```{r}
subs_with_mult_works <- locations %>% 
  filter(type == "work") %>% 
  group_by(subid, type) %>% 
  count() %>% 
  arrange(n) %>% 
  filter(n > 1) %>% 
  pull(subid)

locations %>% 
  filter(type == "work") %>% 
  filter(subid %in% subs_with_mult_works) %>% 
  group_by(subid) %>% 
  mutate( #adding readable month
    month_of_obs = month(date_of_observation, label = TRUE),
    next_lat = lead(lat),
    next_long = lead(long)) %>% 
  arrange(month_of_obs) %>% 
  rowwise() %>% 
  mutate(
    miles_to_next_work = distm(c(long, lat), c(next_long, next_lat))*0.000621371) %>% 
  group_by(subid, type, month_of_obs) %>% 
  summarize(
    n = n(),
    miles_to_next_work = first(miles_to_next_work)) %>% 
  ungroup() %>% 
  kable(caption = "Multiple works", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Similar pattern to homes, although some people have a ton of observations. Most appear to be truly different places.

```{r}
locations %>% 
  filter(type == "work") %>% 
  group_by(subid, type) %>%
  count() %>% 
  filter(n > 5) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "People with over 5 work locations", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

Some people appear to have work that, by its nature, involves traveling to different places. Consider doing analyses in ways that can accomodate this kind of work given how common it is.

#### 2. Understand meaningful, risk-related clusters of labels. We want these labels to be useful for inclusion in models like the kind we are creating for the primary aims of the risk and risk2 projects.


```{r}
locations %>% 
  tabyl(type, drank) %>% 
  tibble() %>% 
  mutate(drink_majority = (yes > no)) %>% 
  arrange(desc(drink_majority)) %>% 
  kable(caption = "Place type by drank", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, alcohol) %>% 
  tibble() %>% 
  mutate(alcohol_majority = (yes > no)) %>% 
  arrange(desc(alcohol_majority)) %>% 
  kable(caption = "Place type by alcohol", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, avoid) %>% 
  tibble() %>% 
  mutate(avoid_majority = (yes > no)) %>% 
  arrange(desc(avoid_majority)) %>% 
  kable(caption = "Place type by avoid", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, risk) %>% 
  tibble() %>% 
  arrange(desc(no)) %>% 
  kable(caption = "Place type by risk", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")

locations %>% 
  group_by(type) %>% 
  summarize(mean_risk = mean(as.numeric(risk), na.rm = TRUE),
            sd_risk = sd(as.numeric(risk), na.rm = TRUE)) %>% 
  arrange(desc(mean_risk)) %>% 
  kable(caption = "Place type by mean risk", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```

```{r}
locations %>% 
  tabyl(type, emotion) %>% 
  tibble() %>% 
  arrange(desc(pleasant)) %>% 
  kable(caption = "Place type by emotion", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")

locations %>% 
  group_by(type) %>% 
  summarize(mean_emotion = mean(as.numeric(emotion), na.rm = TRUE),
            sd_emotion = sd(as.numeric(emotion), na.rm = TRUE)) %>% 
  arrange(desc(mean_emotion)) %>% 
  kable(caption = "Place type by mean emotion", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```


#### 3. Identify any "other" labels that fit existing factor levels. The goal is for these labels to be as accurate as possible, since they serve as ground truth.


```{r}
locations %>% 
  mutate(description = coalesce(description.x, description.y)) %>% 
  filter(!is.na(description)) %>% 
  select(subid, long, lat, description)  %>% 
  kable(caption = "Descriptions of 'other' places", table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left")
```


Many of these clearly fit existing categories. Also, new categories that can be created include:
- Entertainment/Sports
- Library
- Temporary residence (e.g., hotel, airbnb)
- Bus stop
- Airport


#### Misc -- investigating type NA values

```{r}
locations %>% 
  filter(is.na(type))
```

The second of these (subid == 131, vacation == yes) is at a landmark in colorado.

The first appears (subid == 110) appears to be a house, but this person seems to work in lots of different places, including places nearby.


