---
title: "Review of other locations"
author: "Hannah Moshontz"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "P:/studydata/risk/knits/context")
  })
---


### Notes

Purpose: This file reviews categories for 'other'-labeled places for the context project. 

Inputs:  other_labels.csv


### Setup

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(purrr)
library(kableExtra)
```

### Import file

```{r}
other_locations <- read_csv("P:/studydata/risk/data_processed/context/other_locations.csv") %>% 
  mutate(final = str_replace(final, "public drinking spaces", "public drinking space"),
         final = as.factor(final)) %>% 
  rename(proposed_label = final) %>% 
  glimpse()
```

### Review 

```{r}
other_locations %>% 
  tabyl(proposed_label)
```

### Investigate "work" as that was an option people could have selected....

```{r}
other_locations %>% 
  filter(proposed_label == "work") %>% 
  pull(description) %>% 
  unique()
```


```{r}
other_locations %>% 
  filter(str_detect(description, "conference")) %>% 
  pull(description) %>% 
  unique()
```

### Investigate "school" as that was also an option

```{r}
other_locations %>% 
  filter(proposed_label == "school") %>% 
  pull(description) %>% 
  unique()
```

### Looking at the descriptions that we are labeling public drinking spaces

```{r}
other_locations %>% 
  filter(proposed_label == "public drinking space") %>% 
  pull(description) %>% 
  unique()
```

Minor inferences here around venues that are not specified.

```{r}
other_locations %>% 
  filter(proposed_label == "recovery and health" | proposed_label == "healthcare") %>% 
  pull(description) %>% 
  unique()
```

There were a lot of sports-related boundary cases. For example, golfing, hunting, volleyball, walking / walking trail.

### Looking at the bigger categories that might have heterogeneity


```{r}
other_locations %>% 
  filter(proposed_label == "temporary residence") %>% 
  pull(description) %>% 
  unique()
```

```{r}
other_locations %>% 
  filter(proposed_label == "errands") %>% 
  pull(description) %>% 
  unique()
```

```{r}
other_locations %>% 
  filter(proposed_label == "community space / recreation") %>% 
  pull(description) %>% 
  unique()
```




