---
title: "Review and resolution of each participants work/school locations"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "P:/studydata/risk/knits/context")
  })
---


### Notes

Purpose: This file reviews each person's GPS data to resolve issues related to multiple work and school locations.

Inputs:  user_locations_check.csv, which is a copy of a sheet in "workbook_sent_from_xinyi.xlsx" with cleaned variable names. Many of the columns we will not use (the binary description and decision columns Xinyi created), but many contain information about activity zones that we do not otherwise have.


### Setup

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(purrr)
library(kableExtra)
library(tidylog)
library(ggmap)  
register_google(key = "AIzaSyBBwIG1tC4QZi5QrTnhXXLktIPD8NlVVI0") #API key
```

### Import file

```{r import locations check}
location_descriptions <- read_csv("./user_locations_check.csv",
                            col_names = TRUE) %>% 
  clean_names("snake") %>% 
  glimpse()
```

```{r import locations}
locations <- read_csv("P:/studydata/risk/data_processed/gps/to_share/locations.csv",
                      col_names = TRUE) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  clean_names("snake") %>% 
  mutate(time = lubridate::as_datetime(utc, tz = "America/Chicago")) %>% 
  glimpse()
```

```{r import gps}
gps <- read_rds("P:/studydata/risk/data_processed/shared/gps.rds") %>% 
  rename(long = lon) %>% 
  glimpse()

```


### Merge

```{r create combined dataset}
location_check <- gps %>% 
  mutate(location_source = "gps_data") %>% 
  select(subid, lat, long, time, location_source) %>% 
  bind_rows(
    locations %>% 
      mutate(location_source = "labeled_home") %>% 
      filter(type == "HOME") %>% 
      select(subid, lat, long, time, location_source)) %>% 
  group_by(subid) %>% 
  nest() %>% 
  left_join(
    select(
      location_descriptions,
      subid, type, n_home_locations, n_work_locations, 
      n_home_zones = n_home_zone, n_work_zones), 
    by = "subid") %>% 
  rename(gps_data = data)
```

#### Check for issues

```{r check issues}

#check for subids only in location_description
missing_ids <- unique(location_descriptions$subid)[!unique(location_descriptions$subid) %in% unique(gps$subid)]

#clean up
rm(gps)

```

There are `r length(missing_ids)` subjects that are in location descriptions and have locations, but are not in the processed gps dataset. Their subids are: `r paste(missing_ids)`.

TODO: Get more information about where their removal is documented. "studydata/risk/knits/gps/mak_gps_enriched.html" does not note their removal. Do not see another mak_gps html but the gps file was created in the last month. The notes file does not have any entry for 24 or 67. Clearly these people had data at some point, because they have locations.

### Examine participants

#### Set up variables

```{r}
location_check <- location_check %>% 
  mutate(action = case_when(type == 1 ~ "use as is",
                                type == 2 ~ "use with modification",
                                type == 0 ~ "remove all data")) 
```


#### Categorize particpants with unique labeled and observed home and work

```{r}
location_check <- location_check %>% 
  mutate(action = case_when(n_home_locations == 1 & 
                     n_work_locations == 1 &
                     n_home_zones == 1 &
                     n_work_zones == 1 ~ "use as is",
                     TRUE ~ action))
```

#### Check participants with multiple home locations

```{r}
multiple_homes_ids <- locations %>% 
  filter(type == "HOME") %>% 
  group_by(subid) %>% 
  count() %>% 
  filter(n > 1) %>% 
  pull(subid)

#function that takes subid and creates maps around each home
#this will iterate through multiple_homes_ids list

check_labeled_homes <- function(subid){
  
subject <- as.numeric(subid) #renaming to prevent issues  
  
gps <- location_check %>% 
  filter(subid == subject) %>% 
  pull(gps_data) %>% 
  pluck(1) %>% 
  mutate(location_source = case_when(location_source == "labeled_home" ~ "home",
                                     location_source == "gps_data" ~ "observed location"))

homes <- gps %>% 
  filter(location_source == "home") %>% 
  select(long, lat) 

plots <- map2(homes$long, homes$lat, 
     ~ggmap(
       get_map(
         c(.x, .y), zoom = 18)) +
       geom_point(aes(x = long, 
                      y = lat,
                      color = location_source),
                  data = gps) +
       ggtitle(paste0("subid ", subject, "'s home and surrounding gps observations"))) 

return(plots)

}
```

```{r map function for all people with multiple homes}

all_maps <- map(multiple_homes_ids, ~check_labeled_homes(.x))

all_maps
```

### closer look for folks who have spent time at both homes

```{r}
investigate_homes <- function(subid){
  
  #need to expand for three homes
  
  subject <- subid
  
  home1 <- location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    filter(location_source == "labeled_home") %>% 
    select(long, lat) %>% .[1,]
  
  home2 <- location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    filter(location_source == "labeled_home") %>% 
    select(long, lat) %>% .[2,]
  
  
  homes_subid <- location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    mutate(near_home1 = case_when(long > home1[[1]]-.001 & 
                                    long < home1[[1]]+.001 & 
                                    lat < home1[[2]]+.001 & 
                                    lat > home1[[2]]-.001 ~ "yes",
                                  TRUE ~ "no"),
           near_home2 = case_when(long > home2[[1]]-.001 & 
                                    long < home2[[1]]+.001 & 
                                    lat < home2[[2]]+.001 & 
                                    lat > home2[[2]]-.001 ~ "yes",
                                  TRUE ~ "no")) 
  
  
  map1 <- ggmap(
    get_map(
      c(home1[[1]], home1[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = homes_subid) +
    ggtitle(paste0("subject ", subject, "'s time spent near home 1 over time"))
  
  
  map2 <- ggmap(
    get_map(
      c(home2[[1]], home2[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = homes_subid) +
    ggtitle(paste0("subject ", subject, "'s time spent near home 2 over time"))
  
  
  #homes_subid %>% 
  #  filter(near_home1 == "yes" | near_home2 == "yes") %>% 
  #  arrange(time) 
  
  tables <- homes_subid %>% 
    mutate(month = lubridate::month(time)) %>% 
    group_by(month, near_home1, near_home2) %>% 
    count() %>% 
    filter(near_home1 == "yes" | near_home2 == "yes")
  
  return(list(map1, map2, tables))
  
}
```


```{r homes sub 6}

investigate_homes(6)

#set action  
location_check$action[location_check$subid == "6"] <- "use with modification"

```


```{r homes sub 27}

investigate_homes(27)

#set action  
location_check$action[location_check$subid == "27"] <- "use with modification"

```



43, 77, 79, 86, 93, 119, 135, 156, 162, 172, 201, 222, 240, 259, 270



###### Notes 

1. Subid 3 -- home locations are identical, should be combined
2. Subid 6 -- although the proportion of time spent at each home changes, they spend time at both houses throughout the study, but throughout they spend more time at home 2 than home 1. either delete home 1 or restrict data to august and september
3. Subid 27 -- seems to have moved in december, but doesn't spend much time at home 2 (mostly just stopped spending time at home 1). remove the label for home 2 for analysis.
4. Subid 29 -- home locations are identical, should be combined
5. Subid 30 -- no observations near home location 2 (Main St)
6. Subid 43 -- has three homes *check*
7. Subid 65 -- home 1 is a temporary home (pops up on google as a hotel), should be relabeled as such
8. Subid 77 -- much less time at home 2 *check*
9. Subid 79 -- address looks a bit off on 79 home 1 -- also looks like a temporary residence, many more observations at home 2 and 3 *check*
10. Subid 86 -- two homes are very close *check*
11. Subid 93 -- *check*
12. Subid 119 -- location 2 looks like a temporary home or vacation *check*
13. Subid 135 -- looks like a move *check*
14. Subid 156 -- less time at home 1 *check*
15. Subid 162 -- less time at home 1 *check*
16. Subid 172 -- looks like a move *check*
17. Subid 201 -- very few obs at home 1 *check*
18. Subid 222 -- looks like a move *check*
19. Subid 240 -- looks like a move *check*
20. Subid 259 -- much less time spent at home 1 *check*
21. Subid 270 -- much less time spent at home 2 *check*, almost no time spent at home 3, should be removed

Additional notes:
- Apartment addresses are often a little removed from their gps location