---
title: "Review and resolution of each participants work/school locations"
author: "Hannah Moshontz"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 6
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "P:/studydata/risk/knits/context")
  })
---


### Notes

Purpose: This file reviews each person's GPS data to resolve issues related to multiple work and school locations.

Inputs:  user_locations_check.csv, which is a copy of a sheet in "workbook_sent_from_xinyi.xlsx" with cleaned variable names. Many of the columns we will not use (the binary description and decision columns Xinyi created), but many contain information about activity zones that we do not otherwise have.

TODO:
1. List all unusual cases for Xinyi to check
2. Generate values of 'type' / action
3. Manually transfer notes to spreadsheet

### Setup

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(purrr)
library(here)
library(kableExtra)
#library(tidylog)
library(ggmap)
register_google(key = "AIzaSyBBwIG1tC4QZi5QrTnhXXLktIPD8NlVVI0") #API key
```

### Import file

```{r import locations check}
location_descriptions <- read_csv("./user_locations_check.csv",
                            col_names = TRUE) %>% 
  clean_names("snake") %>% 
  glimpse()

```

```{r import locations}
locations <- read_csv("P:/studydata/risk/data_processed/gps/to_share/locations.csv",
                      col_names = TRUE) %>% 
  mutate(subid = as.numeric(subid)) %>% 
  clean_names("snake") %>% 
  mutate(time = lubridate::as_datetime(utc, tz = "America/Chicago")) %>% 
  mutate(type = tolower(type)) %>% 
  glimpse()

#fixing minor typos in type
locations$type[locations$type == "coffee shop/café"] <- "coffee shop/cafe"
locations$type[locations$type == "coffe shop/café"] <- "coffee shop/cafe"

#imputing missing lat/long 
locations_imputed <- locations %>%
  filter(is.na(lat)) %>% 
  mutate(address = str_c(street_address, city, state, sep = ", "), 
         imputed_location = geocode(address)) %>% 
           select(-address) 

locations_imputed$imputed_long <- locations_imputed$imputed_location$lon
locations_imputed$imputed_lat <- locations_imputed$imputed_location$lat

locations <- locations_imputed %>% 
  select(subid, imputed_long, imputed_lat, street_address) %>% 
  left_join(locations, ., by = c("subid", "street_address")) %>% 
  mutate(lat = coalesce(lat, imputed_lat),
         long = coalesce(long, imputed_long)) 

rm(locations_imputed)
```

```{r import gps}
gps <- read_rds("P:/studydata/risk/data_processed/shared/gps.rds") %>% 
  rename(long = lon) %>% 
  glimpse()
```


### Merge

```{r create combined dataset}
location_check <- gps %>% 
  mutate(location_source = "gps_data") %>% 
  select(subid, lat, long, time, location_source) %>% 
    bind_rows(
    locations %>% 
      mutate(location_source = case_when(
        type == "school" ~ "labeled_work",
        type == "work" ~ "labeled_work",
        type == "home" ~ "labeled_home",
        TRUE ~ "other")) %>% 
      select(subid, lat, long, time, location_source)) %>%
  group_by(subid) %>% 
  nest() %>% 
  left_join(
    select(
      location_descriptions,
      subid, type, n_home_locations, n_work_locations, 
      n_home_zones = n_home_zone, n_work_zones), 
    by = "subid") %>% 
  rename(gps_data = data)
```

#### Check for issues

```{r check issues}

#check for subids only in location_description
missing_ids <- unique(location_descriptions$subid)[!unique(location_descriptions$subid) %in% unique(gps$subid)]

#clean up
rm(gps)

```

There are `r length(missing_ids)` subjects that are in location descriptions and have locations, but are not in the processed gps dataset. Their subids are: `r paste(missing_ids)`.

TODO: Get more information about where their removal is documented. "studydata/risk/knits/gps/mak_gps_enriched.html" does not note their removal. Do not see another mak_gps html but the gps file was created in the last month. The notes file does not have any entry for 24 or 67. Clearly these people had data at some point, because they have locations.


### Examine participants

#### Set up variables

```{r}

#starting new action variable from scratch so that we are consistent in our evaluations


#location_check <- location_check %>% 
#  mutate(action = case_when(type == 1 ~ "use as is",
#                                type == 2 ~ "use with modification",
#                                type == 0 ~ "remove all data")) 
```

### Characterizing the issue

```{r}
location_check %>% 
  tabyl(n_home_locations, n_home_zones) %>% 
  kable(caption = "Table of the number of labeled homes by the number of associated zones") %>% 
  kable_styling()

location_check %>% 
  tabyl(n_work_locations, n_work_zones)  %>% 
  kable(caption = "Table of the number of labeled works by the number of associated zones") %>% 
  kable_styling()
```

#### Categorize particpants with unique labeled and observed home and work

```{r}
location_check <- location_check %>% 
  mutate(action = case_when(n_home_locations == 1 & 
                     n_work_locations == 1 &
                     n_home_zones == 1 &
                     n_work_zones == 1 ~ "use as is"))
```

#### Check home locations

```{r}
multiple_homes_ids <- location_check %>% 
  filter(n_home_zones > 1) %>% 
  group_by(subid) %>% 
  pull(subid)

#function that takes subid and creates maps around each home
#this will iterate through multiple_homes_ids list

check_labeled_places <- function(subid, place_type){
  
message(paste0("processing subject", subid))  
  
subject <- as.numeric(subid) #renaming to prevent issues  
  
gps <- location_check %>% 
  filter(subid == subject) %>% 
  pull(gps_data) %>% 
  pluck(1) %>% 
  mutate(location_source = case_when(location_source == paste0("labeled_", place_type) ~ place_type,
                                     location_source == "gps_data" ~ "observed location"))

places <- gps %>% 
  filter(location_source == place_type) %>% 
  select(long, lat) 

plots <- map2(places$long, places$lat, 
     ~ggmap(
       get_map(
         c(.x, .y), zoom = 18)) +
       geom_point(aes(x = long, 
                      y = lat,
                      color = location_source),
                  data = gps) +
       ggtitle(paste0("subid ", subject, "'s ", place_type," and surrounding gps observations"))) 

return(plots)

}
```

```{r map function for all people with multiple homes}

#all_maps <- map(multiple_homes_ids, ~check_labeled_places(.x, "home"))

#all_maps
```

##### Closer look at ppl who have spent time at both homes

```{r}
investigate_homes <- function(subid){
  
  subject <- subid
  
  homes <-   location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    filter(location_source == "labeled_home")
  
  home1 <- homes %>% 
    select(long, lat) %>% .[1,]
  
  home2 <- homes %>% 
    select(long, lat) %>% .[2,]
  
  
  homes_subid <- location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    mutate(near_home1 = case_when(long > home1[[1]]-.001 & 
                                    long < home1[[1]]+.001 & 
                                    lat < home1[[2]]+.001 & 
                                    lat > home1[[2]]-.001 ~ "yes",
                                  TRUE ~ "no"),
           near_home2 = case_when(long > home2[[1]]-.001 & 
                                    long < home2[[1]]+.001 & 
                                    lat < home2[[2]]+.001 & 
                                    lat > home2[[2]]-.001 ~ "yes",
                                  TRUE ~ "no")) 

  
  map1 <- ggmap(
    get_map(
      c(home1[[1]], home1[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = homes_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near home 1 over time"))
  
  
  map2 <- ggmap(
    get_map(
      c(home2[[1]], home2[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = homes_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near home 2 over time"))
  

  #homes_subid %>% 
  #  filter(near_home1 == "yes" | near_home2 == "yes") %>% 
  #  arrange(time) 
  
  tables <- homes_subid %>% 
    mutate(near = case_when(near_home1 == "yes" ~ "home1",
                            near_home2 == "yes" ~ "home2")) %>% 
    group_by(near) %>% 
    summarize(first = min(time),
              last = max(time))
  
  results <- list(tables, map1, map2)
  
  
      if (nrow(homes) == 3) {
    
        message("three homes detected")
        
    home3 <- homes %>% 
      select(long, lat) %>% .[3,]
    
    homes_subid <-  homes_subid %>% 
      mutate(
        near_home3 = case_when(long > home3[[1]]-.001 & 
                                 long < home3[[1]]+.001 & 
                                 lat < home3[[2]]+.001 & 
                                 lat > home1[[2]]-.001 ~ "yes",
                               TRUE ~ "no"))
    
    map3 <- ggmap(
    get_map(
      c(home3[[1]], home3[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = homes_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near home 3 over time"))
    
    tables <- homes_subid %>% 
    mutate(near = case_when(near_home1 == "yes" ~ "home1",
                            near_home2 == "yes" ~ "home2",
                            near_home3 == "yes" ~ "home3")) %>% 
    group_by(near) %>% 
    summarize(first = min(time),
              last = max(time))
    
     results <- list(tables, map1, map2, map3)
  
      }

  if (length(homes_subid) > 3) message(paste0("subject", subject, " has more than 3 homes"))
  
  return(results)
  
}
```


```{r, echo = FALSE}
home_maps <- map(multiple_homes_ids, ~investigate_homes(.x))
```

###### Results

```{r}
home_maps
```

#### Check participants with multiple work locations


```{r  map function for all people with multiple works, echo = FALSE}

multiple_works_ids <- location_check %>% 
  filter(n_work_zones > 1) %>% 
  pull(subid)

#all_work_maps <- map(multiple_works_ids, ~check_labeled_places(.x, "work"))
```

```{r}
#all_work_maps
```

##### Closer look at people with multiple works


```{r}
investigate_works <- function(subid){
  
  subject <- subid
  
  works <-   location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    filter(location_source == "labeled_work")
  
  work1 <- works %>% 
    select(long, lat) %>% .[1,]
  
  work2 <- works %>% 
    select(long, lat) %>% .[2,]
  
  
  works_subid <- location_check %>% 
    filter(subid == subject) %>% 
    pull(gps_data) %>% 
    pluck(1) %>% 
    mutate(near_work1 = case_when(long > work1[[1]]-.001 & 
                                    long < work1[[1]]+.001 & 
                                    lat < work1[[2]]+.001 & 
                                    lat > work1[[2]]-.001 ~ "yes",
                                  TRUE ~ "no"),
           near_work2 = case_when(long > work2[[1]]-.001 & 
                                    long < work2[[1]]+.001 & 
                                    lat < work2[[2]]+.001 & 
                                    lat > work2[[2]]-.001 ~ "yes",
                                  TRUE ~ "no")) 

  
  map1 <- ggmap(
    get_map(
      c(work1[[1]], work1[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = works_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near work 1 over time"))
  
  
  map2 <- ggmap(
    get_map(
      c(work2[[1]], work2[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = works_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near work 2 over time"))
  

  #works_subid %>% 
  #  filter(near_work1 == "yes" | near_work2 == "yes") %>% 
  #  arrange(time) 
  
  tables <- works_subid %>% 
    mutate(near = case_when(near_work1 == "yes" ~ "work1",
                            near_work2 == "yes" ~ "work2")) %>% 
    group_by(near) %>% 
    summarize(first = min(time),
              last = max(time))
  
  results <- list(tables, map1, map2)
  
  
      if (nrow(works) == 3) {
    
        message("three works detected")
        
    work3 <- works %>% 
      select(long, lat) %>% .[3,]
    
    works_subid <-  works_subid %>% 
      mutate(
        near_work3 = case_when(long > work3[[1]]-.001 & 
                                 long < work3[[1]]+.001 & 
                                 lat < work3[[2]]+.001 & 
                                 lat > work1[[2]]-.001 ~ "yes",
                               TRUE ~ "no"))
    
    map3 <- ggmap(
    get_map(
      c(work3[[1]], work3[[2]]), zoom = 18)) +
    geom_point(aes(x = long, 
                   y = lat,
                   shape = location_source,
                   color = time),
               data = works_subid) +
    ggtitle(paste0("subject ", subject, "'s obs near work 3 over time"))
    
    tables <- works_subid %>% 
    mutate(near = case_when(near_work1 == "yes" ~ "work1",
                            near_work2 == "yes" ~ "work2",
                            near_work3 == "yes" ~ "work3")) %>% 
    group_by(near) %>% 
    summarize(first = min(time),
              last = max(time))
    
     results <- list(tables, map1, map2, map3)
  
      }
  
  if (length(works_subid) > 3) message(paste0("subject", subject, " has more than 3 works"))

  return(results)
  
}
```



```{r echo = FALSE}
work_maps <- map(multiple_works_ids, ~investigate_works(.x))
```

###### Results

```{r}
work_maps
```


### Notes 

1. Subid 3 -- home locations are identical, should be combined. same for work locations 1 and 2.
2. Subid 6 -- although the proportion of time spent at each home changes, they spend time at both houses throughout the study, but throughout they spend more time at home 2 than home 1. either delete home 1 or restrict data to august and september. *investigate works -- is one labelled school?*
3. Subid 27 -- seems to have moved in december, but doesn't spend much time at home 2 (mostly just stopped spending time at home 1). remove the label for home 2 for analysis. *investigateworks*
4. Subid 29 -- home locations are identical, should be combined
5. Subid 30 -- no observations near home location 2 (Main St)
6. Subid 43 -- has three homes, appears to have moved 3 times. it may make sense to restrict data to the time period when they were living at location 1 or location 3.
7. Subid 65 -- home 1 is a temporary home (pops up on google as a hotel), should be relabeled as such
8. Subid 77 -- much less time at home 2, and during a very narrow time-frame. this home is outside of madison. consider relabeling home 2 as a temporary home or hotel.
9. Subid 79 -- address looks a bit off on 79 home 1 -- also looks like a temporary residence, as they spent almost no time there. remove home 1. looks like a move between home 2 and 3 occured so we should restrict to times when they lived at one.
10. Subid 86 -- they moved between two homes that are very close. may make sense to pick house 2 as they seem to have moved early in the study.
11. Subid 93 -- data is pretty sparse. consider restricting to before August 10th or so, to focus on home 1, and then delete home 2. 
12. Subid 119 -- location 2 should be marked as a temporary home.
13. Subid 135 -- apartment address is a little off for 1. this looks like a move.... focus on home 1 or keep both.
14. Subid 156 -- less time at home 1, and all focused at the begining of the study. consider removing obs before nov 15th or so and removing home 1, or labeling home 1 as a temporary residence. 
15. Subid 162 -- much less time spent at time 1, which looks like it was a temporary home. 
16. Subid 172 -- a move. go with home 2 if we have to pick, and restrict to before feb 10th or so
17. Subid 201 -- almost no obs at home 1; mark as a temporary home or remove
18. Subid 222 -- a move... not sure what to do as they appear to be about equal.
19. Subid 240 -- a move, choice will have to be arbitrary if we restrict in time
20. Subid 259 -- much less time spent at home 1, consider marking as a temporary home 
21. Subid 270 --  home 2 looks like an error -- not a residence -- consider removing
22. Subid 1 -- Has multiple work locations, several of which they have not spent much time at. The following should be deleted: 2, 3, 4, 5, 6, 7 
23. Subid 5 -- Looks like this person has a school location and a work location; should not be disqualifying. 
24. Subid  7 -- This is difficult because students might be at really different places on campus...This person has multiple work/school points, but they are all on campus.
25. Subid 9 -- *check if one of these is labeled work and one school*
26. Subid 10 -- Seems to visit schools as part of work. Delete locations: 2, 3, 4, 5. Keep 6 if we allow for people who attend university to have multiple visits to campus.
27. Subid 11 -- *check timing* delete work 3, 4, 5, 6?
28. Subid 15 -- delete location 2
29. Subid 16 -- delete location 2
30. Subid 17 -- *check timing* likely need to delete several locations -- it looks like this person does delivery service and/or works at a liquor store? or just labeled a lot as work? plus, all the locations are duplicated.
31. Subid 18 -- delete location 2
32. Subid 19 -- delete location 2, 3, 10. And depending on our decision about universities, location 4, 5, 6, 7, 8, 9.
33. Subid 20 -- 1 and 2 are the same location, 3+ is a little off and needs *check timing* -- may need to delete
34. Sub 21 looks to be a university janitor or something, should probably delete all their work locations.
35. Sub 23 location 2 appears to be mislabeled; this person seems to work at multiple branches of the same bank...
36. Subject 25 -- location 1 they have hardly been to. location 2 and 3 are the same.
37. Subject 28 -- *investigate works* seems like an unreliable measurement for 28, or they have a very odd job. consider deleting all points.
38. Subject 40 has many work locations they have not been to

Additional notes:
- Apartment addresses are often a little removed from their gps location -- it looks like the lat, long were generated from addresses rather than as an average of observed locations
- Is it possible to keep two homes if people moved? if we can have multiple retaurants, etc. why not multiple homes? (see subject 86 as a good example of a case we should keep)
- Is it worth reviewing all other locations to make sure that people actually went there? (In this study, some people described places they go before we had any GPS data)
- It might be worth formalizing exclusion criteria for each labeled place... like people must have visited each place X number of times (defined by an observation within a particular distance) to be included in analyses, and/or observations must span their data collection time.
- Can we keep work and school separate? That will probably help us identify work 
- Check for duplicate locations in the data. For some reason there may be several duplicates.

General issues:
- Many people have lots of work places listed
- Combining work and school creates a lot more duplicate locations
- People who are affiliated with the university, and have multiple locations marked on campus.
- Similarly, some work places are large and there are multiple labels for the place. (see subid 37) 
- People who work at multiple locations of the same business.
- People who switched work or home during the study. I'm not sure why work and home have to be exclusive, though.
- People marking work or home locations that they have hardly spent any time at.
- People who seem to be labeling anything they do while at work as their workplace.
