---
title: "Demographic Descriptives"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
---

### Notes

This script assesses demographics for all participants who completed the screen (N = 208) separated by participants who completed through at least followup 1 vs participants who screened out or discontinued or were withdrawn prior to completing the first month follow-up. To look for group differences we combined several demographic variables to create the final measures of:  
1. age (numeric)  
2. Hispanic (numeric; 1 = yes, 0 = no)  
3. White (numeric; 1 = yes, 0 = no)  
4. Male (numeric; 1 = yes, 0 = no)  
5. Income (numeric)  
6. Education (ordered factor)  
7. Employed (numeric; 1 = employed, 0 = not employed)  
8. Married (numeric; 1 = married, 0 = not married)  
9. DSM5 AUD symptom count (numeric)  
10. Number of types of AUD treatment participant received (numeric)  
11. Number of quit attempts (numeric)  
12. Number of other drugs particpant used in their lifetime (numeric)  
13. Average age reported for various AUD milestones (numeric)  

We then ran independent samples t-tests with a bonferroni-holm adjustment to account for family-wise error on all derived variables.    


### Setup

```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

packages
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(janitor)
library(psych)
library(cowplot)
library(rstatix)
```

path
```{r}
path_data <- "/Volumes/private/StudyData/RISK/analysis/shared/data"
path_burden <- "/Volumes/private/StudyData/RISK/analysis/burden/data"
```

### Read in data
```{r}
screen <- read_csv(file.path(path_data, "screen.csv"), col_types = cols()) 
disposition <- read_csv(file.path(path_burden, "disposition.csv"), col_types = cols()) 
```

### Prepare data for analyses
Remove ineligible participants
```{r}
eligible_sample <- disposition %>%  
  filter(reason_no_intake != "ineligible" | is.na(reason_no_intake))

screen <- screen %>% 
  filter(subid %in% eligible_sample$subid)
```

2 subids do not have a screen because they did not complete screen - discontinued or not consented
```{r}
eligible_sample %>% 
  filter(!subid %in% screen$subid)
```


Select demographic, AUH variables, and lifetime drug use (assist_1_1:assist_1_8)
```{r}
screen <- screen %>% 
  select(subid, dem_1:dem_8, -dem_3_1, -dem_4_1, -dem_6_1, auh_1:auh_7, -auh_6_7_text, 
         starts_with("dsm5_"), assist_1_1:assist_1_8) 
```


Add grouping variable - participants who completed follow-up 1 vs did not complete through followup 1
```{r}
sample_completed <- disposition %>% 
  filter(last_visit != "screen" & last_visit != "intake")
screen <- screen %>% 
  mutate(disposition = case_when(subid %in% sample_completed$subid ~ "continued",
                                 TRUE ~ "discontinued"))

tabyl(screen$disposition) %>% 
  adorn_totals("row")
```

Give descriptive names to variables and recode
```{r}
screen <- screen %>% 
  # demographics
  rename(age = dem_1,
         sex = dem_2,
         race = dem_3,
         Hispanic = dem_4,
         education = dem_5,
         employment = dem_6,
         income = dem_7,
         marrital_status = dem_8) %>% 
  mutate(male = recode(sex, "Male" = 1, "Female" = 0),
         race = factor(race, levels = c("American Indian/Alaska Native", "Asian",
                                        "Black/African American", "Other/Multiracial",
                                        "White/Caucasian"), labels = c("American Indian or Alaska Native", "Asian",
                                        "Black/African American", "Multiracial or not listed above",
                                        "white")),
         Hispanic = case_when(Hispanic == "No, I am not of Hispanic, Latino, or Spanish origin" ~ 0,
                         TRUE ~ 1),
         education = factor(education, 
                         levels = c("Less than high school or GED degree", "High school or GED", 
                         "Some college", "2-Year degree", "College degree", "Advanced degree"),
                         ordered = TRUE),
         employment = factor(employment),
         marrital_status = factor(marrital_status)) %>% 
  # AUH 
  rename(age_first_drink = auh_1,
         age_reg_drink = auh_2,
         age_problem_drink = auh_3,
         age_first_quit = auh_4,
         num_quit_attempts = auh_5,
         lt_residential_tx = auh_6_1,
         st_residential_tx = auh_6_2,
         outpatient_tx = auh_6_3,
         individ_counseling = auh_6_4,
         group_counseling = auh_6_5,
         aa_or_na = auh_6_6,
         other_tx = auh_6_7,
         med_for_aud = auh_7) %>% 
  # recode tx vars as ordered no yes factors
  mutate(lt_residential_tx = case_when(lt_residential_tx == "Long-Term Residential Treatment (more than 6 months)" ~ 1,
                                       TRUE ~ 0),
         st_residential_tx = case_when(st_residential_tx == "Short-Term Residential Treatment (less than 6 months)" ~ 1,
                                       TRUE ~ 0),
         outpatient_tx = case_when(outpatient_tx == "Outpatient Treatment" ~ 1,
                                       TRUE ~ 0),
         individ_counseling = case_when(individ_counseling == "Individual Counseling" ~ 1,
                                       TRUE ~ 0),
         group_counseling = case_when(group_counseling == "Group Counseling" ~ 1,
                                       TRUE ~ 0),
         aa_or_na = case_when(aa_or_na == "Alcoholics Anonymous/Narcotics Anonymous" ~ 1,
                                       TRUE ~ 0),
         other_tx = case_when(other_tx == "Other" ~ 1,
                                       TRUE ~ 0),
         med_for_aud = recode(med_for_aud, "No" = 0, "Yes" = 1)) %>% 
  # Assist
  mutate(tobacco = recode(assist_1_1, "No" = 0, "Yes" = 1),
         cannabis = recode(assist_1_2, "No" = 0, "Yes" = 1),
         cocaine = recode(assist_1_3, "No" = 0, "Yes" = 1),
         amphetamine = recode(assist_1_4, "No" = 0, "Yes" = 1),
         inhalant = recode(assist_1_5, "No" = 0, "Yes" = 1),
         sedative = recode(assist_1_6, "No" = 0, "Yes" = 1),
         hallucinogen = recode(assist_1_7, "No" = 0, "Yes" = 1),
         opiate = recode(assist_1_8, "No" = 0, "Yes" = 1)) %>% 
  # dsm5
  mutate(across(dsm5_1:dsm5_11, ~ recode(., "No" = 0, "Yes" = 1))) %>% 
  # remove duplicate vars
  select(-c(assist_1_1:assist_1_8), -sex) %>% 
  select(subid, disposition, everything()) %>% 
  glimpse()
```

Combine vars
```{r}
screen_combined <- screen %>% 
  # calculate total dsm5 score by adding up dsm5_1 through dsm5_11
  rowwise() %>% 
  mutate(dsm5_total = sum(dsm5_1, dsm5_2, dsm5_3, dsm5_4, dsm5_5, dsm5_6, dsm5_7, 
                            dsm5_8, dsm5_9, dsm5_10, dsm5_11),
         num_types_tx = sum(lt_residential_tx, st_residential_tx, outpatient_tx, 
                            individ_counseling, group_counseling, aa_or_na, other_tx, med_for_aud),
         num_other_drugs = sum(tobacco, cannabis, cocaine, amphetamine, inhalant,
                               sedative, hallucinogen, opiate),
         avg_age_aud_milestones = sum(age_first_drink, age_reg_drink, age_problem_drink,
                                       age_first_quit)/ 4) %>% 
  ungroup() %>% 
  select(-c(age_first_drink:age_first_quit, lt_residential_tx:dsm5_11, tobacco:opiate)) %>% 
  glimpse()
```

Due to uneven cell sizes, grouping race as white and non-white participants
```{r}
tabyl(screen$race) %>% 
  adorn_totals("row")

screen_combined <- screen_combined %>%
  mutate(white = case_when(race == "white" ~ 1,
                          TRUE ~ 0)) %>% 
  select(-race) 
```

Create category for employed vs not employed  
```{r}
tabyl(screen$employment)

screen_combined <- screen_combined %>%
  mutate(employed = case_when(employment == "Employed" ~ 1,
                          TRUE ~ 0)) %>% 
  select(-employment)
```

group marital status as married vs not married  
```{r}
tabyl(screen$marrital_status)

screen_combined <- screen_combined %>%
  mutate(married = case_when(marrital_status == "Married" ~ 1,
                          TRUE ~ 0)) %>% 
  select(subid, disposition, age, male, white, employed, married, everything(), -marrital_status) %>% 
  glimpse()
```


### Alpha of all combined variable groups

number of other drugs used
```{r}
screen %>% 
  select(tobacco:opiate) %>% 
  alpha()
```

avg age for AUD milestones
```{r}
screen %>% 
  select(age_first_drink:age_first_quit) %>% 
  alpha()
```


dsm5 total
```{r}
screen %>% 
  select(dsm5_1:dsm5_11) %>% 
  alpha()
```

number of types of tx
```{r}
screen %>% 
  select(lt_residential_tx:med_for_aud) %>% 
  alpha()
```


### Get correlation matrices

continued participants
```{r}
screen_combined %>% 
  filter(disposition == "continued") %>% 
  # change ordered factors to numeric
  mutate(across(where(is.ordered), as.numeric)) %>% 
  select(-c(subid, disposition)) %>% 
  cor() %>% 
  corrplot::corrplot.mixed(tl.cex = 0.6)
```

Discontinued participants
```{r}
screen_combined %>% 
  filter(disposition == "discontinued") %>% 
  # change ordered factors to numeric
  mutate(across(where(is.ordered), as.numeric)) %>% 
  select(-c(subid, disposition)) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  corrplot::corrplot.mixed(tl.cex = 0.6)
```


### Summary statistics by group (continued vs discontinued)

Continued participants
```{r}
screen_combined %>% 
  filter(disposition == "continued") %>% 
  mutate(across(where(is.ordered), as.numeric)) %>%
  select(-c(subid, disposition)) %>% 
  describe() %>% 
  select(n, mean, sd, median, min, max, skew) %>% 
  kbl(caption = "continued participants",
      digits = 1) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped"))
```

Discontinued participants
```{r}
screen_combined %>% 
  filter(disposition == "discontinued") %>% 
  mutate(across(where(is.ordered), as.numeric)) %>%
  select(-c(subid, disposition)) %>% 
  describe() %>% 
  select(n, mean, sd, median, min, max, skew) %>% 
  kbl(caption = "discontinued participants",
      digits = 1) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped"))
```



### t-tests with correction for inflated family wise error

After holm-bonferroni adjustment, no significant differences between groups
```{r}
screen_combined_long <- screen_combined %>%
  select(-subid) %>% 
  mutate(education = as.numeric(education)) %>% 
  pivot_longer(-disposition, names_to = "variables", values_to = "value") %>% 
  glimpse()

screen_combined_long %>%
  group_by(variables) %>%
  t_test(value ~ disposition) %>%
  adjust_pvalue(method = "holm") %>%
  add_significance() %>% 
  kbl(digits = 2) %>% 
  kable_styling(bootstrap_options = c("condensed", "striped"))
```


