---
title: "Checking Voice Data"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
 
This script checks data from RISK participants' voice calls by computing descriptives and checking 
for missingness and potential errors.  

Thoughts for discussion:  
1. How do we want to handle spam/irrelevant calls for analyses?  
2. What does a call with contact_type self mean?  
3. Differences between call_type rejected vs. refused?  
4. Is there a way to identify calls with study staff? It is possible they may be contributing to the
large number of calls with no contact_type identified.
  
  
### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths 
```{r}
path_data <- "./analysis/shared/data"
```

Packages
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
```


### Import Data and glimpse 

Voice data
```{r}
voice <- read_rds(file.path(path_data, "ds_voice.rds"))  
voice <- voice %>%
  mutate(time_central = as_datetime(utc, tz = 'America/Chicago')) %>%
  mutate(date_central = date(time_central), 
         hour_central = hour(time_central),
         minute_central = minute(time_central), 
         second_central = second(time_central)) %>%
  select(-c(utc, time_central)) %>%
  glimpse()
```

`r length(unique(voice$subid))` participants contribute to a total of `r nrow(voice)` voice call 
observations.  The earliest recorded sms message is from `r min(voice$date_central)` and the last 
is from `r max(voice$date_central)`.

Missing values
```{r}
if(any(is.na(voice))){
  missing <- voice %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There are `r sum(is.na(voice))` missing values (NA) from `r length(missing$var)` unique 
variables in the entire dataset.

Closer look at missing values
```{r}
voice %>% 
  filter(is.na(contact_type)) %>% 
  select(-c(date_central:second_central)) %>% 
  head(n = 30) %>% 
  kable(caption = "Sample observations with missing contact type") %>% 
  kable_styling(bootstrap_options = "condensed")

missing_contacttype <- voice %>% 
  filter(is.na(contact_type)) %>% 
  group_by(subid) %>% 
  summarise(n_NA = n())

missing_contacttype %>% 
  head(n = 20) %>% 
  kable(caption = "Table head of number of missing contact_type values per subid",
        table.attr = "style='width:40%;'") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed")
```

`r length(unique(missing_contacttype$subid))` participants have voice call observations with missing
contact type values. Participants on average have `r round(mean(missing_contacttype$n_NA), 2)` missing
contact type values each.

COMMENT KW 2020-08-11: Do we have study calls to participants regularly? I see a lot of repeated 
numbers within contact_type NA. 


Spam/irrelevant calls
```{r}
spam <- voice %>%
  filter(contact_type == "IRRELEVANT/SPAM") %>% 
  select(-c(date_central:second_central)) 

spam_NA <- spam %>% 
  filter(across(c(drank_past:emotion), ~is.na(.)))

spam %>% 
  head(n = 20) %>% 
  kable(caption = "Sample from spam subset", 
          table.attr = "style='width:40%;'") %>%
  kable_styling(position = "left", bootstrap_options = "condensed")
```

There are `r nrow(spam)` spam calls and `r nrow(spam_NA)` of the spam calls are missing values for 
all context variables. Will create voice_withoutspam dataframe (below) to run all context analyses.

Spam/Irrelevant calls and missing values
```{r}
voice_withoutspam <- voice %>% 
  filter(!contact_type == "IRRELEVANT/SPAM" | is.na(contact_type))

if(any(is.na(voice_withoutspam))){
  missing <- voice_withoutspam %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values after spam calls removed", 
          table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

Once irrelevant and spam calls are removed we now have a new total of `r nrow(voice_withoutspam)` 
voice calls and missing values decreased from `r sum(is.na(voice))` to `r sum(is.na(voice_withoutspam))`.  
The majority of remaining missing values are then of contact type NA or self (see below).   

```{r}
voice_withoutspam %>% 
  mutate(contact_type = tolower(contact_type)) %>% 
  group_by(contact_type) %>% 
  summarise(across(drank_past:emotion, ~sum(is.na(.)))) %>%
    kable(caption = "Missing values by contact type after spam calls removed") %>%
    kable_styling()
```


COMMENT KW 2020-08-11: What are calls with contact type self?


### Descriptives

#### Voice calls

Call type
```{r}
voice %>% 
  tabyl(type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Type of voice call") %>%
  kable_styling(full_width = FALSE, position = "left")
```


COMMENT KW 2020-08-12: Not sure what these call types are. Numbers in codebook also seem off:  
1 = incoming, 2 = outgoing, 3 = draft, 5 = unknown/undefined, 19 = unknown/undefined, -1 = unknown/undefined.  
Code block below inspects these types --> see comment after code block for resolution.  


```{r}
# type 3 - call duration = 0
voice %>% 
  filter(type == 3) %>% 
  select(subid, duration, contact_type) %>% 
  head(n = 15) %>% 
  kable(caption = "Sample from type 3") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 5 - call duration = 0
voice %>% 
  filter(type == 5) %>% 
  select(subid, duration, contact_type) %>% 
  head(n = 15) %>% 
  kable(caption = "Sample from type 5") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 6 - call duration = 0 
voice %>% 
  filter(type == 6) %>% 
  select(subid, duration, contact_type) %>% 
  head(n = 15) %>% 
  kable(caption = "Sample from type 6") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 7 - from subid 214 --> call duration = 0
voice %>% 
  filter(type == 7) %>% 
  select(subid, duration, contact_type) %>% 
  group_by(subid, duration, contact_type) %>%
  summarise(n_obs = n()) %>% 
  kable(caption = "Type 7") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 8 - from subid 52
voice %>% 
  filter(type == 8) %>% 
  select(subid, duration, contact_type) %>% 
  head(n = 15) %>% 
  kable(caption = "Sample from type 8") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 9 - from subid 52
voice %>% 
  filter(type == 9) %>% 
  select(subid, duration, contact_type)%>% 
  head(n = 15) %>% 
  kable(caption = "Sample from type 9") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 10 - from subid 52 and 63 --> call duration = 0
voice %>% 
  filter(type == 10) %>% 
  select(subid, duration, contact_type)%>% 
  group_by(subid, duration, contact_type) %>%
  summarise(n_obs = n()) %>% 
  adorn_totals() %>% 
  kable(caption = "Type 10") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 1000 - from subid 82 
voice %>% 
  filter(type == 1000) %>% 
  select(subid, duration, contact_type) %>% 
  group_by(subid, duration, contact_type) %>%
  summarise(n_obs = n()) %>% 
  adorn_totals() %>% 
  kable(caption = "Type 1000") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 1001 - from subid 74 and 82
voice %>% 
  filter(type == 1001) %>% 
  select(subid, duration, contact_type) %>% 
  group_by(subid, duration, contact_type) %>%
  summarise(n_obs = n()) %>% 
  adorn_totals() %>% 
  kable(caption = "Type 1001") %>%
  kable_styling(full_width = FALSE, position = "left")

# type 1002 - from subid 74 and 82  --> call duration = 0
voice %>% 
  filter(type == 1002) %>% 
  select(subid, duration, contact_type) %>% 
  group_by(subid, duration, contact_type) %>%
  summarise(n_obs = n()) %>% 
  adorn_totals() %>% 
  kable(caption = "Type 1002") %>%
  kable_styling(full_width = FALSE, position = "left")
```
  
  
From inspection above, it appears:  
1 = incoming  
2 = outgoing  
3, 5, 6 = rejected/missed/sent to voicemail - all have call duration of 0  
7 = mislabeled, 1 person in category and has call duration of 0  
8, 9 = mislabeled, all from subid 52  
10 = mislabeled, from subid 52 and 63 - call duration of 0  
1000 = mislabeled, from subid 82  
1001 = mislabeled, from subid 74 and 82  
1002 = mislabeled, from subid 74 and 82 - call duration of 0  
  
Labels according to SMS codebook:  
1 = incoming  
2 = outgoing  
3 = incoming/missed  
4 = incoming/voicemail  
5 = incoming/rejected  
6 = incoming/refused  
7 = no label  
8-10, 1000-1002 = unknown/undefined  
  
Analyes will use labels 1-6 & undefined until we determine how to proceed for labels 7-10/1000-1002.  
NOTE: not using unknown in label because do not want to confuse with being an unknown contact (contact 
types include spouse/significant other and friend) as these are undefined due to labeling error. 


```{r}
voice <- voice %>% 
  mutate(call_type = case_when(
    type == "1" ~ "incoming",
    type == "2" ~ "outgoing",
    type == "3" ~ "missed",
    type == "4" ~ "voicemail",
    type == "5" ~ "rejected",
    type == "6" ~ "refused",
    TRUE ~ "undefined"))

voice %>%
  mutate(call_type = fct_relevel(call_type, c("incoming", 
                                              "outgoing", 
                                              "missed", 
                                              "voicemail", 
                                              "rejected", 
                                              "refused", 
                                              "undefined"))) %>% 
  tabyl(call_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Type of voice call", 
        table.attr = "style='width:50%;'") %>%
  kable_styling(position = "left") 

voice %>%
  mutate(call_type = fct_relevel(call_type, c("incoming", 
                                              "outgoing", 
                                              "missed", 
                                              "voicemail", 
                                              "rejected", 
                                              "refused", 
                                              "undefined"))) %>% 
  ggplot(aes (x = call_type)) +
  geom_bar() +
  xlab("call type") +
  ggtitle("Frequency plot of type of participants' voice calls") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Total number of voice calls per participant
```{r}
voice %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of total voice calls") +
  ggtitle("Histogram of total voice calls per subject") +
  theme_classic()
```

Average number of calls per day (per participant)
```{r}
mean_avg_calls_per_day <- voice %>%                                                          
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_calls = mean(n_obs)) %>% 
  .$avg_calls %>% 
  mean()

max_calls_per_day <- voice %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(max = max(n_obs)) %>% 
  .$max %>% max()

voice %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_calls_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_calls_per_day)) +
  geom_histogram(bins = 15) +
  xlab("avg number of voice calls") +
  ggtitle("Histogram of average voice calls per day") +
  theme_classic()
```

On average, participants had an average of `r round(mean_avg_calls_per_day, 2)` voice calls per day 
(max = `r max_calls_per_day`).

Average number of calls per day (not including spam)
```{r}
mean_avg_calls_per_day_nospam <- voice_withoutspam %>%                                                          
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_calls = mean(n_obs)) %>% 
  .$avg_calls %>% 
  mean()

max_calls_per_day_nospam <- voice_withoutspam %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(max = max(n_obs)) %>% 
  .$max %>% max()

voice_withoutspam %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_calls_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_calls_per_day)) +
  geom_histogram(bins = 15) +
  xlab("avg number of non-spam voice calls") +
  ggtitle("Histogram of average non-spam voice calls per day") +
  theme_classic()
```

With spam calls removed, participants had an average of `r round(mean_avg_calls_per_day_nospam, 2)` 
voice calls per day (max = `r max_calls_per_day_nospam`).

Average number of incoming calls per day
```{r}
voice %>% 
  group_by(subid, date_central) %>% 
  filter(type == "1") %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_calls_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_calls_per_day)) +
  geom_histogram(bins = 15) +
  xlab("avg number of incoming voice calls") +
  ggtitle("Histogram of average incoming calls per day") +
  theme_classic()
```

Average number of outgoing calls per day
```{r}
voice %>% 
  group_by(subid, date_central) %>% 
  filter(type == "2") %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_calls_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_calls_per_day)) +
  geom_histogram(bins = 15) +
  xlab("avg number of outgoing voice calls") +
  ggtitle("Histogram of average outgoing calls per day") +
  theme_classic()
```

Length of call (in seconds)
```{r}
voice %>%
  ggplot(aes(x = duration)) +
  geom_histogram() +
  xlab("call duration (seconds)") +
  ggtitle("Histogram of length of voice calls") +
  theme_classic()
```

Calls with duration of 0 seconds
```{r}
duration_0 <- voice %>% 
  filter(duration == 0) 
```

`r nrow(duration_0)` calls (`r (round(nrow(duration_0)/nrow(voice), 4))*100`%) had a duration of 0 seconds. 

Contact relationship type
```{r}
voice %>%
  mutate(contact_type = tolower(contact_type),
         contact_type = fct_infreq(factor(contact_type))) %>% 
  tabyl(contact_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Relationship with voice call contact") %>%
  kable_styling(full_width = FALSE, position = "left")

voice %>%
  mutate(contact_type = tolower(contact_type),
         contact_type = fct_infreq(factor(contact_type))) %>%
  ggplot(aes (x = contact_type)) +
  geom_bar() +
  xlab("contact relationship type") +
  ggtitle("Frequency plot of contact relationship from voice call") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

`r sum(is.na(voice$contact_type))` voice calls (`r (round((sum(is.na(voice$contact_type)))/(nrow(voice)), 4))*100`%) 
were from unknown contacts. 

Number of calls from known contacts per participant
```{r}
voice %>%
  filter(!is.na(contact_type)) %>%
  group_by(subid) %>%
  summarise(n_obs = n()) %>%
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of calls from known contacts") +
  ggtitle("Histogram of voice calls with known contacts per subject") +
  theme_classic()
```

Number of calls from unknown contacts per participant (contact_type = NA)
```{r}
voice %>%
  filter(is.na(contact_type)) %>%
  group_by(subid) %>%
  summarise(n_obs = n()) %>%
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of calls from unknown contacts") +
  ggtitle("Histogram of voice calls with unknown contacts per subject") +
  theme_classic()
```

Number of calls from spam
```{r}
voice %>%
  filter(contact_type == "IRRELEVANT/SPAM") %>%
  group_by(subid) %>%
  summarise(n_obs = n()) %>%
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of calls from spam") +
  ggtitle("Histogram of number of spam voice calls per subject") +
  theme_classic()
```

Average call length by contact type
```{r}
voice %>%
  mutate(contact_type = tolower(contact_type),
         contact_type = fct_reorder(contact_type, desc(duration), .fun = "mean")) %>%
  group_by(contact_type) %>% 
  summarise(avg_duration = mean(duration)) %>% 
  ggplot(aes (x = contact_type, y = avg_duration)) +
  geom_col() +
  xlab("contact relationship type") +
  ylab("average duration of call (seconds)") +
  ggtitle("Plot of average call duration by contact type") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Average number of contacts per participant
```{r}
voice %>%
  group_by(subid) %>%
  mutate(n_contacts = n_distinct(phone))  %>%
  summarise(avg_contacts_per_sub = mean(n_contacts)) %>%
  ggplot(aes(x = avg_contacts_per_sub)) +
  geom_histogram(bins = 15) +
  xlab("avg number of contacts per participant") +
  ggtitle("Histogram of average number of voice contacts per participant") +
  theme_classic()
```

Average number of contacts per day (per participant)
```{r}
voice %>%
  group_by(subid, date_central) %>%
  mutate(n_contacts = n_distinct(phone))  %>%
  summarise(avg_contacts_perday = mean(n_contacts)) %>%
  ggplot(aes(x = avg_contacts_perday)) +
  geom_histogram(bins = 15) +
  xlab("avg number of contacts called each day") +
  ggtitle("Histogram of average number of contacts per day by participant") +
  theme_classic()
```


#### Context variables

Context analyses are run on dataframe with spam/irrelevant calls removed because these calls have
no context information.

Drank alcohol in past
```{r}
voice_withoutspam %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_relevel(factor(drank_past, c("never/almost never", "occasionally",
                                                        "almost always/always")))) %>%
  tabyl(drank_past, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Level of drinking with voice contact in the past") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_relevel(factor(drank_past, c("never/almost never", "occasionally",
                                                        "almost always/always")))) %>%
  ggplot(aes (x = drank_past)) +
  geom_bar() +
  xlab("past drinking status with contact") +
  ggtitle("Frequency plot of level of past drinking with voice contact") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Drinker status
```{r}
voice_withoutspam %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_relevel(factor(drinker_status, c("drinker", "nondrinker",
                                                        "dont know")))) %>%
  tabyl(drinker_status, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Drinking status of voice contact") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_relevel(factor(drinker_status, c("drinker", "nondrinker",
                                                        "dont know")))) %>%
  ggplot(aes (x = drinker_status)) +
  geom_bar() +
  xlab("drinking status of voice contact") +
  ggtitle("Frequency plot of the drinking status of participants' voice contacts") +
  theme_classic()
```

Drink in your presence 
```{r}
voice_withoutspam %>%
  mutate(drink_future = tolower(drink_future),
         drink_future = fct_relevel(factor(drink_future, c("yes", "no",
                                                        "uncerain")))) %>%
  tabyl(drink_future, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Is voice contact likely to drink in your presence?") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(drink_future = tolower(drink_future),
         drink_future = fct_relevel(factor(drink_future, c("yes", "no",
                                                        "uncertain")))) %>%
  ggplot(aes (x = drink_future)) +
  geom_bar() +
  xlab("likelihood of contact drinking in front of participant in future") +
  ggtitle("Frequency plot of likelihood contact will drink in front of participant in future") +
  theme_classic()
```

In recovery
```{r}
voice_withoutspam %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_relevel(factor(recovery, c("yes", "no",
                                                        "dont know")))) %>%
  tabyl(recovery, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Is voice contact in recovery?") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_relevel(factor(recovery, c("yes", "no",
                                                        "dont know")))) %>%
  ggplot(aes (x = recovery)) +
  geom_bar() +
  xlab("recovery status of voice contact") +
  ggtitle("Frequency plot of whether voice contact is in recovery") +
  theme_classic()
```

Support of recovery
```{r}
voice_withoutspam %>%
  mutate(support = tolower(support),
         support = fct_relevel(factor(support, c("supportive", "unsupportive", "mixed", 
                                                 "neutral", "dont know", "no")))) %>%
  tabyl(support, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contact's support of participant's recovery goals") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(support = tolower(support),
         support = fct_relevel(factor(support, c("supportive", "unsupportive", "mixed", 
                                                 "neutral", "dont know", "no")))) %>%
  ggplot(aes (x = support)) +
  geom_bar() +
  xlab("contact support of participant recovery") +
  ggtitle("Frequency plot of level of voice contacts' support of participants' recovery") +
  theme_classic()
```

Emotion from experiences with contact
```{r}
voice_withoutspam %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", 
                                                 "mixed", "neutral")))) %>%  
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Emotion from experiences with voice contact") %>%
  kable_styling(full_width = FALSE, position = "left")

voice_withoutspam %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", 
                                                 "mixed", "neutral")))) %>% 
  ggplot(aes (x = emotion)) +
  geom_bar() +
  xlab("emotion from experiences with voice contact") +
  ggtitle("Frequency plot of types of emotion participants feel from voice contact interactions") +
  theme_classic()
```
