---
title: "chk_dates"
author: "Ali Colmenares and Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---
### Notes
This script checks data from RISK participants' meaningful dates by computing descriptives and checking for missingness and potential errors


### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```

Paths
```{r}
path_data <- "./analysis/shared/data"
```

Packages
```{r}
library(janitor)
library(lubridate)
library(kableExtra)
library(tidyverse)
library(psych)
```


### Import Data and Glimpse

Dates report data
```{r}
dates <- read_rds(file.path(path_data, "ds_dates_report.rds")) %>% 
  glimpse()
```

Check for missing values
```{r}
if(any(is.na(dates))){
  missing <- dates %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There are `r nrow(dates)` date observations with no missing values.  
Dates are from `r length(unique(dates$subid))` uniques participants.  
KW: I thought sample size was about 154. Did we gather dates on all subids?  

### Overall Descriptives

Type of date
```{r}
dates %>%
  mutate(type = fct_infreq(factor(type))) %>% 
  tabyl(type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left") %>% 
  add_header_above(c("Type of meaningful dates" = 3))

dates %>%
  mutate(type = fct_infreq(factor(type))) %>%
  ggplot(aes (x = type)) +
  geom_bar() +
  xlab("date type") +
  ggtitle("Frequency plot of type of meaningful dates") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

KW: Do we have written responses for other? 

Most meaningful month
```{r}
dates %>% 
  mutate(month = month(date)) %>% 
  group_by(month) %>% 
  summarise(n_dates = n()) %>% 
  ggplot(aes(x = as.factor(month), y = n_dates)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  labs(x = "month",
       y = "frequency",
       title = "Bar plot of most meaningful dates by month")
```

December is the most meaningful month. Most likely due to holidays (see breakdown by type below).  

Types of dates in December
```{r}
dates %>% 
  mutate(month = month(date)) %>% 
  filter(month == 12) %>% 
  group_by(type) %>% 
  summarise(n_dates = n()) %>% 
  arrange(desc(n_dates)) %>% 
  kable(table.attr = "style='width:60%;'") %>% 
  kable_styling(position = "left") %>% 
  add_header_above(c("December date types" = 2))
```


### Participant Averages

Dates per participant
```{r}
dates_per_par <- dates %>% 
  group_by(subid) %>% 
  summarise(n_dates = n())

describe(dates_per_par$n_dates) %>% 
  kable() %>% 
  kable_styling() %>% 
  add_header_above(c("Dates per participant statistics" = 14))

dates_per_par %>% 
  ggplot(aes(x = n_dates)) +
  geom_histogram() +
  theme_classic() +
  labs(x = "number of dates per participant",
       title = "Histogram of number of meaningful dates per participant")
```

Participants with over 20 meaningful dates
```{r}
subs_over20 <- dates_per_par %>% 
  filter(n_dates > 20)

dates %>% 
  filter(subid %in% subs_over20$subid) %>% 
  group_by(subid, type) %>% 
  summarise(n_dates = n()) %>% 
  kable(table.attr = "style='width:60%;'", align = "l") %>% 
  kable_styling(position = "left") %>% 
  add_header_above(c("Participants with over 20 dates" = 3))

```

One participant (subid 18) has `r max(subs_over20$n_dates)` dates. 12 of these are labeled "Other".  
One participant (subid 243) has `r min(subs_over20$n_dates)` dates. 8 of which are labeled "Other".

