---
title: "Checking SMS Data"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
 
This script checks data from RISK participants' sms messages by computing descriptives and checking for 
missingness and potential errors. 
  
Thoughts for discussion:  
1. Many of the most relevant words that come up in the plots at the end of the script are in Spanish. This 
may be making them appear more "relevant" by the tf-idf metric. We should discuss possibly translating 
these words or another way to work around this. Will look into how to find percentage of words that are 
not English.
  

### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths 
```{r}
path_data <- "./analysis/shared/data"
```

Packages
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
library(psych)
library(tidytext)
library(tm)
library(textclean)
library(textrecipes)
```


### Import Data and glimpse 

SMS data
```{r}
sms <- read_rds(file.path(path_data, "ds_sms.rds"))  
sms <- sms %>%
  mutate(time_central = as_datetime(utc, tz = 'America/Chicago')) %>%
  mutate(date_central = date(time_central), 
         hour_central = hour(time_central),
         minute_central = minute(time_central), 
         second_central = second(time_central)) %>%
  select(-c(utc, time_central)) %>%
  glimpse()
```

Check for SurveySignal/automated messages from study
```{r}
surveysignal_count <- sms %>% 
  filter(str_detect(text, "surveysignal")) %>% 
  select(subid, phone, contact_type, text) 

surveysignal_count %>%
  head(n = 30) %>% 
  kable(caption = "Preview of messages containing surveysignal") %>% 
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")

surveysignal_per_sub <- surveysignal_count %>% 
  group_by(subid) %>% 
  summarise(n = n())

surveysignal_per_sub %>% 
  kable(caption = "Number of surveysignal messages per participant", table.attr = "style='width:30%;'") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed")
```

Remove `r nrow(surveysignal_count)` messages that contain surveysignal and have contact_type = irrelevant 
from a total of `r nrow(surveysignal_per_sub)` participants.   
ASSUMPTION = these are study messages  

Final dataset
```{r}
sms <- sms %>% 
  filter(!(str_detect(text, "surveysignal")) & contact_type != "IRRELEVANT/SPAM") %>% 
  glimpse()
```

`r length(unique(sms$subid))` participants contribute to a total of `r nrow(sms)` sms observations.  
The earliest recorded sms message is from `r min(sms$date_central)` and the last is from `r max(sms$date_central)`.  

Blank messages
```{r}
sms_blank <- sms %>%
  filter(text == "")

sms_blank %>% 
  group_by(contact_type) %>% 
  summarise(n_obs = n()) %>% 
  arrange(desc(n_obs)) %>% 
  kable(caption = "Number of blank messages by contact type") %>% 
  kable_styling(full_width = FALSE, position = "left")
```

`r n_distinct(sms_blank$subid)` participants contributed to `r nrow(sms_blank)` blank text messages.   
`r nrow(subset(sms_blank, contact_type == NA))` of the blank messages are from unknown contacts.  

Missing (NA) values
```{r}
if(any(is.na(sms))){
  missing <- sms %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```

There are `r sum(is.na(sms))` missing values (NA) from `r length(missing$var)` unique 
variables in the entire dataset.


Pull unique contacts for descriptive analysis
```{r}
sms_uniq <- sms %>% 
  select(-c(text, type, date_central, hour_central, minute_central, second_central)) %>% 
  distinct()
```

`r nrow(sms_uniq)` unique



### Untokenized data

#### Descriptives
##### Overall

Type of sms
```{r}
sms %>% 
  mutate(sms_type = case_when(
    type == "1" ~ "incoming", 
    type == "2" ~ "outgoing",
    type == "3" ~ "incoming, missed", 
    type == "4" ~ "incoming, voicemail",
    type == "5" ~ "incoming, rejected")) %>%
  tabyl(sms_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Type of sms message") %>%
  kable_styling(full_width = FALSE, position = "left")
```

`r nrow(subset(sms, type == "3"))` sms messages were labeled as incoming - missed, `r nrow(subset(sms, type == "4"))`
messages were labeled as incoming - voicemail, and `r nrow(subset(sms, type == "5"))` messages were marked as incoming -
rejected. These three categories will subsequently be collapsed into the incoming category (see below).  

```{r}
sms <- sms %>% 
  mutate(sms_type = case_when(
    type == "1" ~ "incoming",
    type == "3" ~ "incoming",
    type == "4" ~ "incoming",
    type == "5" ~ "incoming",
    type == "2" ~ "outgoing"))

sms %>%
  tabyl(sms_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Type of sms message") %>%
  kable_styling(full_width = FALSE, position = "left") 
```

Contact relationship
```{r}
sms_uniq %>%
  mutate(contact_type = tolower(contact_type),
         contact_type = fct_infreq(factor(contact_type))) %>% 
  tabyl(contact_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Relationship with sms contact") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(contact_type = tolower(contact_type),
         contact_type = fct_infreq(factor(contact_type))) %>%
  ggplot(aes (x = contact_type)) +
  geom_bar() +
  xlab("contact relationship type") +
  ggtitle("Frequency plot of contact relationship from sms messages") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

`r sum(is.na(sms$contact_type))` sms messages (`r (round((sum(is.na(sms$contact_type)))/(nrow(sms)), 4))*100`%) 
were from unknown contacts.  

Drank alcohol in past
```{r}
sms %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_relevel(factor(drank_past, c("never/almost never", "occasionally",
                                                        "almost always/always")))) %>%
  tabyl(drank_past, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Level of drinking with sms contact in the past") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_relevel(factor(drank_past, c("never/almost never", "occasionally",
                                                        "almost always/always")))) %>%
  ggplot(aes (x = drank_past)) +
  geom_bar() +
  xlab("past drinking status with contact") +
  ggtitle("Frequency plot of level of past drinking with sms contact") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Drinker status
```{r}
sms %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_relevel(factor(drinker_status, c("drinker", "nondrinker",
                                                        "dont know")))) %>%
  tabyl(drinker_status, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Drinking status of sms contact") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_relevel(factor(drinker_status, c("drinker", "nondrinker",
                                                        "dont know")))) %>%
  ggplot(aes (x = drinker_status)) +
  geom_bar() +
  xlab("drinking status of sms contact") +
  ggtitle("Frequency plot of the drinking status of participants' sms contacts") +
  theme_classic()
```

Drink in your presence 
```{r}
sms %>%
  mutate(drink_future = tolower(drink_future),
         drink_future = fct_relevel(factor(drink_future, c("yes", "no",
                                                        "uncerain")))) %>%
  tabyl(drink_future, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Is sms contact likely to drink in your presence?") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(drink_future = tolower(drink_future),
         drink_future = fct_relevel(factor(drink_future, c("yes", "no",
                                                        "uncertain")))) %>%
  ggplot(aes (x = drink_future)) +
  geom_bar() +
  xlab("likelihood of contact drinking in front of participant in future") +
  ggtitle("Frequency plot of likelihood contact will drink in front of participant in future") +
  theme_classic()
```

In recovery
```{r}
sms %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_relevel(factor(recovery, c("yes", "no",
                                                        "dont know")))) %>%
  tabyl(recovery, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Is sms contact in recovery?") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_relevel(factor(recovery, c("yes", "no",
                                                        "dont know")))) %>%
  ggplot(aes (x = recovery)) +
  geom_bar() +
  xlab("recovery status of sms contact") +
  ggtitle("Frequency plot of whether sms contact is in recovery") +
  theme_classic()
```

Support of recovery
```{r}
sms %>%
  mutate(support = tolower(support),
         support = fct_relevel(factor(support, c("supportive", "unsupportive", "mixed", 
                                                 "neutral", "dont know", "no")))) %>%
  tabyl(support, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contact's support of participant's recovery goals") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(support = tolower(support),
         support = fct_relevel(factor(support, c("supportive", "unsupportive", "mixed", 
                                                 "neutral", "dont know", "no")))) %>%
  ggplot(aes (x = support)) +
  geom_bar() +
  xlab("contact support of participant recovery") +
  ggtitle("Frequency plot of level of sms contacts' support of participants' recovery") +
  theme_classic()
```


COMMENT KW 2020-08-06: (support) Not sure what "no" is because question is double-barrelled and no is not 
an answer on codebook. Question = "Do they know about your recovery goals and if so are they supportive?"
No possibly means they do not know about participant's recovery goals. But then does "don't know" mean
participant doesn't know if they know about their recovery goals or doesn't know if they are supportive?

HM: Agree that this is a badly written Q, and unfortunately there isn't anything we can do about that now, except to make sure that we keep this ambiguity in mind as we do analyses. This item does capture whether a contact is actively supportive (knows + supports), but the negative case, as you note, is heterogenous(doesn't know; knows + doesn't support),  


Emotion from experiences with contact
```{r}
sms %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", 
                                                 "mixed", "neutral")))) %>%  
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Emotion from experiences with sms contact") %>%
  kable_styling(full_width = FALSE, position = "left")

sms %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_relevel(factor(emotion, c("pleasant", "unpleasant", 
                                                 "mixed", "neutral")))) %>% 
  ggplot(aes (x = emotion)) +
  geom_bar() +
  xlab("emotion from experiences with sms contact") +
  ggtitle("Frequency plot of types of emotion participants feel from sms contact interactions") +
  theme_classic()
```


##### Per subject
Number of messages (sent, received, total)
```{r}
sms %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of total sms messages") +
  ggtitle("Histogram of total sms messages per subject") +
  theme_classic()

sms %>% 
  group_by(subid) %>% 
  filter(type == 1) %>%
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of incoming sms messages") +
  ggtitle("Histogram of incoming sms messages per subject") +
  theme_classic()

sms %>% 
  group_by(subid) %>% 
  filter(type == 2) %>%
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 15) +
  xlab("number of outgoing sms messages") +
  ggtitle("Histogram of outgoing sms messages per subject") +
  theme_classic()
```

Average number of messages per day
```{r}
mean_avg_sms_per_day <- sms %>%                                                          
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_sms_per_day = mean(n_obs)) %>% 
  .$avg_sms_per_day %>% 
  mean()

max_sms_per_day <- sms %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(max = max(n_obs)) %>% 
  .$max %>% max()

sms %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_sms_per_day = mean(n_obs)) %>% 
  ggplot(aes(x = avg_sms_per_day)) +
  geom_histogram(bins = 15) +
  xlab("avg number of sms messages") +
  ggtitle("Histogram of average sms messages per day") +
  theme_classic()
```

On average, participants had an average of `r round(mean_avg_sms_per_day, 2)` sms messages per day (max = `r max_sms_per_day`).  

Average number of messages per contact (phone number)
```{r}
sms %>% 
  group_by(subid, phone) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_sms_per_contact = mean(n_obs)) %>% 
  ggplot(aes(x = avg_sms_per_contact)) +
  geom_histogram(bins = 15) +
  xlab("avg number of sms messages per contact") +
  ggtitle("Histogram of average sms messages per contact") +
  theme_classic()
```

Average number of contacts per participant
```{r}
sms %>%
  group_by(subid) %>%
  mutate(n_contacts = n_distinct(phone))  %>%
  summarise(avg_contacts_per_sub = mean(n_contacts)) %>%
  ggplot(aes(x = avg_contacts_per_sub)) +
  geom_histogram(bins = 15) +
  xlab("avg number of contacts per participant") +
  ggtitle("Histogram of average number of sms contacts per participant") +
  theme_classic()
```

Average number of contacts messaged each day
```{r}
sms %>%
  group_by(subid, date_central) %>%
  mutate(n_contacts = n_distinct(phone))  %>%
  summarise(avg_contacts_perday = mean(n_contacts)) %>%
  ggplot(aes(x = avg_contacts_perday)) +
  geom_histogram(bins = 15) +
  xlab("avg number of contacts messaged each day") +
  ggtitle("Histogram of average number of contacts messaged each day") +
  theme_classic()
```

<!-- Removed due to 100% of contacts being known contacts now. -->
<!-- Average number of messages from known contacts -->
<!-- ```{r} -->
<!-- sms %>%  -->
<!--   filter(!is.na(contact_type)) %>%  -->
<!--   group_by(subid) %>%  -->
<!--   summarise(n_obs = n()) %>%  -->
<!--   ggplot(aes(x = n_obs)) + -->
<!--   geom_histogram(bins = 15) + -->
<!--   xlab("number of messages from known contacts") + -->
<!--   ggtitle("Histogram of sms messages with known contacts per subject") + -->
<!--   theme_classic() -->
<!-- ``` -->

<!-- Messages from unknown contacts (contact_type = NA) -->
<!-- ```{r} -->
<!-- sms %>%  -->
<!--   filter(is.na(contact_type)) %>%  -->
<!--   group_by(subid) %>%  -->
<!--   summarise(n_obs = n()) %>%  -->
<!--   ggplot(aes(x = n_obs)) + -->
<!--   geom_histogram(bins = 15) + -->
<!--   xlab("number of messages from unknown contacts") + -->
<!--   ggtitle("Histogram of sms messages with unknown contacts per subject") + -->
<!--   theme_classic() -->
<!-- ``` -->


### Tidy text data

Basic text cleaning
```{r}
sms_tidy <- sms %>% 
      mutate(text = removeNumbers(text)) %>%
      mutate(text = tolower(text))%>% 
      mutate(text = removePunctuation(text)) %>% 
      mutate(text = replace_symbol(text)) %>% 
      mutate(text = stripWhitespace(text)) # condenses whitespace into a single space

# Remove blank sms messages for word count statistics
sms_tidy <- sms_tidy %>% 
  filter(!text == " " & !text == "") 
```

Tokenize tidy text data
```{r}
sms_tidy <- sms_tidy %>% 
  unnest_tokens(word, text) %>% 
  glimpse()
```

Get word counts and tf_idf
```{r}
sms_features <- sms_tidy %>%
  anti_join(get_stopwords(), by = "word") %>%
  count(subid, word) %>%
  bind_tf_idf(word, subid, n) %>%
  glimpse()
```


#### Descriptives

Number of unique words used by subid
```{r}
unique_words <- sms_tidy %>%
  group_by(subid) %>%
  summarize(n_unique_words = n_distinct(word)) 

describe(unique_words$n_unique_words) %>%
  kable(caption = "Number of unique words per participant") %>%
  kable_styling()

unique_words %>%
  ggplot(aes(x = n_unique_words)) +
  geom_histogram(bins = 15) +
  xlab("number of unique words per participant") +
  ggtitle("Histogram of participants' number of unique words in sms messages") +
  theme_classic()
```

Most common words by participant
```{r}
sms_words <- sms_tidy %>% 
  count(subid, word, sort = TRUE) %>% 
  bind_tf_idf(word, subid, n)

sms_words %>%
  arrange(desc(n)) %>%
  head(n = 20) %>%
  kable(caption = "Most common words by frequency (n)") %>% 
  kable_styling(full_width = FALSE, position = "left")

sms_words %>%
  arrange(desc(tf_idf)) %>%
  head(n = 20) %>%
  kable(caption = "Most relevant words by tf_idf") %>% 
  kable_styling(full_width = FALSE, position = "left")

sms_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  top_n(25, tf_idf) %>%
  ggplot(aes(word, tf_idf, fill = subid)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Twenty-five most relevant words by tf_idf") +
  coord_flip() +
  theme_classic()
```

Remove irrelevant top words

Word selection for stopwords is temporary as experimentation. Can determine system for selecting
stopwords in future.

```{r}
mystopwords <- data_frame(word = c("gm", "ns", "mal"))

sms_words <- anti_join(sms_words, mystopwords, by = "word")

sms_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  top_n(25, tf_idf) %>%
  ggplot(aes(word, tf_idf, fill = subid)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Twenty-five most relevant words by tf_idf") +
  coord_flip() +
  theme_classic()
```

Example of top ten words (tf-idf) from a single participant
```{r}
sms_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 215) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 215") %>% 
  kable_styling(full_width = FALSE, position = "left")

sms_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 143) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 143") %>% 
  kable_styling(full_width = FALSE, position = "left")

sms_words %>%
  arrange(desc(tf_idf)) %>%
  filter(subid == 15) %>% 
  head(n = 10) %>%
  kable(caption = "Subid 15") %>% 
  kable_styling(full_width = FALSE, position = "left")
```

Top words (tf-idf) by contact_type
```{r dpi = 200}
sms_contact <- sms_tidy %>% 
  count(contact_type, word) %>% 
  bind_tf_idf(word, contact_type, n) %>% 
  arrange(desc(tf_idf))

sms_contact %>%
  group_by(contact_type) %>% 
  top_n(8, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = contact_type)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top words by contact relationship type") +
  facet_wrap(~contact_type, ncol = 4, scales = "free") +
  coord_flip() +
  theme_classic()
```

Remove stop words

Word selection for stopwords is temporary as experimentation. Can determine system for selecting
stopwords in future.

```{r dpi = 200}
mystopwords <- data_frame(word = c("los", "will", "oh", "vr", "she", "igc", "dps", "pvp", 
                                   "from", "seb", "bgs", "ill"))

sms_contact <- anti_join(sms_contact, mystopwords, by = "word")

sms_contact %>%
  group_by(contact_type) %>% 
  top_n(8, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = contact_type)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top words by contact relationship type") +
  facet_wrap(~contact_type, ncol = 4, scales = "free") +
  coord_flip() +
  theme_classic()
```


Top words (tf-idf) by contact drinking status
```{r}
sms_drinker <- sms_tidy %>%
  count(drinker_status, word) %>% 
  bind_tf_idf(word, drinker_status, n) %>% 
  arrange(desc(tf_idf))

sms_drinker %>%
  group_by(drinker_status) %>% 
  top_n(25, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = drinker_status)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 25 words by drinking status of contact") +
  facet_wrap(~drinker_status, scales = "free") +
  coord_flip() +
  theme_classic()
```

Working on getting NAs to show on facet_wrap as its own factor level. (causing warning message as is)

Remove stop words --> experimentation
```{r}
mystopwords <- data_frame(word = c("asra", "atd", "phos", "adol", "tca", "sut", "nav", "dps", 
                                   "pvp", "bgs"))

sms_drinker <- anti_join(sms_drinker, mystopwords, by = "word")

sms_drinker %>%
  group_by(drinker_status) %>% 
  top_n(25, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = drinker_status)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 25 words by drinking status of contact") +
  facet_wrap(~drinker_status, scales = "free") +
  coord_flip() +
  theme_classic()
```

Top words (tf-idf) by past drinking with contact
```{r}
sms_drankpast <- sms_tidy %>%
  count(drank_past, word) %>% 
  bind_tf_idf(word, drank_past, n) %>% 
  arrange(desc(tf_idf))

sms_drankpast %>%
  group_by(drank_past) %>% 
  top_n(25, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = drank_past)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 25 words by past drinking history with contact") +
  facet_wrap(~drank_past, scales = "free") +
  coord_flip() +
  theme_classic()
```

Top words (tf-idf) by likelihood of contact drinking in front of sub in future
```{r}
sms_drinkfuture <- sms_tidy %>%
  count(drink_future, word) %>% 
  bind_tf_idf(word, drink_future, n) %>% 
  arrange(desc(tf_idf))

sms_drinkfuture %>%
  group_by(drink_future) %>% 
  top_n(25, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = drink_future)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 25 words by likeliness to drink in front of sub in future") +
  facet_wrap(~drink_future, scales = "free") +
  coord_flip() +
  theme_classic()
```

Top words (tf-idf) by recovery status of contact
```{r}
sms_recovery <- sms_tidy %>%
  count(recovery, word) %>% 
  bind_tf_idf(word, recovery, n) %>% 
  arrange(desc(tf_idf))

sms_recovery %>%
  group_by(recovery) %>% 
  top_n(25, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = recovery)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 25 words by recovery status of contact") +
  facet_wrap(~recovery, scales = "free") +
  coord_flip() +
  theme_classic()
```

Top words (tf-idf) by support provided by contact
```{r}
sms_support <- sms_tidy %>%
  count(support, word) %>% 
  bind_tf_idf(word, support, n) %>% 
  arrange(desc(tf_idf))

sms_support %>%
  group_by(support) %>% 
  top_n(20, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = support)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 20 words by support provided by contact") +
  facet_wrap(~support, scales = "free") +
  coord_flip() +
  theme_classic()
```

Top words (tf-idf) by emotion from interactions with contact
```{r}
sms_emotion <- sms_tidy %>%
  count(emotion, word) %>% 
  bind_tf_idf(word, emotion, n) %>% 
  arrange(desc(tf_idf))

sms_emotion %>%
  group_by(emotion) %>% 
  top_n(20, tf_idf) %>% 
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>% 
  ggplot(aes(word, tf_idf, fill = emotion)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf", title = "Top 20 words by emotion from interactions with contact") +
  facet_wrap(~emotion, scales = "free") +
  coord_flip() +
  theme_classic()
```


### Document Term Matrix

Create dtm
```{r}
(sms_dtm <- sms_features %>%
  cast_dtm(subid, word, tf_idf))
```

Matrix is 96% sparse. This means 96% of document-word pairs are zero.