---
title: "Checking GPS Data"
author: "Hannah Moshontz and Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes

This script checks data from RISK participants' gps observations by computing descriptives and checking for missingness and potential errors.

### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```
  
Paths
```{r}
path_data <- "./analysis/shared/data"
```
  
Packages
```{r}
library(tidyverse)
library(janitor)
library(psych)
library(lubridate)
library(kableExtra)
library(readxl)
library(data.table)
library(ggplot2)
```

  
### Import Data and glimpse()
  
GPS data
```{r}
gps <- read_rds(file.path(path_data, "ds_gps.rds")) %>%  
  as.data.table() %>% #using data.table because this is a large file and dt is faster with big files
  glimpse()

gps <- gps %>%
  mutate(date_central = date(time_central), 
         hour_central = hour(time_central),
         subid = as.double(subid))
```
  
Staff notes
```{r}
gps_notes <- read_xlsx(file.path("./analysis/notes/gps_review_notes.xlsx")) %>%
  clean_names("snake") %>%
    glimpse()
```
  
Visit dates
```{r}
visits <- read_rds(file.path(path_data, "ds_visits.rds")) %>% 
  mutate(n_study_days = as.numeric( #calculate days on study
    difftime(end_study, start_study, units = "days")) + 1) %>%
  glimpse()
```

Location reports
```{r}
locations <- read_rds(file.path(path_data, "ds_locations_report.rds")) %>% 
  select(subid, city, state, type, drank, alcohol, emotion, risk, avoid, vacation, 
         long, lat, utc) %>% 
  mutate(type = tolower(type),
         drank = tolower(drank),
         alcohol = tolower(alcohol),
         emotion = tolower(emotion),
         risk = tolower(risk),
         avoid = tolower(avoid),
         vacation = tolower(vacation)) %>% 
  mutate(state = case_when(state == "Wi" ~ "WI",
                           TRUE ~ state)) %>% #FIX in processing and then remove
  glimpse() 

## ERROR NOTE -- there's a typo. Subject 242's place of work is listed as being in the state of "Wi" rather than "WI"

```

    
There are `r length(unique(gps$subid))` subjects contributing `r nrow(gps)` gps observations. 

We have notes from staff on `r length(na.omit(gotes$notes))` subjects.



### Descriptives
  
#### Continuous variables
```{r}
gps %>% 
  select(next_time, next_dist, hour_central) %>% 
  mutate(next_time = as.numeric(next_time)) %>% 
  describe(na.rm = TRUE)
```

Next time is extremely skewed, as in next distance, suggesting that there are some major gaps in gps.


#### Data type
```{r}
gps %>% 
  tabyl(data_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")

gps %>% 
  tabyl(data_type, app_source, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

The vast majority of gps observations were labeled as gps as opposed to network-type observations. Only followmee produced network-type observations.

#### App source
```{r}
gps %>% 
  tabyl(app_source, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

About half of observations came from each app.

#### Known place types
```{r}
gps %>% 
  mutate(known_place_type = tolower(known_place_type)) %>% 
  tabyl(known_place_type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

The majority of gps observations are not associated with a known place. 

#### Place qualities: drank

```{r}
locations %>% 
  tabyl(drank, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places were places where participants had not drank previously.

```{r}
gps %>% 
  mutate(drank = tolower(drank)) %>% 
  tabyl(drank, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Gps observations at known places were a roughly equal mix of visits to places where participants had drank and those they had not.

#### Place qualities: alcohol

```{r}
locations %>% 
  tabyl(alcohol, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Of known places, the slight majority were places where alcohol was not available.

```{r}
gps %>% 
  mutate(alcohol = tolower(alcohol)) %>% 
  tabyl(alcohol, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Of gps observations at known places, a slight majority were at places where alcohol was not available compared places where alcohol was available.

#### Place qualities: risk
```{r}
locations %>% 
  tabyl(risk, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places posed no risk to participants' sobriety.

```{r}
gps %>% 
  mutate(risk = tolower(risk)) %>% 
  tabyl(risk, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Gps observations at known places were often at places that posed no or low risk to their sobriety.

#### Place qualities: avoid
```{r}
locations %>% 
  tabyl(avoid, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places were places participants were not avoiding.

```{r}
gps %>% 
  mutate(avoid = tolower(avoid)) %>% 
  tabyl(avoid, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

People rarely went to places that they were avoiding.

#### Place qualities: emotion
```{r}
locations %>% 
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places were rated as pleasant.

```{r}
gps %>%
  mutate(emotion = tolower(emotion)) %>% 
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Gps observations at known places were often at places rated as pleasant (rather than neutral, mixed, or unpleasant).


#### Place qualities: vacation
```{r}
locations %>% 
  tabyl(vacation, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places were not associated with a vacation.

```{r}
gps %>% 
  mutate(known_vacation = tolower(known_vacation)) %>% 
  tabyl(known_vacation, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Almost all gps observations were not associated with a vacation.

#### Place qualities: city and state

```{r}
locations %>% 
  count(state, sort = TRUE) %>% 
  kable(label = "State frequencies of all known places") %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")

locations %>% 
  filter(vacation == "no") %>% 
  count(state, sort = TRUE) %>% 
  kable(label = "State frequencies of known places not associated with vacation") %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most known places are in WI. A few are outside of the continental US (Mexico and Hawaii). All known places outside of the US are associated with a vacation.

```{r}
#used this video to help guide my map exploration https://youtu.be/O1oDIQV6VKU
locations %>% 
  filter(state != "Mexico", state != "HI") %>% #focusing just on continental US
  ggplot(aes(long, lat, color = vacation)) +
  geom_point() +
  borders("state") +
  coord_map() +
  theme_void() +
  ggtitle("Map of known places in the continental US, by vacation")
```

Map of known places helps us see some low frequency US states, and suggests that the vacation label doesn't cover all travel (e.g., work-related travel).

```{r}
gps %>%
  filter(lat >= 25, long >= -120) %>% #restricting to continental US
  ggplot(aes(long, lat)) +
  geom_point() + 
  borders("state") +
  coord_map() +
  theme_void() +
  ggtitle("Map of gps observations in the continental US")
```

Map of all GPS observations is hard to make sense of because frequency is not well-represented.

```{r}
gps_averaged <- gps %>% #calculating each person's centroid
  group_by(subid) %>% 
  summarize(n_obs = n(),
            long_avg = mean(long),
            lat_avg = mean(lat),
            long_sd = sd(long),
            lat_sd = sd(lat))

gps_averaged %>% #mapping centroids
  ggplot(aes(long_avg, lat_avg)) +
  geom_point() + 
  borders("state") +
  coord_map() +
  theme_void() +
  ggtitle("Map of gps observation centroids per subject")
```
Most people spent most of their time in the Madison, WI area.

#### Place qualities: home

```{r}
locations %>% 
  group_by(subid) %>%
  filter(type == "home") %>% 
  summarize(number_of_homes = n()) %>% 
  ungroup() %>% 
  tabyl(number_of_homes) %>% 
  kable(label = "Frequencies of known places per subject categorized as home") %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most people had one known place that they categorized as their home.

```{r}
subjects_with_twoplus_homes <- locations %>% 
  group_by(subid) %>%
  filter(type == "home") %>% 
  summarize(number_of_homes = n()) %>% 
  filter(number_of_homes > 1) %>% 
  pull(subid)

locations %>%
  filter(subid %in% subjects_with_twoplus_homes,
         type == "home") %>% #restricting to continental US
  mutate(subid = as.factor(subid)) %>% 
  ggplot(aes(long, lat, color = subid)) +
  geom_point() + 
  borders("state", "WI") +
  coord_map() +
  theme_void() +
  ggtitle("Map of the homes of subjects with multiple homes")
```

Multiple homes appear to be due to in-town moves (rather than second homes or errors).

```{r}
locations %>% 
    filter(subid %in% subjects_with_twoplus_homes,
         type == "home") %>%
  mutate(time_central = as_datetime(utc, tz = "America/Chicago")) %>% 
  group_by(subid) %>% 
  mutate(previous_home_time = lag(time_central),
         homes_sep_in_time = case_when(previous_home_time < time_central ~ "yes",
                                       previous_home_time == time_central ~ "no")) %>% 
  select(subid, type, long, lat, time_central, homes_sep_in_time) %>% 
  filter(!is.na(homes_sep_in_time)) %>% 
  tabyl(homes_sep_in_time) %>% 
  kable(label = "Frequencies of whether second home reported in a session after the first home reported among subjects with multiple homes") %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```

Most people with multiple homes reported their second home after their first (e.g., first home was reported on intake, second home was reported at a follow-up).

```{r, results = FALSE}
locations %>% 
  filter(subid %in% subjects_with_twoplus_homes,
         type == "home") %>% 
  mutate(report_date = date(as_datetime(utc))) %>% 
  left_join(
    visits %>% 
      filter(subid %in% subjects_with_twoplus_homes) %>% 
      select(subid, intake, followup1, followup2, final_visit) %>% 
      pivot_longer(c(intake, followup1, followup2, final_visit),
                   names_to = "visit_type",
                   values_to = "report_date"),
    by = c("subid", "report_date")) %>% 
  select(subid, city, state, long, lat, report_date, visit_type) 
```

Some people reported multiple homes in the same visit; they may have moved during that month.

### Frequency of GPS Sampling 
  
Plots Overall
```{r}
gps %>% 
  mutate(next_time = ifelse(
    (as.numeric(next_time) > 180), 
    181, next_time)) %>% 
  ggplot(aes(x = as.numeric(next_time))) +
  geom_histogram(bins = 10) +
  xlab("time between gps observations (minutes)") +
  ggtitle("Histogram of gps sampling rate (truncated at 3 hours)") +
  theme_classic()

gps %>% 
  filter(next_time < 15) %>% 
  ggplot(aes(x = as.numeric(next_time))) +
  geom_histogram(bins = 10) +
  xlab("time between gps observations (minutes)") +
  ggtitle("Histogram of gps sampling rate (less than 15 mins)") +
  theme_classic()


gps %>% 
  filter(next_time < 5) %>% 
  ggplot(aes(x = as.numeric(next_time))) +
  geom_histogram(bins = 10) +
  xlab("time between gps observations (minutes)") +
  ggtitle("Histogram of gps sampling rate (less than 5 mins)") + 
  theme_classic()

```

On average, gps was sampled every `r round(mean(as.numeric(gps$next_time), na.rm = TRUE), 2)` minutes.z
  
By app
```{r}
gps %>% 
  filter(!is.na(app_source)) %>% 
  mutate(next_time = ifelse(
    (as.numeric(next_time) > 180), 
    181, next_time)) %>% 
  ggplot(aes(x = as.numeric(next_time))) + 
  facet_grid(.~app_source) +
  geom_histogram(bins = 10) +
  xlab("time between gps observations (minutes)") +
  ggtitle("Histogram of gps sampling rate (truncated at 3 hours)") +
  theme_classic()

gps %>% 
  filter(!is.na(app_source), next_time < 5)  %>% 
  ggplot(aes(x = as.numeric(next_time))) + 
  facet_grid(.~app_source) +
  geom_histogram(bins = 10) +
  xlab("time between gps observations (minutes)") +
  ggtitle("Histogram of gps sampling rate (less than 5 minutes)") +
  theme_classic()
```

Sampling rates differed by app. For moves, gps was sampled every `r round(mean(as.numeric(gps$next_time[which(gps$app_source == "moves")]), na.rm = TRUE), 2)` minutes on average. For followmee, gps was sampled every `r round(mean(as.numeric(gps$next_time[which(gps$app_source == "followmee")]), na.rm = TRUE), 2)` minutes on average.
  
### Geographic Spacing of Consecutive GPS Observations 
  
Plots Overall
```{r}
gps %>% 
  ggplot(aes(x = round(next_dist, 2))) +
  geom_histogram(bins = 10) +
  xlab("distance between gps observations (meters)") +
  ggtitle("Histogram of gps sampling distance") +
  theme_classic()

gps %>% 
  filter(next_dist < 2000) %>% 
  ggplot(aes(x = round(next_dist, 2))) +
  geom_histogram(bins = 10) +
  xlab("distance between gps observations (meters)") +
  ggtitle("Histogram of gps sampling distance (less than 2000m)") +
  theme_classic()
```

The median gps sampling distance was `r round(median(gps$next_dist, na.rm = TRUE), 2)` meters.

By app
```{r}
gps %>% 
  filter(!is.na(app_source), next_dist < 2000) %>% 
  ggplot(aes(x = next_dist)) + 
  facet_grid(.~app_source) +
  geom_histogram(bins = 10) +
  xlab("distance between gps observations (meters)") +
  ggtitle("Histogram of gps sampling distance (less than 2000m") +
  theme_classic()
```

Sampling distnace differed by app. For moves, median distance between gps observations was `r round(median(gps$next_dist[which(gps$app_source == "moves")], na.rm = TRUE), 2)`. For followmee, median distance between gps observations `r round(median(gps$next_dist[which(gps$app_source == "followmee")], na.rm = TRUE), 2)`

### Null Island

```{r}
gps %>% 
  filter(lat <= 1 & long <= 1, lat >= -1 & long >= -1)
```
  
There are no (0,0) GPS observations.
  
### Number of Observations per Person

```{r}
gps %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 10) +
  xlab("number of gps observations") +
  ggtitle("Histogram of gps observations per subject") +
  theme_classic()

gps %>% 
  filter(!is.na(known_place_id)) %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 10) +
  xlab("number of known places") +
  ggtitle("Histogram of gps known-place observations per subject") +
  theme_classic()
```

  
### Number of Observations per Non-Missing Day

```{r}
mean_avg_obs_per_day <- gps %>%    
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_obs_per_day = mean(n_obs)) %>% 
  .$avg_obs_per_day %>% 
  mean()

max_obs_per_day <- gps %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>% 
  summarise(avg_obs_per_day = mean(n_obs),
            sd = sd(n_obs),
            min = min(n_obs),
            max = max(n_obs)) %>% 
  .$max %>% max()
```

On average, participants provided an average of `r mean_avg_obs_per_day` observations per non-missing day (max = `r max_obs_per_day`).

```{r}
gps %>% 
  group_by(subid, date_central) %>% 
  summarise(n_obs = n()) %>% 
  group_by(subid) %>%
  summarise(avg_obs_per_day = mean(n_obs),
            min = min(n_obs),
            max = max(n_obs)) %>% 
  ggplot(aes(x = avg_obs_per_day)) +
  geom_histogram(bins = 10) +
  xlab("avg number of gps observations") +
  ggtitle("Histogram of average observations per non-missing day") +
  theme_classic()
```
  

```{r}
gps %>% 
  mutate(home_or_not = 
           case_when(
             known_place_type == "HOME" ~ "home", 
             known_place_type != "HOME" ~ "not home",
             is.na(known_place_type) ~ "unknown")) %>% 
  group_by(subid, date_central, home_or_not) %>% 
  summarize(count_per_day = n()) %>%
  mutate(count_per_day = as.double(count_per_day)) %>% 
  mutate(count_per_day = case_when(count_per_day > 300 ~ 300,
                                   TRUE ~ count_per_day)) %>% 
  ggplot(aes(x = count_per_day)) +
  geom_histogram(bins = 10) +
  facet_wrap(~home_or_not) + 
  xlab("frequency of gps obs per non-missing day (values > 300 coded as 300)") +
  theme_classic()

```

### Missing GPS data

```{r}
gps %>% 
  filter(is.na(lat)) %>% 
  group_by(subid) %>% 
  summarise(n_obs = n()) %>% 
  ggplot(aes(x = n_obs)) +
  geom_histogram(bins = 10) +
  xlab("number of missing observations") +
  ggtitle("Histogram of gps missing observations per subject") +
  theme_classic()
```


```{r}
missing_gps_days <- gps %>%
  filter(is.na(lat)) %>% 
  group_by(subid) %>% 
  summarize(n_days_missing = n()) %>% 
  arrange(desc(n_days_missing))
```
  
`r  nrow(filter(missing_gps_days, n_days_missing >= 30))` subjects were missing data for at least 30 on-study days. 


```{r}
missing_gps_days %>% 
  filter(n_days_missing >= 30) %>% 
  kable() %>%
  kable_styling(
    bootstrap_options = "condensed", 
    full_width = FALSE, 
    position = "left")
```

Some of these high missing day counts might be due to errors in the visits file.

```{r}
gps %>% 
  group_by(subid, date_central) %>% 
  count() %>% # count gps obs per on-study day per subject
  filter(n > 1, n <= 5) %>% #filter to between 1 (which includes null obs, and 5)
  tabyl(subid) %>% # count number of days with 2 to 5 observations per subject
  filter(n > 10) %>% #look just at people who had more than 5 days with 2 to 5 observations
  rename(n_low_obs_days = n) %>% 
  kable(label = "Frequencies of days with at least one gps observation but no more than 5 per subject") %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = "condensed")
```


### Observations per App
  
Frequency and percentage of participants per app
```{r}
tabyl(gps, app_source) %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")
```
  

Date ranges of app usage
```{r}
gps %>% 
  group_by(app_source) %>% 
  summarise(min = min(date_central),
            max = max(date_central)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")
```
  

### Jumps in Distance

```{r}
gps %>% 
  mutate(meters_per_min = next_dist/as.numeric(next_time)) %>% 
  arrange(desc(next_dist)) %>% 
  select(subid, next_dist, next_time, meters_per_min) %>% 
  head()
```
These movements are consistent with travel, confirmed by investigating specific subjects (e.g., 037, 044, 207)

