---
title: "Contacts Check Script"
author: "Ali Colmenares and Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    code_folding: show
    toc: true 
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---
### Notes
This script checks data from RISK participants' contacts reports by computing descriptives and checking for missingness and potential errors


### Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = TRUE)
```

Paths
```{r}
path_data <- "./analysis/shared/data"
```


Packages
```{r}
library(janitor)
library(lubridate)
library(kableExtra)
library(tidyverse)
library(psych)
```


### Import Data and Glimpse

Contacts data
```{r}
contacts <- read_rds(file.path(path_data, "ds_contacts_report.rds")) %>% 
  glimpse()
```

narrow phone types to type and phone column
```{r}
# add identifier for contacts since some have more than one number
contacts <- contacts %>% 
  mutate(cont_sub = 1000 + (1:nrow(contacts)))

# gather to separate phone numbers into their own rows
contacts <- contacts %>% 
  gather(phone_type, number, home_phone:other_phone2) %>% 
  filter(!is.na(number)) %>% 
  select(subid, cont_sub, phone_type, number, 
         contact_type = type,
         everything(),
         -utc) %>% 
  glimpse()
```


### Missing data

View _contacts with missing data
```{r}
if(any(is.na(contacts))){
  missing <- contacts %>%
    summarise(across(everything(), ~sum(is.na(.)))) %>%
    gather(key = "var", value = "num_NA" ) %>%
    filter(num_NA > 0)
  missing %>%
    kable(caption = "Variables with missing values", table.attr = "style='width:40%;'") %>%
    kable_styling(position = "left", bootstrap_options = "condensed")
}else {
  paste("No missing values")
}
```
There are now `r sum(is.na(contacts))` missing values (NA) from `r length(missing$var)` unique 
variables in the entire dataset

Missing contact_type
```{r}
contacts %>% 
  filter(is.na(contact_type)) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "condensed")
```
It appears as though the NA should be either reclassified as "other" or removed
Because the rest of the variables have valid data, the contacts will be classified as "other"

Reclassify type from NA to other
```{r}
contacts <- contacts %>% 
  mutate( 
    contact_type = case_when( 
    subid == 16 & is.na(contact_type) ~ "OTHER", 
    subid == 18 & is.na(contact_type) ~ "OTHER",
    subid == 56 & is.na(contact_type) ~ "OTHER",
    TRUE ~ contact_type))
```

There are `r nrow(subset(contacts, contact_type == "IRRELEVANT/SPAM"))` irrelevant/spam contacts and about `r nrow(subset(contacts, is.na(drank_past)))` contacts with missing context variables.  

Missing context variables
```{r}
contacts %>% 
  filter(contact_type != "IRRELEVANT/SPAM" & is.na(drank_past)) %>% 
  group_by(contact_type) %>% 
  summarise(n = n()) %>% 
  kable(table.attr = "style='width:60%;'") %>% 
  kable_styling(position = "left")
```

`r nrow(subset(contacts, contact_type == "SELF"))` of the `r nrow(subset(contacts, contact_type != "IRRELEVANT/SPAM" & is.na(drank_past)))` non-spam contacts with missing context variables are identified as self.  

Participants with self contact
```{r}
contacts %>% 
  filter(contact_type == "SELF") %>% 
  group_by(subid) %>% 
  summarise(n = n())

contacts %>% 
  filter(contact_type == "SELF") %>% 
  group_by(subid) %>% 
  summarise(n = n()) %>% 
  filter(n > 1)
```

KW: Not sure what self is defined as. 144 unique subids have self contact with 12 of them having multiple self contacts. Will temporarily remove from dataset because missing context variables and cannot do much analyses without more information (call logs)

Temporarily remove self contacts
```{r}
contacts <- contacts %>% 
  filter(contact_type != "SELF")
```

Remaining missing values
```{r}
contacts %>% 
  filter(contact_type != "IRRELEVANT/SPAM") %>% 
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  gather(key = "var", value = "num_NA" ) %>%
  filter(num_NA > 0) %>% 
  kable(table.attr = "style='width:60%;'") %>% 
  kable_styling(position = "left")
```

Missing context variables
```{r}
contacts %>% 
  filter(contact_type != "IRRELEVANT/SPAM") %>% 
  filter(is.na(drink_future)) %>% 
  kable() %>% 
  kable_styling()
```

Subids 26, 6, 66 make up 12 of the 22 contacts with missing context variables  

### Descriptives

#### Contacts per participant

Average number of contacts for each participant
```{r}
n_contacts <- contacts %>% 
  group_by(subid) %>%
  summarise(n_contacts = length(unique(cont_sub)))

describe(n_contacts$n_contacts) %>% 
  round(2) %>% 
  select(n:se) %>% 
  kable() %>% 
  kable_styling() %>% 
  add_header_above(c("Total number of contacts per participant (with spam)" = 13))
```

The overall average number of contacts reported by participants was `r round(mean(n_contacts$n_contacts), 2)`.  

facet by spam
```{r}
contacts <- contacts %>% 
  mutate(spam = case_when(contact_type == "IRRELEVANT/SPAM" ~ "spam", 
                          contact_type != "IRRELEVANT/SPAM" ~ "contact")) 

contacts %>% 
  group_by(subid, spam) %>%
  summarise(n_contacts = length(unique(cont_sub))) %>% 
  mutate(n_contacts = case_when(n_contacts > 100 ~ as.double(100),
                   TRUE ~ as.double(n_contacts))) %>% 
  ggplot(aes(x = n_contacts, fill = spam)) +
  geom_histogram() +
  facet_wrap(~spam) +
  theme_classic() + 
  theme(legend.position = "none") +
  xlim(0,101) +
  scale_fill_manual(values = c("midnightblue", "darksalmon")) +
  labs(x = "number of contacts per participant",
       title = "Total number of contacts per participant faceted by spam") +
  geom_vline(aes(xintercept = means), contacts %>% 
  group_by(subid, spam) %>%
  summarise(n_contacts = length(unique(cont_sub))) %>% 
  group_by(spam) %>% 
  summarise(means = mean(n_contacts)), color = "red")
```

#### Numbers per contact

Average number of numbers per contact
```{r}
contacts %>% 
  group_by(cont_sub) %>% 
  summarise(n = n()) %>% 
  describe() %>% 
  filter(vars == 2) %>% 
  kable() %>% 
  kable_styling() %>% 
  add_header_above(c("Total number of numbers per contact" = 14))
```

Contacts with more than one number
```{r}
cont_multiplenums <- contacts %>% 
  group_by(cont_sub) %>% 
  summarise(n = n()) %>% 
  filter(n > 1)
```

`r nrow(cont_multiplenums)` contacts had more than one number listed. The most numbers listed for one contact was `r max(cont_multiplenums$n)` numbers.  

#### Contact type

Frequency of contact type
```{r}
 contacts %>%
  mutate(type = fct_infreq(factor(contact_type))) %>%
  tabyl(type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contact type", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")
```

```{r}
contacts %>%
  mutate(type = fct_infreq(factor(contact_type))) %>%
  ggplot(aes (x = type, fill = type)) +
  geom_bar() +
  xlab("contact type") +
  ggtitle("Frequency plot of types of contacts reported") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")
```


#### Phone type

```{r}
contacts %>%
  mutate(type = fct_infreq(factor(phone_type))) %>%
  tabyl(type, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Phone type", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")
```


#### Context variables

Removing spam for context checks
```{r}
contacts <- contacts %>% 
  filter(spam == "contact")
```

drank past
```{r}
contacts %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_infreq(factor(drank_past))) %>% 
  tabyl(drank_past, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Drank in past with contact", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(drank_past = tolower(drank_past),
         drank_past = fct_infreq(factor(drank_past))) %>%
  ggplot(aes (x = drank_past, fill = drank_past)) +
  geom_bar() +
  xlab("Drinking history with participant") +
  ggtitle("Frequency plot of drinking history with contact") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")
```

Contacts' Drinking Status 
```{r}
contacts %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_infreq(factor(drinker_status))) %>% 
  tabyl(drinker_status, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contacts' drinking status", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(drinker_status = tolower(drinker_status),
         drinker_status = fct_infreq(factor(drinker_status))) %>%
  ggplot(aes (x = drinker_status, fill = drinker_status)) +
  geom_bar() +
  xlab("Contacts' drinking status") +
  ggtitle("Frequency plot of contacts' drinking status") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")
```

Does Participant expect that contact would drink in presence of participant 
```{r}
contacts %>%
  mutate(drink_future = tolower(drink_future),
         drink_future = fct_infreq(factor(drink_future))) %>% 
  tabyl(drink_future, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Drink future", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(drink_future = tolower(drink_future),
         drinker_status = fct_infreq(factor(drink_future))) %>%
  ggplot(aes (x = drink_future, fill = drink_future)) +
  geom_bar() +
  xlab("future_drink") +
  ggtitle("Frequency plot of expectation for contact to drink in their presence") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")
```

Is contact in recovery
```{r}
contacts %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_infreq(factor(recovery))) %>% 
  tabyl(recovery, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contacts' recovery status", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(recovery = tolower(recovery),
         recovery = fct_infreq(factor(recovery))) %>%
  ggplot(aes (x = recovery, fill = recovery)) +
  geom_bar() +
  xlab("Is contact currently in recovery?") +
  ggtitle("Frequency plot of contacts' recovery status") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position="none")
```

Contacts' support of participant's recovery goals 
```{r}
contacts %>%
  mutate(support = tolower(support),
         support = fct_infreq(factor(support))) %>% 
  tabyl(support, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Contacts' support of participants' recovery goals", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(support = tolower(support),
         support = fct_infreq(factor(support))) %>%
  ggplot(aes (x = support, fill = support)) +
  geom_bar() +
  xlab("support") +
  ggtitle("Frequency plot of contacts' support for participants' recovery goals") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position="none")
```

Error: "no" was not a possible response to the item "Do they know about your recovery goals, if so are they supportive"  

Participant with "no" response 
```{r}
contacts %>% 
  filter(support == "NO") %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "condensed")
```

Emotion associated with typical interactions
```{r}
contacts %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_infreq(factor(emotion))) %>% 
  tabyl(emotion, show_na = TRUE) %>% 
  adorn_totals("row") %>%
  kable(caption = "Emotion associated with typical interactions", table.attr = "style='width:60%;'") %>%
  kable_styling(position = "left")

contacts %>%
  mutate(emotion = tolower(emotion),
         emotion = fct_infreq(factor(emotion))) %>%
  ggplot(aes (x = emotion, fill = emotion)) +
  geom_bar() +
  xlab("emotion") +
  ggtitle("Emotion associated with typical interactions") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position="none")
```


