---
title: "Processing open text responses for locations"
author: "Ali Colmenares"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
Purpose: This script assesses the RISK 'other locations' responses and recommends additional location types for RISK 2    

Inputs:

* locations_abby REAL.csv


### Setup
```{r setup, include = FALSE}
knitr::opts_chunk$set(message = TRUE, warning = TRUE)

```

```{css, echo = FALSE}
pre {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
 
}
```

Paths 
```{r}
path_other_locations <- "./raw_data/locations"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(tidytext)
library(wordcloud)
library(gt)
```

### Import and wrangle

```{r}

other_location_names <- read_csv("./raw_data/locations/locations_abby REAL.csv") %>% #for now, just using abby's codes
  filter(!is.na(description)) %>% 
  mutate(description = tolower(description)) %>% 
  pull(description) 
  
```


#### Describe 'other' places

Tokenized Phrases
```{r}
text_df <- tibble(line = 1:length(other_location_names), 
                  text = other_location_names) %>%
  unnest_tokens(word, text) %>% 
  rename(text = word) %>% 
  anti_join(stop_words, by = c("text" = "word")) %>%
  count(text, sort = TRUE) 


text_df %>% 
  filter(n > 4) %>% 
  gt()


wordcloud(text_df$text, text_df$n,
          min.freq = 5) 

```
The ten most commonly used tokens are 'library', 'hotel', 'airport', 'bus','church', 'stop', 'store', 'center', 'school', and 'house'. 

Complete Phrases 
```{r}
text_df <- tibble(line = 1:length(other_location_names), 
                  text = other_location_names) %>%
  anti_join(stop_words, by = c("text" = "word")) %>% 
  count(text, sort = TRUE)


text_df %>% 
  filter(n > 4) %>% 
  gt() 

wordcloud(text_df$text, text_df$n,
          min.freq = 5)
```

The 5 most common phrases were 'library', 'hotel', 'airport', 'church', 'bus stop', 'movies', 'mall', 'golf course', 'gas station', and 'concert venue'

Assess Risk2 measure
```{r}
new_text_df <- filter(text_df, !text %in% c("library", "hotel", "church", "bus stop", "bus station", "motel", "hospital", "p.o", "transfer point", "bank", "community center", "west transfer point")) 

new_text_df %>% 
  filter(n > 4) %>% 
  gt() 

wordcloud( new_text_df$text, new_text_df$n,
          min.freq = 5)

```
After filtering out the most commonly used 'other' places that are already represented in the RISK 2 locations measure, the 10 most common places are 'airport', 'movies', 'golf course', 'gas station', 'concert venue', 'movie theatre', 'salon', 'tour', and 'airbnb'

Recommended actions:

* Create an 'Entertainment Venue (Movie Theater, Concert)' option
* Create a  'Malls'
* Consider adding 'Airport' to the examples for transportation point.
* Consider creating a 'Salon/Barbershop' category 
* Consider creating a 'Gas station' category
* Consider creating a 'Recreational activity (Golf, Swimming, Camping, Etc.)' option
* Consider creating a 'Child's School/Daycare' option