---
title: "Helper file for examining lapses"
author: "SS"
date: "5/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setup-----------------------------------------
This file helps to open up relevant data sources while going over cases in the examine_lapses file
You will still need to manually check the master datalog to see if anything was recorded there

```{r}
library(tidyverse)
library(lmSupport)
library(knitr)
library(xlsx) #install.packages("xlsx")
data_path <- "P:/StudyData/RISK/analysis/shared/data"
raw_data <- "P:/StudyData/RISK/raw_data"
```

#Opening main files-------------------------------------------
You only need to run this code chunk once to get the main ema and lapses files, you will subset down to individual subjects later

```{r}
ema <- read_rds(file.path(data_path,"ds_ema.rds"))

ema$date <- ema$utc %>% #converting into human readable form
  as.numeric %>% 
  as.POSIXct(tz='America/Chicago', origin="1970-01-01")

#Set timezones for time vars
attributes(ema$start_date)$tzone <- "America/Chicago"
attributes(ema$end_date)$tzone <- "America/Chicago"
attributes(ema$ema_1_1)$tzone <- "America/Chicago"
attributes(ema$ema_1_3)$tzone <- "America/Chicago"

#Now filter down to just the lapses for the lapse tibble
lapses <- ema %>% 
  filter(ema_1==2) %>%
  mutate(lapse_start = ema_1_1) %>% 
  mutate(lapse_end = ema_1_3)

#create variables for lapse length and length since report
lapses <- lapses %>% 
 mutate(lapse_length = lapse_end - lapse_start) %>% 
  mutate(lapse_length = lapse_length/3600) %>% 
  mutate(lapse_length = as.numeric(lapse_length)) %>% 
  select(-c(ema_1_1, ema_1_3))

lapses <- lapses %>% 
 mutate(report_length_from_start = start_date - lapse_start) %>% 
  mutate(report_length_from_start = report_length_from_start/3600) %>%
  mutate(report_length_from_start =as.numeric(report_length_from_start))

lapses <- lapses %>% 
  select(c(response_id,utc,subid, start_date, end_date, lapse_start, lapse_end,lapse_length, report_length_from_start))

#Open big audio file
audio <- read.xlsx(file.path(raw_data, "audio.xlsx"),sheetName = "Sheet1") %>% 
  select(c(MessageName,Text)) %>% 
  mutate(MessageName = as.character(MessageName)) %>% 
  mutate(Text = as.character(Text))
  

audio <- audio %>% 
  separate(MessageName, into = c("sub_id", "year","date","time"), sep = "_") 

audio <- audio %>% 
  separate(date, into = c("month","day"), sep = 2)

audio <- audio %>% 
  mutate(date = str_c(audio$month,"/",audio$day,"/",audio$year)) %>% 
  select(c(sub_id,date,Text))

## Open list of subs wiht vacation files
vacation_subs <- read_rds("P:/StudyData/RISK/analysis/shared/scripts_chk/dev/chk_lapses/vacation_subs.rds")

vacation_subs

##open gps
path_shared_data <- "P:/StudyData/RISK/analysis/shared/data" 
library(lutz)
gps <- read_rds(file.path(path_shared_data, "ds_gps.rds"))
tz <- read_rds("P:/StudyData/RISK/analysis/shared/scripts_chk/dev/chk_lapses/gps_tz.rds")
tz = as_tibble(tz)
gps$lutz_tz = tz$value

#ROUGH UTC OFFSETS
#When its summer, you can add one (e.g. -5 becomes -4)
EST -5
CST -6
Mountain -7
Pacific -8
```

## Open full ema, lapse, and audio for subject---------------------------------------------------
To run quickly, just enter the subid and then click the green play arrow in the right --->
```{r}
# Enter subid here
sub <- 37


#Subjects full audio Messages
#Note -- if you hover over the message in View, it will display the whole text
View(audio[audio$sub_id==varPadString(sub,3),])

#Subjects full lapse file
View(lapses[lapses$subid==sub,])

#Subjects full ema file
View(ema[ema$subid==sub,])

#Subjects vacation file if they have it
if (varPadString(sub,3) %in% vacation_subs){
  vacations <- read.xlsx(file.path("P:/StudyData/RISK/raw_data",varPadString(sub,3),str_c(varPadString(sub,3),"_Vacations.xlsx")),sheetIndex = "Vacations") #Megan change sheetIndex if you get an error
View(vacations)
}

#gps
gps_tz %>% filter(subid == varPadString(sub,3)) %>% View()


```

If you want to zoom into emas based on response dates, or print individual voice messages, use this box------------------------------------
Make sure to enter resp_id for ema and date for audio check ins.
```{r}
## EMA around response -----------------------------------

#Enter response ID here
resp_id <-"R_3h9jBssRo3T7q1I"

#Subjects EMA narrowed to 3 before and  after the current response
#I change the response ID of the lapse in question to "Focal lapse" to make it easier to see
position <- which(str_detect(ema$response_id, resp_id))
ema %>% mutate(response_id = ifelse(str_detect(response_id, resp_id), "Focal lapse", response_id)) %>% 
  slice((position-3):(position+3)) %>% 
  View()

## Print just one message by date-------------------------------------
#(enter date as mm/dd/yyyy)
audio %>% 
  filter(sub_id==varPadString(sub,3)) %>% 
  filter(date=="09/22/2017") %>% 
  pull(Text) %>% 
  print()

```

