---
title: "Context Analyses"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
---

### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Source training controls 
```{r}
source('./meta/chtc/training/training_controls_model_selection.R')
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
# library(conflicted) 
#  conflict_prefer("filter", "dplyr")
#  conflict_prefer("select", "dplyr")
#  conflict_prefer("spec", "yardstick")

library(here)  
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)
library(vip)
library(tictoc)

theme_set(theme_classic()) 
```

Set additional paths
```{r}
path_models <- "./meta/ana_scripts/model_output"
path_results <- "P:/studydata/risk/chtc/meta/jobs/training/model_selection/output/results"
path_features <- "P:/studydata/risk/chtc/meta/jobs/training/model_selection/input"
```

Source function scripts from lab support
```{r  source_script, message=FALSE, warning=FALSE}
source(here("../lab_support/chtc/fun_chtc.R"))
source(here("../lab_support/print_kbl.R"))
```

### Notes
This script does model comparisons on the best models for the meta project.

### Read in results

```{r}
# individual results
result_files <- list.files(path_results, full.names = TRUE)
results_all <- vroom::vroom(result_files, col_types = vroom::cols()) %>% 
  glimpse()

# aggregate results
results_aggregate <- vroom::vroom(here(path_models, "results_aggregate.csv"), col_types = vroom::cols()) %>% 
  glimpse()

# features
data_all <- read_rds(here(path_features, "data_trn.rds")) %>% 
  rename(y = {{y_col_name}}) %>% 
  glimpse()
```


### Active and Passive Model Performance

Balanced accuracy by algorithm
```{r}
results_aggregate %>% 
  group_by(feature_set) %>% 
  arrange(desc(bal_accuracy)) %>% 
  slice(1) %>% 
  select(feature_set, algorithm, feature_fun_type, bal_accuracy)
```


### Best Active model compared to Best Passive model

Best models
```{r}
best_active <- results_aggregate %>% 
  filter(feature_set == "feat_all") %>% 
  slice_max(bal_accuracy) %>% 
  glimpse()

best_passive <- results_aggregate %>% 
  filter(feature_set == "feat_all_passive") %>% 
  slice_max(bal_accuracy) %>% 
  glimpse()
```

Bayesian correlated t-test (10 x 10 fold)
```{r}
# make splits 
set.seed(102030)
splits <- make_splits(d = data_all, cv_type = "group_kfold_10_x_10", group = group)

# build recipes
rec_passive <- build_recipe(d = data_all, job = best_passive)
rec_active <- build_recipe(d = data_all, job = best_active)

# fit passive model
if (best_passive$algorithm == "glmnet") {
  best_passive_fits <- logistic_reg(penalty = best_passive$hp2,
                                    mixture = best_passive$hp1) %>%
      set_engine("glmnet") %>%
      set_mode("classification") %>%
      fit_resamples(preprocessor = rec_passive,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
  
} else if (best_passive$algorithm == "random_forest") {
  best_passive_fits <- rand_forest(mtry = best_passive$hp1,
                        min_n = best_passive$hp2,
                        trees = best_passive$hp3) %>%
      set_engine("ranger",
                  importance = "impurity",
                  respect.unordered.factors = "order",
                  oob.error = FALSE,
                  seed = 102030) %>%
      set_mode("classification") %>%
      fit_resamples(preprocessor = rec_passive,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
  
} else if (best_passive$algorithm == "knn") {
    best_passive_fits <- nearest_neighbor(neighbors = best_passive$hp1) %>% 
      set_engine("kknn") %>% 
      set_mode("classification") %>% 
      fit_resamples(preprocessor = rec_passive,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
}

# fit active model
if (best_active$algorithm == "glmnet") {
    best_active_fits <- logistic_reg(penalty = best_active$hp2,
                                    mixture = best_active$hp1) %>%
      set_engine("glmnet") %>%
      set_mode("classification") %>%
      tune_grid(preprocessor = rec_active,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
  
} else if (best_active$algorithm == "random_forest") {
    best_active_fits <- rand_forest(mtry = best_active$hp1,
                        min_n = best_active$hp2,
                        trees = best_active$hp3) %>%
      set_engine("ranger",
                  importance = "impurity",
                  respect.unordered.factors = "order",
                  oob.error = FALSE,
                  seed = 102030) %>%
      set_mode("classification") %>%
      tune_grid(preprocessor = rec_active,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
  
} else if (best_active$algorithm == "knn") {
    best_active_fits <- nearest_neighbor(neighbors = best_active$hp1) %>% 
      set_engine("kknn") %>% 
      set_mode("classification") %>% 
      tune_grid(preprocessor = rec_active,
                resamples = splits,
                metrics = metric_set(bal_accuracy))
}

# save fits
write_rds(best_passive_fits., here(path_models, "best_passive_10_x_10_fold_fits.rds"))
write_rds(best_active_fits., here(path_models, "best_active_10_x_10_fold_fits.rds"))
```

Run bayesian correlate t-test - each have 100 bal_accuracy to pass into baysian correlated t
```{r}
rope_min <- -0.01
rope_max <- 0.01
plot_min = -.14 
plot_max = .14 # may need to get bigger
results_ttest <- bayesian_correlated_t_test(best_passive_fits, best_active_fits, 
                                      rope_min = rope_min, 
                                      rope_max = rope_max, 
                                      k = 10, 
                                      plot_min = plot_min, plot_max = plot_max)

ggplot(mapping = aes(x = results_ttest$plot_diffs, y = results_ttest$pdf)) +
  geom_line() +
  geom_vline(mapping = aes(xintercept  = rope_min), linetype = "dashed") +
  geom_vline(mapping = aes(xintercept  = rope_max), linetype = "dashed") +
  scale_x_continuous(breaks=seq(plot_min, plot_max, .02)) +
  labs(x = "Accuracy Difference (Full - Compact Model)",
       y = "Posterior Probability")

results_ttest$left
results_ttest$rope
results_ttest$right
```


### Top Features

Best model's top features   
FIX: look at glmnet coefficients for interpretability
FIX: add VI plot for all 3 algorithms
FIX: add VI plot for active and passive
```{r}
# fit best model on all data
best_model <- slice_max(results_aggregate, bal_accuracy) %>% 
  glimpse()
    
rec <- build_recipe(d = data_all, job = best_model)

feat_all <-  rec %>% 
  step_rm(has_role(match = "id variable")) %>% 
  prep(training = data_all, strings_as_factors = FALSE) %>% 
  bake(new_data = data_all)
    
if (best_model$algorithm == "glmnet") {
  model <- logistic_reg(penalty = best_model$hp2,
                        mixture = best_model$hp1) %>% 
    set_engine("glmnet") %>%
    set_mode("classification") %>%
    fit(y ~ .,
        data = feat_all)
  # view variable importance indexes
  x <- feat_all %>% 
    select(-y) %>% 
    as.matrix()
  y <- feat_all %>% 
    pull(y)
  
  acc_perm <- function(actual, predicted) {
    accuracy_vec(actual, predicted)
    }
      
  pred_perm <- function(object, newdata) {
    preds <- predict(object, newdata, type = "response", s = best_model$hp2)[, 1]  
    preds <- if_else(preds >= .5, "yes", "no") 
    preds <- factor(preds, levels = c("no", "yes"))
    return(preds)
    }
       
  set.seed(102030)  # for reproducibility in vi_permute ()
  vi_plot <- model %>%
    vip::vi(method = "permute", 
            train = x, 
            target = y,
            metric = acc_perm,
            pred_wrapper = pred_perm,  
            smaller_is_better = FALSE, 
            nsim = 1) 
  
  vi_plot %>% 
      mutate(Variable = fct_reorder(Variable, Importance)) %>% 
      filter(Importance != 0) %>% 
      ggplot(aes(x = Importance, y = Variable)) +
      geom_col() +
      scale_x_continuous(expand = c(0, 0)) +
      labs(y = NULL, title = "glmnet")
        
  # save vi_plot for editing later
  write_rds(vi_plot, here(path_models, "vi_glmnet.rds"))

} else if (best_model$algorithm == "random_forest") {
  model <- rand_forest(mtry = best_model$hp1,
                       min_n = best_model$hp2,
                       trees = best_model$hp3) %>%
    set_engine("ranger",
               importance = "impurity",
               respect.unordered.factors = "order",
               seed = 102030) %>%
    set_mode("classification") %>%
    fit(y ~ .,
        data = feat_all)
      
  # view variable importance indexes
  x <- feat_all
        
  acc_perm <- function(actual, predicted) {
    accuracy_vec(truth = actual, estimate = predicted)
    }

  pred_perm <- function(object, newdata) {
    preds <- predict(object, data = newdata)$predictions
    preds <- if_else(preds[, 2] >= .5, "yes", "no") 
    preds <- factor(preds, levels = c("no", "yes"))
    return(preds)
    }
        
  set.seed(102030)  # for reproducibility in vi_permute ()
  vi_plot <- model %>%
    vip::vi(method = "permute", 
            train = x, 
            target = "y",
            metric = acc_perm,
            pred_wrapper = pred_perm,
            smaller_is_better = FALSE, 
            nsim = 1) 
  vi_plot %>% 
    mutate(Variable = fct_reorder(Variable, Importance)) %>% 
    filter(Importance != 0) %>% 
    ggplot(aes(x = Importance, y = Variable)) +
    geom_col() +
    scale_x_continuous(expand = c(0, 0)) +
    labs(y = NULL, title = "random forest")
        
  # save vi_plot for editing later
  write_rds(vi_plot, here(path_models, "vi_random_forest.rds"))

  } else if (best_model$algorithm == "knn") {
    model <- nearest_neighbor(neighbors = best_model$hp1) %>% 
      set_engine("kknn") %>% 
      set_mode("classification") %>% 
      fit(y ~ .,
          data = feat_all)
          
    x <- feat_trn 

    acc_perm <- function(actual, predicted) {
      accuracy_vec(truth = actual, estimate = predicted)
      }

    pred_perm <- function(object, newdata) {
      predict(object, newdata)
      }
          
    set.seed(102030)  # for reproducibility in vi_permute ()
    vi_plot <- model %>%
      vip::vi(method = "permute", 
              train = x, 
              target = "y",
              metric = acc_perm,
              pred_wrapper = pred_perm,  
              smaller_is_better = FALSE, 
              nsim = 1) 
     
    vi_plot %>% 
      mutate(Variable = fct_reorder(Variable, Importance)) %>% 
      filter(Importance != 0) %>% 
      ggplot(aes(x = Importance, y = Variable)) +
      geom_col() +
      scale_x_continuous(expand = c(0, 0)) +
      labs(y = NULL, title = "knn")
        
  # save vi_plot for editing later
  write_rds(vi_plot, here(path_models, "vi_knn.rds"))
  }
```

