---
title: "Model Performance"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
---

### Setup

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Source training controls 
```{r}
source('./meta/chtc/training/training_controls_model_selection.R')
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
# library(conflicted) 
#  conflict_prefer("filter", "dplyr")
#  conflict_prefer("select", "dplyr")
#  conflict_prefer("spec", "yardstick")

library(here)  
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(ggplot2)
library(kableExtra)
library(vip)
library(tictoc)

theme_set(theme_classic()) 
```

Set additional paths
```{r}
path_models <- "meta/ana_scripts/model_output"
path_results <- "P:/studydata/risk/chtc/meta/jobs/training/model_selection/output/results"
path_features <- "P:/studydata/risk/chtc/meta/jobs/training/model_selection/input"
path_figures <- "meta/ana_scripts/figures"
```

Source function scripts from lab support
```{r  source_script, message=FALSE, warning=FALSE}
source(here("meta/fun_meta.R"))
source(here("../lab_support/chtc/fun_chtc.R"))
source(here("../lab_support/print_kbl.R"))
```

### Notes
This script does model comparisons on the best models for the meta project.

### Read in results

```{r}
# individual results
result_files <- list.files(path_results, full.names = TRUE)
results_all <- vroom::vroom(result_files, col_types = vroom::cols()) %>% 
  glimpse()

# aggregate results
results_aggregate <- vroom::vroom(here(path_models, "results_aggregate.csv"), col_types = vroom::cols()) %>% 
  glimpse()

# features
data_all <- read_rds(here(path_features, "data_trn.rds")) %>% 
  rename(y = {{y_col_name}}) %>% 
  glimpse()
```


### Model performance by algorithm

Balanced accuracy by algorithm
```{r}
results_aggregate %>% 
  group_by(algorithm) %>% 
  arrange(desc(bal_accuracy)) %>% 
  slice(1) %>% 
  select(algorithm, feature_set, feature_fun_type, bal_accuracy)
```


Subset best fits for each top algorithm model
```{r}
results_best <- results_aggregate %>%
  group_by(algorithm) %>% 
  arrange(desc(bal_accuracy)) %>% 
  slice(1) %>% 
  mutate(algorithm_best = "best") %>% 
  select(-c(accuracy:roc_auc)) %>% 
  right_join(results_all, 
             by = c("algorithm", "feature_set", "feature_fun_type", "resample", "hp1", "hp2", "hp3", "n_feats")) %>% 
  filter(algorithm_best == "best") %>% 
  select(-algorithm_best) %>% 
  glimpse()
```


Plot performance metrics across folds   
```{r}
# refit glmnet to pull out fold perf
best_glmnet <- results_aggregate %>% 
  filter(algorithm == "glmnet") %>% 
  slice_max(., bal_accuracy)

rec_glmnet <- build_recipe(data_all, best_glmnet)
# remove nzv if training controls set to TRUE
if (remove_nzv) {
  rec_glmnet <- rec_glmnet %>% 
    step_nzv(all_predictors())
}

# replicate chtc splits
set.seed(102030)
splits_glmnet <- make_splits(data_all, cv_type, group = group)

fits_glmnet <- logistic_reg(penalty = best_glmnet$hp2,
                            mixture = best_glmnet$hp1) %>%
      set_engine("glmnet") %>%
      set_mode("classification") %>%
      fit_resamples(preprocessor = rec_glmnet,
                resamples = splits_glmnet,
                metrics = metric_set(bal_accuracy))

results_glmnet <- collect_metrics(model = fits_glmnet, summarize = FALSE) %>% 
    pivot_wider(., names_from = "metric",
                values_from = "estimate") %>%   
    bind_cols(best_glmnet, .)
    

ba_hist <- results_best %>% 
  filter(algorithm != "glmnet") %>% 
  bind_rows(results_glmnet) %>% 
  group_by(algorithm) %>% 
  ggplot(aes(x = bal_accuracy)) +
  geom_histogram(color = "black", fill = "light grey") +
  facet_wrap(~ algorithm) +
  scale_y_continuous(breaks = seq(1, 10, by = 1), labels = seq(1, 10, by = 1)) +
  xlab("balanced accuracy") +
  labs(title = "model performance across 10 folds") +
  geom_vline(aes(xintercept = mean_ba), results_best %>% 
  filter(algorithm != "glmnet") %>% 
  bind_rows(results_glmnet) %>% 
  group_by(algorithm) %>% 
  summarise(mean_ba = mean(bal_accuracy)))

ba_hist

# save figure
ggsave("ba_hist.png", plot = ba_hist,  path_figures, width = 5, height = 7, units = "in", device = "png",  dpi = 500)
```



### Best model 

Best model
```{r}
best_model <- results_aggregate %>% 
  slice_max(bal_accuracy) %>% 
  glimpse()
```


#### Compared to Null   
Bayesian correlated t-test (10 x 10 fold)
```{r}
# make splits 
set.seed(102030)
splits <- make_splits(d = data_all, cv_type = "group_kfold_10_x_10", group = group)

# make recipes
# need all vars to be numeric
rec_null <- recipe(y ~ ., data = data_all) %>%
  update_role(subid, dttm_label, new_role = "id variable") %>%
  step_rm(label_num, starts_with("id_"), starts_with("label_")) %>% 
  step_string2factor(y, levels = c("no", "yes")) %>% 
  step_string2factor(all_nominal()) %>%
  step_dummy(all_nominal(), -y) %>% 
  step_impute_median(all_numeric())

rec_best <- build_recipe(d = data_all, job = best_model)


# fit and save out each fold to make data smaller size to work with
jobs <- expand.grid(n_fold = 1:10,
                    n_repeat = 1:10) %>% 
  rowid_to_column(var = "job_num")

for (i in 1:max(jobs$job_num)) {
  
  job <- slice(jobs, i)
  
  # fit null model
  features <- make_features(job = job, folds = splits, rec = rec_null, 
                            cv_type = "group_kfold_10_x_10")
  feat_in <- features$feat_in
  feat_out <- features$feat_out
  
  fit_null <- null_model() %>%
    set_engine("parsnip") %>% 
    set_mode("classification") %>%
    fit(y ~ .,
        data = feat_in)
  
  # save results
  get_metrics(model = fit_null, feat_out = feat_out) %>% 
    pivot_wider(., names_from = "metric",
                values_from = "estimate") %>%   
    mutate(algorithm = "null_model",
           rec = "rec_null") %>% 
    relocate(algorithm, rec) %>% 
    bind_cols(job, .)  %>% 
    write_csv(., here(path_models, 
                      str_c("null_model_fits/null_res_", 
                            job$job_num, ".csv")))
  
  
  # fit best model
  features <- make_features(job = job, folds = splits, rec = rec_best, 
                            cv_type = "group_kfold_10_x_10")
  feat_in <- features$feat_in
  feat_out <- features$feat_out
  
  if(best_model$algorithm == "random_forest") {
    fit_best <- rand_forest(mtry = best_model$hp1,
                            min_n = best_model$hp2,
                            trees = best_model$hp3) %>%
      set_engine("ranger",
                 respect.unordered.factors = "order",
                 oob.error = FALSE,
                 seed = 102030) %>%
      set_mode("classification") %>%
      fit(y ~ .,
          data = feat_in)
  } else if(best_model$algorithm == "knn") {
    fit_best <- nearest_neighbor(neighbors = best_model$hp1) %>% 
      set_engine("kknn") %>% 
      set_mode("classification") %>% 
      fit(y ~ .,
          data = feat_in)
    
  } else if(best_model$algorithm == "glmnet") {
    fit_best <- logistic_reg(penalty = best_model$hp2,
                             mixture = best_model$hp1) %>%
      set_engine("glmnet") %>%
      set_mode("classification") %>% 
      fit(y ~ .,
          data = feat_in)
  }
 
  
  # save results
  get_metrics(model = fit_best, feat_out = feat_out) %>% 
    pivot_wider(., names_from = "metric",
                values_from = "estimate") %>%   
    mutate(algorithm = best_model$algorithm,
           rec = "rec_best") %>% 
    relocate(algorithm, rec) %>% 
    bind_cols(job, .) %>%
    write_csv(., here(path_models, 
                      str_c("best_model_fits/best_res_", 
                            job$job_num, ".csv")))
  
  # save predictions for out of sample subids
  predict(fit_best, feat_out, type = "prob") %>% 
    select(pred_yes = `.pred_yes`) %>% 
    bind_cols(feat_out %>% select(subid, dttm_label, y), .) %>% 
    write_csv(., here(path_models, 
                      str_c("best_model_preds/preds_", 
                            job$job_num, ".csv")))
  
}
```

Model fits
```{r}
results_best_files <- list.files(here(path_models, "best_model_fits"), 
                              full.names = TRUE)
results_best <- vroom::vroom(results_best_files, col_types = vroom::cols()) %>% 
  glimpse()

results_best %>% 
  tabyl(bal_accuracy)
```


Run bayesian correlate t-test - compare 100 bal_accuracies to NULL (bal_accuracy = .5)
```{r}
# pull out vector of estimates
best_fits <- results_best$bal_accuracy

rope_min <- .49
rope_max <- .51
plot_min = .1
plot_max = 1.0 # may need to get bigger

# fix pass in bal_accuracy estimates instead of model fits
results_ttest <- bayesian_correlated_t_test(best_fits, 
                                      rope_min = rope_min, 
                                      rope_max = rope_max, 
                                      k = 10, 
                                      plot_min = plot_min, plot_max = plot_max)

best_posterior <- ggplot(mapping = aes(x = results_ttest$plot_diffs, y = results_ttest$pdf)) +
  geom_line() +
  geom_vline(mapping = aes(xintercept  = rope_min), linetype = "dashed") +
  geom_vline(mapping = aes(xintercept  = rope_max), linetype = "dashed") +
  scale_x_continuous(breaks=seq(plot_min, plot_max, .02)) +
  labs(x = "Accuracy Difference (Best - Null Model)",
       y = "Posterior Probability")

best_posterior

# save figure
ggsave("best_posterior.png", plot = best_posterior,  path_figures, width = 9, height = 5, units = "in", device = "png",  dpi = 500)
```

get values
```{r}
results_ttest$left
results_ttest$rope
results_ttest$right
```


#### Individual Predictions

Pull out individual predictions
```{r}
preds_files <- list.files(here(path_models, "best_model_preds"), 
                              full.names = TRUE)
predictions <- vroom::vroom(preds_files, col_types = vroom::cols()) %>% 
  glimpse()
```

<!-- FIX: temp fix to add dttm_label and y back in sample preds - will not need to do this after rerun -->
<!-- ```{r} -->
<!-- for (i in 1:10) { -->
<!--   job <- slice(jobs, i) -->

<!--   features <- make_features(job = job, folds = splits, rec = rec_best,  -->
<!--                             cv_type = "group_kfold_10_x_10") -->
<!--   feat_out <- features$feat_out -->

<!--   feat_labels <- if(i == 1) { -->
<!--     feat_out %>% select(subid, dttm_label) -->
<!--   } else { -->
<!--     feat_labels %>% bind_rows(feat_out %>% select(subid, dttm_label)) -->
<!--   } -->
<!-- } -->
<!-- predictions <- feat_labels %>% bind_cols(predictions %>% select(-subid)) -->

<!-- predictions <- predictions %>% left_join(., data_all %>% select(subid, dttm_label, y),  -->
<!--                                          by= c("subid", "dttm_label")) -->
<!-- ``` -->


Check 10 predictions for each observation (10 x 10 grouped kfold)
```{r}
predictions %>% 
  count(subid, dttm_label) %>% 
  tabyl(n)
```

Average over observations
```{r}
predictions <- predictions %>% 
  group_by(subid, dttm_label) %>% 
  summarise(mean = mean(pred_yes), .groups = "drop")
```


plot predictions by participant   
Fix: Change x-axis to day on study instead of exact date?   
```{r fig.height = 60}
pred_plot <- predictions %>% 
  group_by(subid) %>% 
  ggplot(aes(x = dttm_label, y = mean, color = y)) +
  geom_point(size = .9) +
  facet_wrap(~ subid, scales = "free_x", ncol = 3) + 
  scale_color_manual(values = c("gray70", "red3")) +
  theme(legend.position = "none") +
  ylim(0, 1)

pred_plot

# save plot
ggsave("pred_plot.png", plot = pred_plot,  path_figures, width = 5, height = 60, units = "in", device = "png",  dpi = 500, limitsize = FALSE)
```
