---
title: "Evaluate models' performance in held out outer folds for version `r version`"
author: "Gaylen Fronk, John Curtin, & Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

### Code Status

In use with iterative improvement

### Notes
This is a generic script that reproduces the CV metrics for the best model configuration, calculates various performance metrics from that resampling, makes plots, and then fits the best config to the final sample to do feature importance.


### Set Up Environment

```{r set_values}
study <- "insight"
version <- "v2"
cv <- "nested"
```

Function conflicts
```{r, packages_workflow}
#| message: false
#| warning: false

# source
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")

# handle conflicts
options(conflicts.policy = "depends.ok")
tidymodels_conflictRules()
```

Packages for script
```{r, packages_script}
#| message: false
#| warning: false

library(tidyverse)
library(tidymodels)
library(tidyposterior)
# library(SHAPforxgboost)
# library(rstanarm)

theme_set(theme_classic()) 
```

Source support functions
```{r source_functions}
# EDA
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

# CHTC support functions
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/chtc/static_files/fun_chtc.R?raw=true")
```


Absolute paths
```{r, absolute_paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_input <- str_c("P:/studydata/risk/chtc/", study)
          path_processed <- str_c("P:/studydata/risk/data_processed/", study)
          path_models <- str_c("P:/studydata/risk/models/", study)
          path_knits <- str_c("P:/studydata/risk/knits/", study)},
        
        # IOS paths
        Darwin = {
          path_input <- str_c("/Volumes/private/studydata/risk/chtc/", study)
          path_processed <- str_c("/Volumes/private/studydata/risk/data_processed/",
                                  study)
          path_models <- str_c("/Volumes/private/studydata/risk/models/", study)
          path_knits <- str_c("/Volumes/private/studydata/risk/knits/", study)},
        
        # Linux paths
        Linux = {
          path_input <- str_c("~/mnt/private/studydata/risk/chtc/", study)
          path_processed <- str_c("~/mnt/private/studydata/risk/data_processed/",
                                  study)
          path_models <- str_c("~/mnt/private/studydata/risk/models/", study)
          path_knits <- str_c("~/mnt/private/studydata/risk/knits/", study)}
)
```


Chunk Defaults
```{r defaults}
#| include: false

knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


Source training controls 
```{r source}
# EDA
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

# CHTC support functions
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/chtc/static_files/fun_chtc.R?raw=true")

# ML functions
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_ml.R?raw=true")

```

Knit to specific directory
```{r, eval = FALSE, include=FALSE}
# Render knit file manually to different location

rmarkdown::render(input = file.path(
  "insight/mak_scripts/3_eval_outer.qmd"),
  output_dir = file.path(path_knits),
  output_file = str_c("3_eval_outer_", version, ".html"),
  env = new.env())
```


### Model Performance Metrics

```{r read_metrics_preds}
all_files <- list.files(path_models, full.names = TRUE) 
preds_files <- all_files[str_detect(all_files, "outer_preds_") &
                           str_detect(all_files, version)]

preds_out <- preds_files |> 
  map(\(file) read_rds(file) |> 
        mutate(model = str_extract(file, "(?<=outer_preds_)[:graph:]+(?=_v2_)")) |> 
        select(model, outer_split_num, prob_raw, label)) |> 
  list_rbind()

glimpse(preds_out)

metrics_files <- all_files[str_detect(all_files, "outer_metrics_") & 
                             str_detect(all_files, version)]

metrics_out <- metrics_files |> 
  map(\(file) read_rds(file) |> 
        mutate(model = str_c(outcome, "_", feature_set))) |> 
  list_rbind()

glimpse(metrics_out)

```

#### Inner Loop AUC

Best model configurations were selected using the median AUCs across 10 inner folds.  30 (3x10) models were selected.  

```{r}
metrics_out |> 
  group_by(model) |> 
  summarize(median(roc_auc_in), mean(roc_auc_in), min(roc_auc_in), max(roc_auc_in), sd(roc_auc_in))
```

#### Outer AUC

Best model configurations were evaluated using the AUCs from the 30 (3x10) outer folds

Outer overall
```{r metrics_out}
metrics_out |> 
  group_by(model) |> 
  summarize(median(roc_auc), mean(roc_auc))
```

Side by side of inner & outer median AUCs
```{r}
metrics_out |> 
  group_by(model) |> 
  summarize(median(roc_auc), median(roc_auc_in))
```

Plot outer folds
```{r plot_outer}
# histograms faceted by model
metrics_out |> 
  ggplot(aes(x = roc_auc)) +
  geom_histogram(bins = 10) +
  facet_wrap(vars(model), ncol = 2)

# overlaid density plots
med_roc <- metrics_out |> 
  group_by(model) |> 
  summarize(median = median(roc_auc))

metrics_out |> 
  ggplot(aes(x = roc_auc, fill = as.factor(model))) +
  geom_density(alpha = 0.5) +
  geom_vline(data = med_roc, aes(xintercept = median, 
                                 color = as.factor(model)), linewidth = 1) +
  labs(fill = "Model", color = "Model")
```

Table for each outer fold
```{r metrics_out_kbl}
models <- unique(metrics_out$model)

metrics_out |> 
  filter(model == "1week_all") |> 
  print_kbl()

metrics_out |> 
  filter(model == "1week_insight_only") |> 
  print_kbl()

metrics_out |> 
  filter(model == "1week_aase_only") |> 
  print_kbl()

metrics_out |> 
  filter(model == "dichotomous_aase_only") |> 
  print_kbl()

```

#### Outer individual metrics

*1 week / all features model*

Default threshold (0.5)
```{r}

(cm <- preds_out |> 
   filter(model == "1week_all") |> 
   mutate(estimate = if_else(prob_raw > .5, "Lapse", "No lapse"), # note changed from prob_beta while debugging
          estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

```

Confusion matrix at optimal cut-point (based on Youdens J index)

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1444894/
https://pubmed.ncbi.nlm.nih.gov/15405679/

```{r}
roc_data <- preds_out %>%
  filter(model == "1week_all") |> 
  roc_curve(prob_raw, truth = label)

j_thres_roc <- roc_data |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out |> 
    filter(model == "1week_all") |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "Lapse", "No lapse"), # note changed from prob_beta while debugging
           estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()
```

*1 week / insight_only model*

Default threshold (0.5)
```{r}

(cm <- preds_out |> 
   filter(model == "1week_insight_only") |> 
   mutate(estimate = if_else(prob_raw > .5, "Lapse", "No lapse"), # note changed from prob_beta while debugging
          estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

```

Confusion matrix at optimal cut-point (based on Youdens J index)

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1444894/
https://pubmed.ncbi.nlm.nih.gov/15405679/

```{r}
roc_data <- preds_out %>%
  filter(model == "1week_insight_only") |> 
  roc_curve(prob_raw, truth = label)

j_thres_roc <- roc_data |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out |> 
    filter(model == "1week_insight_only") |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "Lapse", "No lapse"), # note changed from prob_beta while debugging
           estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()
```

*1 week / aase_only model*

Default threshold (0.5)
```{r }

(cm <- preds_out |> 
   filter(model == "1week_aase_only") |> 
   mutate(estimate = if_else(prob_raw > .5, "Lapse", "No lapse"), # note changed from prob_beta while debugging
          estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

```

Confusion matrix at optimal cut-point (based on Youdens J index)

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1444894/
https://pubmed.ncbi.nlm.nih.gov/15405679/

```{r }
roc_data <- preds_out %>%
  filter(model == "1week_aase_only") |> 
  roc_curve(prob_raw, truth = label)

j_thres_roc <- roc_data |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out |> 
    filter(model == "1week_aase_only") |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "Lapse", "No lapse"), # note changed from prob_beta while debugging
           estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()
```

*Dichotomous / aase_only model*

Default threshold (0.5)
```{r }

(cm <- preds_out |> 
   filter(model == "dichotomous_aase_only") |> 
   mutate(estimate = if_else(prob_raw > .5, "Lapse", "No lapse"), # note changed from prob_beta while debugging
          estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

```

Confusion matrix at optimal cut-point (based on Youdens J index)

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1444894/
https://pubmed.ncbi.nlm.nih.gov/15405679/

```{r }
roc_data <- preds_out %>%
  filter(model == "dichotomous_aase_only") |> 
  roc_curve(prob_raw, truth = label)

j_thres_roc <- roc_data |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out |> 
    filter(model == "dichotomous_aase_only") |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "Lapse", "No lapse"), # note changed from prob_beta while debugging
           estimate = factor(estimate, levels = c("Lapse", "No lapse"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()
```

### Feature Importance

#### Grouped Features

```{r read_shaps_grp}
shaps_files <- all_files[str_detect(all_files, "outer_shapsgrp") &
                           str_detect(all_files, version)]

shapsgrp_out <- shaps_files |> 
  map(\(file) read_rds(file) |> 
        mutate(model = str_extract(file, 
                                   "(?<=outer_shapsgrp_)[:graph:]+(?=_v2_)"))) |> 
  list_rbind()

glimpse(shapsgrp_out)
```

Global importance Shapley value plot for grouped features

*1 week / all features model*
```{r }
shapsgrp_out %>% 
  filter(model == "1week_all") |> 
  group_by(variable_grp) %>% 
  summarize(mean_value = mean(abs(value)), .groups = "drop") %>% 
  arrange(mean_value) %>% 
  mutate(variable_grp = factor(variable_grp),
         variable_grp = fct_inorder(variable_grp)) %>% 
  ggplot(mapping = aes(x = variable_grp, y = mean_value)) +
  geom_point(size = 2, color = "red") +
  geom_segment(aes(x = variable_grp, y = mean_value, xend = variable_grp), 
               yend = 0, colour = "grey50")  +
  ylab("Mean |Shapley value|") +
  coord_flip()
```

Sina plot for grouped features

*1 week / all features model*
```{r}
# downsample to 10% of observations for plot
ids <- shapsgrp_out |> 
  filter(model == "1week_all") |> 
  pull(id_obs) |> 
  unique()
ids <- ids |> 
  sample(size = round(length(ids)/(1/.1)))

shapsgrp_out |> 
  filter(model == "1week_all" & id_obs %in% ids) |> 
  group_by(variable_grp) |> 
  mutate(variable_grp = factor(variable_grp)) |> 
  ggplot(mapping = aes(x = variable_grp, y = value)) +
  ggforce::geom_sina(method = "counts", maxwidth = 0.7, alpha = 0.4) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(-2, 3), breaks = seq(-2, 3)) +
  ylab("Shapley value") +
  xlab("") +
  theme(axis.text = element_text(size = 9.5)) +
  coord_flip()

```

