---
title: "Make features for Insight"
author: "Gaylen Fronk"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/insight", 
      "/Volumes/private/studydata/risk/knits/insight")
    )
  })
---

### Code Status

This script updates mak_features_chtc.R to a) run locally, and b) work for project Insight

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_insight <- "P:/studydata/risk/data_processed/insight"
          path_shared <- "P:/studydata/risk/data_processed/shared"},
        
        # IOS paths
        Darwin = {
          path_insight <- "/Volumes/private/studydata/risk/data_processed/insight"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"}
)
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
library(here) 
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
```

Source functions file
```{r}
source("./shared/fun_features.R")
```

### Setup all required data files

Read in ema.csv
```{r}
ema <- read_csv(here(path_insight, "ema.csv"),
                show_col_types = FALSE) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tz = "America/Chicago"),
         ema_2 = ema_2,  
         ema_3 = ema_3,
         ema_4 = ema_4,
         ema_5 = ema_5)  %>%   
  arrange(subid, dttm_obs) %>% 
  glimpse()
```

Make ema_count
```{r}
ema_count <- ema %>% 
  mutate(count = if_else(is.na(ema_7), NA_character_, "ema")) %>% 
  select(dttm_obs, subid, count) %>% 
  glimpse()
```

Pivot to long format
```{r}
ema_long <- ema %>% 
  pivot_longer(
    cols = starts_with("ema_"),
    names_to = "ema_num",
    values_to = "response") %>% 
  glimpse()
```

Read in lapses.csv
```{r}
lapses <- read_csv(here(path_insight, "lapses.csv"),
                show_col_types = FALSE) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tz = "America/Chicago")) %>% 
  glimpse()
```

Read in labels.csv
```{r}
labels <- read_csv(here(path_insight, "labels_1week.csv"),
                show_col_types = FALSE) %>%
  mutate(across(c(ema_start, ema_end, window_start, window_end,
                  study_start_time, study_end_time),
                ~ with_tz(., tz = "America/Chicago"))) %>% 
  select(subid, response_id, window_start, window_end, lapse) %>% 
  glimpse()

labels <- labels %>% 
  mutate(label_num = seq(1, nrow(labels), by = 1)) 
```

Read in study_dates.csv
```{r}
dates <- read_csv(here(path_insight, "study_dates.csv"),
                show_col_types = FALSE) %>% 
  select(subid, data_start = study_start) %>% 
  mutate(data_start = with_tz(data_start, tz = "America/Chicago")) %>% 
  glimpse()
```

Read in screen.csv (shared demographics file)
```{r}
demos <- read_csv(here(path_shared, "screen.csv"),
                  show_col_types = FALSE) %>% 
  select(subid,
         demo_age = dem_1,
         demo_sex = dem_2,
         dem_3, dem_4,
         demo_educ = dem_5,
         demo_marital = dem_8) %>% 
  mutate(demo_race = if_else(str_detect(dem_3, "White/Caucasian"), 
                             "White/Caucasian", "Other"),
         demo_race = if_else(str_detect(dem_4, "Yes"), 
                             "Other", demo_race),
         demo_educ = str_replace(demo_educ, "High school or GED", 
                                 "High school or less"),
         demo_educ = str_replace(demo_educ, 
                                 "Less than high school or GED degree", 
                                 "High school or less"),
         demo_educ = str_replace(demo_educ, "2-Year degree", "Some college"),
         demo_educ = str_replace(demo_educ, 
                                 "College degree", "College or more"),
         demo_educ = str_replace(demo_educ, 
                                 "Advanced degree", "College or more"),
         demo_marital = str_replace(demo_marital, "Divorced", "Other"),
         demo_marital = str_replace(demo_marital, "Widowed", "Other"),
         demo_marital = str_replace(demo_marital, "Separated", "Other")) %>% 
  select(-dem_3, -dem_4) %>% 
  glimpse()
```

### Make features

Set period durations for features
```{r}
period_durations_morning <- c(24, 48, 72, 168) # feature duration window for items 8-10
period_durations_later <- c(12, 24, 48, 72, 168) # feature duration window for items 2-7 
```

Calculate features in loop
```{r}
features <- foreach (i_label = 1:nrow(labels), .combine = "rbind") %do% {

  label <- labels %>% slice(i_label)
  subid <- label$subid 
  dttm_label <-  label$window_start
  the_label_num <- label$label_num
  
  # day of lapse label
  feature_row <- score_label_day(the_subid = subid, 
                                 the_dttm_label = dttm_label, 
                                 the_tz = "America/Chicago")
  
  # hour of lapse label
  feature_row <- feature_row %>%   
    full_join(score_label_hour(the_subid = subid, 
                               the_dttm_label = dttm_label, 
                               levels = 2, 
                               the_tz = "America/Chicago"),
              by = c("subid", "dttm_label"))
  
  # rate of previous lapses
  feature_row <- feature_row %>%   
    full_join(score_ratecount_value(the_subid = subid, 
                                    the_dttm_label = dttm_label, 
                                    x_all = lapses, 
                                    period_durations = period_durations_later, 
                                    lead = lead, 
                                    data_start = dates, 
                                    col_name = "count", 
                                    col_values = "lapse"),
              by = c("subid", "dttm_label"))
  
  
  # rate of previous emas completed
  # made count item in ema_count df and set to "ema" when ema was completed through ema_7
  feature_row <- feature_row %>%
    full_join(score_ratecount_value(the_subid = subid,
                                    the_dttm_label = dttm_label,
                                    x_all = ema_count,
                                    period_durations  = period_durations_later, 
                                    lead = lead,
                                    data_start = dates,
                                    col_name = "count",
                                    col_values = "ema"),
              by = c("subid", "dttm_label"))
  
  # most recent score
  feature_row <- feature_row %>%
    full_join(score_most_recent(the_subid = subid,
                           the_dttm_label = dttm_label,
                           x_all  = ema_long,
                           lead = lead,
                           data_start = dates,
                           col_name = "response",
                           data_type_col_name = "ema_num",
                           data_type_values = str_c("ema_", 2:10)),
              by = c("subid", "dttm_label"))

  # median; use because may be more stable than mean
  # ema_1 not included b/c handled by lapses above
  feature_row <- feature_row %>%
    full_join(score_median(the_subid = subid,
                           the_dttm_label = dttm_label,
                           x_all  = ema_long,
                           period_durations = period_durations_morning, 
                           lead = lead,
                           data_start = dates,
                           col_name = "response",
                           data_type_col_name = "ema_num",
                           data_type_values = str_c("ema_", 8:10)),
              by = c("subid", "dttm_label"))
  
  feature_row <- feature_row %>%
    full_join(score_median(the_subid = subid,
                           the_dttm_label = dttm_label,
                           x_all  = ema_long,
                           period_durations = period_durations_later,
                           lead = lead,
                           data_start = dates,
                           col_name = "response",
                           data_type_col_name = "ema_num",
                           data_type_values = str_c("ema_", 2:7)),  
              by = c("subid", "dttm_label"))

  # max
  # ema_1 not included b/c handled by lapses above
  feature_row <- feature_row %>%
    full_join(score_max(the_subid = subid,
                        the_dttm_label = dttm_label,
                        x_all  = ema_long,
                        period_durations = period_durations_morning,
                        lead = lead,
                        data_start = dates,
                        col_name = "response",
                        data_type_col_name = "ema_num",
                        data_type_values = str_c("ema_", 8:10)),
              by = c("subid", "dttm_label"))
  
  feature_row <- feature_row %>%
    full_join(score_max(the_subid = subid,
                        the_dttm_label = dttm_label,
                        x_all  = ema_long,
                        period_durations = period_durations_later,
                        lead = lead,
                        data_start = dates,
                        col_name = "response",
                        data_type_col_name = "ema_num",
                        data_type_values = str_c("ema_", 2:7)),
              by = c("subid", "dttm_label"))

  # min
  # ema_1 not included b/c handled by lapses above
  feature_row <- feature_row %>%
    full_join(score_min(the_subid = subid,
                        the_dttm_label = dttm_label,
                        x_all  = ema_long,
                        period_durations = period_durations_morning,
                        lead = lead,
                        data_start = dates,
                        col_name = "response",
                        data_type_col_name = "ema_num",
                        data_type_values = str_c("ema_", 8:10)),
              by = c("subid", "dttm_label"))
  
  feature_row <- feature_row %>%
    full_join(score_min(the_subid = subid,
                        the_dttm_label = dttm_label,
                        x_all  = ema_long,
                        period_durations = period_durations_later,
                        lead = lead,
                        data_start = dates,
                        col_name = "response",
                        data_type_col_name = "ema_num",
                        data_type_values = str_c("ema_", 2:7)),
              by = c("subid", "dttm_label"))
  
  feature_row <- feature_row %>% 
    mutate(label_num = the_label_num)
  
  feature_row
}
```

Add demographics
```{r}
features <- features %>% 
  left_join(demos, by = "subid")
```

Add outcome label
```{r}
features <- features %>%
  mutate(lapse = labels$lapse) 
```

### Review & save

```{r}
features %>% 
  relocate(label_num, subid, dttm_label, lapse) %>% 
  glimpse() %>% 
  write_csv(here(path_insight, "features.csv"))

```



