---
title: "Create AASE dichotomous outcome features file"
author: "Gaylen Fronk"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/insight", 
      "/Volumes/private/studydata/risk/knits/insight")
    )
  })
---

### Code Status

Bringing in code from mak_jobs.R (from EMA project) to make lapses.csv file needed for making features

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_shared <- "P:/studydata/risk/data_processed/shared"
          path_insight <- "P:/studydata/risk/data_processed/insight"},
        
        # IOS paths
        Darwin = {
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_insight <- "/Volumes/private/studydata/risk/data_processed/insight"}
)
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
```

var_score() function

```{r}
var_score <- function(d, forward_items, reverse_items = NULL, item_range = NULL, 
                      prorate = TRUE, max_miss = .20) {
  library(dplyr)
  
  # select relevant items
  d <- d %>% 
    select(all_of(forward_items), all_of(reverse_items))
  
  # check for out of range
  if (!is.null(item_range)) {
    if (!((min(d, na.rm = TRUE) %in% item_range || max(d, na.rm = TRUE) %in% item_range))) {
      stop("Item score(s) out of range")
    }
  }
  
  # check that length of range == 2 if reverse is not null
  if (!is.null(reverse_items) && length(item_range) != 2) {
    stop("Must specify item range (range) to reverse score items")
  }
  
  # reverse score relevant items
  if (!is.null(reverse_items)) {
    for (v in reverse_items) {                  
      d <- d %>% mutate({{v}} := (sum(item_range) - .data[[v]]))
    }   
  }
  
  max_missing_cols <- ncol(d) * max_miss
  d <- d %>% 
    rowwise() %>% 
    mutate(total = if_else(prorate,
                           mean(c_across(), na.rm = TRUE) * ncol(.), # if true
                           sum(c_across(), na.rm = TRUE))) %>%       # if false
    mutate(missing_cols = sum(is.na(c_across(!contains("total"))))) %>% # count miss cols excluding total
    mutate(total = if_else(missing_cols > max_missing_cols,  # set total to NA if too many missing
                           NA_real_,
                           total)) %>% 
    ungroup()
  return(d$total)
}
```

### Read in data 

Read in lapses.csv (insight)

```{r}
lapses <- read_csv(file.path(path_insight, "lapses.csv"),
                   show_col_types = FALSE) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tz = "America/Chicago")) %>% 
  glimpse()
```

Read in study_dates.csv (insight)

```{r}
dates <- read_csv(file.path(path_insight, "study_dates.csv"),
                  show_col_types = FALSE) %>% 
  select(subid, study_start, ema_end) %>% 
  mutate(across(c(study_start, ema_end), 
                ~ with_tz(., tz = "America/Chicago"))) %>% 
  glimpse()
```

Read in intake.csv (shared)

```{r}
intake <- read_csv(file.path(path_shared, "intake.csv"), 
                   show_col_types = F) %>% 
  select(subid, starts_with("aase")) %>% 
  mutate(across(starts_with("aase"),
                ~ case_when(
                  . == "Not at all" ~ 0,
                  . == "Not very" ~ 1,
                  . == "Moderately" ~ 2,
                  . == "Very" ~ 3,
                  . == "Extremely" ~ 4,
                  TRUE ~ NA_integer_
                ))) %>% 
  mutate(aase_total = var_score(., forward_items = str_c("aase_", 1:20),
                                item_range = c(0, 4))) %>% 
  select(subid, aase_total) %>% 
  glimpse()
```

### Combine data

Remove any lapses outside study dates

```{r}
included_lapses <- lapses %>% 
  left_join(., dates, by = "subid") %>% 
  filter(dttm_obs > study_start) %>% 
  filter(dttm_obs < ema_end) %>% 
  glimpse()
  
```
(none excluded, still 1029 observations)

Create dichotomous outcome variable (any lapses during study period or not)

```{r}
subs_with_lapses <- unique(included_lapses$subid)

aase_dich <- intake %>% 
  mutate(lapse = if_else(subid %in% subs_with_lapses, "yes", "no")) %>% 
  glimpse()
```

Confirm counts

```{r}
janitor::tabyl(aase_dich$lapse)

length(subs_with_lapses)
```

Include only N = 151 sample

```{r}
aase_dich <- aase_dich %>% 
  right_join(., dates, by = "subid") %>% 
  select(subid, lapse, aase_total)
```

### Dichotomous lapse proportion among sample

```{r}
janitor::tabyl(aase_dich$lapse)
```
Matches summary stats from EMA project (ana_lapses)

### Write out aase_dich features file

```{r}
aase_dich %>% 
  write_csv(file.path(path_insight, "aase_dich_v1.csv"))
```



