---
title: "Opens & reviews combined feature file from CHTC"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Code Status

In Use

### Notes   

This script opens the aggregate features.csv file from CHTC, checks for missing jobs, and completes other EDA.

Inputs:  

Returned CHTC files: 

* features.csv

Jobs input file   

* jobs.csv 

Raw EMA file to confirm insight question (ema_10) values

* ema.csv

Output:

* features_[version].csv (write to processed data path)


### Set Up Environment

Version
```{r}
version <- "v1"
```


Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) 
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("cols", "readr")
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
library(tidyverse)  
library(janitor) 
library(lubridate)
library(stringr)
library(skimr)
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
```

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_jobs <- str_c("P:/studydata/risk/chtc/insight/features")
          path_processed <- str_c("P:/studydata/risk/data_processed/insight")},
        
        # IOS paths
        Darwin = {
          path_jobs <- str_c("/Volumes/private/studydata/risk/chtc/insight/features")
          path_processed <- str_c("/Volumes/private/studydata/risk/data_processed/insight")},
        
        # Linux paths
        Linux = {
          path_jobs <- str_c("~/mnt/private/studydata/risk/chtc/insight/features")
          path_processed <- str_c("~/mnt/private/studydata/risk/data_processed/insight")}
)
```

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


### Check raw files

Read job file
```{r read_jobs}
jobs <- read_csv(file.path(path_jobs, "input", "jobs.csv"), 
                 show_col_types = FALSE, 
                 col_names = FALSE) %>% 
  rename(job_start = X1, job_end = X2) %>% 
  glimpse()
```

Get counts of labels
```{r count_labels}
(n_labels <- jobs %>% 
   mutate(n_bundle = job_end - job_start + 1) %>% 
   summarise(n_labels = sum(n_bundle)) %>% 
   pull(n_labels))
```

Read ema.csv file
```{r read_ema}
ema <- read_csv(file.path(path_processed, "ema.csv"),
                show_col_types = FALSE) %>% 
  select(dttm_obs, subid, ema_10) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tz = "America/Chicago")) %>% 
  glimpse()
```

Read features.csv (aggregate CHTC file)

```{r read_features}
features <- read_csv(file.path(path_jobs, "output", "features.csv"),
                     show_col_types = FALSE) %>% 
  mutate(dttm_label = with_tz(dttm_label, tz = "America/Chicago")) %>% 
  glimpse()

```

Have already confirmed no non-zero error files at CHTC.

### Brief EDA on Features

#### Basic Checks

Check for correct number of features (matches number of labels)  
```{r eda_feature_count}
if (nrow(features) == n_labels) {
  message("Features detected for ", n_labels, " labels.  Correct!")
} else {
  stop("Missing features for label_num: \n", 
       subset(1:n_labels, !1:n_labels %in% features$label_num))
}
```

Check for duplicate labels
```{r eda_labels}
features %>% 
  count(subid, dttm_label) %>% 
  filter(n > 1)
```

(none!)

Confirm outcome distribution
```{r eda_outcome}
features %>% 
  tabyl(lapse)
```

Confirm all subjects
```{r eda_sample}
length(unique(features$subid))
```

Should be N = 151

Count observations per subject
```{r eda_obs_per_sub}
features %>% 
  tabyl(subid) %>% 
  arrange(desc(n))
```

Subid 193 has only 1 observation --> keep an eye on this during analyses

Check for NaN.  Select only columns with NaN
```{r eda_nan}
features %>% 
  summarise(across(everything(), ~ sum(is.nan(.x)))) %>% 
  select(where(function(x) x < 0)) %>% 
  glimpse() 
```

(none!)

#### Descriptives on numeric variables

Skim features
```{r eda_skim_features}
stats <- features %>% skim_without_charts()

stats %>% summary()
```

Missing values
```{r eda_missing}
# all
stats %>% 
  yank("numeric") %>% 
  select(skim_variable, n_missing, complete_rate) %>% 
  arrange(complete_rate, skim_variable) %>% 
  print_kbl

```

No missing values on any variables.

Spread
```{r eda_spread}
#  all
stats %>% 
  yank("numeric") %>% 
  mutate(range = p100 - p0) %>% 
  select(skim_variable, sd, range, p0, p100) %>% 
  filter(!skim_variable == "subid" & !skim_variable == "label_num") %>% 
  arrange(desc(range), skim_variable) %>% 
  print_kbl

# just "raw" (rrecent) ema variables & demos (age) to make sure ranges seem appropriate
# ema 2-5: valid values range from 0 to 12
# ema 6-10: valid values range from 1 to 11
stats %>% 
  yank("numeric") %>% 
  mutate(range = p100 - p0) %>% 
  select(skim_variable, sd, range, p0, p100) %>% 
  filter(str_detect(skim_variable, "rrecent") | str_detect(skim_variable, "demo")) %>% 
  arrange(desc(range), skim_variable) %>% 
  print_kbl

# ema_10 (insight) specifically
stats %>% 
  yank("numeric") %>% 
  mutate(range = p100 - p0) %>% 
  select(skim_variable, sd, range, p0, p100) %>% 
  filter(str_detect(skim_variable, "ema_10")) %>% 
  arrange(desc(range), skim_variable) %>% 
  print_kbl
```

Central tendency
```{r eda_central_tendency}
# all
stats %>% 
  yank("numeric") %>% 
  select(skim_variable, mean, p50, p0, p100) %>% 
  filter(!skim_variable == "subid" & !skim_variable == "label_num") %>% 
  arrange(desc(mean), skim_variable) %>% 
  print_kbl

# ema_10 (insight) specifically
stats %>% 
  yank("numeric") %>% 
  select(skim_variable, mean, p50, p0, p100) %>% 
  filter(str_detect(skim_variable, "ema_10")) %>% 
  arrange(desc(mean), skim_variable) %>% 
  print_kbl
```

#### Review character variables

Unique values
```{r}
chr_vars <- stats %>% 
  yank("character") %>% 
  filter(!str_detect(skim_variable, "lapse")) %>% 
  pull(skim_variable)

for (chr_var in chr_vars) {
  message(str_c("Unique values for ", chr_var, ":"))
  features %>% 
    select(all_of(chr_var)) %>% 
    pull(chr_var) %>% 
    unique(.) %>% 
    print()
}
```

### Compare to "raw" insight values

```{r eda_compare_insight}
ema_comp <- ema %>% 
  filter(!is.na(ema_10)) %>% 
  filter(subid %in% features$subid) %>% 
  rename(raw_ema_10 = ema_10) %>% 
  mutate(dttm_label = dttm_obs + seconds(1)) 

feat_comp <- features %>% 
  select(subid, starts_with("dttm"), 
         recent_ema_10 = ema_10.p0.l0.rrecent_response)

insight_comp <- feat_comp %>% 
  left_join(., ema_comp, by = c("subid", "dttm_label")) %>% 
  arrange(subid, dttm_label) %>% 
  select(subid, raw_ema_10, recent_ema_10, 
         dttm_obs, dttm_label)

print_kbl(insight_comp)

identical(insight_comp$raw_ema_10, insight_comp$recent_ema_10)

identical(insight_comp$dttm_label, (insight_comp$dttm_obs + seconds(1)))
```

### Write feature file

```{r save_features}
features %>% 
  write_csv(file.path(path_processed, str_c("features_", version, ".csv")))
```

```{r, eval = FALSE, include=FALSE}
# Render knit file manually to different location

rmarkdown::render(input = file.path(
  "insight/mak_scripts/mak_combined_features.Rmd"),
  output_dir = file.path("P:/studydata/risk/knits/insight"),
  output_file = str_c("mak_combined_features_", version,
                      ".html"),
  env = new.env())
```

