---
title: "Downloads all qualtrics surveys via API"
author: "John Curtin"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
Get all qualtrics data via API.  Saves individual files using labels rather than
numeric codes


Outputs
* see file_info df

### Setup
Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(StudySupport)
# source('P:/toolboxes/lab_support/download_qualtric.R') # replaces apiGetSurvey, but I left commented since you needed StudySupport anyhow
```

Paths 
```{r}
path_out <- "raw_data/qualtrics"
```


This is a df with the names (for saving file) and survey ids for all surveys.
There are multiple versions of most of the sessions forms.  Their associated dates 
of use are noted in comments.

Note from Susan: there is one session form for followup_12 (SV_5cMpUmQsiX7z8Ff, 09/29/2017) that looks like it may 
have no data so not downloaded. 

```{r file_info}
file_info <- tribble(
  ~name,                            ~id,
  "screen.csv",                     "SV_4GfoMwQRJXoTJQ1",
  "intake.csv",                     "SV_b49P4TTAAlVMjUF",
  "followup_12.csv",                "SV_3a8KivBmHug8f65",
  "followup_3.csv",                 "SV_6rn6hZggROy1Mvr",
  "ema_morning.csv",                "SV_bBGKAzNQeyXuN6Z",
  "ema_later.csv",                  "SV_aViOZNT66b7wff7",
  "sleep_schedule.csv",             "SV_exqjLqg1OohSqvX",
  "session_screen_v1.csv",          "SV_eQIxBIm5yNmza4J",  # 12/02/2017-10/04/2017
  "session_screen_v2.csv",          "SV_9nLLkVXQa8Fr7SJ",  # 10/09/2017-11/22/2017
  "session_screen_v3.csv",          "SV_8dHQWRHtYVPXjvf",  # 01/17/2018-09/19/2018
  "session_intake_v1.csv",          "SV_3VmIJvblYsSRLFj",  # 02/02/2017-10/04/2017
  "session_intake_v2.csv",          "SV_9Z7jcYTueFJhXNz",  # 10/14/2017-03/01/2018
  "session_intake_v3.csv",          "SV_bKOWdAaAvbYDZjL",  # 02/28/2018-09/25/2019  
  "session_followup_12_v1.csv",     "SV_3sZaisKdLIzqrg9",  # 03/31/2017-10/02/2017  
  "session_followup_12_v2.csv",     "SV_25cfIkcmAg5CqkR",  # 11/01/2017-05/01/2018
  "session_followup_12_v3.csv",     "SV_0TYHA6ZZJIIG2EZ",  # 05/01/2018-11/07/2019
  "session_followup_3_v1.csv",      "SV_7NWbgwJi9HraNed",  # 06/05/2017              
  "session_followup_3_v2.csv",      "SV_3OZHtzKM3DobAMZ",  # 09/15/2017-10/04/2017
  "session_followup_3_v3.csv",      "SV_aVKJF1YIymDGxlr",  # 10/19/2017-03/27/2018
  "session_followup_3_v4.csv",      "SV_cMahpnPZchotCW9",  # 05/03/2018-12/05/2019
  "phone_screen_v1.csv",            "SV_50dTQxEbednaSWh",  # 01/19/2017-08/03/2017
  "phone_screen_v2.csv",            "SV_bE1Hc7S4qX04FZH",  # 09/14/2017-04/30/2018
  "phone_screen_v3.csv",            "SV_9EwFgEzJrMj6Uap",  # 03/27/2018-06/07/2018
  "phone_screen_v4.csv",            "SV_bKHIZeF1RBMTSXr",  # 04/13/2018-09/10/2019
  "feedback.csv",                   "SV_3mda25xsdUcADNr",
  "enrollment_raw.csv",             "SV_er3BuWp5ZLOjAzP")
```


Download and save all files in the file_info df
```{r get_surveys}
get_and_save <- function(id, name, path_out){
  apiGetSurvey(SurveyID=id, UseLabels = TRUE) %>%   # from StudySupport
    write_csv(file.path(path_out, name))
}

walk2(file_info$id, file_info$name, get_and_save,  path_out = path_out)
```

Also get a formatted version of the enrollment database
```{r get_formatted_enroll}
edbGetCleanDB(SurveyID = "SV_er3BuWp5ZLOjAzP") %>% 
  write_csv(file.path(path_out, "enrollment_database_formatted.csv"))
```