---
title: "Characterize best GPS model"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/gps", 
      "/Volumes/private/studydata/risk/knits/gps")
    )
  })
---

### Code Status

in development

### Notes
This script aggregates all results/metrics for a batch or batches of jobs
that train all model configurations for a specific outcome/label window.  Set label here

```{r}
window <- "1day"
```


### Set Up Environment

Absolute paths
```{r, absolute paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          #path_shared <- "P:/studydata/risk/data_processed/shared"
          path_gps_input <- "P:/studydata/risk/chtc/gps"
          path_gps_processed <- "P:/studydata/risk/data_processed/gps"},

        # IOS paths
        Darwin = {
          #path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"
          path_gps_input <- "/Volumes/private/studydata/risk/chtc/gps"
          path_gps_processed <- "/Volumes/private/studydata/risk/data_processed/gps"}
        )
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("spec", "yardstick")
conflict_prefer("col_factor", "vroom")

library(here)  # establish project directory consistently as working directory
```


Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)
library(lubridate)
library(vroom)
library(purrr)
library(furrr)
library(janitor)
library(ggplot2)
library(kableExtra)
library(vip)

theme_set(theme_classic()) 
```


Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


Source training controls 
```{r}
# source("gps/chtc/training/training_controls_1day.R")
# 
source(here("../lab_support/chtc/static_files/input/fun_chtc.R"))
source(here("../lab_support/print_kbl.R"))

```





### Review View best performing models   

Open average metrics
```{r}
metrics_avg <- 
  vroom(here(path_gps_processed, str_c("metrics_avg_train_", window, ".csv")), show_col_types = FALSE)
```

Best AUC for algorithms x feature sets
```{r}
metrics_avg %>% 
  group_by(algorithm, feature_set, resample) %>% 
  arrange(desc(roc_auc)) %>% 
  slice(1) %>% 
  ungroup %>% 
  arrange(desc(roc_auc)) %>% 
  print_kbl()
```





### Refit best model locally

TEMP.  HARD CODE FOR NOW
Best model is glmnet (CURRENTLY)
```{r}
path_best <- "P:/studydata/risk/chtc/gps/train_1day_glmnet/input"   #UPDATE/EDIT
source(here(path_best, "training_controls.R"))
```


Read in data and create splits
```{r}
d <- vroom(here(path_best, "data_trn.csv.xz")) %>% 
  rename(y = {{y_col_name}})

set.seed(102030)
splits <- if (str_split(str_remove(cv_type, "_x"), "_")[[1]][1] == "group") {
  make_splits(d = d, cv_type = cv_type, group = group)
} else { 
  make_splits(d = d, cv_type = cv_type)
}
```

```{r}
config_best <- metrics_avg %>% 
  arrange(desc(roc_auc)) %>% 
  slice(1) %>% 
  glimpse()
```

Replicates best CHTC models using decision metric specified in study's training controls  
```{r}
# build recipe
rec <- build_recipe(d = d, job = config_best)
    
# fit model and get results
fit_best <- tune_best_model(best_model = config_best, rec = rec, folds = splits, cv_type = cv_type)

metrics_best <- fit_best[[3]]
preds_best <- fit_best[[2]] %>% 
  select(truth = y,
         estimate = .pred_class,
         prob = .pred_yes)
```


```{r}
metrics_best %>% collect_metrics()
```


```{r}
cm <- preds_best %>% 
  conf_mat(truth, estimate)

plot_cm <- cm %>% 
  autoplot()

cm %>% summary(event_level = "second")
```

```{r}
plot_probs <- preds_best %>% 
  ggplot(data = ., aes(x = prob)) + 
   geom_histogram(bins = 15) +
   facet_wrap(~truth, nrow = 2) +
   xlab("Pr(Lapse)")
plot_probs
```

Here is single ROC by concatenating all folds.
Could also plot ROC by fold but maybe too confusing?
```{r}
roc_data <- preds_best %>% 
  roc_curve(prob, truth = truth, event_level = "second")

# # not best method b/c across folds.  Better to use average roc across folds?
# preds_best %>% 
#   roc_auc(prob, truth = truth, event_level = "second")

plot_roc <- roc_data %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path() +
  geom_abline(lty = 3) +
  coord_equal() +
  labs(x = "1 - Specificity (FPR)",
       y = "Sensitivity (TPR)")
```


printing plots
```{r}
# library(ggplot2)
# myplot1 <- ggplot(iris, aes(Sepal.Length, Sepal.Width)) + 
#   geom_point()
# myplot2 <- ggplot(iris, aes(Species, Sepal.Length)) + 
#   geom_boxplot()
# 
# # Print plots to a pdf file
# pdf("ggplot.pdf")
# print(myplot1)     # Plot 1 --> in the first page of PDF
# print(myplot2)     # Plot 2 ---> in the second page of the PDF
# dev.off() 

# jpeg(filename = "Rplot%03d.jpg",
#      width = 480, height = 480, units = "px", pointsize = 12,
#      quality = 75,
#      bg = "white", res = NA, family = "", restoreConsole = TRUE,
#      type = c("windows", "cairo"), antialias,
#      symbolfamily="default")

```



