---
title: "Posterior probabilities across models for Insight study (version `r version`)"
author: "John Curtin"
date: "`r lubridate::today()`"
format:
  html:
    embed-resources: true
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Code Status

In use with iterative improvement.

Updating for use with study-insight

### Notes
Can review online docs for 

* [how to use rstanarm](https://cran.r-project.org/web/packages/rstanarm/vignettes/rstanarm.html)
* [priors](https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html)
* [warnings](https://mc-stan.org/misc/warnings.html)
* [tutorial on rstanarm and shinystan](https://www.tqmp.org/RegularArticles/vol14-2/p099/p099.pdf)
* [R Bloggers on perf_mod](https://www.r-bloggers.com/2019/12/tidyposteriors-bayesian-approach-to-model-comparison/)

### Set Up Environment

```{r}
study <- "insight"
version <- "v2"
```



Packages for script
```{r packages_script, message=FALSE, warning=FALSE}
library(tidyposterior)
library(tidyverse)
library(tidymodels)

theme_set(theme_classic()) 
```

Absolute paths
```{r absolute_paths}

switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_shared <- str_c("P:/studydata/risk/data_processed/shared")
          path_processed <- str_c("P:/studydata/risk/data_processed/", study)
          path_models <- str_c("P:/studydata/risk/models/", study)},
        
        # IOS paths
        Darwin = {
          path_shared <- str_c("P:/studydata/risk/data_processed/shared")
          path_processed <- str_c("/Volumes/private/studydata/risk/data_processed/",
                                  study)
          path_models <- str_c("/Volumes/private/studydata/risk/models/",
                               study)},
        
        # Linux paths
        Linux = {
          path_shared <- str_c("~/mnt/private/studydata/risk/data_processed/shared")
          path_processed <- str_c("~/mnt/private/studydata/risk/data_processed/",
                                  study)
          path_models <- str_c("~/mnt/private/studydata/risk/models/",
                               study)}
)
```


Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```


Source training controls 
```{r source}
# EDA
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
```


### Read in preds and metrics for best model

```{r load_preds_metrics}

auc_1w_all <- read_rds(file.path(path_models, 
                                 str_c("outer_metrics_1week_all_", 
                                       version, "_nested.rds"))) |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10), 3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_1w_ins <- read_rds(file.path(path_models, 
                                 str_c("outer_metrics_1week_insight_only_", 
                                       version, "_nested.rds"))) |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_1w_aase <- read_rds(file.path(path_models, 
                                  str_c("outer_metrics_1week_aase_only_", 
                                        version, "_nested.rds"))) |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_dich_aase <- read_rds(file.path(path_models, 
                                    str_c("outer_metrics_dichotomous_aase_only_", 
                                          version, "_nested.rds"))) |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc <- auc_1w_all %>% 
  rename(week_all = roc_auc) %>% 
  mutate(week_ins = auc_1w_ins$roc_auc,
         week_aase = auc_1w_aase$roc_auc,
         dich_aase = auc_dich_aase$roc_auc) %>% 
  glimpse()
```

```{r auc_plots}
auc_1w_all %>% 
  ggplot() + 
  geom_histogram(aes(x = roc_auc), bins = 10)

auc_1w_ins %>% 
  ggplot() + 
  geom_histogram(aes(x = roc_auc), bins = 10)

auc_1w_aase %>% 
  ggplot() + 
  geom_histogram(aes(x = roc_auc), bins = 10)

auc_dich_aase %>% 
  ggplot() + 
  geom_histogram(aes(x = roc_auc), bins = 10)
```

### All models

```{r bayes}
# from ?perf_mod()
# Repeated CV (id = repeat, id2 = fold within repeat)
# with a common variance:  statistic ~ model + (model | id2/id)
set.seed(101)
pp <- auc |> 
  rename(id = repeat_num,
         id2 = fold_num) |> 
  perf_mod(formula = statistic ~ model + (1 | id2/id),
           # prior_intercept = rstanarm::student_t(autoscale = TRUE),
           # prior = rstanarm::student_t(autoscale = TRUE),
           transform = tidyposterior::logit_trans,  # for skewed & bounded AUC
           # iter = 2000, chains = 4,  
           adapt_delta = .99,
           # cores = 4, seed = 12345,
           family = gaussian, 
  )  
```

```{r}
rstanarm::prior_summary(pp$stan)
```

```{r}
summary(pp$stan)
```

```{r}
# shinystan::launch_shinystan(pp$stan)
```

```{r}
pp %>%  write_rds(file.path(path_models, 
                            str_c("posteriors_", version, "_nested.rds")))
```

### Model posterier CIs

```{r}
pp_tidy <- pp %>% 
  tidy(seed = 123)

q = c(.025, .5, .975)
pp_tidy %>% 
  group_by(model) %>% 
  summarize(median = quantile(posterior, probs = q[2]),
            lower = quantile(posterior, probs = q[1]), 
            upper = quantile(posterior, probs = q[3])) %>% 
  mutate(model = factor(model, 
                        levels = c("week_all", "week_ins", 
                                   "week_aase", "dich_aase"),
                        labels = c("One week / All Features",
                                   "One week / Insight only", 
                                   "One week / AASE only",
                                   "Dichotomous / AASE only")),
         y = 1000) |> 
  arrange(model)

```


### Model contrasts

```{r}
pp_contrasts <- contrast_models(pp, 
                                list("week_ins", "week_ins", "week_ins"), 
                                list("week_aase", "dich_aase", "week_all"))

summary(pp_contrasts, size = 0.01, prob = 0.95)
pp_contrasts %>% autoplot(size = 0)
```

### Plots

Model posteriors
```{r}
ci <- pp_tidy %>% 
  summary() %>% 
  mutate(model = factor(model, 
                        levels = c("week_all", "week_ins", 
                                   "week_aase", "dich_aase"),
                        labels = c("One week / All Features",
                                   "One week / Insight only", 
                                   "One week / AASE only",
                                   "Dichotomous / AASE only")),
         y = 1000)

pp_tidy %>% 
  mutate(model = factor(model, 
                        levels = c("week_all", "week_ins", 
                                   "week_aase", "dich_aase"),
                        labels = c("One week / All Features",
                                   "One week / Insight only", 
                                   "One week / AASE only",
                                   "Dichotomous / AASE only")),
         y = 1000) %>%
  ggplot() + 
  geom_histogram(aes(x = posterior, fill = model), 
                 color = "black", alpha = .4, 
                 bins = 30) +
  geom_segment(mapping = aes(y = y+100, yend = y-100, x = mean, xend = mean,
                             color = model),
               data = ci) +
  geom_segment(mapping = aes(y = y, yend = y, x = lower, 
                             xend = upper, color = model),
               data = ci) +
  facet_wrap(vars(model), ncol = 1) +
  scale_y_continuous("Posterior Probability", 
                     breaks = c(0, 500, 1000)) +
  # ylab("Posterior Probability Density") +
  xlab("Area Under ROC Curve") +
  labs(color = "Model", fill = "Model")
```

model contrast posteriors

```{r model_contrast_posteriors}
ci <- pp %>%
  contrast_models(list("week_ins", "week_ins", "week_ins"), 
                  list("week_aase", "dich_aase", "week_all")) %>% 
  summary(size = .01) %>% 
  mutate(contrast = factor(contrast, 
                           levels = c("week_ins vs dich_aase", 
                                      "week_ins vs week_aase", 
                                      "week_ins vs week_all"),
                           labels = c("Insight vs. AASE (dichotomous)", 
                                      "Insight vs. AASE (week)", 
                                      "Insight vs. All Features")),
         y = 700)

pp %>% 
  tidy(seed = 123) %>%   
  group_by(model) %>% 
  mutate(sample = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(names_from = model, values_from = posterior) %>% 
  mutate(ins_vs_aasewk = week_ins - week_aase,
         ins_vs_aasedich = week_ins - dich_aase,
         ins_vs_all = week_ins - week_all) %>% 
  pivot_longer(cols = ins_vs_aasewk:ins_vs_all,
               names_to = "contrast",
               values_to = "posterior") %>% 
  mutate(contrast = factor(contrast, 
                           levels = c("ins_vs_aasedich", 
                                      "ins_vs_aasewk", 
                                      "ins_vs_all"),
                           labels = c("Insight vs. AASE (dichotomous)", 
                                      "Insight vs. AASE (week)", 
                                      "Insight vs. All Features"))) %>% 
  ggplot() +
  geom_histogram(aes(x = posterior, fill = contrast), 
                 color = "black", alpha = .4, bins = 30) +
  geom_vline(xintercept = -.01, color = "yellow", 
             linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = .01, color = "yellow", 
             linetype = "dashed", linewidth = 1) +
  geom_segment(mapping = aes(y = y+100, yend = y-100, x = mean, xend = mean,
                             color = contrast), data = ci) +
  geom_segment(mapping = aes(y = y, yend = y, x = lower, xend = upper, 
                             color = contrast), data = ci) +
  facet_wrap(~contrast, ncol = 1) +
  ylab("Posterior Probability") +
  xlab("Model Contrast for AUC")
```


