---
title: "Meta Feature Engineering Shell"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
editor_options: 
  chunk_output_type: console
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/meta", 
      "/Volumes/private/studydata/risk/knits/meta")
    )
  })
---

### Code status

This shell is still in progress. Currently includes a demo of get_feature_period function. Working on improving demo of make_features().    


### Conclusions



### Notes

This script serves as a shell for the feature engineering script for meta study.


### Set up Environment

Chunk Defaults
```{r defaults, include=FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

Absolute paths
```{r, paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_meta <- "P:/studydata/risk/data_processed/meta"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_meta <- "/Volumes/private/studydata/risk/data_processed/meta"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"}
        )
```

Relative paths
```{r}
path_fun_risk <- "shared"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}
library(conflicted) # detect and warn about function conflicts
 conflict_prefer("filter", "dplyr")
 conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}
# for data wrangling
library(tidyverse)  # always need this
library(janitor) # cleaning and EDA
library(lubridate)
library(purrr)
library(vroom)

# for plots and tables
library(ggplot2)
theme_set(theme_bw()) # or theme_set(theme_classic())
library(kableExtra)
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_fun_risk, "fun_risk.R"))
```

### Read in Data

Meta logs dataframe  
```{r}
logs <- vroom(here(path_meta, "meta_logs.csv"), col_types = vroom::cols()) %>% 
  mutate(dttm_obs = with_tz(dttm_obs, tzone = "America/Chicago")) %>% 
  glimpse()
```

Lapse labels dataframe
```{r}
labels_05 <- vroom(here(path_shared, "labels_05.csv"), col_types = vroom::cols()) %>% 
  select(subid, dttm_label = hour) %>% 
  mutate(dttm_label = with_tz(dttm_label, tzone = "America/Chicago")) %>% 
  glimpse()
```

### Create Demo Data

Narrow down to logs for only 10 random subids for demo
```{r}
set.seed(20210606)

subids_demo <- logs %>% 
  count(subid) %>% 
  slice_sample(n = 10)

logs_demo <- logs %>% 
  filter(subid %in% subids_demo$subid) %>% 
  glimpse()
```


Narrow down lapse labels to 10 random lapses for demo
```{r}
labels_demo <- labels_05 %>% 
  filter(subid %in% subids_demo$subid) %>% 
  slice_sample(n = 10)

labels_demo
```



### Demo of make_features

Run function w/ 72 hour period duration hours and 0 lead hours    

Add features for sms variables
```{r}
logs_demo_sms <- logs_demo %>% 
  filter(log_type == "sms") %>% 
  glimpse()


fun_list <- list(n_yes = ~sum(.x == "yes", na.rm = TRUE))


logs_features <- map2_dfr(labels_demo$subid,
                          labels_demo$dttm_label,
                          ~make_features(
                              the_subid = .x,
                              the_dttm_label = .y,
                              data = logs_demo_sms,
                              lead_hours = 0, 
                              period_duration_hours = 72,
                              data_type = "sms",
                              col_list = c(read = "message_read", 
                                           group = "message_is_group", 
                                           failed = "message_failed"),
                              fun_list = fun_list)) %>% 
  glimpse()

# add count of incoming sms messages and total sms messages
logs_features <- logs_features %>% 
  full_join(map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                        the_subid = .x,
                        the_dttm_label = .y,
                        data = logs_demo_sms,
                        lead_hours = 0, 
                        period_duration_hours = 72,
                        data_type = "sms",
                        col_list = c("originated"),
                        fun_list = list(n_incoming = ~sum(.x == "incoming", na.rm = TRUE),
                                        total_n = ~n()))),
            by = c("subid", "dttm_label")) %>% 
  rename_with(~str_replace(.x, "_originated", "")) %>% 
  glimpse()
```



Add features for Voice variables

```{r}
logs_demo_voice <- logs_demo %>% 
  filter(log_type == "voice") %>% 
  glimpse()


logs_features <- logs_features %>% 
  full_join(map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                       the_subid = .x,
                       the_dttm_label = .y,
                       data = logs_demo_voice,
                       lead_hours = 0, 
                       period_duration_hours = 72,
                       data_type = "voice",
                       col_list = c(answered = "is_answered"),
                       fun_list = list(n_yes = ~sum(.x == "yes", na.rm = TRUE)))),
            by = c("subid", "dttm_label")) %>% 
  glimpse()

# add count of incoming calls and total calls
logs_features <- logs_features %>% 
  full_join(map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 72,
                      data_type = "voice",
                      col_list = c("originated"),
                      fun_list = list(n_incoming = ~sum(.x == "incoming", na.rm = TRUE),
                                      total_n = ~n()))),
            by = c("subid", "dttm_label")) %>% 
  rename_with(~str_replace(.x, "_originated", "")) %>% 
  glimpse()

# add stats on call duration
logs_features <- logs_features %>% 
  full_join(map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 72,
                      data_type = "voice",
                      col_list = c(duration = "call_duration"),
                      fun_list = list(mean = ~round(mean(.x, na.rm = TRUE), 2),
                                      sd = ~round(sd(.x, na.rm = TRUE), 2),
                                      min = ~round(min(.x, na.rm = TRUE), 2),
                                      max = ~round(max(.x, na.rm = TRUE), 2)))),
            by = c("subid", "dttm_label")) %>% 
  glimpse()
```


**NOTE: if there are no voice call observations to use for calculating descriptive stats it returns NaN, Inf, or NA**

```{r}
get_feature_period(the_subid = labels_demo$subid[3], 
                   the_dttm_label = labels_demo$dttm_label[3],
                   data = logs_demo_voice,
                   lead_hours = 0, 
                   period_duration_hours = 24)
```

```{r}
fun_list_descriptive <- list(mean = ~round(mean(.x, na.rm = TRUE), 2),
                             sd = ~round(sd(.x, na.rm = TRUE), 2),
                             min = ~round(min(.x, na.rm = TRUE), 2),
                             max = ~round(max(.x, na.rm = TRUE), 2))

test_na <- map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 24,
                      data_type = "voice",
                      col_list = c(duration = "call_duration"),
                      fun_list = fun_list_descriptive)) %>% 
  glimpse()
```


To prevent warning message and unreliable coercion to Inf, -Inf, NaN, Na values surround function with an if else statement   
Note: if_else correctly parses the values as NA but the warning messages still show up. Instead use full if else statement
```{r}
fun_list_descriptive <- list(mean = function(.x) {if (length(.x) > 0) round(mean(.x, na.rm = TRUE), 2)
                                                    else  as.numeric(NA)},
                             sd =   function(.x) {if (length(.x) > 0) round(sd(.x, na.rm = TRUE), 2)
                                                    else as.numeric(NA)},
                             min =  function(.x) {if (length(.x) > 0) round(min(.x, na.rm = TRUE), 2)
                                                    else  as.numeric(NA)},
                             max =  function(.x) {if (length(.x) > 0) round(max(.x, na.rm = TRUE), 2)
                                                    else  as.numeric(NA)})

test_na <- map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 24,
                      data_type = "voice",
                      col_list = c(duration = "call_duration"),
                      fun_list = fun_list_descriptive)) %>% 
  glimpse()
```

Counts do not need to be surrounded by if else because they will simply be 0. Proportions however do need an if else statement - otherwise it will be parsed as NaN by default.   
```{r}
fun_list_originated <- list(n_incoming = ~sum(.x == "incoming", na.rm = TRUE), 
                            n_outgoing = ~sum(.x == "outgoing", na.rm = TRUE), 
                            prop_incoming = ~round(sum(.x == "incoming", na.rm = TRUE)/n(), 2), 
                            n_total = ~n())  

test_na_2 <- map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 24,
                      data_type = "voice",
                      col_list = c("originated"),
                      fun_list = fun_list_originated)) %>% 
  glimpse()
```

```{r}
fun_list_originated <- list(n_incoming = ~sum(.x == "incoming", na.rm = TRUE), 
                            n_outgoing = ~sum(.x == "outgoing", na.rm = TRUE), 
                            prop_incoming = function (.x) {
                              if (length(.x) > 0) {
                              round(sum(.x == "incoming", na.rm = TRUE)/n(), 2)
                            } else as.numeric(NA)}, 
                            n_total = ~n()) 

test_na_2 <- map2_dfr(labels_demo$subid,
                     labels_demo$dttm_label,
                     ~make_features(
                      the_subid = .x,
                      the_dttm_label = .y,
                      data = logs_demo_voice,
                      lead_hours = 0, 
                      period_duration_hours = 24,
                      data_type = "voice",
                      col_list = c("originated"),
                      fun_list = fun_list_originated)) %>% 
  glimpse()
```

