---
title: "discontinuation_summary"
author: "Hannah"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---

### Notes
Purpose: This document summarizes reasons for discontinuation in RISK1.

Inputs:

* Notes (notes.csv)
* Compliance information for discontinued people (OffStudyParticipantCompliance.xlsx)


### Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, results = "hold")
```

Paths 
```{r}
path_compliance <- "administration/Participants/Compliance"
path_notes <- "analysis/notes"
```

Packages and Source
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(readxl)
library(purrr)
library(kableExtra)
```

### Import

```{r notes}

notes <- read_csv(file.path(path_notes, "notes.csv")) %>% 
  slice(-1)

```


```{r compliance}

read_compliance_excel <- function(subid_sheet, xlsx) {
  read_excel(file.path(path_compliance, xlsx),
           sheet = subid_sheet)
}

off_study_sheets <- excel_sheets(file.path(path_compliance, "OffStudyParticipantCompliance.xlsx"))

discontinue_ids <- notes %>% filter(disposition == "discontinue") %>% 
  pull(subid)

discontinue_ids_with_compliance_info <- intersect(off_study_sheets, discontinue_ids)

discontinue_ids_wo_compliance_info <- setdiff(discontinue_ids, off_study_sheets)

discontinue_compliance <- map(discontinue_ids_with_compliance_info, ~read_compliance_excel(.x, "OffStudyParticipantCompliance.xlsx"))
```

### Coding reasons

```{r}
#disposition == "discontinue"
#manually categorized reasons from notes_general
deliberate_discontinue <- c("041", "022", "182", "024")
no_show <- c("036", "008", "017", "062", "173")
discontinued_by_staff <- c("177", "267", "105", "087")
other <- c("055", "061")
no_reason_listed <- notes %>% 
  filter(disposition == "discontinue") %>% 
  filter(is.na(notes_general)) %>% 
  pull(subid)

#disposition == "complete_partial"
#manually categorized reasons from notes_general
deliberate_discontinue <- append(deliberate_discontinue, c("232", "093", "059"))
no_show <-  append(no_show, c("265", "221", "218", "092", "029"))
discontinued_by_staff <- append(discontinued_by_staff, c("209", "205", "200", "172", "116", "082", "047"))
no_reason_listed <- notes %>% 
  filter(disposition == "complete_partial") %>% 
  filter(is.na(notes_general)) %>% 
  pull(subid) %>% append(no_reason_listed)

#dispostion == "withdrawn"
discontinued_by_staff <- append(discontinued_by_staff, "237")
notes <- notes %>% 
  mutate(discontinue_reason = case_when(
    subid %in% deliberate_discontinue ~ "asked to discontinue",
    subid %in% no_show ~ "no show",
    subid %in% discontinued_by_staff ~ "discontinued by staff",
    subid %in% other ~ "other",
    subid %in% no_reason_listed ~ "reason not known"
  ))
```

### Frequency of dispositions

```{r}
notes %>% 
  tabyl(disposition) %>% 
  kable() %>% 
  kable_styling()
```


### Summary of discontinued participants

```{r}

notes %>% 
  select(subid, disposition, discontinue_reason, starts_with("notes")) %>% 
  tabyl(discontinue_reason, show_na = TRUE) %>% 
  mutate(notes = 
           c("", 
             "didn't show up, was out of contact", 
             "details not always given, but often was related to compliance", "one participant was discontinued twice under two subids (005 and 061)", "no notes or information", "not discontinued")) %>% 
  kable() %>% 
  kable_styling()

```

## Compliance information 

The compliance information is not consistent and not consistently formatted. It might not be worth the necessary labor to programatically summarize.
