---
title: "Convert CHTC text log to tibble and get summary statistics"
author: "Kendra Wyant"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
params:
  job_path: "P:/studydata/risk/chtc/meta/train_1day_0_v2_glmnet/"
---

### Code Status

First version of script

### Notes
This script reads in a chtc log and jobs file, runs summary statistics, and outputs 
a csv log tibble with one row per job.  


### Set Up Environment

```{r set_params}
job_path <- params$job_path
```


```{r defaults, include = FALSE}
knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')
options(tibble.print_max = Inf)
```


libraries
```{r warning = FALSE, message = FALSE}
library(tidyverse)
library(here)
library(ggplot2)
library(skimr)
library(janitor)
library(vroom)
```

source function
```{r warning = FALSE, message = FALSE}
source(here("shared/fun_local.R"))
```

### Read in data

Read in log
```{r}
log_raw <- read_lines(here(job_path, "output",
                           list.files(here(job_path, "output"), pattern = "*.log")))

# check log file read in
if (is_empty(log_raw)) {
  stop("Log not read in. Check log is in ", job_path, "output")
}
```

Read in jobs
```{r}
jobs <- vroom(here(job_path, "input/jobs.csv"), col_types = vroom::cols())

# check jobs file is read in
if (is_empty(jobs)) {
  stop("Jobs file not read in. Check jobs file is in ", job_path, "input")
}
```

### Convert log to tibble   
```{r}
log <- convert_log(log_raw, jobs) %>% 
  glimpse()
```

Save log
```{r}
write_csv(log, here(job_path, "output/log.csv"))
```


### Check for unfinished jobs

`r nrow(subset(log, is.na(termination_dttm)))` incomplete jobs
```{r}
log %>% 
  filter(is.na(termination_dttm)) %>% 
  print(n = Inf)

log %>% 
  filter(is.na(termination_dttm)) %>% 
  tabyl(algorithm)

log %>% 
  filter(is.na(termination_dttm)) %>% 
  tabyl(resample)
```


### Skim Run time (minutes)

```{r}
log %>% 
  skim(run_time)
```

```{r}
log %>% 
  group_by(resample) %>% 
  skim(run_time)
```

### Skim memory
```{r}
log %>% 
  skim(contains("memory"))
```

By resample type
```{r}
log %>% 
  group_by(resample) %>% 
  skim(contains("memory"))
```

### Skim disk space
```{r}
log %>% 
  skim(contains("disk"))
```

By resample type
```{r}
log %>% 
  group_by(resample) %>% 
  skim(contains("disk"))
```

### Skim CPUs
```{r}
log %>% 
  skim(contains("cpus"))
```

By resample type
```{r}
log %>% 
  group_by(resample) %>% 
  skim(contains("cpus"))
```


