---
title: "Create lapse labels"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
    code_folding: show
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "P:/studydata/risk/knits/shared"
    )
  })
---

### Set up Environment

Absolute paths
```{r, paths}

# path_admin <- "P:/administration"
path_lab_support <- "P:/toolboxes/lab_support"
path_processed <- "P:/studydata/risk/data_processed/shared"
path_raw <- "P:/studydata/risk/data_raw"
```

Packages for lab workflow 
```{r, packages_workflow, message=FALSE, warning=FALSE}

library(conflicted) # detect and warn about function conflicts
conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

library(here)  # establish project directory consistently as working directory
```

Packages for script
```{r, packages_script, message=FALSE, warning=FALSE}

# for data wrangling
library(tidyverse)  # always need this
library(vroom)
library(janitor)
```

Source for script
```{r, source_script, message=FALSE, warning=FALSE}
source(here(path_lab_support, "print_kbl.R"))
```


### Get Raw Data


EMA lapse reports
```{r}
emam <- vroom(here(path_processed, "ema_morning.csv")) %>% 
  rename_with(~ str_replace(.x, "emam_", "ema_"))


emal <- vroom(here(path_processed, "ema_later.csv"))%>% 
  rename_with(~ str_replace(.x, "emal_", "ema_"))

ema <- bind_rows(emam, emal) %>% 
  select(subid, start_date, end_date, utc, finished,
         contains("ema_1"), -ema_1_5, -ema_10_1) %>% 
  filter(ema_1 == "Yes")

ema %>% print_kbl()
```

Interview lapse reports

* All reported in America/Chicago tz so dropped this variable
* Times indicated only when clearly reported by participant based on notes
* Source is both staff and EDA by Sarah.  Dropped this variable.
* Retained notes to check any suspect reports
```{r}
interview <- vroom(here(path_raw, "additional_lapses.csv")) %>% 
  select(-report_date, -ema_1_5, -time_zone, -source)

interview %>% print_kbl()
```

### EDA for lapses

Confirm with Sarah that all EMA lapses (even cleaned are in America/Chicago)
Discuss with Sarah finished == 0, some with and some without lapse info

#### EMA

KENDRA TO DO


#### Interview

KENDRA TO DO

### Create lapse inputs

#### Make lapses
Merge lapse reports

* Deleted EMA reports that were from unfinished surveys and had NO info about lapse onset
```{r}
# KENDRA - I am deleted unfinished reports with no start time.
# Not sure this will be our final decision but here for now
ema <- ema %>% 
  filter(!(finished == 0 & is.na(ema_1_1) & is.na(ema_1_2))) %>% 
  select(-start_date, -end_date, -utc, -finished, -ema_1, -ema_1_5)
         
lapses <- interview %>% 
  select(subid, ema_1_1, ema_1_2, ema_1_3, ema_1_4) %>% 
  bind_rows(ema)
```


Timestamp lapses
```{r}
# To recode start and end times from EMA
recode_military <- function (time_12hr) {
    case_when(
    time_12hr == "Midnight" ~ "00:00",
    time_12hr == "1 AM" ~ "01:00",
    time_12hr == "2 AM" ~ "02:00",
    time_12hr == "3 AM" ~ "03:00",
    time_12hr == "4 AM" ~ "04:00",
    time_12hr == "5 AM" ~ "05:00",
    time_12hr == "6 AM" ~ "06:00",
    time_12hr == "7 AM" ~ "07:00",
    time_12hr == "8 AM" ~ "08:00",
    time_12hr == "9 AM" ~ "09:00",
    time_12hr == "10 AM" ~ "10:00",
    time_12hr == "11 AM" ~ "11:00",
    time_12hr == "Noon" ~ "12:00",
    time_12hr == "1 PM" ~ "13:00",
    time_12hr == "2 PM" ~ "14:00",
    time_12hr == "3 PM" ~ "15:00",
    time_12hr == "4 PM" ~ "16:00",
    time_12hr == "5 PM" ~ "17:00",
    time_12hr == "6 PM" ~ "18:00",
    time_12hr == "7 PM" ~ "19:00",
    time_12hr == "8 PM" ~ "20:00",
    time_12hr == "9 PM" ~ "21:00",
    time_12hr == "10 PM" ~ "22:00",
    time_12hr == "11 PM" ~ "23:00",
    is.na(time_12hr) ~ NA_character_,
    TRUE ~ "ERROR!")
}

lapses <- lapses %>% 
  mutate(start_time = recode_military(ema_1_2),
         end_time = recode_military(ema_1_4),
         start_lapse = str_c(ema_1_1, " ", start_time),
         end_lapse = str_c(ema_1_3, " ", end_time),
         start_lapse = as_datetime(start_lapse, format = "%m-%d-%Y %H:%M", tz = "America/Chicago"),
         end_lapse = as_datetime(end_lapse, format = "%m-%d-%Y %H:%M", tz = "America/Chicago"),
         duration = difftime(end_lapse, start_lapse, unit = "hour"))
```

Parse ill-formed lapses
```{r}

```

#### EDA lapses

```{r}
hist(as.numeric(lapses$duration))

lapses %>% tabyl(duration)

lapses <- lapses %>% 
  mutate(start_lapse = if_else(duration < 0, NA_POSIXct_, start_lapse))
```

