---
title: "IOS/Voice Logs"
author: "Kendra Wyant"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    pandoc_args: [
      "+RTS", "-K1000m",
      "-RTS"
      ]
    toc: yes
    toc_depth: 3
---

### Notes
Purpose: This script does further cleaning and pre-processing on the ios voice logs specifically for meta study.    

Preprocessing steps:   

1. Correct any identified errors in clean script    

* 2 dates with year 2024   
* Change <<RecentsNumberLocationNotFound>> in location to NA   

2. Tidy responses   

* Recode known variables to character strings   

3. Format numbers to match contacts   

* Contact numbers only have country codes if they non-US numbers   
* No + signs before non-US country codes and no punctuation or spaces in numbers (don't delete * from numbers that use it for blocking numbers)   

Inputs:  
- voice_ios.csv (path_in)    

Output:   
- meta_voice_ios.csv (path_out)  

### Setup
```{css, echo = FALSE}
pre, code {
  max-height: 500px;
  overflow-y: auto;
  white-space: pre !important; 
  overflow-x: auto
}
```

Paths 
```{r}
path_in <- "/Volumes/private/studydata/risk/data_processed/shared"
path_out <- "/Volumes/private/studydata/risk/data_processed/meta"
```

Packages and Source
```{r, message = FALSE}
library(tidyverse)
library(kableExtra)
library(lubridate)
library(janitor)

source("~/lab_support/fun_phone_numbers.R")
```


### Read in logs
Manually specifying column types because for some reason it was reading ZNAME in as logical and losing the little data available
```{r}
logs <- read_csv(file.path(path_in, "voice_ios.csv"), col_types = "iTiiiiiniiiincccccccTTcc") %>% 
  glimpse()
```

### Clean errors identified in clean script EDA

FIX: 2 dates with year 2024 - change to NA and filter out
```{r}
logs %>% 
  arrange(desc(zdate))


logs <- logs %>% 
  mutate(zdate = case_when(date(zdate) == "2024-11-26" ~ as_datetime(NA),
                           TRUE ~ zdate)) %>% 
  filter(!is.na(zdate))
```

FIX: Replace <<RecentsNumberLocationNotFound>> with NA in location
```{r}
logs <- logs %>% 
  mutate(zlocation = case_when(zlocation == "<<RecentsNumberLocationNotFound>>"~ as.character(NA),
                               TRUE ~ zlocation)) %>% 
  glimpse()
```


### Tidy responses

Recode known variable responses to character strings
```{r}

```





<br>


### Format numbers

#### Clean standard variants of numeric numbers with function

Clean numbers with function
```{r}
logs$number_formatted <- map_chr(logs$zaddress, extract_number)
```


























<!-- <br> -->

<!-- #### Spaces and dashes -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "[[:space:]-]")) %>% -->
<!--   select(number, number_formatted) -->
<!-- ``` -->

<!-- <br> -->

<!-- #### Country codes    -->
<!-- *US numbers either have no country code, a +1, a 1 or a +. Some also have no area code.*    -->

<!-- **US country codes that start with +1** -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^\\+1")) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- Pull out area codes to look for any possible exceptions     -->
<!-- One number has area code as 000   -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   # filter to numbers of interest -->
<!--   filter(str_detect(number, "^\\+1") & nchar(number) == 12) %>% -->
<!--   # convert to numbers to vector -->
<!--   select(number) %>%  -->
<!--   unlist() %>%  -->
<!--   # extract first 3 digits after +1 and count -->
<!--   str_sub(3, 5) %>%  -->
<!--   janitor::tabyl()  -->
<!-- ``` -->


<!-- +1 not eliminated on following numbers -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "\\+1") & is.na(number_formatted)) %>%  -->
<!--   filter(is.na(number_formatted)) %>%  -->
<!--   select(number, number_formatted)  -->
<!-- ``` -->

<!-- <br> -->

<!-- **US country codes that start with 1**     -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^1")) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- Pull out area codes to look for any possible exceptions    -->
<!-- Area codes all seem reasonable -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   # filter to numbers of interest -->
<!--   filter(str_detect(number, "^1") & nchar(number) == 11) %>% -->
<!--   # convert to numbers to vector -->
<!--   select(number) %>%  -->
<!--   unlist() %>%  -->
<!--   # extract first 3 digits after 1 and count -->
<!--   str_sub(2, 4) %>%  -->
<!--   janitor::tabyl()  -->
<!-- ``` -->


<!-- 1 not eliminated on following numbers -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^1") & is.na(number_formatted)) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- <br> -->

<!-- **US numbers that start with +**     -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^\\+") & nchar(number) == 11) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- Pull out area codes to look for any possible exceptions      -->
<!-- Don't remove + from 000 number -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   # filter to numbers of interest -->
<!--   filter(str_detect(number, "^\\+") & nchar(number) == 11) %>% -->
<!--   # convert to numbers to vector -->
<!--   select(number) %>%  -->
<!--   unlist() %>%  -->
<!--   # extract first 3 digits after 1 and count -->
<!--   str_sub(2, 4) %>%  -->
<!--   janitor::tabyl()  -->
<!-- ``` -->

<!-- Plus sign not eliminated on following numbers -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^\\+") & is.na(number_formatted)) %>%  -->
<!--   count(number) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- <br> -->

<!-- **Numbers in correct format (10 digits & no country code)**    -->
<!-- 10 digit numbers  -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^[0-9]") & nchar(number) == 10) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- Pull out area codes to look for any possible exceptions    -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   # filter to numbers of interest -->
<!--   filter(nchar(number) == 10) %>% -->
<!--   # convert to numbers to vector -->
<!--   select(number) %>%  -->
<!--   unlist() %>%  -->
<!--   # extract first 3 digits and count -->
<!--   str_sub(1, 3) %>%  -->
<!--   janitor::tabyl() -->
<!-- ``` -->

<!-- Some numbers start with a 0 or 1 - do not move to formatted column (US area codes don't start with 1) -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^[0-1]") & nchar(number) == 10) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- <br> -->

<!-- **7 digit US numbers (no area code)**     -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^[1-9]") & nchar(number) == 7) %>%  -->
<!--   select(number, number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- Match numbers to contacts and extract area code.  -->
<!-- ```{r} -->
<!-- numbers_7_digits <- logs %>%  -->
<!--   filter(str_detect(number, "^[1-9]") & nchar(number) == 7) %>%  -->
<!--   select(number) %>%  -->
<!--   unlist(use.names = FALSE) -->
<!-- ``` -->

<!-- Contact matches to 7 digit numbers -->
<!-- ```{r message = FALSE} -->
<!-- contacts <- read_csv(file.path(path_in, "contacts.csv"), col_types = cols()) -->

<!-- contacts_7_digits <- tibble(subid = as.numeric()) -->

<!-- for (i in seq_along(numbers_7_digits)) { -->
<!--   match <- contacts %>%  -->
<!--     filter(str_detect(phone_number, numbers_7_digits[i])) %>%  -->
<!--     mutate(pattern = numbers_7_digits[i]) -->
<!--   if(nrow(match) != 0) {   -->
<!--     contacts_7_digits <- contacts_7_digits %>% full_join(match) -->
<!--   } -->
<!-- } -->

<!-- contacts_7_digits %>%  -->
<!--   select(subid, phone_number, pattern, contact_type) %>%  -->
<!--   print(n = Inf)  -->
<!-- ``` -->

<!-- Remove duplicate contacts    -->
<!-- NOTE: just doing a quick filter because I am only interested in the number, not the context variables right now -->
<!-- ```{r} -->
<!-- contacts_7_digits <- contacts_7_digits %>%  -->
<!--   group_by(subid, phone_number, pattern) %>%  -->
<!--   slice(1) -->
<!-- ``` -->

<!-- Join numbers with log entries and replace formatted number with contact number       -->
<!-- FIX: Looks like we picked up 6 rows from the join. I cannot figure out where these are coming from -->
<!-- ```{r} -->
<!-- logs <- logs %>%  -->
<!--   left_join(contacts_7_digits %>%  -->
<!--               select(subid, contact_number = phone_number, number = pattern),  -->
<!--             by = c("subid", "number")) %>%  -->
<!--   glimpse() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # log entries with contact numbers -->
<!-- logs %>%  -->
<!--   filter(!is.na(contact_number)) %>%  -->
<!--   select(subid, number, contact_number, date, contact_name) %>%  -->
<!--   print(n = Inf) -->

<!-- logs <- logs %>%  -->
<!--   mutate(number_formatted = case_when(!is.na(contact_number) ~ as.character(contact_number), -->
<!--                                       TRUE ~ number_formatted))  -->

<!-- # check -->
<!-- logs %>%  -->
<!--   filter(!is.na(contact_number)) %>%  -->
<!--   select(subid, number, contact_number, number_formatted) %>%  -->
<!--   print(n = Inf) -->

<!-- # remove contact number -->
<!-- logs <- logs %>%  -->
<!--   select(-contact_number) -->
<!-- ``` -->


<!-- <br> -->

<!-- **Non-US country codes**    -->
<!-- A lot of the frequent out of country numbers are not known contacts (see below) -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^\\+") & nchar(number) > 7) %>%  -->
<!--   filter(is.na(number_formatted)) %>%  -->
<!--   count(number) %>%  -->
<!--   arrange(desc(n)) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- Meaningful out of country numbers from contacts    -->
<!-- *Not sure what 114 or 80/8000 is - cant locate information on it yet.* -->
<!-- ```{r} -->
<!-- contacts %>%  -->
<!--   filter(nchar(phone_number) > 10) %>%  -->
<!--   select(subid, phone_number) -->
<!-- ``` -->

<!-- https://countrycode.org/     -->
<!-- 91 = India     -->
<!-- 57 = Colombia     -->


<!-- Most out of country calls are from subid 117 -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "^\\+") & nchar(number) > 7) %>%  -->
<!--   filter(is.na(number_formatted)) %>%  -->
<!--   count(subid) %>%  -->
<!--   arrange(desc(n)) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- <br> -->

<!-- ##### Other processing edits -->

<!-- All known contact numbers are 10 characters in length except for the following -->
<!-- ```{r} -->
<!-- contacts %>%  -->
<!--   filter(nchar(phone_number) != 10) %>%  -->
<!--   select(subid, phone_number) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- **numbers with less than 7 characters**      -->
<!-- * 86 - calls voicemail for verizon phones    -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_length(number) < 7) %>%  -->
<!--   count(number) %>%  -->
<!--   arrange(desc(n)) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- All contact numbers with less than seven characters are Irrelevant/spam or Other -->
<!-- ```{r} -->
<!-- contacts %>%  -->
<!--   filter(nchar(phone_number) < 7) %>%  -->
<!--   select(subid, phone_number, contact_type) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- **numbers with more than 10 characters and no country + sign**    -->
<!-- May want to create new variable for calls blocked with * 67 -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_length(number) > 10 & !str_detect(number, "^\\+")) %>%  -->
<!--   filter(is.na(number_formatted)) %>%  -->
<!--   count(number) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->


<!-- FIX: Do we want to clean unavailable numbers to NA in function?    -->
<!-- NOTE: 12 numbers have number listed as unavailable - presentation type is 1 suggesting the number was not blocked, but contact name is unknown and all calls are incoming or missed. Will correct this by changing to NA.    -->
<!-- 11/12 of these came from subid 204 so maybe this is specific to a certain android OS or model phone -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(number == "unavailable") %>%  -->
<!--   select(-c(log_file, created, modified)) -->
<!-- ``` -->

<!-- Change numbers to NA and presentation to NA     -->
<!-- ```{r} -->
<!-- logs <- logs %>%  -->
<!--   mutate(number = case_when(number == "unavailable" ~ as.character(NA), -->
<!--                             TRUE ~ number), -->
<!--          presentation = case_when(number == "unavailable" ~ as.numeric(NA), -->
<!--                                   TRUE ~ presentation)) -->
<!-- ``` -->

<!-- **Other punctuation** -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(str_detect(number, "[*#]")) %>%  -->
<!--   count(number,  number_formatted) %>%  -->
<!--   arrange(desc(n)) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->





<!-- **Final numbers**    -->
<!-- formatted numbers -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(!is.na(number_formatted)) %>%  -->
<!--   select(number_formatted) %>%  -->
<!--   print(n = Inf) -->
<!-- ``` -->

<!-- All numbers are 10 digits -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(!is.na(number_formatted)) %>%  -->
<!--   filter(nchar(number_formatted) != 10) -->
<!-- ``` -->

<!-- Unformatted numbers -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(is.na(number_formatted)) %>%  -->
<!--   count(number) %>%  -->
<!--   arrange(desc(n)) %>%  -->
<!--   print(n = Inf)  -->
<!-- ``` -->

<!-- <br> -->

<!-- *Currently have + still on out of country phone numbers - this is to retain info for feature engineering. Will need to remove when matching to contacts or add + to out of country contact numbers.*      -->

<!-- <br> -->

<!-- ### Additional EDA -->

<!-- Missing data -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   naniar::miss_var_summary() -->

<!-- logs %>%  -->
<!--   naniar::vis_miss() -->
<!-- ``` -->

<!-- Duration -->
<!-- ```{r} -->
<!-- psych::describe(logs$duration) -->
<!-- ``` -->

<!-- Type -->
<!-- ```{r} -->
<!-- janitor::tabyl(logs$type) -->
<!-- ``` -->
<!-- https://developer.android.com/reference/android/provider/CallLog.Calls#TYPE    -->
<!-- 1 = incoming    -->
<!-- 2 = outgoing    -->
<!-- 3 = missed    -->
<!-- 4 = voicemail     -->
<!-- 5 = rejected    -->
<!-- 6 = blocked (automatically - block list)      -->
<!-- 7 = answered externally (different device)    -->


<!-- #### presentation -->
<!-- ```{r} -->
<!-- janitor::tabyl(logs$presentation) -->
<!-- ``` -->
<!-- https://developer.android.com/reference/android/provider/CallLog.Calls#PRESENTATION_ALLOWED   -->
<!-- 1 = number displayed (presentation allowed)   -->
<!-- 2 = number is blocked by user    -->
<!-- 3 = number is not specified or unknown by network    -->
<!-- 4 = payphone   -->

<!-- blocked and unknown numbers are NA and have presentation 2 or 3 -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(presentation == 2 | presentation == 3) %>%  -->
<!--   janitor::tabyl(number) -->

<!-- logs %>%  -->
<!--   filter(is.na(number)) %>%  -->
<!--   janitor::tabyl(presentation) -->
<!-- ``` -->

<!-- No blocked calls are outgoing (type = 2) -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   filter(presentation == 2 | presentation == 3) %>%  -->
<!--   janitor::tabyl(type) -->

<!-- logs %>%  -->
<!--   filter(is.na(number)) %>%  -->
<!--   janitor::tabyl(type) -->
<!-- ``` -->


<!-- #### contact name -->
<!-- ```{r} -->
<!-- logs %>%  -->
<!--   group_by(contact_name) %>%  -->
<!--   slice(1) %>%  -->
<!--   select(contact_name) %>%  -->
<!--   kbl() %>%  -->
<!--   kable_styling() %>%  -->
<!--   scroll_box(width = "50%", height = "500px") -->
<!-- ``` -->

<!-- <br> -->


<!-- ### Write csv -->
<!-- ```{r} -->
<!-- write_csv(logs, file.path(path_out, "meta_voice_android.csv")) %>% glimpse() -->
<!-- ``` -->

<!-- **Dates saved as UTC** -->

<!-- <br> -->
