---
title: "Multimedia Appendix 2: Supplemental Analyses"
subtitle: "Acceptability of Personal Sensing among People with Alcohol Use Disorder"
author: "Kendra Wyant, Hannah Moshontz, Stephanie Ward, John Curtin"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: 
  html_document:
    toc: true 
    toc_depth: 4
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = dplyr::if_else(Sys.info()[["sysname"]] == "Windows",
      "P:/studydata/risk/knits/burden", 
      "/Volumes/private/studydata/risk/knits/burden")
    )
  })
---

<br>

Purpose: This file is the supplemental analysis script for *Acceptability of Personal Sensing among People with Alcohol Use Disorder*. It includes all supplemental figures, tables, and statistical analyses.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r}
path_data <- "P:/studydata/risk/data_processed/burden"
path_shared <- "P:/studydata/risk/data_processed/shared"
```

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(kableExtra)
library(ggtext)
library(cowplot)
library(patchwork)
library(rstatix)
library(janitor)

theme_set(theme_bw())
options(knitr.kable.NA = '')
```


```{r}
# self-report acceptability data
data <- read_csv(file.path(path_data, "acceptability.csv"), col_types = cols())
```



<br>

### Physiology Analysis


We initially monitored participants physiology using an early version of the Empatica E4 wristband monitor. Due to a complicated sensing platform and software bugs we discontinued the wristband after nine participants. Below are the self-reported acceptability ratings (interference, dislike, willingness to continue for one year) for this sensing method from the nine participants who used it (Figure S1 from the manuscript). 

```{r fig.height = 6}
# subset to physiology variables
wristband_descr <- data %>% 
  select(c(subid, date, contains("wristband"))) %>% 
  filter(!is.na(wristband_interfere)) %>%
  group_by(subid) %>% 
  arrange(desc(date)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select("Interference" = wristband_interfere, 
         "Dislike" = wristband_dislike, 
         "Willingness to Continue" = wristband_1year) %>% 
  gather(key = "measure")

wrist_int <- wristband_descr %>% 
  filter(measure == "Interference") %>% 
  mutate(value = factor(value, levels = c(-2:2),
                        labels = c("Strongly agree", "Agree", "Undecided", "Disagree", "Strongly disagree"))) %>% 
  ggplot(aes(x = value, y = ..prop.., group = measure)) +
  geom_bar(color = "black", fill = "#FFDEDE") +
  facet_wrap(~measure) +
  theme_classic() +
  ylim(0, .7) +
  labs(y = "Proportion",
       x = NULL) +
  scale_x_discrete(drop=FALSE) +
    theme(legend.position = "none",
        text = element_text(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(aes(xintercept = mean(as.numeric(value))), linetype = "solid", size = .705, color = "#b44343") +
  geom_vline(aes(xintercept = "Undecided"), linetype = "dashed", size = .4, color = "#787575")

wrist_dis <- wristband_descr %>% 
  filter(measure == "Dislike") %>% 
  mutate(value = factor(value, levels = c(-2:2),
                        labels = c("Strongly agree", "Agree", "Undecided", "Disagree", "Strongly disagree"))) %>% 
  ggplot(aes(x = value, y = ..prop.., group = measure)) +
  geom_bar(color = "black", fill = "#FFDEDE") +
  facet_wrap(~measure) +
  theme_classic() +
  ylim(0, .7) +
  labs(y = NULL,
       x = NULL) +
    theme(legend.position = "none",
        text = element_text(),
        axis.text.y =element_blank(),
        axis.ticks.y=element_blank(),
        axis.line.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(aes(xintercept = mean(as.numeric(value))), linetype = "solid", size = .705, color = "#b44343") +
  geom_vline(aes(xintercept = "Undecided"), linetype = "dashed", size = .4,  color = "#787575")

wrist_1yr <- wristband_descr %>% 
  filter(measure == "Willingness to Continue") %>% 
  mutate(value = factor(value, levels = c(-2:2),
                        labels = c("Strongly disagree", "Disagree", "Undecided", "Agree", "Strongly agree"))) %>% 
  ggplot(aes(x = value, y = ..prop.., group = measure)) +
  geom_bar(color = "black", fill = "#FFDEDE") +
  facet_wrap(~measure) +
  theme_classic() +
  ylim(0, .7) +
  labs(y = NULL,
       x = NULL) +
    theme(legend.position = "none",
        text = element_text(),
        axis.text.y=element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(aes(xintercept = mean(as.numeric(value))), linetype = "solid", size = .705, color = "#b44343") +
  geom_vline(aes(xintercept = "Undecided"), linetype = "dashed", size = .4,  color = "#787575")


p_wrist <- wrap_plots(wrist_int, wrist_dis, wrist_1yr) 
p_wrist +
 plot_annotation(
   title = "Figure S1<br><br> Physiology Acceptability",
  caption =  "<i>Note:</i> Sample size is 9. Solid red line represents the mean and dashed line represents the neutral/<br>ambivalent score.</i>"
) &
  theme(plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1),
        text = element_text(),
        plot.title = element_markdown(size = 12),
        plot.subtitle = element_markdown(size = 12))
```

----

<br>

### Time Analysis


```{r}
# Create dataframe of only subids with three time points (N = 133).
acceptability_time <- data %>% 
  # filter out wristband and carrying_phone
  select(-c(contains("wristband"), contains("phone"))) %>% 
  group_by(subid) %>% 
  mutate(n_obs = n()) %>% 
  filter(n_obs == 3) %>% 
  # create time variable
  arrange(date) %>%
  mutate(time = row_number()) %>% 
  ungroup()
```

The figure below is Figure S2 from the manuscript. We examined acceptability ratings over time for participants who completed the study through follow-up 3 (N = 133). We see average acceptability ratings for each personal sensing data stream are relatively stable across time.   

```{r warning = FALSE, fig.height=6, fig.width=8}
# create grouping variables to use for figure
dislike <- acceptability_time %>% 
  select(contains("dislike")) %>% 
  pivot_longer(everything(), "measure")
interfere <- acceptability_time %>% 
  select(contains("interfere")) %>% 
  pivot_longer(everything(), "measure")
oneyear <- acceptability_time %>% 
  select(contains("1year")) %>% 
  pivot_longer(everything(), "measure")
logs <- acceptability_time %>% 
  select(contains("all_logs")) %>% 
  pivot_longer(everything(), "measure")
sleep <- acceptability_time %>% 
  select(contains("sleep")) %>% 
  keep(~is.numeric(.x)) %>% 
  pivot_longer(everything(), "measure")
audio <- acceptability_time %>% 
  select(contains("audio")) %>% 
  keep(~is.numeric(.x)) %>% 
  pivot_longer(everything(), "measure")
ema <- acceptability_time %>% 
  select(contains("daily_survey"), -daily_survey_1_1year) %>% 
  keep(~is.numeric(.x)) %>% 
  pivot_longer(everything(), "measure")
geolocation <- acceptability_time %>% 
  select(contains("location")) %>% 
  keep(~is.numeric(.x)) %>% 
  pivot_longer(everything(), "measure")
text_content <- acceptability_time %>% 
  select(contains("sms")) %>% 
  keep(~is.numeric(.x)) %>% 
  pivot_longer(everything(), "measure")

# prepare data for plot
time_plot <- acceptability_time %>% 
  select(time,
         contains("interfere"),
         contains("dislike"),
         contains("1year")) %>% 
  pivot_longer(sleep_interfere:all_logs_1year, "measure") %>% 
  mutate(acceptability = case_when(measure %in% dislike$measure ~ "Dislike",
                             measure %in% interfere$measure ~ "Interference",
                             measure %in% oneyear$measure ~ "Willingness to Continue"),
         acceptability = factor(acceptability, levels = c("Interference", "Dislike", "Willingness to Continue"))) %>% 
  mutate(method = case_when(measure %in% logs$measure ~ "Cellular Communication Logs",
                                  measure %in% sleep$measure ~ "Sleep Quality",
                                  measure %in% audio$measure ~ "Audio Check-in",
                                  measure %in% ema$measure ~ "EMA",
                                  measure %in% geolocation$measure ~ "Geolocation",
                                  measure %in% text_content$measure ~ "Text Message Content")) 


time_plot %>% 
  group_by(method, time, acceptability) %>% 
  # missing values due to two participants who didn't complete survey at time point 2
  summarise(mean = mean(value, na.rm = TRUE), .groups = "drop") %>% 
  ggplot(aes(x = time, y = mean, group = method, color = method)) +
  geom_point() +
  geom_line() +
  facet_wrap(~acceptability) +
  theme_classic() +
  scale_color_manual(values = c("dodgerblue4",  "skyblue3", "azure3", 
                                "thistle1", "thistle3", "plum4")) +
  scale_x_continuous(name = "Time Point", 
                     breaks = c(1, 2, 3)) +
  scale_y_continuous(name = "Mean Score", 
                     breaks = c(-2, -1, 0, 1, 2), 
                     limits = c(-2, 2)) +
  labs(title = "Figure S2<br><br>Acceptability over Time by Personal Sensing Data Stream",
       caption = "<i>Note:</i>  Participant ratings (<i>N</i> = 133) for each measure of acceptability at three different time points one-month <br>apart. Sleep quality N = 87. Each measure is on a 5-point bipolar scale anchored around a neutral/<br>ambivalent response of 0 (i.e., undecided) with higher values representing higher acceptability. Dashed line <br>represents neutral score.") +
  theme(legend.title = element_blank(),
        legend.text = element_markdown(),
        plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1.25),
        text = element_text(),
        plot.title = element_markdown(),
        plot.subtitle = element_markdown(size = 12, lineheight = 1.25)) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", size = .3)
```



<br>

-----

<br>

### Analysis on willingness to use EMA one time daily

Participants reported on their willingness to continue an EMA method that was one time daily for one year. This method was hypothetical in that although they were asked about a one time daily EMA they were expected to do four daily EMAs. Below is the distribution of responses for this question (Figure S3 from the manuscript).   


```{r}
# pull out data for 1x EMA
ema_1x <- data %>% 
  select(subid, date, daily_survey_1_1year) %>% 
  group_by(subid) %>% 
  arrange(desc(date)) %>% 
  slice(1) %>% 
  ungroup()

plot_ema_1x <- ema_1x %>% 
  rename(`Willingness to Continue for One Year` = daily_survey_1_1year) %>% 
  pivot_longer(`Willingness to Continue for One Year`, names_to = "measure") %>% 
  mutate(value = factor(value, levels = c(-2:2),
                        labels = c("Strongly disagree", "Disagree", "Undecided", "Agree", "Strongly agree"))) %>% 
  ggplot(aes(x = value, y = ..prop.., group = measure)) +
  geom_bar(color = "black", fill = "#FFDEDE") +
  facet_wrap(~measure) +
  theme_classic() +
  ylim(0, .7) +
  labs(y = "Proportion",
       x = NULL) +
    theme(legend.position = "none",
        text = element_text(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(aes(xintercept = mean(as.numeric(value))), linetype = "solid", size = .705, color = "#b44343") +
  geom_vline(aes(xintercept = "Undecided"), linetype = "dashed", size = .4, color = "#787575")

plot_ema_1x +
 plot_annotation(
  title = "Figure S3<br><br>Willingness to Complete a Once Daily Ecological Momentary Assessment for One Year",
  caption =  "<i>Note:</i> Sample size is 154. Solid red line represents the mean and dashed line represents the neutral/<br>ambivalent score."
) &
  theme(plot.caption = element_markdown(hjust = 0, size = 10, lineheight = 1),
        text = element_text(),
        plot.title = element_markdown(size = 12),
        plot.subtitle = element_markdown(size = 12))
```

<br>

A one sample t-test revealed that the mean willingness score (depicted as the solid red line in Figure S3) was significantly more acceptable than 0 (gray dashed line indicating undecided), t(153) = 15.21, p < .001.

```{r}
# model_ema_1x <- lm(daily_survey_1_1year ~ 1, data = ema_1x)
# summary(model_ema_1x)
```


Additionally, we ran a paired samples t-test to compare participants' willingess to use a one time daily EMA for 1 year compared to a four time daily EMA. We found that Participants were significantly more likely to be willing to complete EMA's one time daily (M = 1.26, SD = 1.03) compared to four times daily (M = 0.64, SD = 1.22) for one year to help their recovery, t(153) = -8.32, p < .001.   

```{r}
# create long dataframe
# ema_1x_and_4x <- data %>% 
#   select(subid, date, `EMA 1x` = daily_survey_1_1year, `EMA 4x` = daily_survey_4_1year) %>% 
#   group_by(subid) %>% 
#   arrange(desc(date)) %>% 
#   slice(1) %>% 
#   ungroup() %>% 
#   pivot_longer(`EMA 1x`:`EMA 4x`, names_to = "ema_frequency")
# 
# # t-test
# m_ema_1x_and_4x <- lme4::lmer(value ~ ema_frequency + (1| subid), data = ema_1x_and_4x)
# summary(m_ema_1x_and_4x)
# car::Anova(m_ema_1x_and_4x, type = 3, test = "F")
```

<br>
 

----

<br>


### Group differences between continued and discontinued participants

We ran a series of t-tests to compare demographic information and information relevant to participants’ alcohol use and DSM-5 AUD symptoms in participants who continued vs. discontinued. Continued participants included all participants who were used in the study analyses (i.e., completed through first month followup; N = 154). Discontinued participants consisted of eligible participants who did not enroll or discontinued prior to the first month follow-up (N = 36). We found no significant differences between groups (Table S1).     


```{r}
# read in additional data on participant dipsosition
screen <- read_csv(file.path(path_shared, "screen.csv"), col_types = cols()) 
disposition <- read_csv(file.path(path_data, "disposition.csv"), col_types = cols()) 

# remove ineligible participants
eligible_sample <- disposition %>%  
  filter(reason_no_intake != "ineligible" | is.na(reason_no_intake))
screen <- screen %>% 
  filter(subid %in% eligible_sample$subid)

# select demographic and AUD variables
screen <- screen %>% 
  select(subid, dem_1:dem_8, -dem_3_1, -dem_4_1, -dem_6_1, auh_1:auh_7, -auh_6_7_text, 
         starts_with("dsm5_"), assist_1_1:assist_1_8) 

# add grouping variable (completed 1st month vs discontinued)
sample_completed <- disposition %>% 
  filter(last_visit != "screen" & last_visit != "intake")
screen <- screen %>% 
  mutate(disposition = case_when(subid %in% sample_completed$subid ~ "continued",
                                 TRUE ~ "discontinued"))

# give descriptive names to variables and recode
screen <- screen %>% 
  # demographics
  rename(age = dem_1,
         sex = dem_2,
         race = dem_3,
         Hispanic = dem_4,
         education = dem_5,
         employment = dem_6,
         income = dem_7,
         marrital_status = dem_8) %>% 
  mutate(male = dplyr::recode(sex, "Male" = 1, "Female" = 0),
         race = factor(race, levels = c("American Indian/Alaska Native", "Asian",
                                        "Black/African American", "Other/Multiracial",
                                        "White/Caucasian"), labels = c("American Indian or Alaska Native", "Asian",
                                        "Black/African American", "Multiracial or not listed above",
                                        "white")),
         Hispanic = case_when(Hispanic == "No, I am not of Hispanic, Latino, or Spanish origin" ~ 0,
                         TRUE ~ 1),
         education = factor(education, 
                         levels = c("Less than high school or GED degree", "High school or GED", 
                         "Some college", "2-Year degree", "College degree", "Advanced degree"),
                         ordered = TRUE),
         employment = factor(employment),
         marrital_status = factor(marrital_status)) %>% 
  # AUH 
  rename(age_first_drink = auh_1,
         age_reg_drink = auh_2,
         age_problem_drink = auh_3,
         age_first_quit = auh_4,
         num_quit_attempts = auh_5,
         lt_residential_tx = auh_6_1,
         st_residential_tx = auh_6_2,
         outpatient_tx = auh_6_3,
         individ_counseling = auh_6_4,
         group_counseling = auh_6_5,
         aa_or_na = auh_6_6,
         other_tx = auh_6_7,
         med_for_aud = auh_7) %>% 
  # recode tx vars as ordered no yes factors
  mutate(lt_residential_tx = case_when(lt_residential_tx == "Long-Term Residential Treatment (more than 6 months)" ~ 1,
                                       TRUE ~ 0),
         st_residential_tx = case_when(st_residential_tx == "Short-Term Residential Treatment (less than 6 months)" ~ 1,
                                       TRUE ~ 0),
         outpatient_tx = case_when(outpatient_tx == "Outpatient Treatment" ~ 1,
                                       TRUE ~ 0),
         individ_counseling = case_when(individ_counseling == "Individual Counseling" ~ 1,
                                       TRUE ~ 0),
         group_counseling = case_when(group_counseling == "Group Counseling" ~ 1,
                                       TRUE ~ 0),
         aa_or_na = case_when(aa_or_na == "Alcoholics Anonymous/Narcotics Anonymous" ~ 1,
                                       TRUE ~ 0),
         other_tx = case_when(other_tx == "Other" ~ 1,
                                       TRUE ~ 0),
         med_for_aud = dplyr::recode(med_for_aud, "No" = 0, "Yes" = 1)) %>% 
  # Assist
  mutate(tobacco = dplyr::recode(assist_1_1, "No" = 0, "Yes" = 1),
         cannabis = dplyr::recode(assist_1_2, "No" = 0, "Yes" = 1),
         cocaine = dplyr::recode(assist_1_3, "No" = 0, "Yes" = 1),
         amphetamine = dplyr::recode(assist_1_4, "No" = 0, "Yes" = 1),
         inhalant = dplyr::recode(assist_1_5, "No" = 0, "Yes" = 1),
         sedative = dplyr::recode(assist_1_6, "No" = 0, "Yes" = 1),
         hallucinogen = dplyr::recode(assist_1_7, "No" = 0, "Yes" = 1),
         opiate = dplyr::recode(assist_1_8, "No" = 0, "Yes" = 1)) %>% 
  # dsm5
  mutate(across(dsm5_1:dsm5_11, ~ dplyr::recode(., "No" = 0, "Yes" = 1))) %>% 
  # remove duplicate vars
  select(-c(assist_1_1:assist_1_8, sex))

# combine variables
screen_combined <- screen %>% 
  # calculate total dsm5 score by adding up dsm5_1 through dsm5_11
  rowwise() %>% 
  mutate(dsm5_total = sum(dsm5_1, dsm5_2, dsm5_3, dsm5_4, dsm5_5, dsm5_6, dsm5_7, 
                            dsm5_8, dsm5_9, dsm5_10, dsm5_11),
         num_types_tx = sum(lt_residential_tx, st_residential_tx, outpatient_tx, 
                            individ_counseling, group_counseling, aa_or_na, other_tx, med_for_aud),
         num_other_drugs = sum(tobacco, cannabis, cocaine, amphetamine, inhalant,
                               sedative, hallucinogen, opiate),
         avg_age_aud_milestones = sum(age_first_drink, age_reg_drink, age_problem_drink,
                                       age_first_quit)/ 4,
         white = case_when(race == "white" ~ 1,
                          TRUE ~ 0),
         employed = case_when(employment == "Employed" ~ 1,
                          TRUE ~ 0),
         married = case_when(marrital_status == "Married" ~ 1,
                          TRUE ~ 0)) %>% 
  ungroup() %>% 
  select(-c(age_first_drink:age_first_quit, lt_residential_tx:dsm5_11, tobacco:opiate, race,
            employment, marrital_status)) 
```


```{r}
# pivot longer
screen_combined_long <- screen_combined %>% 
  select(-subid) %>% 
  mutate(education = as.numeric(education)) %>% 
  pivot_longer(-disposition, names_to = "variables", values_to = "value")

screen_combined_long %>%
  group_by(variables) %>%
  t_test(value ~ disposition) %>%
  select(` ` = variables,
         t = statistic,
         df,
         p) %>% 
  kbl(digits = 2,
      align = c("l", "c", "c", "c"),
      caption = "<b>Table S1<br><br>Pairwise T-tests to Compare Group Differences between Continued (N = 154) and Discontinued (N = 36) Participants</b>") %>% 
  kable_classic(html_font = "Arial")
```


<br>

-----

<br>


### Uncorrected pairwise comparisons among personal sensing data streams

Table S2 contains all possible combinations of pairwise comparisons among active and passive personal sensing data streams.   

```{r}
# dataframe of last survey
# pull out last available sleep monitor data since this date will be earlier than last survey date for some
last_sleep <- data %>% 
  select(-contains("wristband")) %>% 
  filter(!is.na(sleep_interfere)) %>% 
  group_by(subid) %>% 
  arrange(desc(date)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(c(subid, starts_with("sleep_")))
  
# pull out most recent survey for each subid
last_data <- data %>% 
  select(-c(starts_with("sleep_"), contains("wristband"))) %>% 
  group_by(subid) %>% 
  arrange(desc(date)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  # join with sleep data
  full_join(last_sleep, by = c("subid"))
```


```{r}
int_pair <- last_data %>% 
  select(`EMA` = daily_survey_interfere,
         `Audio Check-in` = audio_checkin_interfere,
         `Sleep Quality` = sleep_interfere) %>%
  pivot_longer(cols = everything(), names_to = "signal") %>% 
  mutate(signal = factor(signal)) 

# uncomment to only look at comparisons within interference measure
# pairwise.t.test(int_pair$value, int_pair$signal, p.adj = "none") 

dis_pair <- last_data %>% 
  select(`EMA` = daily_survey_dislike,
         `Audio Check-in` = audio_checkin_dislike,
         `Sleep Quality` = sleep_dislike,
         `Geolocation` = location_dislike,
         `Cellular Communication Logs` = all_logs_dislike,
         `Text Message Content` = sms_content_dislike) %>%
  pivot_longer(cols = everything(), names_to = "signal") %>% 
  mutate(signal = factor(signal)) 

# uncomment to only look at comparisons within dislike measure
# pairwise.t.test(dis_pair$value, dis_pair$signal, p.adj = "none") 

will_pair <- last_data %>% 
  select(`EMA` = daily_survey_4_1year,
         `Audio Check-in` = audio_checkin_1year,
         `Sleep Quality` = sleep_1year,
         `Geolocation` = location_1year,
         `Cellular Communication Logs` = all_logs_1year,
         `Text Message Content` = sms_content_1year) %>%
  pivot_longer(cols = everything(), names_to = "signal") %>% 
  mutate(signal = factor(signal)) 

# uncomment to only look at comparisons within willingness measure
# pairwise.t.test(will_pair$value, will_pair$signal, p.adj = "none") 
```

 
```{r}
# format table
tibble(
  Measure = c("EMA", "Sleep Quality",
              "EMA", "Sleep Quality", "Geolocation", "Cellular Communication Logs", "Text Message Content",
              "EMA", "Sleep Quality", "Geolocation", "Cellular Communication Logs", "Text Message Content"),
  "Audio Check-in" = c(
                       # interference
                       ".25", "< .001***", 
                       # dislike
                       "< .001***", "< .001***", "< .001***", ".001***", ".56", 
                       # willingness
                       ".47", ".46", ".14", ".42", ".96"), 
  "EMA" = c(
                     # interference
                     NA, "< .001***", 
                     # Dislike
                     NA, ".30", ".56", ".63", ".002**",
                     # willingness
                     NA, ".18", ".03*", ".13", ".44"), 
  "Sleep Quality" = c(
                      # interference
                      NA, NA, 
                      # dislike
                      NA, NA, ".59", ".15", "< .001***", 
                      # willingness
                      NA, NA, ".60", ".97", ".49"), 
  "Geolocation" = c(
                 # interference
                 NA, NA,  
                 # dislike 
                 NA, NA, NA, ".29", "< .001***", 
                 # willingness 
                 NA, NA, NA, ".50", ".15"), 
  "Cellular Communication Logs" = c(
                        # interference
                        NA, NA, 
                        # dislike
                        NA, NA, NA, NA, ".01**", 
                        # willingness
                        NA, NA, NA, NA, ".44")) %>% 
  kbl(align = c("l", "c", "c", "c", "c", "c"),
      caption = "<b>Table S2<br><br>Uncorrected Pairwise Comparison P Values for Pairs of Personal Sensing Data Streams across the Three Measures of Self Reported Acceptability</b>",
      escape = FALSE) %>% 
  kable_classic(html_font = "Arial") %>% 
  pack_rows("Interference", 1, 2, bold = FALSE) %>% 
  pack_rows("Dislike", 3, 7, bold = FALSE) %>% 
  pack_rows("Willingness to Continue", 8, 12, bold = FALSE) %>% 
  footnote("Sample size for all personal sensing measures is 154 except for the sleep quality which had a sample size of 87.<br>* <i>p</i> < .05, ** <i>p</i> < .01, *** <i>p</i> < .001", escape = FALSE)
```


<br>


