---
title: "Untitled"
format: pdf
csl: https://raw.githubusercontent.com/jjcurtin/lab_support/main/rmd_templates/csl/elsevier-vancouver.csl
geometry: margin=.5in
fontsize: 11pt
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---



<!--General notes


-->

```{r knitr_settings, include = FALSE}
# settings
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, cache = FALSE, 
                      message = FALSE)
options(knitr.kable.NA = '')
knitr::opts_chunk$set(fig.pos = "ht", out.extra = "")
```

```{r setup, include = FALSE}
library(knitr)
# library(yardstick) # for roc_curve
library(kableExtra)
library(janitor)
# library(corx)
library(patchwork)
library(ggtext)
library(consort)
library(tidyverse)
library(tidymodels)
library(tidyposterior)
library(cowplot)

theme_set(theme_classic()) 
```


```{r paths}
switch (Sys.info()[['sysname']],
        # PC paths
        Windows = {
          path_input <- "P:/studydata/risk/chtc/insight"
          path_processed <- "P:/studydata/risk/data_processed/insight"
          path_models <- "P:/studydata/risk/models/insight"
          path_shared <- "P:/studydata/risk/data_processed/shared"},

        # IOS paths
        Darwin = {
          path_input <- "/Volumes/private/studydata/risk/chtc/insight"
          path_processed <- "/Volumes/private/studydata/risk/data_processed/insight"
          path_models <- "/Volumes/private/studydata/risk/models/insight"
          path_shared <- "/Volumes/private/studydata/risk/data_processed/shared"},
        
        # Linux paths
        Linux = {
          path_input <- "~/mnt/private/studydata/risk/chtc/insight"
          path_processed <- "~/mnt/private/studydata/risk/data_processed/insight"
          path_models <- "~/mnt/private/studydata/risk/models/insight"
          path_shared <- "~/mnt/private/studydata/risk/data_processed/shared"}
        )
```

```{r load_data}
```

# Introduction


## Current Study


# Method

## Research Transparency

## Participants

## Procedure


## Measures
### EMA

### Individual Differences

## Data Analytic Strategy

### Lapse Labels


### Feature Engineering



### Model Training and Evaluation


\newpage


# Results


## Demographic and Clinical Characteristics



<!-- Demographics table-->



\newpage


## Model Performance

### auROC



### Other Performance Metrics


### Feature Importance






# Discussion

## 1. Model Performance

## 2. Understanding & Contextualizing Model Performance

## 3. Clinical Implementation


## 4. Additional Future Directions & Limitations



\clearpage


# References